### 2024-07-25 paper.tex
add paper

\documentclass[12pt,psamsfonts]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{blkarray}
\usepackage{upquote}
\usepackage{tikz}
\usepackage{bbm}
\usepackage{url}
\usepackage{tikz-cd}
\usepackage{enumerate}

\newcommand{\deriv}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\stab}{stab}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\Ind}{Ind}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Image}{Image}
\DeclareMathOperator{\cof}{cof}
\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\real}{Re}
\DeclareMathOperator{\arccot}{arccot}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\atan2}{atan2}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\Br}{Br}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\inv}{inv}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\gl}{\mathfrak{gl}}
\DeclareMathOperator{\spl}{\mathfrak{sl}}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\opp}{\mathrm{opp}}
\newcommand{\un}{\mathrm{un}}
\newcommand{\al}{\mathrm{al}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\comment}{}

\usepackage[capitalize,nameinlink,noabbrev]{cleveref} % to emulate \autoref style

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
% \newcommand{\theoremautorefname}{Theorem}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\definitionautorefname}{Definition}

\bibliographystyle{plain}
\usepackage{nicematrix}

% \author{Owen Conoly}
% \date{Date}
% \title{Title}

\begin{document}

% \maketitle
\section{Definition of one thing}
Let \(G \subseteq \GL_m(\mathbb{C})\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m(\mathbb{C})\) be its Lie algebra.
% ^I take this scope because it is about what Yuzhou Gu said.
Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
Let \(\mathcal{F}l\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{m}, n) : n \in \mathfrak{m}\} \subseteq \mathcal{M} \times \mathcal{N}\).
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.

\section{Slodowy slice}
A basis for \(\spl_2(\mathbb{C})\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (???).
If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.
\par Let
\[e = \begin{pNiceArray}{ccc|ccccc}
    & & & & & & & \\
    & & & & & & &    \\
    & & & & & & & \\
   \hline
     & & & 0 \\
   & & & 1 & 0 \\
   & & &  & 1 & \ddots \\
   & & &  &   & \ddots & 0 \\
   & & &  &   &  & 1 & 0
   \end{pNiceArray} \in \mathfrak{sl}_{m + n},\]
where there are \(n\) ones.
We will find the Slodowy slice at \(e\).
\par As a first step, we will find an \(\spl_2\) triple with \(e\) as its first element.
Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
\(eh\) is the last \(n\) rows of \(h\), shifted down one, and \(he\) is the last \(n - 1\) columns of \(h\), shifted left one.
Somehow (TODO: fill in) we conclude that \(f\) and \(h\) are something.

\section{Definition of springer fiber at slodowy slice}
% Explain why these are Springer fibers at Slodowy slices.
\par Let \(\mathcal{N}_m \subseteq \gl_m(\mathbb{C})\) be the subset consisting of nilpotent elements.
For \(X \in \mathcal{N}\) and \(a, b \in \mathbb{C}^m\), let
\[A_{X, a, b} = \begin{pNiceArray}{ccc|ccccc}
 & & & & & & & \vert \\
 & X & & & & & & b    \\
 & & & & & & & \vert \\
\hline
\text{---} & a & \text{---} & 0 \\
& & & 1 & 0 \\
& & &  & 1 & \ddots \\
& & &  &   & \ddots & 0 \\
& & &  &   &  & 1 & 0
\end{pNiceArray} \in \mathfrak{gl}_{m + n}(\mathbb{C}).\]

% \par Note that \(X \mapsto A_{X, a, b}\) gives a map \(\gl_m(\mathbb{C}) \to \gl_{m + n}(\mathbb{C})\).
Let \(\mathcal{M}\) be the variety of Borel subalgebras of \(\gl_{m + n}(\mathbb{C})\).
Let
\[\widetilde{\mathcal{N}} = \{(\mathfrak{m}, a, b, X) : A_{X, a, b} \in \mathfrak{m}\} \subseteq \mathcal{M} \times \mathbb{C}^m \times \mathbb{C}^m \times \mathcal{N}.\]
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the last coordinate.
For \(X \in \mathcal{N}\), we call \(\pi^{-1}(X)\) the \emph{other Springer fiber at \(X\)}.
\section{Finding the Springer fibers of section 2}
We have \(\mathcal{M} = \{AHA^{-1} : A \in \GL_{m + n}(\mathbb{C})\}\), where \(H \subseteq \gl_{m + n}(\mathbb{C})\) is the set of upper triangular matrices.
We say a map \(X : \gl_{m + n} \to \gl_{m + n}\) preserves a flag \(V_0 \subseteq \cdots \subseteq V_{m + n}\) if \(XV_i \subseteq V_i\) for each \(i\).
Let \(E_0 \subseteq \cdots \subseteq E_{m + n}\) be the standard flag of \(\mathbb{C}^{m + n}\).
Since \(H\) is the set of \(X\) which preserve \(E\),
\[\mathcal{M} = \{\{X : \forall i. \; X(AE_i) \subseteq AE_i\} : A \in \GL_n(\mathbb{C})\}.\]
So, for \(X \in \mathcal{N}\),
\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\}.\]
\par In this section we will find the irreducible components of \(\pi^{-1}(X)\).
Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
\par Let \(\lambda\) be the shape of \(X\), and let \((e_{ij})_{i \leq r, j \leq \lambda_i}\) be a Jordan basis for \(X\), with \(X e_{ij} = e_{i,j - 1}\).
Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).

\subsection{A necessary condition for \(A_{X, a, b}\) to be nilpotent}
Suppose \(A := A_{X, a, b}\) is nilpotent.
Define the \emph{height} of a vector \(v \in \mathbb{C}^{m + n}\) as the smallest \(k \geq 0\) such that \(A_{X, a, b}^k v = 0\).
Clearly, for \(i \leq j\), we have that the height of \(f_i\) is geq the height of \(f_j\).
Thus, for each \(k \geq 0\), we must have \(A_{X, a, b}^k f_n \in \langle e_{ij} \rangle_{ij}\).
We have \(Af_n = \sum_{ij} b_{ij} e_{ij}\).
Then \(A^2 f_n = \sum_{ij} b_{ij} (e_{i, j - 1} + a_{ij} f_1)\), so we must have \(\sum_{ij} b_{ij} a_{ij} = 0\).
Similarly, since \(A^3 f_n \in \langle e_{ij}\rangle\), we see that \(\sum_{ij} b_{ij} a_{i, j - 1} = 0\).
Continuing in this way, we obtain that for all \(k \geq 0\),
\[\sum_{ij} b_{ij} a_{i,j - k} = 0.\]
In fact this is in fact a sufficient condition for \(A_{X, a, b}\) to be nilpotent, as can be seen from the characteristic polynomial of \(A_{X, a, b}\).
However, we will not do this calculation here, instead just showing that it is sufficient by giving a Jordan basis.

\subsection{When \(X\) is all zeroes}
In this case we have \(A(y, z) = (z_n b, (a \cdot y, z_1, ..., z_{n - 1}))\), and the condition becomes
\[\sum_i b_i a_i = 0.\]
In this case we will be able to write down explicitly the irreducible components of \(F := \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\} \cong \pi^{-1}(X)\).
For any nonnegative \(\delta_0, \delta_1, ..., \delta_n, \delta_{n + 1}\) summing to \(m\), define the corresponding sequence \(i_0 = \delta_0\), \(i_n = \delta_{n + 1} + i_n\), and for \(j \in \{1, ..., n\}\), \(i_j = i_{j - 1} + 1 + \delta_j\).
Let \(E\) be the span of the \(e_i\)'s, and let \(E' = \{(x, 0) \in E : x \cdot a = 0\}\), where the dot is the \(m\)-dimensional dot product.
Then define \(F_\delta\) as the set of \((V, a, b) \in F\) such that 
\begin{itemize}
    \item \(b \in V_{i_0} \subseteq E'\)
    \item for all \(j \in \{1, ..., n\}\), we have \(f_j \in V_{i_j} \subseteq E' + \langle f_1, ..., f_j \rangle\)
\end{itemize}
I claim that the \(F_\delta\)'s are the irreducible components of \(F\).
To begin, I show that their union is \(F\).

\begin{lemma}
    Let \((V, a, b) \in \mathcal{F}\).
    Write \(f_0 = b\), and \(F = \langle f_0, f_1, ..., f_n \rangle\).
    For each \(i\), either \(F \subseteq V_i\), or else there exists \(j\) such that \(e_j \notin V_i\), but \(\langle e_0, ..., e_{j - 1} \rangle \subseteq V_i \subseteq E' + \langle e_1, ..., e_j \rangle\).
\end{lemma}
\begin{proof}
    For \(i = 0\), we may take \(j = 0\).
    Now assume the statement holds for \(i\), and we will prove it for \(i + 1\).
    If \(F \subseteq V_i\), then \(F \subseteq V_{i + 1}\), and we are done.
    \par So, suppose there is \(j\) such that \(e_j \notin V_i\), but \(\langle e_0, ..., e_{j - 1} \rangle \subseteq V_i \subseteq E' + \langle e_0, ..., e_j \rangle\).
    We have two cases: either \(V_{i + 1} = V_i + \langle e_j \rangle\), or not.
    \begin{itemize}
        \item If so, then either \(j = n\), in which case \(F \subseteq V_{i + 1}\), or else \(j \neq n\), in which case \(e_{j + 1} \notin V_{i + 1}\), but \(\langle e_0, ..., e_j \rangle \subseteq V_{i + 1} \subseteq E' + \langle e_0, ..., e_{j + 1} \rangle\).
        \item If not, then \(e_j \notin V_{i + 1}\).
        Let \(v_{i + 1}\) be so that \(V_{i + 1} = V_i + \langle v_{i + 1} \rangle\).
        I just need to show that \(v_{i + 1} \in Y + \langle e_1, ..., e_j \rangle\).
        It suffices to show that \(v_{i + 1}^\top e_k = 0\) for \(k > j\).
        And to do this, it suffices to show that \((Av_{i + 1})^\top e_{k - 1} = 0\) for \(k > j\).
        \par Note that \(Av_{i + 1} \in V_i \cap A \mathbb{C}^{2n} \subseteq \langle e_1, ..., e_j \rangle\).
        So, for \(k > j + 1\) it is clear that \((Av_{i + 1})^\top e_{k - 1} = 0\).
        Now, suppose for contradiction that \((Av_{i + 1})^\top e_j \neq 0\).
        Then \(Av_{i + 1}\) is linearly independent of \(e_1, ..., e_{j + 1}\).
        Since \(Av_{i + 1} \in \langle e_1, ..., e_j \rangle\), it follows that \(e_j \in \langle e_1, ..., e_{j - 1}, Av_{i + 1} \rangle \subseteq V_i\), a contradiction.
    \end{itemize}
\end{proof}

\begin{corollary}
    \(\mathcal{F} = \bigcup_\delta \mathcal{F}_\delta\)
\end{corollary}
\begin{proof}
    Let \((V, a, b) \in F\).
    Let \(i_0 = \min\{i : b \in V_i\}\), and let \(i' = \max\{i : V_i \subseteq E'\}\).
    We want that \(b \in V_{i_0} \subseteq E'\), so we want that \(i_0 \leq i'\).
    For contradiction, suppose \(i' < i_0\).

\end{proof}

\begin{lemma}
    Each \(\mathcal{F}_\delta\) is a closed subvariety of \(\mathcal{F}\).
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}

\end{lemma}

\subsection{When \(X\) is a Jordan block}
Suppose \(X\) is a single Jordan block of size \(m\).
In this case we just write the basis of \(\mathbb{C}^m\) as \(e_1, ..., e_m\), and the above condition on \(a\) and \(b\) simply becomes
\begin{equation}
    \forall k \geq 0. \; \sum_{i = k + 1}^m b_i a_{i - k} = 0.
\end{equation}
This condition can be simplified even more.
\begin{lemma}
    The condition (1) holds iff there exist nonnegative \(m_1, m_2, m_3\), \(a_1, ..., a_{m_3}\), and \(b_1, ..., b_{m_3}\) satisfying the following conditions.
    \begin{itemize}
        \item \(m = m_1 + m_2 + m_3\)
        \item \(a = (a_1, ..., a_{m_1}, 0, 0, ..., 0)\)
        \item \(b = (0, 0, ..., 0, b_1, ..., b_{m_3})\)
        \item If \(m_1 \neq 0\), then \(a_{m_1} \neq 0\)
        \item If \(m_3 \neq 0\), then \(b_1 \neq 0\)
    \end{itemize}
\end{lemma}
\begin{proof}
    If \(a\) and \(b\) are of this form, then for every \(k \geq 0\) we have \(b_i a_{i - k} = 0\), so clearly the condition holds.
    \par Now suppose (1) holds.
    If \(a\) or \(b\) is zero, this is trivial.
    Otherwise, let \(m_1 = \max\{i : a_i \neq 0\}\), and let \(m_3 = \min\{i : b_i \neq 0\}\).
    We just need to show that \(m_1 < m_3\).
    For contradiction, suppose \(m_1 - m_3\) is nonnegative.
    Then by (1), \(0 = \sum_i b_i a_{i - (m_1 - m_3)} = b_1 a_{m_1}\), contradicting that \(b_1\) and \(a_{m_1}\) are nonzero.
\end{proof}

\subsection{In the case of general \(X\)}
In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
In the general case, it is not clear that such a thing should be true.
And indeed it is not.
However, we will see that we can change basis of \(\mathbb{C}^m\) so that a similar thing is true.
\par Let \(c_{i',j'}^i \in \mathbb{C}\) be some arbitrary coefficients.
Given our Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\), we can define a new Jordan basis \(e_{ij}'\) of \(\mathbb{C}^m\) by 
\[e_{i, \lambda_i}' = e_{i, \lambda_i} + \sum_{\{(i',j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i',j'}.\]
Then we define
\[e_{i,j}' = X^{\lambda_i - j} e_{i, \lambda_i}' = e_{ij} + \sum_{\{(i', j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i', j' - (\lambda_i - j)}.\]
Let us calculate the new value \(a'\) of \(a\) in this new basis.
That is, we want the values \(a_{ij}'\) that satisfy \(Ae_{ij}' = e_{i, j - 1}' + a_{ij}' f_1\).
Looking at the definition of \(e_{ij}'\) above, we see that
\[a_{ij}' = a_{ij} + \sum_{\{(i',j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c_{i',j'}^i a_{i', j' - (\lambda_i - j)}.\]
\par Now, for each \(i\), choose the coefficients \(c_{i',j'}^i\) to maximize the value \(\max\{j : (a_{i,1}', ..., a_{i, j}') = 0\}\).
In other words, we choose \(c_{i'j'}^i\) to zero out the largest possible prefix of \((a_{i, 1}, ..., a_{i, \lambda_i})\).

\subsection{TODO}
\begin{itemize}
    \item Why are SOn flags what they are.
\end{itemize}

\bibliography{paper}
\end{document}

### 2024-07-25 paper.tex
say what a, b look like in case of general X

@@
 Continuing in this way, we obtain that for all \(k \geq 0\),
-\[\sum_{ij} b_{ij} a_{i,j - k} = 0.\]
+\begin{equation}\label{ab_nilp}\sum_{ij} b_{ij} a_{i,j - k} = 0.\end{equation}
 In fact this is in fact a sufficient condition for \(A_{X, a, b}\) to be nilpotent, as can be seen from the characteristic polynomial of \(A_{X, a, b}\).
@@
         \item \(m = m_1 + m_2 + m_3\)
-        \item \(a = (a_1, ..., a_{m_1}, 0, 0, ..., 0)\)
-        \item \(b = (0, 0, ..., 0, b_1, ..., b_{m_3})\)
+        \item \(a = (0, 0, ..., 0, a_1, ..., a_{m_3})\)
+        \item \(b = (b_1, ..., b_{m_1}, 0, 0, ..., 0)\)
         \item If \(m_1 \neq 0\), then \(a_{m_1} \neq 0\)
@@
 In other words, we choose \(c_{i'j'}^i\) to zero out the largest possible prefix of \((a_{i, 1}, ..., a_{i, \lambda_i})\).
+\begin{lemma}
+    The condition of \cref{ab_nilp} on \(a\) and \(b\) holds iff there exist nonnegative \(p_i, q_i, r_i\), \(\alpha_{i, j}\), \(\beta_{i, j}\) such that for each \(i\), the following conditions are satisfied.
+    \begin{itemize}
+        \item \(\lambda_i = p_i + q_i + r_i\)
+        \item \((a_{i,1}, ..., a_{i,\lambda_i}) = (0, 0, ..., 0, \alpha_{i,1}, ..., \alpha_{i, r_i})\)
+        \item \((b_{i, 1}, ..., b_{i, \lambda_i}) = (\beta_{i, 1}, ..., \beta_{i, p_i}, 0, 0, ..., 0)\)
+        \item If \(r_i \neq 0\), then \(a_1 \neq 0\)
+        \item If \(p_i \neq 0\), then \(b_{p_i} \neq 0\)
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+
+\end{proof}
 

### 2024-07-25 paper.tex
fix definition of c's, and write proof of what a,b look like for general X

@@
 Given our Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\), we can define a new Jordan basis \(e_{ij}'\) of \(\mathbb{C}^m\) by 
-\[e_{i, \lambda_i}' = e_{i, \lambda_i} + \sum_{\{(i',j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i',j'}.\]
+\[e_{i, \lambda_i}' = e_{i, \lambda_i} + \sum_{\{(i',j') : i' \geq i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i',j'}.\]
 Then we define
-\[e_{i,j}' = X^{\lambda_i - j} e_{i, \lambda_i}' = e_{ij} + \sum_{\{(i', j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i', j' - (\lambda_i - j)}.\]
+\[e_{i,j}' = X^{\lambda_i - j} e_{i, \lambda_i}' = e_{ij} + \sum_{\{(i', j') : i' \geq i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i', j' - (\lambda_i - j)}.\]
 Let us calculate the new value \(a'\) of \(a\) in this new basis.
@@
 Looking at the definition of \(e_{ij}'\) above, we see that
-\[a_{ij}' = a_{ij} + \sum_{\{(i',j') : i' \leq i, j' \leq \lambda_i\} \setminus \{(i, j)\}} c_{i',j'}^i a_{i', j' - (\lambda_i - j)}.\]
+\[a_{ij}' = a_{ij} + \sum_{\{(i',j') : i' \geq i\} \setminus \{(i, j)\}} c_{i',j'}^i a_{i', j' - (\lambda_i - j)}.\]
 \par Now, for each \(i\), choose the coefficients \(c_{i',j'}^i\) to maximize the value \(\max\{j : (a_{i,1}', ..., a_{i, j}') = 0\}\).
@@
 \begin{lemma}
-    The condition of \cref{ab_nilp} on \(a\) and \(b\) holds iff there exist nonnegative \(p_i, q_i, r_i\), \(\alpha_{i, j}\), \(\beta_{i, j}\) such that for each \(i\), the following conditions are satisfied.
+    If the condition of \cref{ab_nilp} on \(a'\) and \(b'\) holds, then there exist nonnegative \(p_i, q_i, r_i\), \(\alpha_{i, j}\), \(\beta_{i, j}\) such that for each \(i\), the following conditions are satisfied.
     \begin{itemize}
         \item \(\lambda_i = p_i + q_i + r_i\)
-        \item \((a_{i,1}, ..., a_{i,\lambda_i}) = (0, 0, ..., 0, \alpha_{i,1}, ..., \alpha_{i, r_i})\)
-        \item \((b_{i, 1}, ..., b_{i, \lambda_i}) = (\beta_{i, 1}, ..., \beta_{i, p_i}, 0, 0, ..., 0)\)
-        \item If \(r_i \neq 0\), then \(a_1 \neq 0\)
-        \item If \(p_i \neq 0\), then \(b_{p_i} \neq 0\)
+        \item \((a_{i,1}', ..., a_{i,\lambda_i}') = (0, 0, ..., 0, \alpha_{i,1}, ..., \alpha_{i, r_i})\)
+        \item \((b_{i, 1}', ..., b_{i, \lambda_i}') = (\beta_{i, 1}, ..., \beta_{i, p_i}, 0, 0, ..., 0)\)
+        \item If \(r_i \neq 0\), then \(\alpha_{i,1} \neq 0\)
+        \item If \(p_i \neq 0\), then \(\beta_{i, p_i} \neq 0\)
     \end{itemize}
@@
 \begin{proof}
+    We begin with the first row of \(\lambda\), namely \(i = 1\).
+    Let \(k = \min\{j : a'_{1,j} \neq 0\}\) and \(l = \max\{j : b'_{1, j} \neq 0\}\).
+    I just need to show that \(l < k\).
+    Suppose not.
+    Then \((l - k)\) is nonnegative, and by \cref{ab_nilp} we have 
+    \[0 = \sum_{ij} b_{ij}' a_{j - (l - k)}' = b_{1,l}' a_{1,k}' + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{ij} a'_{j - (l - k)}.\]
+    This suggests defining 
+    \[e_{1,\lambda_1}'' = b_{1, l}'e_{1, \lambda_1}' + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{i',j' - (\lambda_1 - l)} e'_{i'j'}.\]
+    Then for \(j \leq k\),
+    \[a_{1,j}'' = b'_{1, l} a'_{1, j} + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{i', j' - (\lambda_1 - l)} a'_{i', j' - (\lambda_1 - j)} = \]
+    \[\sum_{i', j'} b'_{i', j' - (\lambda_1 - l)} a'_{i', j' - (\lambda_1 - j)} = \sum_{i', j'} b'_{i', j'} a'_{i', (j' + (\lambda_1 - l)) - (\lambda_1 - j)} = \sum_{i',j'} b'_{i',j'} a'_{i', j' - (l - j)}.\]
+    This last thing is zero by \cref{ab_nilp}, using that \(l - j \geq 0\).
+    But this contradicts the definition of the \(c_{i'j'}^1\), because we made it so that \((a''_{1, 1}, ..., a''_{1, k}) = 0\).
 

### 2024-07-25 paper.tex
fill in part of proof for all-zero case.  also fix some notation

@@
 Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
-Let \(\mathcal{F}l\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
-Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{m}, n) : n \in \mathfrak{m}\} \subseteq \mathcal{M} \times \mathcal{N}\).
+Let \(\mathcal{B}\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
+Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{b}, n) : n \in \mathfrak{b}\} \subseteq \mathcal{B} \times \mathcal{N}\).
 Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
@@
 \begin{lemma}
+    Each \(\mathcal{F}_\delta\) is irreducible of dimension \(m\).
+\end{lemma}
+\begin{proof}
+    Let \(\mathcal{E}\) be the variety of partial flags of \(E\) of shape \((\delta_0, ..., \delta_{n + 1})\).
+    Define \(g : \mathcal{F}_\delta \to \mathcal{E}\) by
+    \[(V, a, b) \mapsto 0 \subseteq V_{i_0} \cap E \subseteq V_{i_1} \cap E \subseteq \cdots \subseteq V_{i_{n + 1}} \cap E = E.\]
+    It is clear that \(g\) is surjective, as the definition of \(\mathcal{F}_\delta\) places no restriction on the intersections \(V_i \cap E\).
+    Now let's look more closely at the fibers \(g^{-1}(U)\).
+    \par First let's find the flags \(V\) such that there exist \(a, b\) with \(g(V, a, b) = U\).
+    We see that, for instance, \(V_{i_0} \cap E = U_1\).
+    In fact \(V_{i_0} \subseteq E\), so \(V_{i_0} = U_1\).
+    But we are free to choose the vector spaces between \(0\) and \(V_{i_0}\) however we wish, so we get some degrees of freedom like \(\mathcal{F}_{\delta_0}\), the complete flag variety on \(\mathbb{C}^{\delta_0} \cong V_{i_0} / 0\).
+    Similarly, for every \(j = 1, ..., n + 1\), we can choose the vector spaces between \(V_{i_{j - 1}}\) and \(V_{i_j}\) arbitrarily, so we get degrees of freedom like \(\mathcal{F}_{\delta_{i_j}}\), the complete flag variety on \(\mathbb{C}^{\delta_{i_j}} \cong V_{i_j} / V_{i_{j - 1}}\).
+    Finally, to meet the constraint of \((V, a, b)\) being in \(\mathcal{F}_\delta\), we can choose any \(b \in U_1\) and any \(a\) such that \(\overline{a} \in U_n^\perp\).
+    Thus we get an isomorphism
+    \[g^{-1}(U) \cong \mathcal{F}_{\delta_0} \times \cdots \times \mathcal{F}_{\delta_{n + 1}} \times \mathbb{C}^{\delta_0} \times \mathbb{C}^{\delta_{n + 1}}.\]
 
-\end{lemma}
+\end{proof}
+
+\begin{theorem}
+    The \(\mathcal{F}_\delta\)'s are the irreducible components of \(\mathcal{F}\).
+\end{theorem}
 

### 2024-07-25 paper.tex
progress on calculating sl2-triple

@@
 \par Let
-\[e = \begin{pNiceArray}{ccc|ccccc}
-    & & & & & & & \\
-    & & & & & & &    \\
-    & & & & & & & \\
-   \hline
-     & & & 0 \\
-   & & & 1 & 0 \\
-   & & &  & 1 & \ddots \\
-   & & &  &   & \ddots & 0 \\
-   & & &  &   &  & 1 & 0
-   \end{pNiceArray} \in \mathfrak{sl}_{m + n},\]
-where there are \(n\) ones.
+\[e = \begin{pNiceArray}{ccccc}
+ 0 \\
+    1 & 0 \\
+  & 1 & \ddots \\
+   & & \ddots & 0 \\
+   &   &  & 1 & 0
+   \end{pNiceArray} \in \mathfrak{sl}_{n},\]
+where there are \(n - 1\) ones.
 We will find the Slodowy slice at \(e\).
-\par As a first step, we will find an \(\spl_2\) triple with \(e\) as its first element.
+\par As a first step, we will find an \(\spl_2\)-triple with \(e\) as its first element.
 Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
@@
 In particular, \(he - eh = 2e\).  
-\(eh\) is the last \(n\) rows of \(h\), shifted down one, and \(he\) is the last \(n - 1\) columns of \(h\), shifted left one.
-Somehow (TODO: fill in) we conclude that \(f\) and \(h\) are something.
+The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
+Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
+We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
+Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
+\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
+We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
+Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i, i}\), that \(f_{1,2} = h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
 

### 2024-07-25 paper.tex
finish with the sl2-triple

@@
 By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.
+
+\subsection{Finding an \(\spl_2\)-triple in a simple case}
 \par Let
@@
 We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
-Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i, i}\), that \(f_{1,2} = h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
+Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
+From the first equation we find that
+\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
+\[\sum_i h_{ii} = 0.\]
+This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
+So we have determined \(h\); it is 
+\[h = \begin{pmatrix}
+    n - 1  & \\
+    & n - 3 \\
+    & & \ddots \\
+    & & & 3 - n \\
+    & & & & 1 - n 
+\end{pmatrix}.\]
+Now, we can use our expression for \(f\) in terms of \(h\) to obtain
+\[f = \begin{pmatrix}
+    0 & 1 - n \\
+    & 0 & (1 - n) + (3 - n) \\
+    & & \ddots & \ddots \\
+    & & & 0 & (1 - n) + \cdots + (n - 1) \\
+    & & & & 0
+\end{pmatrix} = \]
+\[\begin{pmatrix}
+    0 & 1 (1 - n) \\
+      & 0 & 2 (2 - n) \\
+    & & 0 & (n - 2) (-2) \\
+    & & & 0 & (n - 1) (-1)\\
+    & &  & & 0
+\end{pmatrix}.\]
+
+\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
+Now, suppose \(e = \)
 

### 2024-07-25 paper.tex
start on other sl2-tripel

@@
 \[\sum_i h_{ii} = 0.\]
+Oops, I didn't actually need to prove that, since \(h \in \spl_n\)... it's nice to know that it's the unique solution in \(\gl_n\) though?
 This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
@@
 \subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
-Now, suppose \(e = \)
+Now, let 
+\[E = \begin{pmatrix}
+    0 & 0 \\
+    0 & e
+\end{pmatrix} \in \spl_{m + n},\]
+with \(e\) as in the previous subsection.
+We will find \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
+Writing \(F = \begin{pmatrix}
+    F_{11} & F_{12} \\
+    F_{21} & f
+\end{pmatrix}\), and similarly for \(H\), we have
+\[2E = [H, E] = \begin{pmatrix}
+    0 & H_{12}e \\
+    0 & he
+\end{pmatrix} - \begin{pmatrix}
+    0 & 0 \\
+    e H_{21} & eh
+\end{pmatrix},\]
+\[H = [E, F] = \begin{pmatrix}
+    0 & 0 \\
+    e F_{21} & ef
+\end{pmatrix} - \begin{pmatrix}
+    0 & F_{12}e \\
+    0 & fe
+\end{pmatrix}.\]
+From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in the previous subsection.
+We also see that \(H_{11} = 0\).
+Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
+Similarly for \(F_{12}\) and \(F_{21}\).
+Then our final constraint is that 
+\[-2F = [H, F] = \]
+\[\begin{pmatrix}
+    H_{12} F_{21} & H_{12} F_{22} \\
+    H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
+\end{pmatrix} - \begin{pmatrix}
+    F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
+    F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
+\end{pmatrix}.\]
+Now \(H_{12} F_{21} = F_{12} H_{21} = 0\), by our facts about them from further above.
+By the equation above then, we also get \(F_{11} = 0\).
+So, the equation above simplifies to 
+\[-2F = \begin{pmatrix}
+    0 & H_{12} f \\
+    h F_{21} & H_{21} F_{12}
+\end{pmatrix} - \begin{pmatrix}
+    0 & F_{12} h \\
+    f H_{21} & F_{21} H_{12}
+\end{pmatrix}.\]
 

### 2024-07-25 paper.tex
finish other sl2-triple

@@
 Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
-Similarly for \(F_{12}\) and \(F_{21}\).
+% Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
 Then our final constraint is that 
@@
 \end{pmatrix}.\]
-Now \(H_{12} F_{21} = F_{12} H_{21} = 0\), by our facts about them from further above.
-By the equation above then, we also get \(F_{11} = 0\).
-So, the equation above simplifies to 
+Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
+Substituting in the equation above then,
 \[-2F = \begin{pmatrix}
-    0 & H_{12} f \\
-    h F_{21} & H_{21} F_{12}
+    F_{12} e F_{21} & F_{12}e f \\
+    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
 \end{pmatrix} - \begin{pmatrix}
-    0 & F_{12} h \\
-    f H_{21} & F_{21} H_{12}
+    F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
+    f eF_{21} & F_{21} F_{12}e + fh
+\end{pmatrix} =\]
+\[\begin{pmatrix}
+    0 & F_{12}(fe + h) \\
+    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
+\end{pmatrix} - \begin{pmatrix}
+    0 & F_{11} F_{12}e + F_{12} h \\
+    (ef - h)F_{21} & F_{21} F_{12}e + fh
+\end{pmatrix} =\]
+\[\begin{pmatrix}
+    0 & F_{12}fe \\
+    eF_{21} F_{11} & eF_{21} F_{12} + hf
+\end{pmatrix} - \begin{pmatrix}
+    0 & F_{11} F_{12}e \\
+    ef F_{21} & F_{21} F_{12}e + fh
 \end{pmatrix}.\]
+Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
+This shows that \(H_{12} = H_{21} = 0\).
+We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
 

### 2024-07-25 paper.tex
about no progress on finding slodowy slices
find slodowy slices

@@
 We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
+
+\subsection{Finding the previous Slodowy slices}
+First we find \(\ker \ad_f\).
+We have \((fX)_{ij} = i (n - i) A_{i + 1,j}\), and \((Xf)_{ij} = (j - 1) (n - (j - 1)) A_{i, j - 1}\).
+So, for all \(i, j \in \{1, ..., n\}\), we have 
+\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{1, j - 1}.\]
+Taking \(j = 1\), we find that \(A_{i,1} = 0\) for \(i \geq 2\).
+Then, taking \(j > 1\), we find that for \(i, j \in \{1, ..., n - 1\}\),
+\[A_{i + 1, j + 1} = \frac{(j - 1)(n - (j - 1))}{i(n - i)} A_{ij}.\]
+So, \(\ker\ad_f\) is the set of matrices which are upper triangular and satisfy the above condition.
+\par To find the Slodowy slice associated to the previous \(\spl_2\)-triple \((E, H, F)\), we just need to find \(\ker\ad_F\).
+We have 
+\[[F, X] = \begin{pmatrix}
+    0 & 0 \\
+    f X_{21} & fX_{22}
+\end{pmatrix} - \begin{pmatrix}
+    0 & X_{12} f\\
+    0 & X_{22} f
+\end{pmatrix}.\]
+Thus, \(X_{21}\) must be all zeroes except for the first row, and \(X_{12}\) must be all zeroes except for the last column, and \(X_{22} \in \ker\ad_f\).
+This describes \(\ker\ad_F\).
 

### 2024-07-26 paper.tex
find intersection of one slodowy slice with nilpotent elts

@@
 So, for all \(i, j \in \{1, ..., n\}\), we have 
-\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{1, j - 1}.\]
+\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{i, j - 1}.\]
 Taking \(j = 1\), we find that \(A_{i,1} = 0\) for \(i \geq 2\).
@@
 Thus, \(X_{21}\) must be all zeroes except for the first row, and \(X_{12}\) must be all zeroes except for the last column, and \(X_{22} \in \ker\ad_f\).
+There is no restriction on \(X_{11}\).
 This describes \(\ker\ad_F\).
+
+\begin{lemma}
+    Let \(J\) be a jordan block with zeroes along the diagonal, and let  \(A\) be upper triangular and nonzero.
+    Then \(J + A\) is not nilpotent.
+\end{lemma}
+\begin{proof}
+    It is straightforward to show by induction that if \(v_i = 0\) for \(i < j\), and \(v_j \neq 0\), then \(((J + A)^k v_j)_{j + k} = v_j\).
+    Let \(i\) be such that \(Ae_i \neq 0\).
+    Then \((J + A)^{i - 1} e_1\) has nonzero \(e_i\)-component.
+    Then \((J + A)^i e_1\) has some nonzero \(e_{i'}\)-component for some \(i' \leq i\).
+    Then \((J + A)^{i + (n - i')} e_1\) has some nonzero \(e_n\)-component.
+    And \(i + (n - i') \geq n\), so we're done.
+\end{proof}
 

### 2024-07-29 makematrix.py
add printing thing for mathematica

@@ -1,0 +1,21 @@
+def matrix(a, b, n):
+	m = sum(len(row) for row in a)
+	out = ""
+	out += "SparseArray[{"
+	boxnum = 1
+	for i in range(1, len(a) + 1):
+		for j in range(1, len(a[i-1]) + 1):
+			if j < len(a[i-1]):
+				out += f"{{{boxnum}, {boxnum+1}}} -> 1,"
+			if a[i-1][j-1] != 0:
+				out += f"{{{m + 1}, {boxnum}}} -> {a[i-1][j-1]},"
+			if b[i-1][j-1] != 0:
+				out += f"{{{boxnum}, {m + n}}} -> {b[i-1][j-1]},"
+			boxnum += 1
+	for i in range(m + 1, m + n + 1):
+		if i != m + n:
+			out += f"{{{i}, {i+1}}} -> 1,"
+	if out[-1] == ",":
+		out = out[:-1]
+	out += f"}}, {{{m + n}, {m + n}}}]\n"
+	return out

### 2024-07-29 makematrix.py
fix matrix printer

@@ -1,4 +1,6 @@
 def matrix(a, b, n):
+	a = [row[::-1] for row in a]
+	b = [row[::-1] for row in b]
 	m = sum(len(row) for row in a)
 	out = ""
 	out += "SparseArray[{"
@@ -6,7 +8,7 @@ def matrix(a, b, n):
 	for i in range(1, len(a) + 1):
 		for j in range(1, len(a[i-1]) + 1):
 			if j < len(a[i-1]):
-				out += f"{{{boxnum}, {boxnum+1}}} -> 1,"
+				out += f"{{{boxnum+1}, {boxnum}}} -> 1,"
 			if a[i-1][j-1] != 0:
 				out += f"{{{m + 1}, {boxnum}}} -> {a[i-1][j-1]},"
 			if b[i-1][j-1] != 0:
@@ -14,7 +16,7 @@ def matrix(a, b, n):
 			boxnum += 1
 	for i in range(m + 1, m + n + 1):
 		if i != m + n:
-			out += f"{{{i}, {i+1}}} -> 1,"
+			out += f"{{{i+1}, {i}}} -> 1,"
 	if out[-1] == ",":
 		out = out[:-1]
 	out += f"}}, {{{m + n}, {m + n}}}]\n"

### 2024-07-30 paper.tex
find what nilpotent elements of slodowy slice are. define "n-dim-slodowy-slice springer fiber"

@@
 This describes \(\ker\ad_F\).
+\par For \(X \in \mathcal{S}_{m,n}\), define \(u(X) := X_{11}\).
+
+\subsection{Finding \(\widetilde{\mathcal{N}}_{m,n}\)}
+Let \(\mathcal{N}_m \subseteq \gl_m\) be the nilpotent elements.
+Let \(\mathcal{S}_{m,n}'\) be the set of \(X \in \mathcal{S}_{m,n}\) such that both \(X\) and \(u(X)\) are nilpotent.
+Let \(\widetilde{\mathcal{N}}_{m,n} = \{(\mathfrak{b}, X) : X \in \mathfrak{b}\} \subseteq \mathcal{B}_{m + n} \times \mathcal{S}_{m,n}'\).
+Define \(\pi_{m,n} : \widetilde{\mathcal{N}}_{m,n} \to \mathcal{N}_m\) by \((\mathfrak{b}, X) \mapsto X_{11}\).
+For \(Y \in \gl_m\), we call \(\pi_{m,n}^{-1}(Y)\) the \emph{n-dim-Slodowy-slice Springer fiber} at \(Y\).
 
@@
 \end{proof}
+
+\begin{lemma}
+    Let \(X \in \gl_m\), and let 
+    \[Y = \begin{pmatrix}
+        y_{11} & y_{12} & y_{13} & \cdots & y_{1,n-1} & y_{1n} \\
+        d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
+            & d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
+            & & \ddots & \cdots & \vdots  & \vdots \\
+            & & & d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
+            & & & & d_{n - 1} & y_{nn}
+    \end{pmatrix} \in \gl_n.\]
+    For any \(a, b \in \mathbb{C}^m\),
+    \[\det 
+    \begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y & \\
+       & & &  \\
+       \end{pNiceArray} = \]
+       \[\det X \det Y + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+            & & & \vert \\
+            & X & & b     \\
+            & & & \vert \\
+            \hline 
+        \text{---} & a & \text{---} & 0
+       \end{pNiceArray}\]
+\end{lemma}
+\begin{proof}
+    By induction on \(n\).
+    In the case \(n = 1\), expanding along the last row (taking the usual interpretation of the empty product) gives the desired result.
+    \par Now suppose \(n > 1\).
+    Expanding along the last row, we get 
+    \[d_{n - 1} \det \begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y_{n,n-1} & \\
+       & & &  \\
+       \end{pNiceArray} -
+    y_{nn} \det \begin{pNiceArray}{ccc|ccc}
+        & & & & & \\
+        & X & & & &   \\
+        & & & & & \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y_{n,n} & \\
+       & & &  \\
+       \end{pNiceArray}.\]
+    Using our inductive hypothesis for the first determiniant, and using that \(\det \begin{pNiceArray}{c|c}
+        A_{11} & 0 \\
+        A_{21} & A_{22}
+    \end{pNiceArray} = \det A_{11} \det A_{22}\) for the second, the expression becomes
+    \[d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}\right)
+   - y_{nn} \det X \det Y_{nn} = \]
+   \[(d_{n - 1} Y_{n,n-1} - y_{nn} \det Y_{nn})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray} = \]
+   \[\det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}.\]
+\end{proof}
+
+\begin{corollary}
+    If \(X\) is nilpotent, and
+    \[\begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y & \\
+       & & &  \\
+       \end{pNiceArray}\]
+    is nilpotent  as well, then \(Y\) is nilpotent (TODO: and that other determinant is zero).
+    \begin{proof}
+        By the previous lemma, the characteristic polynomial of the big matrix is
+        \[g_X(\lambda) g_Y(\lambda) + f(\lambda),\]
+        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
+    \end{proof}
+\end{corollary}
+\par Now, taking the previous corolloary and the first lemma together, we see that 
+\[\mathcal{S}_{m,n}' = \left\{ \begin{pNiceArray}{ccc|cccc}
+    & & & & & & \vert \\
+    & X & & & & & b    \\
+    & & & & & & \vert \\
+   \hline
+   \text{---} & a & \text{---} & 0 \\
+    & & & 1 & 0  & \\
+    &  & & & \ddots & \ddots  \\
+    & & & & & 1 & 0
+   \end{pNiceArray} : a, b \in \mathbb{C}^m, X \in \gl_m \textrm{ is nilpotent}\right\}.\]
 

### 2024-07-30 paper.tex
write about m^2 thing

@@
 
+\section{A different variety}
+Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).
+We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
+(TODO: why is this a subvariety?  Is it?  Is this even the right way of explaining the significance of the \(m^2\)?)
+We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
+We will verify these things using our prvious computations of springer fibers.
+
 \subsection{TODO}

### 2024-08-08 paper.tex
mostly finish, and greatly simplify, 'normalization' argument for jordan basis

@@
 
+\subsection{A `normalization' fact about Jordan bases}
+Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
+Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
+
+\begin{lemma}
+    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+\end{lemma}
+\begin{proof}
+    For any change of basis \(P : V \to V\) commuting with \(A\), we obtain a new Jordan basis \((P(e_{ij}) : i \leq m, j \leq \lambda_i)\).
+    For any such \(P\), define 
+    \[S_P = \sum_i \begin{cases}-1, & \forall j. \; f \circ P(e_{ij}) = 0 \\ \lambda_i - \min\{j : f \circ P(e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
+    Let \(P\) be any operator, among all invertible operators commuting with \(A\), which minimizes \(S_P\).
+    Write \(e_{i,j}' := P(e_{i,j})\).
+    \par Suppose for contradiction that there are two distinct \(i\)'s (and some \(j\)'s) with \(f(e_{ij}') \neq 0\).
+    Then we can take \(e_{i_1, j_1}'\) and \(e_{i_2, j_2}'\), where for \(k \in \{1,2\}\) we have \(f(e_{i_k, j_k}') \neq 0\), and \(\forall j < j_k. \; f(e_{i_k, j}') = 0\).
+    Wlog, assume \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
+    Then, we can define \(Q : V \to V\) by
+    \begin{itemize}
+        \item \(Q(e_{i_1, \lambda_1}') := e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\)
+        \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
+        \item For \(i \neq i_1\), \(Q(e_{ij}') = e_{ij}'\).
+    \end{itemize}
+    Clearly \(Q\) is invertible, and it commutes with \(A\).
+    Further, I claim that \(S_{QP}  < S_P\).
+    It suffices to show that \(\forall j \leq j_1. \; f \circ Q(e_{i_1,j}') = 0\).
+    We have 
+    \[f \circ Q(e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\right)\right) =\]
+    \[f\left(e_{i_1, j}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}'\right) = f(e_{i_1, j}') - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e'_{i_2, j_2 + (j - j_1)}.\]
+    Clearly (by design), this expression is zero when \(j = j_1\).
+    And for \(j < j_1\), we have \(f(e'_{i_1, j}) = f(e'_{i_2, j_2 + (j_2 - j_1)}) = 0\), so it is zero then as well.
+    Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.
+    So there must be at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}') \neq 0\).
+    \par If there is no such \(i\), we have found the desired basis.
+    So, suppose there is such an \(i_0\).
+    Let \(U = \langle e_{i_0, j} \rangle\).
+    Simply write \(e_j := e_{i_0, j}\).
+    For any \(P : U \to U\), let \(S_P := \#\{j : f(P(e_j)) \neq 0\}\).
+    Choose \(P\) to minimize \(S_P\), and then let \(e_j' := P(e_j)\).
+    Suppose, for contradiction, that \(S_P > 1\).
+    Then let \(j_0 = \min\{j : f(e_j') \neq 0\}\), and let \(k\) be distinct from \(j\) with \(f(e_k') \neq 0\).
+    Then make the change of basis \(e_{\lambda_{i_0}}'' := e_{\lambda_{i_0}}' + ...\).
+\end{proof}
+
 \subsection{In the case of general \(X\)}
 In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
-In the general case, it is not clear that such a thing should be true.
-And indeed it is not.
-However, we will see that we can change basis of \(\mathbb{C}^m\) so that a similar thing is true.
-\par Let \(c_{i',j'}^i \in \mathbb{C}\) be some arbitrary coefficients.
-Given our Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\), we can define a new Jordan basis \(e_{ij}'\) of \(\mathbb{C}^m\) by 
-\[e_{i, \lambda_i}' = e_{i, \lambda_i} + \sum_{\{(i',j') : i' \geq i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i',j'}.\]
-Then we define
-\[e_{i,j}' = X^{\lambda_i - j} e_{i, \lambda_i}' = e_{ij} + \sum_{\{(i', j') : i' \geq i\} \setminus \{(i, j)\}} c^i_{i',j'} e_{i', j' - (\lambda_i - j)}.\]
-Let us calculate the new value \(a'\) of \(a\) in this new basis.
-That is, we want the values \(a_{ij}'\) that satisfy \(Ae_{ij}' = e_{i, j - 1}' + a_{ij}' f_1\).
-Looking at the definition of \(e_{ij}'\) above, we see that
-\[a_{ij}' = a_{ij} + \sum_{\{(i',j') : i' \geq i\} \setminus \{(i, j)\}} c_{i',j'}^i a_{i', j' - (\lambda_i - j)}.\]
-\par Now, for each \(i\), choose the coefficients \(c_{i',j'}^i\) to maximize the value \(\max\{j : (a_{i,1}', ..., a_{i, j}') = 0\}\).
-In other words, we choose \(c_{i'j'}^i\) to zero out the largest possible prefix of \((a_{i, 1}, ..., a_{i, \lambda_i})\).
-\begin{lemma}
-    If the condition of \cref{ab_nilp} on \(a'\) and \(b'\) holds, then there exist nonnegative \(p_i, q_i, r_i\), \(\alpha_{i, j}\), \(\beta_{i, j}\) such that for each \(i\), the following conditions are satisfied.
-    \begin{itemize}
-        \item \(\lambda_i = p_i + q_i + r_i\)
-        \item \((a_{i,1}', ..., a_{i,\lambda_i}') = (0, 0, ..., 0, \alpha_{i,1}, ..., \alpha_{i, r_i})\)
-        \item \((b_{i, 1}', ..., b_{i, \lambda_i}') = (\beta_{i, 1}, ..., \beta_{i, p_i}, 0, 0, ..., 0)\)
-        \item If \(r_i \neq 0\), then \(\alpha_{i,1} \neq 0\)
-        \item If \(p_i \neq 0\), then \(\beta_{i, p_i} \neq 0\)
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    We begin with the first row of \(\lambda\), namely \(i = 1\).
-    Let \(k = \min\{j : a'_{1,j} \neq 0\}\) and \(l = \max\{j : b'_{1, j} \neq 0\}\).
-    I just need to show that \(l < k\).
-    Suppose not.
-    Then \((l - k)\) is nonnegative, and by \cref{ab_nilp} we have 
-    \[0 = \sum_{ij} b_{ij}' a_{j - (l - k)}' = b_{1,l}' a_{1,k}' + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{ij} a'_{j - (l - k)}.\]
-    This suggests defining 
-    \[e_{1,\lambda_1}'' = b_{1, l}'e_{1, \lambda_1}' + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{i',j' - (\lambda_1 - l)} e'_{i'j'}.\]
-    Then for \(j \leq k\),
-    \[a_{1,j}'' = b'_{1, l} a'_{1, j} + \sum_{i' \geq 1, (i', j') \neq (1, \lambda_1)} b'_{i', j' - (\lambda_1 - l)} a'_{i', j' - (\lambda_1 - j)} = \]
-    \[\sum_{i', j'} b'_{i', j' - (\lambda_1 - l)} a'_{i', j' - (\lambda_1 - j)} = \sum_{i', j'} b'_{i', j'} a'_{i', (j' + (\lambda_1 - l)) - (\lambda_1 - j)} = \sum_{i',j'} b'_{i',j'} a'_{i', j' - (l - j)}.\]
-    This last thing is zero by \cref{ab_nilp}, using that \(l - j \geq 0\).
-    But this contradicts the definition of the \(c_{i'j'}^1\), because we made it so that \((a''_{1, 1}, ..., a''_{1, k}) = 0\).
-
-\end{proof}
+This allowed some tricks with right-shifting.
+In the general case, the parameters \(a\) and \(b\) are not necessarily in such a helpful form.
+We will see, however, that we can change basis of \(\mathbb{C}^m\) to put them in a nice form.
 

### 2024-08-08 paper.tex
reorganized things, started talking about jordan basis

@@
 For \(X \in \mathcal{N}\), we call \(\pi^{-1}(X)\) the \emph{other Springer fiber at \(X\)}.
+
+\section{A necessary condition for \(A_{X, a, b}\) to be nilpotent}
+Suppose \(A := A_{X, a, b}\) is nilpotent.
+Define the \emph{height} of a vector \(v \in \mathbb{C}^{m + n}\) as the smallest \(k \geq 0\) such that \(A_{X, a, b}^k v = 0\).
+Clearly, for \(i \leq j\), we have that the height of \(f_i\) is geq the height of \(f_j\).
+Thus, for each \(k \geq 0\), we must have \(A_{X, a, b}^k f_n \in \langle e_{ij} \rangle_{ij}\).
+We have \(Af_n = \sum_{ij} b_{ij} e_{ij}\).
+Then \(A^2 f_n = \sum_{ij} b_{ij} (e_{i, j - 1} + a_{ij} f_1)\), so we must have \(\sum_{ij} b_{ij} a_{ij} = 0\).
+Similarly, since \(A^3 f_n \in \langle e_{ij}\rangle\), we see that \(\sum_{ij} b_{ij} a_{i, j - 1} = 0\).
+Continuing in this way, we obtain that for all \(k \geq 0\),
+\begin{equation}\label{ab_nilp}\sum_{ij} b_{ij} a_{i,j - k} = 0.\end{equation}
+In fact this is in fact a sufficient condition for \(A_{X, a, b}\) to be nilpotent, as can be seen from the characteristic polynomial of \(A_{X, a, b}\).
+However, we will not do this calculation here, instead just showing that it is sufficient by giving a Jordan basis.
+
+\section{A Jordan basis for \(A_{X, a, b}\)}
+For illustration, we will begin with the case that \(X\) is a single Jordan block.
+Then we will move to the general case.
+
+\subsection{When \(X\) is a Jordan block}
+Suppose \(X\) is a single Jordan block of size \(m\).
+In this case we just write the basis of \(\mathbb{C}^m\) as \(e_1, ..., e_m\), and the above condition on \(a\) and \(b\) simply becomes
+\begin{equation}
+    \forall k \geq 0. \; \sum_{i = k + 1}^m b_i a_{i - k} = 0.
+\end{equation}
+This condition can be simplified even more.
+\begin{lemma}
+    The condition (1) holds iff there exist nonnegative \(m_1, m_2, m_3\), \(a_1, ..., a_{m_3}\), and \(b_1, ..., b_{m_3}\) satisfying the following conditions.
+    \begin{itemize}
+        \item \(m = m_1 + m_2 + m_3\)
+        \item \(a = (0, 0, ..., 0, a_1, ..., a_{m_3})\)
+        \item \(b = (b_1, ..., b_{m_1}, 0, 0, ..., 0)\)
+        \item If \(m_1 \neq 0\), then \(a_{m_1} \neq 0\)
+        \item If \(m_3 \neq 0\), then \(b_1 \neq 0\)
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    If \(a\) and \(b\) are of this form, then for every \(k \geq 0\) we have \(b_i a_{i - k} = 0\), so clearly the condition holds.
+    \par Now suppose (1) holds.
+    If \(a\) or \(b\) is zero, this is trivial.
+    Otherwise, let \(m_1 = \max\{i : a_i \neq 0\}\), and let \(m_3 = \min\{i : b_i \neq 0\}\).
+    We just need to show that \(m_1 < m_3\).
+    For contradiction, suppose \(m_1 - m_3\) is nonnegative.
+    Then by (1), \(0 = \sum_i b_i a_{i - (m_1 - m_3)} = b_1 a_{m_1}\), contradicting that \(b_1\) and \(a_{m_1}\) are nonzero.
+\end{proof}
+
+\subsection{A `normalization' fact about Jordan bases}
+Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
+Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
+
+\begin{lemma}
+    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+\end{lemma}
+\begin{proof}
+    For any change of basis \(P : V \to V\) commuting with \(A\), we obtain a new Jordan basis \((P(e_{ij}) : i \leq m, j \leq \lambda_i)\).
+    For any such \(P\), define 
+    \[S_P = \sum_i \begin{cases}-1, & \forall j. \; f \circ P(e_{ij}) = 0 \\ \lambda_i - \min\{j : f \circ P(e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
+    Let \(P\) be any operator, among all invertible operators commuting with \(A\), which minimizes \(S_P\).
+    Write \(e_{i,j}' := P(e_{i,j})\).
+    \par Suppose for contradiction that there are two distinct \(i\)'s (and some \(j\)'s) with \(f(e_{ij}') \neq 0\).
+    Then we can take \(e_{i_1, j_1}'\) and \(e_{i_2, j_2}'\), where for \(k \in \{1,2\}\) we have \(f(e_{i_k, j_k}') \neq 0\), and \(\forall j < j_k. \; f(e_{i_k, j}') = 0\).
+    Wlog, assume \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
+    Then, we can define \(Q : V \to V\) by
+    \begin{itemize}
+        \item \(Q(e_{i_1, \lambda_1}') := e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\)
+        \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
+        \item For \(i \neq i_1\), \(Q(e_{ij}') = e_{ij}'\).
+    \end{itemize}
+    Clearly \(Q\) is invertible, and it commutes with \(A\).
+    Further, I claim that \(S_{QP}  < S_P\).
+    It suffices to show that \(\forall j \leq j_1. \; f \circ Q(e_{i_1,j}') = 0\).
+    We have 
+    \[f \circ Q(e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\right)\right) =\]
+    \[f\left(e_{i_1, j}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}'\right) = f(e_{i_1, j}') - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e'_{i_2, j_2 + (j - j_1)}.\]
+    Clearly (by design), this expression is zero when \(j = j_1\).
+    And for \(j < j_1\), we have \(f(e'_{i_1, j}) = f(e'_{i_2, j_2 + (j_2 - j_1)}) = 0\), so it is zero then as well.
+    Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.
+    So there must be at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}') \neq 0\).
+    \par If there is no such \(i\), we have found the desired basis.
+    So, suppose there is such an \(i_0\).
+    Let \(U = \langle e_{i_0, j}' \rangle\).
+    Simply write \(e_j := e_{i_0, j}'\).
+    Let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
+    We just have to change basis to zero out \(e_j\) for \(j \neq j_0\).
+    Let \(P_1(e_{\lambda_{i_0}}) := e_{\lambda_{i_0}} - \frac{f(e_{j_0 + 1})}{f(e_{j_0})} e_{\lambda_{i_0} - 1}\), and notice that \(f \circ P_1(e_j) = 0\) for all \(j \leq j_0 + 1\) except for \(j_0\).
+    Then we define \(P_2(e_{\lambda_{i_0}}) := P_1(e_{\lambda_{i_0}}) - \frac{f\circ P_1(e_{j_0 + 2})}{f\circ P_1(e_{j_0})} e_{\lambda_{i_0} - 2}\), and notice that \(f \circ P_2(e_j) = 0\) for all \(j \leq j_0 + 2\) except for \(j_0\).
+    Eventually we get \(P_{\lambda_{i_0} - j_0}\), and by applying this to the \(e_j\)'s we obtain a basis of \(U\), in which there is exactly one \(j\) with \(f \circ P_{\lambda_{i_0} - j_0}(e_j) \neq 0\).
+\end{proof}
+
+\subsection{The general case}
+In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
+This allowed some tricks with right-shifting.
+In the general case, the parameters \(a\) and \(b\) are not necessarily in such a helpful form.
+We will see, however, that we can change basis of \(\mathbb{C}^m\) to put them in a nice form.
+\par Recall our nilpotent operator \(A_{X, a, b}\) on \(\mathbb{C}^m \times \mathbb{C}^n\).
+We can define a map \(\mathbb{C}^m \to \mathbb{C}\) by \(x \mapsto x \cdot a\).
+Then, by the previous lemma, we can choose a Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\) so that at most one \((i, j)\) has \(f(e_{ij}) \neq 0\).
+This implies that there are some \(P, k, b'\) such that \(PA_{X, a, b}P^{-1} = A_{X, 1_k, b'}\).
+So, without loss of generality, we may consider this case, where \(a = 1_k\).
+\par Write our basis of \(\mathbb{C}^m\) as \(e_{ij}\) and our basis of \(\mathbb{C}^n\) as \(f_j\).
+Let \(i_0, r\) be such that \(a = e_{i_0, \lambda_{i_0} - r + 1}\).
+Let \(b' = A^{n + r} e_{i_0, \lambda_{i_0}} = b + e_{i_0, \lambda_{i_0} - r - n}\).
+Let \(b_{ij}'\) be the projection of \(b'\) onto \(e_{ij}\).
+For each \(i\), let \(p_i = \max\{j : b_{ij}' \neq 0\}\).
+Then for each \(i \neq i_0\), let \(q_i = \lambda_i - p_i\).  Let \(q_{i_0} = \lambda_{i_0} - r - p_{i_0}\).
+Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
+Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that.
+\par We have two cases, which will closely resemble the cases we had when \(X\) was a single Jordan block.
+\subsubsection{First case: \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)}
+We list the chains in (roughly) decreasing order.
+First, for each \(i\) such that \(q_i \geq n + r\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
+\par Now we handle \(e_{i_0, \lambda_{i_0}}\).
+Let \(P = \max_{i : q_i < n + r} p_i\).
+Set 
+\[v = e_{i_0, \lambda_{i_0}} - (A^{r + n + P}e_{i_0, \lambda_{i_0}} >> r + n + P).\]
+Note that \(A^{r + n} e_{i_0, \lambda_{i_0}} = b'\), so \(A^{r + n + P} e_{i_0, \lambda_{i_0}} = A^P b' = b' << P\).
+Also note that if we shift \(b'\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n + r\).
+This ensures that the operation of shifting \(b' << P\) right \(r + n + P\) times is invertible by applying \(A\), and thus shifting left, \(r + n + P\) times.
+So, we take the chain of length \(r + n + P\) beginning with \(v\).
+How do we know this is linearly independent from what came before?
+Something to do with the condition on \(n\)...
+\par Now, we handle the \(i\) with \(q_i < n + r\).
+If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
+Otherwise, we set 
+\[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k} e_{i,k + q_i}.\]
+Note that \(v_i\) is just
+
 \section{Finding the Springer fibers of section 2}
@@
 Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).
-
-\subsection{A necessary condition for \(A_{X, a, b}\) to be nilpotent}
-Suppose \(A := A_{X, a, b}\) is nilpotent.
-Define the \emph{height} of a vector \(v \in \mathbb{C}^{m + n}\) as the smallest \(k \geq 0\) such that \(A_{X, a, b}^k v = 0\).
-Clearly, for \(i \leq j\), we have that the height of \(f_i\) is geq the height of \(f_j\).
-Thus, for each \(k \geq 0\), we must have \(A_{X, a, b}^k f_n \in \langle e_{ij} \rangle_{ij}\).
-We have \(Af_n = \sum_{ij} b_{ij} e_{ij}\).
-Then \(A^2 f_n = \sum_{ij} b_{ij} (e_{i, j - 1} + a_{ij} f_1)\), so we must have \(\sum_{ij} b_{ij} a_{ij} = 0\).
-Similarly, since \(A^3 f_n \in \langle e_{ij}\rangle\), we see that \(\sum_{ij} b_{ij} a_{i, j - 1} = 0\).
-Continuing in this way, we obtain that for all \(k \geq 0\),
-\begin{equation}\label{ab_nilp}\sum_{ij} b_{ij} a_{i,j - k} = 0.\end{equation}
-In fact this is in fact a sufficient condition for \(A_{X, a, b}\) to be nilpotent, as can be seen from the characteristic polynomial of \(A_{X, a, b}\).
-However, we will not do this calculation here, instead just showing that it is sufficient by giving a Jordan basis.
 
@@
 
-\subsection{When \(X\) is a Jordan block}
-Suppose \(X\) is a single Jordan block of size \(m\).
-In this case we just write the basis of \(\mathbb{C}^m\) as \(e_1, ..., e_m\), and the above condition on \(a\) and \(b\) simply becomes
-\begin{equation}
-    \forall k \geq 0. \; \sum_{i = k + 1}^m b_i a_{i - k} = 0.
-\end{equation}
-This condition can be simplified even more.
-\begin{lemma}
-    The condition (1) holds iff there exist nonnegative \(m_1, m_2, m_3\), \(a_1, ..., a_{m_3}\), and \(b_1, ..., b_{m_3}\) satisfying the following conditions.
-    \begin{itemize}
-        \item \(m = m_1 + m_2 + m_3\)
-        \item \(a = (0, 0, ..., 0, a_1, ..., a_{m_3})\)
-        \item \(b = (b_1, ..., b_{m_1}, 0, 0, ..., 0)\)
-        \item If \(m_1 \neq 0\), then \(a_{m_1} \neq 0\)
-        \item If \(m_3 \neq 0\), then \(b_1 \neq 0\)
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    If \(a\) and \(b\) are of this form, then for every \(k \geq 0\) we have \(b_i a_{i - k} = 0\), so clearly the condition holds.
-    \par Now suppose (1) holds.
-    If \(a\) or \(b\) is zero, this is trivial.
-    Otherwise, let \(m_1 = \max\{i : a_i \neq 0\}\), and let \(m_3 = \min\{i : b_i \neq 0\}\).
-    We just need to show that \(m_1 < m_3\).
-    For contradiction, suppose \(m_1 - m_3\) is nonnegative.
-    Then by (1), \(0 = \sum_i b_i a_{i - (m_1 - m_3)} = b_1 a_{m_1}\), contradicting that \(b_1\) and \(a_{m_1}\) are nonzero.
-\end{proof}
-
-\subsection{A `normalization' fact about Jordan bases}
-Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
-Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
-
-\begin{lemma}
-    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
-\end{lemma}
-\begin{proof}
-    For any change of basis \(P : V \to V\) commuting with \(A\), we obtain a new Jordan basis \((P(e_{ij}) : i \leq m, j \leq \lambda_i)\).
-    For any such \(P\), define 
-    \[S_P = \sum_i \begin{cases}-1, & \forall j. \; f \circ P(e_{ij}) = 0 \\ \lambda_i - \min\{j : f \circ P(e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
-    Let \(P\) be any operator, among all invertible operators commuting with \(A\), which minimizes \(S_P\).
-    Write \(e_{i,j}' := P(e_{i,j})\).
-    \par Suppose for contradiction that there are two distinct \(i\)'s (and some \(j\)'s) with \(f(e_{ij}') \neq 0\).
-    Then we can take \(e_{i_1, j_1}'\) and \(e_{i_2, j_2}'\), where for \(k \in \{1,2\}\) we have \(f(e_{i_k, j_k}') \neq 0\), and \(\forall j < j_k. \; f(e_{i_k, j}') = 0\).
-    Wlog, assume \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
-    Then, we can define \(Q : V \to V\) by
-    \begin{itemize}
-        \item \(Q(e_{i_1, \lambda_1}') := e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\)
-        \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
-        \item For \(i \neq i_1\), \(Q(e_{ij}') = e_{ij}'\).
-    \end{itemize}
-    Clearly \(Q\) is invertible, and it commutes with \(A\).
-    Further, I claim that \(S_{QP}  < S_P\).
-    It suffices to show that \(\forall j \leq j_1. \; f \circ Q(e_{i_1,j}') = 0\).
-    We have 
-    \[f \circ Q(e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\right)\right) =\]
-    \[f\left(e_{i_1, j}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}'\right) = f(e_{i_1, j}') - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e'_{i_2, j_2 + (j - j_1)}.\]
-    Clearly (by design), this expression is zero when \(j = j_1\).
-    And for \(j < j_1\), we have \(f(e'_{i_1, j}) = f(e'_{i_2, j_2 + (j_2 - j_1)}) = 0\), so it is zero then as well.
-    Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.
-    So there must be at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}') \neq 0\).
-    \par If there is no such \(i\), we have found the desired basis.
-    So, suppose there is such an \(i_0\).
-    Let \(U = \langle e_{i_0, j} \rangle\).
-    Simply write \(e_j := e_{i_0, j}\).
-    For any \(P : U \to U\), let \(S_P := \#\{j : f(P(e_j)) \neq 0\}\).
-    Choose \(P\) to minimize \(S_P\), and then let \(e_j' := P(e_j)\).
-    Suppose, for contradiction, that \(S_P > 1\).
-    Then let \(j_0 = \min\{j : f(e_j') \neq 0\}\), and let \(k\) be distinct from \(j\) with \(f(e_k') \neq 0\).
-    Then make the change of basis \(e_{\lambda_{i_0}}'' := e_{\lambda_{i_0}}' + ...\).
-\end{proof}
-
 \subsection{In the case of general \(X\)}
-In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
-This allowed some tricks with right-shifting.
-In the general case, the parameters \(a\) and \(b\) are not necessarily in such a helpful form.
-We will see, however, that we can change basis of \(\mathbb{C}^m\) to put them in a nice form.
 

### 2024-08-08 paper.tex
mostly finished first case of jordan form

@@
 Otherwise, we set 
-\[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k} e_{i,k + q_i}.\]
-Note that \(v_i\) is just
+\[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k}' e_{i,k + q_i}.\]
+Note that \(A^{q_i} v_i\) is just \(b'\) with row \(i\) zeroed out.
+Then, \(A^{q_i + \max_{k > i} p_k} v_i\) will have, in addition, rows \(k\) zeroed out, for all \(k > i\).
+This ensures that shifting \(A^{q_i + \max_{k > i} p_k} v_i\) right \(q_i + \max_{k > i} p_k\) times will be inverted by applying \(A\), and thus shifting left, \(q_i + \max_{k > i} p_k\) times.
+So, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_i)\), which has length \(q_i + \max_{k > i} p_k\).
+\par TODO: where did I use the fact that \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)?
+
+\subsubsection{Second case: \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\)}
 

### 2024-08-08 paper.tex
finish finding Jordan form

@@
 \subsubsection{Second case: \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\)}
+Again we list the chains in (roughly) decreasing order.
+Note that, since \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\), in particular we have \(n \leq q_{i_0}\), and \(n \leq q_i\) for all \(i \leq i_0\).
+Now, for all \(i \neq i_0\) with \(q_i \geq n\), take the chain of length \(p_i + q_i\) starting with \(e_{i,p_i + q_i}\).
+Then, take the chain starting with \(e_{i_0, \lambda_{i_0}}\), of length \(\lambda_{i_0}\).
+\par Let \(i_1 = \min\{i : n > q_i\}\).
+Let \(P = \max_{i \geq i_1} p_i\).
+Then take the chain beginning with \(f_1 - (A^{n + p} f_1 >> n + p)\), of length  \(n + P\).
+\par Finally, we handle \(i \geq i_1\).  
+(In this case \(q_i < n\).)
+If \(p_i \leq \max_{k > i} p_k\), then take the chain beginning with \(e_{i, p_i + q_i}\) of length \(p_i + q_i\).
+Otherwise, set 
+\[v_i = A^{n - q_i} f_1 - \sum_{k = 1}^{p_i} b_{i,k}' e_{i, q_i + k}.\]
+Note that \(A^{q_i} v_i\) is just \(b'\) with row \(i\) zeroed out.
+Now, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_k)\), of length \(q_i + \max_{k > i} p_k\).
+\par TODO: where did I use the fact that \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\).
 

### 2024-08-08 paper.tex
some introduction

@@
 % \maketitle
-\section{Definition of one thing}
+
+\section{Introduction}
+We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
+For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
+Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
+
+\section{Springer fibers}
 Let \(G \subseteq \GL_m(\mathbb{C})\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m(\mathbb{C})\) be its Lie algebra.
@@
 For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.
+\par We mention some results about Springer fibers, which we will use later in this paper.
+TODO: mention them.
 
@@
 
-\subsection{In the case of general \(X\)}
+\subsection{In the case that \(X\) is a Jordan block}
+This case seems harder to work with explicitly than the case that \(X\) is zero, so our strategy is to reuse
 

### 2024-08-08 paper.tex
more work on intro / setup

@@
 
-\subsection{Finding an \(\spl_2\)-triple in a simple case}
+\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
 \par Let
@@
    &   &  & 1 & 0
-   \end{pNiceArray} \in \mathfrak{sl}_{n},\]
-where there are \(n - 1\) ones.
-We will find the Slodowy slice at \(e\).
-\par As a first step, we will find an \(\spl_2\)-triple with \(e\) as its first element.
+   \end{pNiceArray} \in \mathfrak{gl}_{n},\]
+and let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
+We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
+First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).
+
+\begin{lemma}\label{simple_sl2_triple}
+    There is exactly one way to choose \(h, f \in \gl_n\) so that \((e, h, f)\) is an \(\spl_2\)-triple.
+\end{lemma}
+\begin{proof}
+
 Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
@@
 \[\sum_i h_{ii} = 0.\]
-Oops, I didn't actually need to prove that, since \(h \in \spl_n\)... it's nice to know that it's the unique solution in \(\gl_n\) though?
+Remark: this is just the statement that \(h \in \spl_n\); in other words, we will see that every choice of \(\spl_2\)-triple in \(\gl_{m + n}\) is also an \(\spl_2\)-triple in \(\spl_{m + n}\).
 This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
@@
 \end{pmatrix}.\]
+\end{proof}
 
-\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
-Now, let 
-\[E = \begin{pmatrix}
-    0 & 0 \\
-    0 & e
-\end{pmatrix} \in \spl_{m + n},\]
-with \(e\) as in the previous subsection.
-We will find \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
-Writing \(F = \begin{pmatrix}
+\begin{lemma}\label{sl2_triple}
+    There is exactly one way to choose \(H, F \in \gl_{m + n}\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
+\end{lemma}
+\begin{proof}
+Suppose we have \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
+Writing \(F =: \begin{pmatrix}
     F_{11} & F_{12} \\
@@
 \end{pmatrix}.\]
-From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in the previous subsection.
+From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in \cref{simple_sl2_triple}.
 We also see that \(H_{11} = 0\).
@@
 We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
+\end{proof}
 
-\subsection{Finding the previous Slodowy slices}
+\section{Finding the Slodowy slices with the same \(E\)}
 First we find \(\ker \ad_f\).
@@
 Define \(\pi_{m,n} : \widetilde{\mathcal{N}}_{m,n} \to \mathcal{N}_m\) by \((\mathfrak{b}, X) \mapsto X_{11}\).
-For \(Y \in \gl_m\), we call \(\pi_{m,n}^{-1}(Y)\) the \emph{n-dim-Slodowy-slice Springer fiber} at \(Y\).
+For \(Y \in \gl_m\), we call \(\pi_{m,n}^{-1}(Y)\) the \emph{Springer fiber at the \(n\)-Slodowy slice at \(Y\)}.
 
@@
 \par Now, taking the previous corolloary and the first lemma together, we see that 
-\[\mathcal{S}_{m,n}' = \left\{ \begin{pNiceArray}{ccc|cccc}
+\[\mathcal{S}_{m,n}' = \left\{\begin{pNiceArray}{ccc|cccc}
     & & & & & & \vert \\
@@
 
-\section{Definition of springer fiber at slodowy slice}
-% Explain why these are Springer fibers at Slodowy slices.
+\section{Simplifying the definition of a Springer fiber at a Slodowy slice}
 \par Let \(\mathcal{N}_m \subseteq \gl_m(\mathbb{C})\) be the subset consisting of nilpotent elements.
-For \(X \in \mathcal{N}\) and \(a, b \in \mathbb{C}^m\), let
+For \(X \in \mathcal{N}_m\) and \(a, b \in \mathbb{C}^m\), let
 \[A_{X, a, b} = \begin{pNiceArray}{ccc|ccccc}
@@
 \end{pNiceArray} \in \mathfrak{gl}_{m + n}(\mathbb{C}).\]
-
-% \par Note that \(X \mapsto A_{X, a, b}\) gives a map \(\gl_m(\mathbb{C}) \to \gl_{m + n}(\mathbb{C})\).
-Let \(\mathcal{M}\) be the variety of Borel subalgebras of \(\gl_{m + n}(\mathbb{C})\).
-Let
-\[\widetilde{\mathcal{N}} = \{(\mathfrak{m}, a, b, X) : A_{X, a, b} \in \mathfrak{m}\} \subseteq \mathcal{M} \times \mathbb{C}^m \times \mathbb{C}^m \times \mathcal{N}.\]
-Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the last coordinate.
-For \(X \in \mathcal{N}\), we call \(\pi^{-1}(X)\) the \emph{other Springer fiber at \(X\)}.
+By the definition given in the previous section, we have 
+\[\widetilde{\mathcal{N}}_{m, n} = \{(\mathfrak{b}, X) : X \in \mathfrak{b}\} \subseteq \mathcal{B}_{m + n} \times \mathcal{S}_{m,n}',\]
+and the Springer fiber at the \(n\)-Slodowy slice at a nilpotent \(X \in \gl_m\) is
+\[\pi_{m,n}^{-1}(X) = \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \in \mathcal{S}_{m, n}'\} \] 
+\[= \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{nilpotent}\}\]
+\[\cong \{(\mathfrak{b}, a, b) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{ nilpotent}\}.\]
+We will make one last simplification to this by using a correspondence between Borel subalgebras and complete flags.
+TODO: fix the next few paragraphs, they are out of context.
+\par We have \(\mathcal{M} = \{AHA^{-1} : A \in \GL_{m + n}(\mathbb{C})\}\), where \(H \subseteq \gl_{m + n}(\mathbb{C})\) is the set of upper triangular matrices.
+We say a map \(X : \gl_{m + n} \to \gl_{m + n}\) preserves a flag \(V_0 \subseteq \cdots \subseteq V_{m + n}\) if \(XV_i \subseteq V_i\) for each \(i\).
+Let \(E_0 \subseteq \cdots \subseteq E_{m + n}\) be the standard flag of \(\mathbb{C}^{m + n}\).
+Since \(H\) is the set of \(X\) which preserve \(E\),
+\[\mathcal{M} = \{\{X : \forall i. \; X(AE_i) \subseteq AE_i\} : A \in \GL_n(\mathbb{C})\}.\]
+So, for \(X \in \mathcal{N}\),
+\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\}.\]
+\par In this section we will find the irreducible components of \(\pi^{-1}(X)\).
+Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
+\par Let \(\lambda\) be the shape of \(X\), and let \((e_{ij})_{i \leq r, j \leq \lambda_i}\) be a Jordan basis for \(X\), with \(X e_{ij} = e_{i,j - 1}\).
+Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).
 
@@
 
-\section{Finding the Springer fibers of section 2}
-We have \(\mathcal{M} = \{AHA^{-1} : A \in \GL_{m + n}(\mathbb{C})\}\), where \(H \subseteq \gl_{m + n}(\mathbb{C})\) is the set of upper triangular matrices.
-We say a map \(X : \gl_{m + n} \to \gl_{m + n}\) preserves a flag \(V_0 \subseteq \cdots \subseteq V_{m + n}\) if \(XV_i \subseteq V_i\) for each \(i\).
-Let \(E_0 \subseteq \cdots \subseteq E_{m + n}\) be the standard flag of \(\mathbb{C}^{m + n}\).
-Since \(H\) is the set of \(X\) which preserve \(E\),
-\[\mathcal{M} = \{\{X : \forall i. \; X(AE_i) \subseteq AE_i\} : A \in \GL_n(\mathbb{C})\}.\]
-So, for \(X \in \mathcal{N}\),
-\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\}.\]
-\par In this section we will find the irreducible components of \(\pi^{-1}(X)\).
-Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
-\par Let \(\lambda\) be the shape of \(X\), and let \((e_{ij})_{i \leq r, j \leq \lambda_i}\) be a Jordan basis for \(X\), with \(X e_{ij} = e_{i,j - 1}\).
-Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).
-
 \subsection{When \(X\) is all zeroes}

### 2024-08-10 paper.tex
start talking about centralizer

@@
 
+\section{Finding a centralizer}
+For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
+\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
+Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
+So, we just have to find 
+\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
+We begin by finding 
+\[\{A \in \gl_m : AX = XA\}.\]
+We write the shape of \(X\) as \(\lambda = (\lambda_1, ..., \lambda_k)\), so that 
+\[X = \begin{pmatrix}
+    J_{\lambda_1} & \\
+    & \ddots \\
+    & & J_{\lambda_k}
+\end{pmatrix}.\]
+Then we write \(A\) as the block matrix
+\[A =: \begin{pmatrix}
+    A_{11} & \cdots & A_{1k}\\
+    \vdots & & \vdots\\
+    A_{k1} & \cdots & A_{kk}
+\end{pmatrix},\]
+where \(A_{ij}\) is a block of size \(\lambda_i \times \lambda_j\).
+We have 
+\[XA = \begin{pmatrix}
+    J_{\lambda_1}A_{11} & \cdots & J_{\lambda_1}A_{1k}\\
+    \vdots & & \vdots\\
+    J_{\lambda_k}A_{k1} & \cdots & J_{\lambda_k}A_{kk}
+\end{pmatrix}, \textrm{ and } AX = \begin{pmatrix}
+    A_{11} J_{\lambda_1} & \cdots & A_{1k} J_{\lambda_k}\\
+    \vdots & & \vdots\\
+    A_{k1} J_{\lambda_1} & \cdots & A_{kk} J_{\lambda_k}
+\end{pmatrix}.\]
+So, the constraint that \(XA = AX\) is simply saying that 
+\[\forall i,j. \; J_{\lambda_i} A_{ij} = A_{ij} J_{\lambda_j}.\]
+It's easy to see that left multiplication by \(J_{\lambda_i}\) is just a down-shift by one, and right multiplication by \(J_{\lambda_j}\) is a left-shift by one.
+This means that \(A_{ij}\) is constrained to be a ``lower-left-Toeplitz'' matrix; one of the form
+
 \section{A necessary condition for \(A_{X, a, b}\) to be nilpotent}

### 2024-08-10 paper.tex
more about centralizer

--- 2024-08-08 paper.tex
@@
 \usepackage{enumerate}
+\usepackage{rotating}
+
+\newcommand{\leftshift}{\mathbin{\rotatebox[origin=c]{0}{$\ll$}}}
+\newcommand{\downshift}{\mathbin{\rotatebox[origin=c]{90}{$\ll$}}}
+\newcommand{\rightshift}{\mathbin{\rotatebox[origin=c]{180}{$\ll$}}}
+\newcommand{\upshift}{\mathbin{\rotatebox[origin=c]{270}{$\ll$}}}
 
@@
 
+\section{Finding a centralizer}
+For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
+\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
+Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
+So, we just have to find 
+\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
+We begin by finding 
+\[\{A \in \gl_m : AX = XA\}.\]
+We write the shape of \(X\) as \(\lambda = (\lambda_1, ..., \lambda_k)\), so that 
+\[X = \begin{pmatrix}
+    J_{\lambda_1} & \\
+    & \ddots \\
+    & & J_{\lambda_k}
+\end{pmatrix}.\]
+Then we write \(A\) as the block matrix
+\[A =: \begin{pmatrix}
+    A_{11} & \cdots & A_{1k}\\
+    \vdots & & \vdots\\
+    A_{k1} & \cdots & A_{kk}
+\end{pmatrix},\]
+where \(A_{ij}\) is a block of size \(\lambda_i \times \lambda_j\).
+We have 
+\[XA = \begin{pmatrix}
+    J_{\lambda_1}A_{11} & \cdots & J_{\lambda_1}A_{1k}\\
+    \vdots & & \vdots\\
+    J_{\lambda_k}A_{k1} & \cdots & J_{\lambda_k}A_{kk}
+\end{pmatrix}, \textrm{ and } AX = \begin{pmatrix}
+    A_{11} J_{\lambda_1} & \cdots & A_{1k} J_{\lambda_k}\\
+    \vdots & & \vdots\\
+    A_{k1} J_{\lambda_1} & \cdots & A_{kk} J_{\lambda_k}
+\end{pmatrix}.\]
+So, the constraint that \(XA = AX\) is simply saying that 
+\[\forall i,j. \; J_{\lambda_i} A_{ij} = A_{ij} J_{\lambda_j}.\]
+It's easy to see that left multiplication by \(J_{\lambda_i}\) is just a down-shift by one, and right multiplication by \(J_{\lambda_j}\) is a left-shift by one.
+This means that \(A_{ij}\) is constrained to be a ``lower-left-Toeplitz'' matrix.
+A Toeplitz matrix is one which is constant along diagonal bands: \(\forall ijk. \; x_{ij} = x_{i + k,j + k}\).
+A lower-left-Toeplitz matrix is one which is all zeroes except for the bottom-left corner; that is, the bands start in the bottom-left corner, and continue until hitting the band which includes the lower-right corner or the band which includes the upper-left corner (whichever comes first).
+In other words, an \(n \times m\) lower-left-Toeplitz matrix is one which satisfies \(x_{ij} = 0\) for all \(i,j\) with \(i < j\) and all \(i,j\) with \(i - j < m - n\).
+In yet other words, a matrix is lower-left-Toeplitz if it is Toeplitz, satisfies \(x_{1j} = 0\) for \(j \neq 1\), and satisfies \(x_{in} = 0\) for \(i \neq m\).
+Anyway, it is easy to see that the lower-left-Toeplitz matrices are exactly those matrices \(A\) such that left-shifting \(A\) by one has the same result as down-shifting by one.
+\par So, we have found the set 
+\[C_1 := \{A \in \gl_m : AX = XA\}.\]
+It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
+\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
+\[A_{ij} = \begin{pmatrix}
+    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
+\end{pmatrix}.\]
+Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
+\[v_{ij} = \begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
+Now we determine which matrices of this form satisfy \(aA = a\).
+For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
+(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
+\par In the case that \(a = 0\), clearly every \(A\) works.
+Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
+Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
+That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
+This just requires that for each \(j\), we must have 
+\[v_{ij} = \begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
+So, we have now found the set 
+\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
+It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
+\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
+\par Now we are only left with finding the matrices \(A \in C_2\) satisfying \(Ab = b\).
+This just means finding the matrices \(A\), of the form given above, which satisfy \(Ab = 0\).
+We may restate this as the condition that for every \(i\),
+\[\begin{pmatrix}
+    A_{i1} & \cdots & A_{in}
+\end{pmatrix}b = 0.\]
+Taking the transpose, 
+\[b^\top \begin{pmatrix}
+    A_{i1}^\top\\
+    \vdots\\
+    A_{in}^\top
+\end{pmatrix} = 0.\]
+Now, the rightmost column of \(A_{ij}^\top\) is \(v_{ij}\) upside-down (rows reversed).
+Write \(u_{ij}\) to refer to \(v_{ij}\) upside-down, and \(u_{ij}'\) to refer to \(v_{ij}'\) upside-down.
+Then the second-rightmost column is \(u_{ij} \upshift 1\), and so on until the first column is \(u_{ij} \upshift [\lambda_i - 1]\).
+So, we can reformulate this condition by requiring that for all \(l\),
+\[b^\top \begin{pmatrix}
+    u_{i1} \upshift l\\
+    \vdots\\
+    u_{in} \upshift l
+\end{pmatrix} = 0.\]
+Writing
+\[b = \begin{pmatrix}
+    b_1\\
+    \vdots\\
+    b_k
+\end{pmatrix},\]
+clearly this is equivalent to requiring that for all \(l\),
+\[\begin{pmatrix}
+    b_1^\top \rightshift l & \cdots & b_k^\top \rightshift l
+\end{pmatrix} \begin{pmatrix}
+    u_{i1}\\
+    \vdots\\
+    u_{ik}
+\end{pmatrix} = 0.\]
+Then writing \(b_j = \begin{pmatrix}
+    b_j'\\
+    \vdots
+\end{pmatrix}\), where \(b_j'\) has the same dimension as \(u_{ij}\), we can rewrite this constraint as 
+\[\begin{pmatrix}
+    b_1'^\top \rightshift l & \cdots & b_k'^\top \rightshift l
+\end{pmatrix} \begin{pmatrix}
+    u_{i1}'\\
+    \vdots\\
+    u_{ik}'
+\end{pmatrix} = 0.\]
+Finally, requiring the above equation for all \(l\) is the same thing as requiring
+\[\begin{pmatrix}
+    b_1'^\top \rightshift 0 & \cdots & b_k'^\top \rightshift 0\\
+    \vdots &  & \vdots \\
+    b_1'^\top \rightshift [\lambda_i - 1] & \cdots & b_k'^\top \rightshift [\lambda_i - 1]
+\end{pmatrix} \begin{pmatrix}
+    u_{i1}'\\
+    \vdots\\
+    u_{ik}'
+\end{pmatrix} = 0.\]
+This is the most that we will simplify the constraint.
+Recall that the \(v_{ij}'\) can be chosen arbitrarily, so the \(u_{ij}'\) can be chosen arbitrarily as well.
+That is, the set \(C_3 := \{A \in \gl_m : AX = XA, aA = a, Ab = b\}\) is the set of \(I + A\) for any \(A\) that can be recovered from \(u_{ij}'\) meeting the above condition.
+\par Now we find the dimension of \(C_3\).
+Since the \(u_{ij}'\) can be chosen arbitrarily, apart from the condition above, we just need to add up their dimensions and subtract the rank of the matrix constructed of the \(b\)'s.
+
 \section{A necessary condition for \(A_{X, a, b}\) to be nilpotent}

### 2024-08-10 paper.tex
dimension of centralizer

@@
 Since the \(u_{ij}'\) can be chosen arbitrarily, apart from the condition above, we just need to add up their dimensions and subtract the rank of the matrix constructed of the \(b\)'s.
+The dimension of \(u'_{ij}\) is \(\min(\lambda_i, \lambda_j)\) in the case that \(i \neq i_0\), and \(\min(\lambda_i - j_0, \lambda_j)\) when \(i = i_0\).
+Write \(d_{ij}\) for this dimension.
+For each \(i\), let \(q_i\) be the length of the longest prefix of \(b_i\) which consists of zeroes.
+\par Fix an \(i\).
+I claim the rank of the matrix of \(b\)'s is \(h := \max_j [d_{ij} - q_j]\), or zero if this quantity is always negative.
+First, to see that the rank is at least this big, note that for any \(j \in \argmax_j [d_{ij} - q_j]\), the rank of the \(j\)th ``column block'' of the matrix of \(b\)'s is equal to \(h\).
+Then, to see that the rank is at most this big, note that every row after the first \(h\) rows is just zeroes.
+So, the total degrees of freedom for the \(u_{ij}\) is 
+\[\sum_j d_{ij} - \max(0, \max_j [d_{ij} - q_j]).\]
+Then summing over all the \(i\), we get the dimension of \(C_3\):
+\[\sum_i \sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j]).\]
 

### 2024-08-10 paper.tex
more on dimension

@@
 For each \(i\), let \(q_i\) be the length of the longest prefix of \(b_i\) which consists of zeroes.
+Then if \(A_{X, a, b}\) is nilpotent, we must have \(q_{i_0} \geq j_0\).
+So we may as well set \(q_{i_0} := q_{i_0} - j_0\).
 \par Fix an \(i\).
@@
 Then summing over all the \(i\), we get the dimension of \(C_3\):
-\[\sum_i \sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j]).\]
+\[\sum_i \left[\sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j])\right] = \sum_{ij} d_{ij} - \sum_i \max(0, \max_j[d_{ij} - q_j]).\]
+When \(i \neq i_0\), then \(d_{ii} = \lambda_i \geq q_i\), and therefore \(\max(0, \max_j [d_{ij} - q_j]) = \max_j [d_{ij} - q_j]\).
+When \(i = i_0\), then \(d_{ii} = \lambda_i - j_0 \geq q_{i_0}\).
+So, we can simplify the above expression:
+\[\sum_{ij} d_{ij} - \sum_i \max_j [d_{ij} - q_j].\]
+Note that \(\max_j [d_{ij} - q_j] = \max_j [\min(p_i + q_i, p_j + q_j) - q_j]\).
+This thing being maximized equals \(\min(p_i + q_i - q_j, p_j)\).
+It would be really helpful if I could simplify this to \(p_j\) or something.
+I don't think so, though.
 

### 2024-08-11 paper.tex
started showing correctness of jordan basis by arguing that chains are linearly independent. seems painful, so I will instead show correctness by arguing that the span is big enough

@@
 So, we take the chain of length \(r + n + P\) beginning with \(v\).
-How do we know this is linearly independent from what came before?
-Something to do with the condition on \(n\)...
+\par Now, we want to show that this chain is linearly independent from the chains we have already listed.
+Because \(A^{r + n + P} e_{i_0, \lambda_{i_0}}\) is in the span of the chains we have already listed, it suffices to show that \(A^k e_{i_0, \lambda_{i_0}}\) is linearly independent of the previous chains, for all \(k < r + n + P\).
+Indeed, by the definition of \(P\), we have that \(A^k e_{i_0, \lambda_{i_0}}\) has a nonzero \(e_{ij}\)-component, for some \(i\) with \(q_i < n + r\); and the chains we have listed previously all have \(e_{ij}\)-component equal to zero for \(i\) with \(q_i < n + r\).
 \par Now, we handle the \(i\) with \(q_i < n + r\).
-If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
-Otherwise, we set 
+We take as an inductive hypothesis that for all \(i' < i\) and all \(j\), we have \(e_{i'j}\) in the span of the chains we have already listed.
+\par If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
+To see that this is linearly independent of what came before... TODO.
+\par Otherwise, we set 
 \[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k}' e_{i,k + q_i}.\]

### 2024-08-11 paper.tex
finish showing that span of Jordan basis is big enough

@@
 So, we take the chain of length \(r + n + P\) beginning with \(v\).
-\par Now, we want to show that this chain is linearly independent from the chains we have already listed.
-Because \(A^{r + n + P} e_{i_0, \lambda_{i_0}}\) is in the span of the chains we have already listed, it suffices to show that \(A^k e_{i_0, \lambda_{i_0}}\) is linearly independent of the previous chains, for all \(k < r + n + P\).
-Indeed, by the definition of \(P\), we have that \(A^k e_{i_0, \lambda_{i_0}}\) has a nonzero \(e_{ij}\)-component, for some \(i\) with \(q_i < n + r\); and the chains we have listed previously all have \(e_{ij}\)-component equal to zero for \(i\) with \(q_i < n + r\).
+\par Now, it is clear that \(e_{i_0, p_{i_0} + q_{i_0} + i}\) is in the span of the chains we have listed so far for each \(i \geq 1\).
+It is also clear that \(b' \leftshift k\) is in the span, for each \(k \geq 0\).
 \par Now, we handle the \(i\) with \(q_i < n + r\).
@@
 \par If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
-To see that this is linearly independent of what came before... TODO.
+Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).
 \par Otherwise, we set 
@@
 So, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_i)\), which has length \(q_i + \max_{k > i} p_k\).
-\par TODO: where did I use the fact that \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)?
+\par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.
+Since \(A^{q_i + \max_{k > i} p_k} v_i\) has rows \(k\) zeroed out for \(k \geq i\), our inductive hypothesis tells us that \(A^{q_i + \max_{k > i} p_k} v_i \rightshift q_i + \max_{k > i} p_k\) is in the span of the chains already listed.
+So it suffices to show that the closure of \(\langle v_i \rangle\) under action by \(A\) contains the span of \(e_{ij}\).
+And \(A^{n + r - q_i} e_{i_0, \lambda_{i_0}}\) is also in the span of chains already listed, so it suffices to show that the closure of \(\langle \sum_k b'_{ik} e_{i,k + q_i}\rangle \) under action by \(A\) contains \(\langle e_{ij}\rangle\).
+And this just follows from the fact that \(b'_{i,p_i}\) is nonzero.
+\par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
+TODO: do this.
 

### 2024-08-16 paper.tex
dimension
delete a bunch of stuff that I don't need anymore!

@@
 where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
-\par Now we are only left with finding the matrices \(A \in C_2\) satisfying \(Ab = b\).
-This just means finding the matrices \(A\), of the form given above, which satisfy \(Ab = 0\).
-We may restate this as the condition that for every \(i\),
-\[\begin{pmatrix}
-    A_{i1} & \cdots & A_{in}
-\end{pmatrix}b = 0.\]
-Taking the transpose, 
-\[b^\top \begin{pmatrix}
-    A_{i1}^\top\\
-    \vdots\\
-    A_{in}^\top
-\end{pmatrix} = 0.\]
-Now, the rightmost column of \(A_{ij}^\top\) is \(v_{ij}\) upside-down (rows reversed).
-Write \(u_{ij}\) to refer to \(v_{ij}\) upside-down, and \(u_{ij}'\) to refer to \(v_{ij}'\) upside-down.
-Then the second-rightmost column is \(u_{ij} \upshift 1\), and so on until the first column is \(u_{ij} \upshift [\lambda_i - 1]\).
-So, we can reformulate this condition by requiring that for all \(l\),
-\[b^\top \begin{pmatrix}
-    u_{i1} \upshift l\\
-    \vdots\\
-    u_{in} \upshift l
-\end{pmatrix} = 0.\]
-Writing
-\[b = \begin{pmatrix}
-    b_1\\
-    \vdots\\
-    b_k
-\end{pmatrix},\]
-clearly this is equivalent to requiring that for all \(l\),
-\[\begin{pmatrix}
-    b_1^\top \rightshift l & \cdots & b_k^\top \rightshift l
-\end{pmatrix} \begin{pmatrix}
-    u_{i1}\\
-    \vdots\\
-    u_{ik}
-\end{pmatrix} = 0.\]
-Then writing \(b_j = \begin{pmatrix}
-    b_j'\\
-    \vdots
-\end{pmatrix}\), where \(b_j'\) has the same dimension as \(u_{ij}\), we can rewrite this constraint as 
-\[\begin{pmatrix}
-    b_1'^\top \rightshift l & \cdots & b_k'^\top \rightshift l
-\end{pmatrix} \begin{pmatrix}
-    u_{i1}'\\
-    \vdots\\
-    u_{ik}'
-\end{pmatrix} = 0.\]
-Finally, requiring the above equation for all \(l\) is the same thing as requiring
-\[\begin{pmatrix}
-    b_1'^\top \rightshift 0 & \cdots & b_k'^\top \rightshift 0\\
-    \vdots &  & \vdots \\
-    b_1'^\top \rightshift [\lambda_i - 1] & \cdots & b_k'^\top \rightshift [\lambda_i - 1]
-\end{pmatrix} \begin{pmatrix}
-    u_{i1}'\\
-    \vdots\\
-    u_{ik}'
-\end{pmatrix} = 0.\]
-This is the most that we will simplify the constraint.
-Recall that the \(v_{ij}'\) can be chosen arbitrarily, so the \(u_{ij}'\) can be chosen arbitrarily as well.
-That is, the set \(C_3 := \{A \in \gl_m : AX = XA, aA = a, Ab = b\}\) is the set of \(I + A\) for any \(A\) that can be recovered from \(u_{ij}'\) meeting the above condition.
-\par Now we find the dimension of \(C_3\).
-Since the \(u_{ij}'\) can be chosen arbitrarily, apart from the condition above, we just need to add up their dimensions and subtract the rank of the matrix constructed of the \(b\)'s.
-The dimension of \(u'_{ij}\) is \(\min(\lambda_i, \lambda_j)\) in the case that \(i \neq i_0\), and \(\min(\lambda_i - j_0, \lambda_j)\) when \(i = i_0\).
-Write \(d_{ij}\) for this dimension.
-For each \(i\), let \(q_i\) be the length of the longest prefix of \(b_i\) which consists of zeroes.
-Then if \(A_{X, a, b}\) is nilpotent, we must have \(q_{i_0} \geq j_0\).
-So we may as well set \(q_{i_0} := q_{i_0} - j_0\).
-\par Fix an \(i\).
-I claim the rank of the matrix of \(b\)'s is \(h := \max_j [d_{ij} - q_j]\), or zero if this quantity is always negative.
-First, to see that the rank is at least this big, note that for any \(j \in \argmax_j [d_{ij} - q_j]\), the rank of the \(j\)th ``column block'' of the matrix of \(b\)'s is equal to \(h\).
-Then, to see that the rank is at most this big, note that every row after the first \(h\) rows is just zeroes.
-So, the total degrees of freedom for the \(u_{ij}\) is 
-\[\sum_j d_{ij} - \max(0, \max_j [d_{ij} - q_j]).\]
-Then summing over all the \(i\), we get the dimension of \(C_3\):
-\[\sum_i \left[\sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j])\right] = \sum_{ij} d_{ij} - \sum_i \max(0, \max_j[d_{ij} - q_j]).\]
-When \(i \neq i_0\), then \(d_{ii} = \lambda_i \geq q_i\), and therefore \(\max(0, \max_j [d_{ij} - q_j]) = \max_j [d_{ij} - q_j]\).
-When \(i = i_0\), then \(d_{ii} = \lambda_i - j_0 \geq q_{i_0}\).
-So, we can simplify the above expression:
-\[\sum_{ij} d_{ij} - \sum_i \max_j [d_{ij} - q_j].\]
-Note that \(\max_j [d_{ij} - q_j] = \max_j [\min(p_i + q_i, p_j + q_j) - q_j]\).
-This thing being maximized equals \(\min(p_i + q_i - q_j, p_j)\).
-It would be really helpful if I could simplify this to \(p_j\) or something.
-I don't think so, though.
-
-\section{A necessary condition for \(A_{X, a, b}\) to be nilpotent}
-Suppose \(A := A_{X, a, b}\) is nilpotent.
-Define the \emph{height} of a vector \(v \in \mathbb{C}^{m + n}\) as the smallest \(k \geq 0\) such that \(A_{X, a, b}^k v = 0\).
-Clearly, for \(i \leq j\), we have that the height of \(f_i\) is geq the height of \(f_j\).
-Thus, for each \(k \geq 0\), we must have \(A_{X, a, b}^k f_n \in \langle e_{ij} \rangle_{ij}\).
-We have \(Af_n = \sum_{ij} b_{ij} e_{ij}\).
-Then \(A^2 f_n = \sum_{ij} b_{ij} (e_{i, j - 1} + a_{ij} f_1)\), so we must have \(\sum_{ij} b_{ij} a_{ij} = 0\).
-Similarly, since \(A^3 f_n \in \langle e_{ij}\rangle\), we see that \(\sum_{ij} b_{ij} a_{i, j - 1} = 0\).
-Continuing in this way, we obtain that for all \(k \geq 0\),
-\begin{equation}\label{ab_nilp}\sum_{ij} b_{ij} a_{i,j - k} = 0.\end{equation}
-In fact this is in fact a sufficient condition for \(A_{X, a, b}\) to be nilpotent, as can be seen from the characteristic polynomial of \(A_{X, a, b}\).
-However, we will not do this calculation here, instead just showing that it is sufficient by giving a Jordan basis.
 
 \section{A Jordan basis for \(A_{X, a, b}\)}
-For illustration, we will begin with the case that \(X\) is a single Jordan block.
-Then we will move to the general case.
-
-\subsection{When \(X\) is a Jordan block}
-Suppose \(X\) is a single Jordan block of size \(m\).
-In this case we just write the basis of \(\mathbb{C}^m\) as \(e_1, ..., e_m\), and the above condition on \(a\) and \(b\) simply becomes
-\begin{equation}
-    \forall k \geq 0. \; \sum_{i = k + 1}^m b_i a_{i - k} = 0.
-\end{equation}
-This condition can be simplified even more.
-\begin{lemma}
-    The condition (1) holds iff there exist nonnegative \(m_1, m_2, m_3\), \(a_1, ..., a_{m_3}\), and \(b_1, ..., b_{m_3}\) satisfying the following conditions.
-    \begin{itemize}
-        \item \(m = m_1 + m_2 + m_3\)
-        \item \(a = (0, 0, ..., 0, a_1, ..., a_{m_3})\)
-        \item \(b = (b_1, ..., b_{m_1}, 0, 0, ..., 0)\)
-        \item If \(m_1 \neq 0\), then \(a_{m_1} \neq 0\)
-        \item If \(m_3 \neq 0\), then \(b_1 \neq 0\)
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    If \(a\) and \(b\) are of this form, then for every \(k \geq 0\) we have \(b_i a_{i - k} = 0\), so clearly the condition holds.
-    \par Now suppose (1) holds.
-    If \(a\) or \(b\) is zero, this is trivial.
-    Otherwise, let \(m_1 = \max\{i : a_i \neq 0\}\), and let \(m_3 = \min\{i : b_i \neq 0\}\).
-    We just need to show that \(m_1 < m_3\).
-    For contradiction, suppose \(m_1 - m_3\) is nonnegative.
-    Then by (1), \(0 = \sum_i b_i a_{i - (m_1 - m_3)} = b_1 a_{m_1}\), contradicting that \(b_1\) and \(a_{m_1}\) are nonzero.
-\end{proof}
 
@@
 \subsection{The general case}
-In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
-This allowed some tricks with right-shifting.
-In the general case, the parameters \(a\) and \(b\) are not necessarily in such a helpful form.
-We will see, however, that we can change basis of \(\mathbb{C}^m\) to put them in a nice form.
-\par Recall our nilpotent operator \(A_{X, a, b}\) on \(\mathbb{C}^m \times \mathbb{C}^n\).
-We can define a map \(\mathbb{C}^m \to \mathbb{C}\) by \(x \mapsto x \cdot a\).
-Then, by the previous lemma, we can choose a Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\) so that at most one \((i, j)\) has \(f(e_{ij}) \neq 0\).
-This implies that there are some \(P, k, b'\) such that \(PA_{X, a, b}P^{-1} = A_{X, 1_k, b'}\).
-So, without loss of generality, we may consider this case, where \(a = 1_k\).
-\par Write our basis of \(\mathbb{C}^m\) as \(e_{ij}\) and our basis of \(\mathbb{C}^n\) as \(f_j\).
-Let \(i_0, r\) be such that \(a = e_{i_0, \lambda_{i_0} - r + 1}\).
-Let \(b' = A^{n + r} e_{i_0, \lambda_{i_0}} = b + e_{i_0, \lambda_{i_0} - r - n}\).
-Let \(b_{ij}'\) be the projection of \(b'\) onto \(e_{ij}\).
-For each \(i\), let \(p_i = \max\{j : b_{ij}' \neq 0\}\).
-Then for each \(i \neq i_0\), let \(q_i = \lambda_i - p_i\).  Let \(q_{i_0} = \lambda_{i_0} - r - p_{i_0}\).
+Let \(X\) be nilpotent in Jordan form, and let \(a = \mathbbm{1}_{w,1}\), and let \(b\) be such that \(\forall j. \; b_{wj} = 0\).
+We describe a Jordan basis for \(A_{X, a, b}\).
+
+\par Let \(\mu\) be the result of removing the row \(w\) from \(\lambda\).
+For each row \(i\), let \(p_i = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
+Then set \(q_i = \lambda_i - p_i\).  Let \(q_{i_0} = \lambda_{i_0} - r - p_{i_0}\).
 Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
 Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that.
-\par We have two cases, which will closely resemble the cases we had when \(X\) was a single Jordan block.
-\subsubsection{First case: \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)}
-We list the chains in (roughly) decreasing order.
+We list the chains in (roughly) order of decreasing length.
 First, for each \(i\) such that \(q_i \geq n + r\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
@@
 \par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
-TODO: do this.
-
-\subsubsection{Second case: \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\)}
-Again we list the chains in (roughly) decreasing order.
-Note that, since \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\), in particular we have \(n \leq q_{i_0}\), and \(n \leq q_i\) for all \(i \leq i_0\).
-Now, for all \(i \neq i_0\) with \(q_i \geq n\), take the chain of length \(p_i + q_i\) starting with \(e_{i,p_i + q_i}\).
-Then, take the chain starting with \(e_{i_0, \lambda_{i_0}}\), of length \(\lambda_{i_0}\).
-\par Let \(i_1 = \min\{i : n > q_i\}\).
-Let \(P = \max_{i \geq i_1} p_i\).
-Then take the chain beginning with \(f_1 - (A^{n + p} f_1 >> n + p)\), of length  \(n + P\).
-\par Finally, we handle \(i \geq i_1\).  
-(In this case \(q_i < n\).)
-If \(p_i \leq \max_{k > i} p_k\), then take the chain beginning with \(e_{i, p_i + q_i}\) of length \(p_i + q_i\).
-Otherwise, set 
-\[v_i = A^{n - q_i} f_1 - \sum_{k = 1}^{p_i} b_{i,k}' e_{i, q_i + k}.\]
-Note that \(A^{q_i} v_i\) is just \(b'\) with row \(i\) zeroed out.
-Now, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_k)\), of length \(q_i + \max_{k > i} p_k\).
-\par TODO: where did I use the fact that \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\).
+Indeed, the sum of the lengths is
+\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} \begin{cases}
+    p_i + q_i, & p_i \leq \max_{k > i} p_k \\
+    q_i + \max_{k > i} p_i, & p_i > \max_{k > i} p_k
+\end{cases} = \]
+\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)).\]
+Let \(i_1 < \cdots < i_s\) be the `peaks': that is, the set \(I_1 = \{i : q_i < n + r \land p_i > \max_{k > i} p_k\}\).
+(As I should've mentioned before, we take the max of the empty set to be zero.)
+Let \(I_2 = \{i : q_i < n + r\} \setminus I_1\).
+Then 
+\[\sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)) = \sum_{i \in I_2} (p_i + q_i) + \sum_{k = 1}^s (q_{i_k} + p_{i_{k + 1}}).\]
+Clearly then, the whole sum is \(m + n\).
 

### 2024-08-16 paper.tex
get started

@@
 So, for \(X \in \mathcal{N}\),
-\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\}.\]
-\par In this section we will find the irreducible components of \(\pi^{-1}(X)\).
-Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
-\par Let \(\lambda\) be the shape of \(X\), and let \((e_{ij})_{i \leq r, j \leq \lambda_i}\) be a Jordan basis for \(X\), with \(X e_{ij} = e_{i,j - 1}\).
+\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
+
+\section{Finding the Springer fiber at a Slodowy slice}
+\par Fix any \(X \in \mathcal{N}\).
+In this section we find the irreducible components of
+\[\pi^{-1}(X) \cong V := \{(U, a, b) : \forall i. \; A_{X, a, b} U_{i + 1} \subseteq U_i\}.\]
+
+\begin{lemma}
+    \(V = V_0 \cup \bigcup_{w, r} V_{w,r}\), where 
+    \[V_0 = \{(U, 0, b)\} \subseteq V,\]
+    and
+    \[V_{w,r} = \{(U, a, b) : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \} \subseteq V.\]
+\end{lemma}
+\begin{proof}
+    TODO
+\end{proof}
+Now, we will find the irreducible components of \(V_0\) and the \(V_{w,r}\).
+These will all happen to be equidimensional, so we will see that their closures in \(V\) are the irreducible components of \(V\).
+\par We begin with \(V_0\), which will be easy.
+
+% Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
 Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).

### 2024-08-16 paper.tex
more

@@
 \par Fix any \(X \in \mathcal{N}\).
-In this section we find the irreducible components of
+Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be a Jordan basis for \(X\).
+For convenience we define \(e_{i0} := 0\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
+\par In this section we find the irreducible components of
 \[\pi^{-1}(X) \cong V := \{(U, a, b) : \forall i. \; A_{X, a, b} U_{i + 1} \subseteq U_i\}.\]
+\par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
+\[V_{w,r} := \{(U, a, b) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \}.\]
 
 \begin{lemma}
-    \(V = V_0 \cup \bigcup_{w, r} V_{w,r}\), where 
-    \[V_0 = \{(U, 0, b)\} \subseteq V,\]
-    and
-    \[V_{w,r} = \{(U, a, b) : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \} \subseteq V.\]
+    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
+    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
+    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
 \end{lemma}
@@
 \end{proof}
-Now, we will find the irreducible components of \(V_0\) and the \(V_{w,r}\).
-These will all happen to be equidimensional, so we will see that their closures in \(V\) are the irreducible components of \(V\).
-\par We begin with \(V_0\), which will be easy.
+Now, fix any \(w\) and \(r\).
+We will find the irreducible components of \(V_{w,r}\).
+These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
+\par Let 
+\[G := \{A \in \GL_m : A^{-1} X A = X\},\]
+and 
+\[G_{wr} := \{A \in \GL_m : \forall b. \exists b'. (A^{-1}, I_n) A_{X, e_{wr}, b} (A, I_n) = A_{X, e_{wr}, b'}\}.\]
+If you write out the condition \(A_{X, e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\), it is plain to see that 
+\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
+\par Now, define 
+\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
+Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\), defined by
+\[((U, e_{wr}, b), A) \mapsto (AU, e_{wr}A, Ab)\]
 

### 2024-08-16 paper.tex
more

@@
 \par Fix any \(X \in \mathcal{N}\).
+As we have fixed \(X\), we now write \(A_{a, b} := A_{X, a, b}\).
 Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be a Jordan basis for \(X\).
@@
 \par In this section we find the irreducible components of
-\[\pi^{-1}(X) \cong V := \{(U, a, b) : \forall i. \; A_{X, a, b} U_{i + 1} \subseteq U_i\}.\]
+\[\pi^{-1}(X) \cong V := \{(A_{a, b}, U) : \forall i. \; A_{a, b} U_{i + 1} \subseteq U_i\}.\]
 \par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
-\[V_{w,r} := \{(U, a, b) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{X, a, b} (P, I_n) = A_{X, e_{wr}, b'} \}.\]
+\[V_{w,r} := \{(A_{a, b}, U) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'} \}.\]
 
@@
 \par Let 
-\[G := \{A \in \GL_m : A^{-1} X A = X\},\]
+\[G := \{P \in \GL_m : P^{-1} X P = X\},\]
 and
-\[G_{wr} := \{A \in \GL_m : \forall b. \exists b'. (A^{-1}, I_n) A_{X, e_{wr}, b} (A, I_n) = A_{X, e_{wr}, b'}\}.\]
-If you write out the condition \(A_{X, e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\), it is plain to see that 
+\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
+If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 
 \[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
@@
 \[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
-Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\), defined by
-\[((U, e_{wr}, b), A) \mapsto (AU, e_{wr}A, Ab)\]
+Let \(G\) act on \(V_{wr}\) by
+\[P \cdot (A_{e_{wr},b}, U) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)U) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) U).\]
+\par Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\) defined by
+\[(x, P) \mapsto P \cdot x.\]
+By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
+Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
+\begin{lemma}
+    The map \(\varphi\) is a topological quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
+\end{lemma}
+\begin{proof}
+    TODO.
+    See \url{http://www-fourier.ujf-grenoble.fr/~mbrion/notes_luminy.pdf}, definition 1.18.
+\end{proof}
+Now we only have to find the irreducible components of \(U_{wr} \times G\)
+
+\begin{lemma}
+    Let \(p : X \to Y\) be a topological quotient.
+    Then the irreducible components of \(Y\) are the images of those of \(X\).
+\end{lemma}
+\begin{proof}
+    Let \(C_i\) be the irreducible components of \(X\).
+\end{proof}
 

### 2024-08-17 paper.tex
more

@@
 \begin{lemma}
-    The map \(\varphi\) is a topological quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
+    As an algebraic variety, \(G\) is irreducible.
 \end{lemma}
 \begin{proof}
-    TODO.
-    See \url{http://www-fourier.ujf-grenoble.fr/~mbrion/notes_luminy.pdf}, definition 1.18.
+    not sure why at the moment
 \end{proof}
-Now we only have to find the irreducible components of \(U_{wr} \times G\)
-
 \begin{lemma}
-    Let \(p : X \to Y\) be a topological quotient.
-    Then the irreducible components of \(Y\) are the images of those of \(X\).
+    % The map \(\varphi\) is a geometric quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
+    The map \(\varphi\) is some sort of quotient by the action of \(G_{wr}\).
+    % The map \(X \mapsto \overline{\varphi(X \times G)}\) is a bijection from the irreducible components of \(U_{wr}\) to the irreducible components of \(V_{wr}\).
 \end{lemma}
 \begin{proof}
-    Let \(C_i\) be the irreducible components of \(X\).
+    What kind?
+    % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
+    % Let \(X_1, ..., X_k\) be the irreducible components of \(U_{wr}\).
+    % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
+    % And if we take \(x \in X_i \setminus \bigcup_{j \neq i} X_j\), it is clear (since \(G\) acts faithfully on itself) that \(\varphi(x, I_m)\)
+    % All that remains is to show that \(X_i \notin \bigcup_{j \neq i} \overline{\varphi(X_i \times G)}\).
+    % Indeed, 
 \end{proof}
+Our strategy is to find the irreducible components \(X \subseteq U_{wr}\), and we will then argue that the irreducible components of \(V_{wr}\) are of the form \(\varphi(X \times G)\).
+So, we will now find the irreducible components of \(U_{wr}\).
 

### 2024-08-17 paper.tex
remark about required type of quotient
m

@@
     What kind?
+    All I need is something that allows me to deduce the dimension of the quotient!
     % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
@@
 So, we will now find the irreducible components of \(U_{wr}\).
+\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
+(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
+\begin{theorem}
+    (Needs citation!)
+    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
+    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
+\end{theorem}
+Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
+We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
+We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
 

### 2024-08-17 paper.tex
m

@@
 We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
+So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
+Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
+I think this explanation of intuition is important, so I should try to make it better.
+\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
+Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
+So, we will change basis to make \(r = 0\).
+Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+Let \(X'\) be in Jordan normal form with shape \(\lambda'\).
+Let \(U_{wr}' = \{(A_{X', 0, b}, U) : \forall i. A_{X', 0, b} U_{i + 1} \subseteq U_i\}\).
+Let \(e_{ij}'\) be a Jordan basis for \(X'\).
+Let \(f_1, ..., f_n\) be a Jordan basis for the restriction of \(A_{X, 0, b}\) to \(\mathbb{}\)...
+Set \(m' := m - r\), and \(n' := n + r\).
+Let \(f_1', ..., f_{n'}'\) blah.
+Define the linear map \(Q_{wr} : \mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) by:
+\begin{itemize}
+    \item For \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\)
+    \item For \(j \leq \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\)
+    \item If \(r \neq 0\), then \(e_{w,\lambda_w} \mapsto f_1'\), and blah.
+\end{itemize}
+
+We begin by choosing a new basis to simplify things by setting \(a = 0\) (that is, we will work with the matrices of the form \(A_{X',0,b'}\)).
+Here is the new basis.
+For \(i \neq w\), take the chain beginning with \(e_{i,\lambda_i}\).
+Then take the chain beginning with \(e_{w,r - 1}\).
 

### 2024-08-17 paper.tex
m

@@
 
-\section{Finding the Springer fiber at a Slodowy slice}
+\section{Strategy and setup for finding the irreducible components of a Springer fiber at a Slodowy slice}
 \par Fix any \(X \in \mathcal{N}\).
@@
 Let \(f_1', ..., f_{n'}'\) blah.
-Define the linear map \(Q_{wr} : \mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) by:
+Define the linear map \(Q_{wr} : \mathbb{C}^{m' + n'} \to \mathbb{C}^{m + n}\) by:
 \begin{itemize}
-    \item For \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\)
-    \item For \(j \leq \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\)
-    \item If \(r \neq 0\), then \(e_{w,\lambda_w} \mapsto f_1'\), and blah.
+    \item For all \(i\), \(e_{ij}' \mapsto e_{ij}\).
+    \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,(\lambda_w - r) + j}\).
+    \item For \(j = 1, ..., n\), \(f_j' \mapsto f_j + e_{w, (\lambda_w - r) - n + j}\).
 \end{itemize}
+% The inverse map \(Q_{wr}^{-1} : \mathbb{C}^{m + n} \to \mathbb{C}^{m' + n'}\) is
+% \begin{itemize}
+%     \item For all \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\).
+%     \item For \(j = 1, ..., \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\).
+%     \item For \(j = 1, ..., r\), \(e_{wj} \mapsto f'_{n + j}\).
+%     \item For \(j = 1, ..., n\), \(f_j \mapsto f'_j - e_{w,\lambda_w - n + r}\)
+% \end{itemize}
+Observe that conjugation by \(Q_{wr}\) maps \(U_{wr}\) to \(U'_{wr}\), and conjugation by \(Q_{wr}^{-1}\) maps \(U'_{wr}\) to \(U_{wr}\).
+We conclude that \(U_{wr} \cong U_{wr}'\); so to find the irreducible components of \(U_{wr}\) we just need to find the irreducible components of \(U_{wr}'\).
+To clear the context, which is rather cluttered by now, and to avoid writing primes everywhere, we move to a new section.
 
-We begin by choosing a new basis to simplify things by setting \(a = 0\) (that is, we will work with the matrices of the form \(A_{X',0,b'}\)).
-Here is the new basis.
-For \(i \neq w\), take the chain beginning with \(e_{i,\lambda_i}\).
-Then take the chain beginning with \(e_{w,r - 1}\).
+\section{Finding the irreducible components of \(U\)}
+Let \(X\) be nilpotent of shape \(\lambda\), etc.
+Start fresh finding irreducible components of \(U_{w0}\).
 
-% Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
-Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).
+\section{Finding the irreducible components of a springer fiber at a slodowy slice}
+Apply things from the previous two sections, and conclude.
 

### 2024-08-17 paper.tex
fix action, reason about fibers

@@
 By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
-Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
+Then, letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
 \begin{lemma}
@@
 \begin{proof}
-    What kind?
-    All I need is something that allows me to deduce the dimension of the quotient!
+    Let \(y \in V_{wr}\).
+    By definition of \(V_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in U_{wr}\).
+    We have
+    \[\varphi^{-1}(y) = \{(x, P) : P \cdot x = y = P_y^{-1} \cdot (P_y \cdot y)\} = \]
+    \[\{(x, P) : x = (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \} = \]
+    \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\} = \] 
+    \[(\textrm{taking } Q := P^{-1}P_y^{-1}, \textrm{ so } P = (QP_y)^{-1} = P_y^{-1} Q^{-1})\]
+    \[\{(Q \cdot (P_y \cdot y), P_y^{-1} Q^{-1}) : Q \in G_{wr}\} = \]
+    \[\{Q \cdot (P_y \cdot y, P_y^{-1}) : Q \in G_{wr}\}.\]
+    So we see that the fibers are exactly the \(G_{wr}\)-orbits.
+    \par Now, what kind of quotient is this?
+    All I need is something that allows me to deduce the dimension of the quotient...
     % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.

### 2024-08-17 paper.tex
why is irred
fix notation; move some stuff from section 7 to section 8

@@
 and
-\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
-If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 
 \[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
 \par Now, define 
-\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
+\[U_{wr} = \{(A_{e_{wr}, b}, U) \in V_{wr}\}.\]
 Let \(G\) act on \(V_{wr}\) by
@@
 \begin{proof}
-    not sure why at the moment
+    It's just \(\mathbb{C}^{something}\), since its blocks are the lower-left-toeplitz matrices.
 \end{proof}
@@
 So, we will now find the irreducible components of \(U_{wr}\).
-\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
-(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
-\begin{theorem}
-    (Needs citation!)
-    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
-    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
-\end{theorem}
-Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
-We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
-We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
-So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
-Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
-I think this explanation of intuition is important, so I should try to make it better.
-\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
-Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
+\par Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
 So, we will change basis to make \(r = 0\).
@@
 
-\section{Finding the irreducible components of \(U\)}
-Let \(X\) be nilpotent of shape \(\lambda\), etc.
+\section{Finding the irreducible components of \(U_0\)}
+Let \(X\) be nilpotent of shape \(\lambda\).
+Let 
+\[U_0 = \{\]
 Start fresh finding irreducible components of \(U_{w0}\).
+\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
+(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
+\begin{theorem}
+    (Needs citation!)
+    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
+    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
+\end{theorem}
+Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
+We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
+We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
+So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
+Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
+I think this explanation of intuition is important, so I should try to make it better.
+\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
 

### 2024-08-17 paper.tex
work on section 8

@@
 
-\newcommand{\leftshift}{\mathbin{\rotatebox[origin=c]{0}{$\ll$}}}
-\newcommand{\downshift}{\mathbin{\rotatebox[origin=c]{90}{$\ll$}}}
-\newcommand{\rightshift}{\mathbin{\rotatebox[origin=c]{180}{$\ll$}}}
-\newcommand{\upshift}{\mathbin{\rotatebox[origin=c]{270}{$\ll$}}}
+\newcommand{\leftshift}{$\,\texttt{<<}\,$}
+\newcommand{\downshift}{\mathbin{\rotatebox[origin=c]{90}{\leftshift}}}
+\newcommand{\rightshift}{\mathbin{\rotatebox[origin=c]{180}{\leftshift}}}
+\newcommand{\upshift}{\mathbin{\rotatebox[origin=c]{270}{\leftshift}}}
 
@@
 \section{Finding the irreducible components of \(U_0\)}
-Let \(X\) be nilpotent of shape \(\lambda\).
+Let \(X\) be nilpotent with Jordan basis \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\).
+Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
 Let
-\[U_0 = \{\]
-Start fresh finding irreducible components of \(U_{w0}\).
-\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
+\[U_0 = \{(A_{0,b}, U) \in V\}.\]
+We will find the irreducible components of \(U_0\).
+We note that even finding the irreducible components of \(\{A_{0,0}, U \in V\}\) is a pretty hard problem.
+Not ambitious enough to try to re-solve that problem, we will use its solution.
+\par To find the irreducible components of \(U_0\), we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
 (I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
@@
 We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
-So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
+\par So, our strategy will be to find a subset of \(U_0\) such that \(A_{0,b}\) has some fixed Jordan form \(\mu\), and we have an algebraic map \(b \mapsto P\) such that for \(A_{0,b}\) in the subset, \(PJ(\mu)P^{-1} = A_{0,b}\).
 Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
 I think this explanation of intuition is important, so I should try to make it better.
-\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
+\par Finding the map \(b \mapsto P\) amounts to finding a Jordan basis for \(A_{0,b}\).
+So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).
+
+\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
+For each row \(i\), let \(p_i = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
+Then set \(q_i = \lambda_i - p_i\).
+Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
+Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that: from now on, we assume that \(q_i\) is nonincreasing.
+\par We list the chains of the Jordan basis in (roughly) order of decreasing length.
+First, for each \(i\) such that \(q_i \geq n\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
+\par Now we handle \(f_n\).
+Let \(P = \max_{i : q_i < n} p_i\).
+Set 
+\[v = f_n - (A^{n + P}f_n \rightshift n + P).\]
+Note that \(A^n f_n = b\), so \(A^{n + P} f_n = A^P b = b \leftshift P\).
+By shifting \(b\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n\).
+This ensures that the operation of shifting \(b' \leftshift P\) right \(n + P\) times is invertible by applying \(A\), and thus shifting left, \(n + P\) times.
+So, we take the chain of length \(n + P\) beginning with \(v\).
+\par Now, it is clear that each \(f_i\) is in the span of the chains we have listed so far.
+It is also clear that \(b \leftshift k\) is in the span, for each \(k \geq 0\).
+\par Now, we handle the \(i\) with \(q_i < n\).
+We take as an inductive hypothesis that for all \(i' < i\) and all \(j\), we have \(e_{i'j}\) in the span of the chains we have already listed.
+\par If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
+Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).
+\par Otherwise, we set 
+\[v_i = A^{n - q_i} f_n - \sum_{k = 1}^{p_i}b_{i,k} e_{i,k + q_i}.\]
+Note that \(A^{q_i} v_i\) is just \(b\) with row \(i\) zeroed out.
+Then, \(A^{q_i + \max_{k > i} p_k} v_i\) will have, in addition, rows \(k\) zeroed out, for all \(k > i\).
+This ensures that shifting \(A^{q_i + \max_{k > i} p_k} v_i\) right \(q_i + \max_{k > i} p_k\) times will be inverted by applying \(A\), and thus shifting left, \(q_i + \max_{k > i} p_k\) times.
+So, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_i)\), which has length \(q_i + \max_{k > i} p_k\).
+\par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.
+Since \(A^{q_i + \max_{k > i} p_k} v_i\) has rows \(k\) zeroed out for \(k \geq i\), our inductive hypothesis tells us that \(A^{q_i + \max_{k > i} p_k} v_i \rightshift q_i + \max_{k > i} p_k\) is in the span of the chains already listed.
+So it suffices to show that the closure of \(\langle v_i \rangle\) under action by \(A\) contains the span of \(e_{ij}\).
+And \(A^{n - q_i} f_n\) is also in the span of chains already listed, so it suffices to show that the closure of \(\langle \sum_k b_{ik} e_{i,k + q_i}\rangle \) under action by \(A\) contains \(\langle e_{ij}\rangle\).
+And this just follows from the fact that \(b_{i,p_i}\) is nonzero.
+\par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
+I list the purported basis here:
+\begin{itemize}
+    \item TODO
+\end{itemize}
+Indeed, the sum of the lengths is
+\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} \begin{cases}
+    p_i + q_i, & p_i \leq \max_{k > i} p_k \\
+    q_i + \max_{k > i} p_i, & p_i > \max_{k > i} p_k
+\end{cases} = \]
+\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)).\]
+Let \(i_1 < \cdots < i_s\) be the `peaks': that is, the set \(I_1 = \{i : q_i < n + r \land p_i > \max_{k > i} p_k\}\).
+(As I should've mentioned before, we take the max of the empty set to be zero.)
+Let \(I_2 = \{i : q_i < n + r\} \setminus I_1\).
+Then 
+\[\sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)) = \sum_{i \in I_2} (p_i + q_i) + \sum_{k = 1}^s (q_{i_k} + p_{i_{k + 1}}).\]
+Clearly then, the whole sum is \(m + n\).
 
@@
 
-\subsection{The general case}
-Let \(X\) be nilpotent in Jordan form, and let \(a = \mathbbm{1}_{w,1}\), and let \(b\) be such that \(\forall j. \; b_{wj} = 0\).
-We describe a Jordan basis for \(A_{X, a, b}\).
-
-\par Let \(\mu\) be the result of removing the row \(w\) from \(\lambda\).
-For each row \(i\), let \(p_i = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
-Then set \(q_i = \lambda_i - p_i\).  Let \(q_{i_0} = \lambda_{i_0} - r - p_{i_0}\).
-Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
-Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that.
-We list the chains in (roughly) order of decreasing length.
-First, for each \(i\) such that \(q_i \geq n + r\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
-\par Now we handle \(e_{i_0, \lambda_{i_0}}\).
-Let \(P = \max_{i : q_i < n + r} p_i\).
-Set 
-\[v = e_{i_0, \lambda_{i_0}} - (A^{r + n + P}e_{i_0, \lambda_{i_0}} >> r + n + P).\]
-Note that \(A^{r + n} e_{i_0, \lambda_{i_0}} = b'\), so \(A^{r + n + P} e_{i_0, \lambda_{i_0}} = A^P b' = b' << P\).
-Also note that if we shift \(b'\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n + r\).
-This ensures that the operation of shifting \(b' << P\) right \(r + n + P\) times is invertible by applying \(A\), and thus shifting left, \(r + n + P\) times.
-So, we take the chain of length \(r + n + P\) beginning with \(v\).
-\par Now, it is clear that \(e_{i_0, p_{i_0} + q_{i_0} + i}\) is in the span of the chains we have listed so far for each \(i \geq 1\).
-It is also clear that \(b' \leftshift k\) is in the span, for each \(k \geq 0\).
-\par Now, we handle the \(i\) with \(q_i < n + r\).
-We take as an inductive hypothesis that for all \(i' < i\) and all \(j\), we have \(e_{i'j}\) in the span of the chains we have already listed.
-\par If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
-Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).
-\par Otherwise, we set 
-\[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k}' e_{i,k + q_i}.\]
-Note that \(A^{q_i} v_i\) is just \(b'\) with row \(i\) zeroed out.
-Then, \(A^{q_i + \max_{k > i} p_k} v_i\) will have, in addition, rows \(k\) zeroed out, for all \(k > i\).
-This ensures that shifting \(A^{q_i + \max_{k > i} p_k} v_i\) right \(q_i + \max_{k > i} p_k\) times will be inverted by applying \(A\), and thus shifting left, \(q_i + \max_{k > i} p_k\) times.
-So, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_i)\), which has length \(q_i + \max_{k > i} p_k\).
-\par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.
-Since \(A^{q_i + \max_{k > i} p_k} v_i\) has rows \(k\) zeroed out for \(k \geq i\), our inductive hypothesis tells us that \(A^{q_i + \max_{k > i} p_k} v_i \rightshift q_i + \max_{k > i} p_k\) is in the span of the chains already listed.
-So it suffices to show that the closure of \(\langle v_i \rangle\) under action by \(A\) contains the span of \(e_{ij}\).
-And \(A^{n + r - q_i} e_{i_0, \lambda_{i_0}}\) is also in the span of chains already listed, so it suffices to show that the closure of \(\langle \sum_k b'_{ik} e_{i,k + q_i}\rangle \) under action by \(A\) contains \(\langle e_{ij}\rangle\).
-And this just follows from the fact that \(b'_{i,p_i}\) is nonzero.
-\par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
-Indeed, the sum of the lengths is
-\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} \begin{cases}
-    p_i + q_i, & p_i \leq \max_{k > i} p_k \\
-    q_i + \max_{k > i} p_i, & p_i > \max_{k > i} p_k
-\end{cases} = \]
-\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)).\]
-Let \(i_1 < \cdots < i_s\) be the `peaks': that is, the set \(I_1 = \{i : q_i < n + r \land p_i > \max_{k > i} p_k\}\).
-(As I should've mentioned before, we take the max of the empty set to be zero.)
-Let \(I_2 = \{i : q_i < n + r\} \setminus I_1\).
-Then 
-\[\sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)) = \sum_{i \in I_2} (p_i + q_i) + \sum_{k = 1}^s (q_{i_k} + p_{i_{k + 1}}).\]
-Clearly then, the whole sum is \(m + n\).
-
 \subsection{When \(X\) is all zeroes}

### 2024-08-17 paper.tex
small fix in section 8

@@
 We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
-\par So, our strategy will be to find a subset of \(U_0\) such that \(A_{0,b}\) has some fixed Jordan form \(\mu\), and we have an algebraic map \(b \mapsto P\) such that for \(A_{0,b}\) in the subset, \(PJ(\mu)P^{-1} = A_{0,b}\).
-Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
-I think this explanation of intuition is important, so I should try to make it better.
+\par So, our strategy will be to find a subset of the possible values of \(b\) such that \(A_{0,b}\) has some fixed Jordan form \(\mu\), and we have an algebraic map \(b \mapsto P_b\) such that for \(A_{0,b}\) in the subset, \(P_bJ(\mu)P_b^{-1} = A_{0,b}\).
+Then we obtain an irreducible component by picking one of these subsets of the possible values of \(b\) and picking a Springer fiber at \(J(\mu)\).
 \par Finding the map \(b \mapsto P\) amounts to finding a Jordan basis for \(A_{0,b}\).
 So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).
-
 \par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).

### 2024-08-17 paper.tex
m

@@
 We will find the irreducible components of \(U_0\).
+\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
+For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
+Then set \(q_i(b) = \lambda_i - p_i(b)\).
+When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
+
+For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I'}\) such that (1) \(\rho_i \leq \lambda_i\) and (2) \(\rho_i\) is decreasing with \(i\), define 
+\[U_{I', (\rho_i)} := \{(A_{0, b}, U) \in U_0 : I' = \{i : p_i > \max_{j : q_j > q_i} p_j\} \land \forall i \in I'. \; p_i = \rho_i \}.\]
+\begin{lemma}
+    \(U_0 = \bigcup_{I', (\rho_i)} U_{I', (\rho_i)}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i\) is decreasing as \(i\) increases.
+\end{lemma}
+\begin{proof}
+    Let \((A_{0, b}, U) \in U_0\).
+    Define \(I' = \{i : p_i > \max_{j : q_j > q_i} p_j\}\), and for \(i \in I'\), \(\rho_i := p_i\).
+    All we need to do is show that each \(\rho_i\) is positive and that \(\rho_i\) is decreasing.
+    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i)}\), and we are done.
+    \par Recall that by convention we take that the maximum of the empty set is zero.
+    So, the fact that \(\rho_i > \max_{j : q_j > q_i} p_j\) tells us that \(\rho_i\) is positive.
+    Now, let \(i < i'\), with \(i, i' \in I'\).
+    If we had \(p_i \leq p_{i'}\), then \(q_i \geq q_{i'}\)
+
+\end{proof}
+
 We note that even finding the irreducible components of \(\{A_{0,0}, U \in V\}\) is a pretty hard problem.
@@
 So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).
-\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
-For each row \(i\), let \(p_i = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
-Then set \(q_i = \lambda_i - p_i\).
-Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
+\par Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
 Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that: from now on, we assume that \(q_i\) is nonincreasing.

### 2024-08-18 paper.tex
about to revert some things

@@
 \section{Finding the irreducible components of \(U_0\)}
-Let \(X\) be nilpotent with Jordan basis \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\).
+Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
 Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
@@
 We will find the irreducible components of \(U_0\).
-\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
-For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
-Then set \(q_i(b) = \lambda_i - p_i(b)\).
-When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
+\par We write \(b_{ij}'\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}'\).
+For each row \(i\), let \(p_i'(b) = \max\{j : b_{ij}' \neq 0\}\) (the maximum of the empty set is zero).
+Then set \(q_i'(b) = \lambda_i' - p_i'(b)\).
+When it is clear enough from context, we will just write \(p_i'\) and \(q_i'\) instead of \(p_i'(b)\) and \(q_i'(b)\).
+Then, let \(\{n_1(b), ..., n_k(b)\} = \{1, ..., k\}\) be such that the list 
+\[(q_{n_1}', n_1), ..., (q_{n_k}', n_k)\]
+is in reverse lexicographical order; that is, for any \(\alpha < \beta\), we have either \(q_{n_\alpha}' > q_{n_\beta}'\) or \(q_{n_\alpha}' = q_{n_\beta}' \land n_\alpha > n_\beta\).
+The point is that we want the list \(q_{n_1}', ..., q_{n_k}'\) to be nonincreasing.
+To break ties in an arbitrary canonical way, we say that if \(q_\gamma' = q_\delta'\), then we put the one with the bigger subscript first.
+\par Now, in the rest of this section it will be convenient for us to have the values \(q_i'\) in nonincreasing order.
+To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
 
-For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I'}\) such that (1) \(\rho_i \leq \lambda_i\) and (2) \(\rho_i\) is decreasing with \(i\), define 
+\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_{i_\alpha})_{\alpha \in I'}\) such that (1) \(\rho_{i_\alpha} \leq \lambda_{i_\alpha}\) and (2) \(\rho_{i_\alpha}\) is decreasing with \(\alpha\), define
 \[U_{I', (\rho_i)} := \{(A_{0, b}, U) \in U_0 : I' = \{i : p_i > \max_{j : q_j > q_i} p_j\} \land \forall i \in I'. \; p_i = \rho_i \}.\]

### 2024-08-18 paper.tex
idk

@@
 To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
-
-\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_{i_\alpha})_{\alpha \in I'}\) such that (1) \(\rho_{i_\alpha} \leq \lambda_{i_\alpha}\) and (2) \(\rho_{i_\alpha}\) is decreasing with \(\alpha\), define
+\par TODO: try to introduce the same notation less obnoxiously.
+Agh wait, this doesn't work out with my \(\rho_i\)'s...
+\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I'}\) such that (1) \(\rho_i \leq \lambda_i\) and (2) \(\rho_{i_\alpha}\) is decreasing with \(\alpha\), define 
 \[U_{I', (\rho_i)} := \{(A_{0, b}, U) \in U_0 : I' = \{i : p_i > \max_{j : q_j > q_i} p_j\} \land \forall i \in I'. \; p_i = \rho_i \}.\]

### 2024-08-18 paper.tex
m

@@
 \par TODO: try to introduce the same notation less obnoxiously.
-Agh wait, this doesn't work out with my \(\rho_i\)'s...
-\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I'}\) such that (1) \(\rho_i \leq \lambda_i\) and (2) \(\rho_{i_\alpha}\) is decreasing with \(\alpha\), define 
-\[U_{I', (\rho_i)} := \{(A_{0, b}, U) \in U_0 : I' = \{i : p_i > \max_{j : q_j > q_i} p_j\} \land \forall i \in I'. \; p_i = \rho_i \}.\]
+\par For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i')_{i \in I'}\) such that (1) \(\rho_i' \leq \lambda_i\) and (2) \(\rho_i'\) is decreasing with \(i\), define 
+\[U_{I', (\rho_i')} := \{(A_{0, b}, U) \in U_0 : I' = \{n_i : p_i > \max_{j > i} p_j\} \land \forall i \in I'. \; p_i = \rho_{n_i}' \}.\]
 \begin{lemma}
-    \(U_0 = \bigcup_{I', (\rho_i)} U_{I', (\rho_i)}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i\) is decreasing as \(i\) increases.
+    \(U_0 = \bigcup_{I', (\rho_i')} U_{I', (\rho_i')}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i')\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i'\) is decreasing as \(i\) increases.
 \end{lemma}
@@
     Let \((A_{0, b}, U) \in U_0\).
-    Define \(I' = \{i : p_i > \max_{j : q_j > q_i} p_j\}\), and for \(i \in I'\), \(\rho_i := p_i\).
-    All we need to do is show that each \(\rho_i\) is positive and that \(\rho_i\) is decreasing.
-    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i)}\), and we are done.
-    \par Recall that by convention we take that the maximum of the empty set is zero.
-    So, the fact that \(\rho_i > \max_{j : q_j > q_i} p_j\) tells us that \(\rho_i\) is positive.
-    Now, let \(i < i'\), with \(i, i' \in I'\).
+    Define \(I' := \{n_i : p_i > \max_{j > i} p_j\}\), and for \(n_i \in I'\), \(\rho_{n_i}' := p_i\).
+    All we need to do is show that each \(\rho_i'\) is positive and that \(\rho_i'\) is decreasing.
+    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i')}\), and we are done.
+    \par Recall that by convention the maximum of the empty set is zero.
+    So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_{n_i}' = p_i\) is positive.
+    Now, let \(n_i < n_{i'}\), with \(n_i, n_{i'} \in I'\).
+    We have \(p_i > \max_{j > i} p_j\); that is, \(\) AGH CONFUSION
+    We have two cases: either \(i < i'\), or \(i' < i\).
     If we had \(p_i \leq p_{i'}\), then \(q_i \geq q_{i'}\)

### 2024-08-18 paper.tex
deleting some stuff

@@
 \begin{lemma}
-    \(U_0 = \bigcup_{I', (\rho_i')} U_{I', (\rho_i')}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i')\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i'\) is decreasing as \(i\) increases.
+    \(U_0 = \bigcup_{I', (\rho_i')} U_{I', (\rho_i')}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i')\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that the maps \(i \mapsto \rho_i'\) and \(i \mapsto \lambda'_i - \rho_i'\) are both decreasing with \(i\).
 \end{lemma}
@@
     Let \((A_{0, b}, U) \in U_0\).
-    Define \(I' := \{n_i : p_i > \max_{j > i} p_j\}\), and for \(n_i \in I'\), \(\rho_{n_i}' := p_i\).
+    Define \(I := \{i : p_i > \max_{j > i} p_j\}\), and let \(I' := \{n_i : i \in I\}\).
+    And for \(i \in I\), \(\rho_{n_i}' := p_i\).
     All we need to do is show that each \(\rho_i'\) is positive and that \(\rho_i'\) is decreasing.
@@
     So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_{n_i}' = p_i\) is positive.
-    Now, let \(n_i < n_{i'}\), with \(n_i, n_{i'} \in I'\).
-    We have \(p_i > \max_{j > i} p_j\); that is, \(\) AGH CONFUSION
-    We have two cases: either \(i < i'\), or \(i' < i\).
-    If we had \(p_i \leq p_{i'}\), then \(q_i \geq q_{i'}\)
+    \par For \(i, j \in I\) with \(i < j\), we have \(q_i \geq q_j\) (as \(q\) is nonincreasing), and also \(p_i > p_j\) (as \(i \in I\), and consequently \(p_i > \max_{l > i} p_l\)).
+    Thus, \(\lambda_i > \lambda_j\).
 

### 2024-08-18 paper.tex
fix lemma 8.1

--- 2024-08-18 paper.tex
@@
 We will find the irreducible components of \(U_0\).
-\par We write \(b_{ij}'\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}'\).
-For each row \(i\), let \(p_i'(b) = \max\{j : b_{ij}' \neq 0\}\) (the maximum of the empty set is zero).
-Then set \(q_i'(b) = \lambda_i' - p_i'(b)\).
-When it is clear enough from context, we will just write \(p_i'\) and \(q_i'\) instead of \(p_i'(b)\) and \(q_i'(b)\).
-Then, let \(\{n_1(b), ..., n_k(b)\} = \{1, ..., k\}\) be such that the list 
-\[(q_{n_1}', n_1), ..., (q_{n_k}', n_k)\]
-is in reverse lexicographical order; that is, for any \(\alpha < \beta\), we have either \(q_{n_\alpha}' > q_{n_\beta}'\) or \(q_{n_\alpha}' = q_{n_\beta}' \land n_\alpha > n_\beta\).
-The point is that we want the list \(q_{n_1}', ..., q_{n_k}'\) to be nonincreasing.
-To break ties in an arbitrary canonical way, we say that if \(q_\gamma' = q_\delta'\), then we put the one with the bigger subscript first.
-\par Now, in the rest of this section it will be convenient for us to have the values \(q_i'\) in nonincreasing order.
-To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
-\par TODO: try to introduce the same notation less obnoxiously.
-\par For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i')_{i \in I'}\) such that (1) \(\rho_i' \leq \lambda_i\) and (2) \(\rho_i'\) is decreasing with \(i\), define 
-\[U_{I', (\rho_i')} := \{(A_{0, b}, U) \in U_0 : I' = \{n_i : p_i > \max_{j > i} p_j\} \land \forall i \in I'. \; p_i = \rho_{n_i}' \}.\]
+% \par We write \(b_{ij}'\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}'\).
+% For each row \(i\), let \(p_i'(b) = \max\{j : b_{ij}' \neq 0\}\) (the maximum of the empty set is zero).
+% Then set \(q_i'(b) = \lambda_i' - p_i'(b)\).
+% When it is clear enough from context, we will just write \(p_i'\) and \(q_i'\) instead of \(p_i'(b)\) and \(q_i'(b)\).
+% Then, let \(\{n_1(b), ..., n_k(b)\} = \{1, ..., k\}\) be such that the list 
+% \[(q_{n_1}', n_1), ..., (q_{n_k}', n_k)\]
+% is in reverse lexicographical order; that is, for any \(\alpha < \beta\), we have either \(q_{n_\alpha}' > q_{n_\beta}'\) or \(q_{n_\alpha}' = q_{n_\beta}' \land n_\alpha > n_\beta\).
+% The point is that we want the list \(q_{n_1}', ..., q_{n_k}'\) to be nonincreasing.
+% To break ties in an arbitrary canonical way, we say that if \(q_\gamma' = q_\delta'\), then we put the one with the bigger subscript first.
+% \par Now, in the rest of this section it will be convenient for us to have the values \(q_i'\) in nonincreasing order.
+% To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
+% \par TODO: try to introduce the same notation less obnoxiously.
+\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), and (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), define
+\[U_{I, (\rho_i)} := \] 
+\[\{(A_{0, b}, U) \in U_0 : \{(p_i, q_i) : i \in I\} = \{(p_i, q_i) : p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j \} \] 
+\[\land \forall i \in I. \; p_i = \rho_i \}.\]
 \begin{lemma}
-    \(U_0 = \bigcup_{I', (\rho_i')} U_{I', (\rho_i')}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i')\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i'\) is decreasing as \(i\) increases.
+    \(U_0 = \bigcup_{I, (\rho_i)} U_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) such that \(\rho_i\) and \(\lambda_i - \rho_i\) are both decreasing with \(i\).
+    TODO: something about overlap being small (they're not disjoint).  
+    They are distinct.
+    Is that good enough for my purposes?
 \end{lemma}
@@
     Let \((A_{0, b}, U) \in U_0\).
-    Define \(I' := \{n_i : p_i > \max_{j > i} p_j\}\), and for \(n_i \in I'\), \(\rho_{n_i}' := p_i\).
-    All we need to do is show that each \(\rho_i'\) is positive and that \(\rho_i'\) is decreasing.
-    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i')}\), and we are done.
+    Let \(I' = \{(p_i, q_i) : p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j\}\).
+    Then let \(I = \{\max\{i : (p_i, q_i) = (p, q)\} : (p, q) \in I'\}\).
+    Choosing the maximal \(i\) is an arbitrary choice; we just have to pick one.
+    For \(i \in I\), \(\rho_i := p_i\).
+    All we need to do is show that each \(\rho_i\) is positive, and that \(\rho_i\) and \(\lambda_i - \rho_i\) are decreasing.
+    Then we get that \((A_{0,b}, U) \in U_{I, (\rho_i)}\), and we are done.
     \par Recall that by convention the maximum of the empty set is zero.
-    So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_{n_i}' = p_i\) is positive.
-    Now, let \(n_i < n_{i'}\), with \(n_i, n_{i'} \in I'\).
-    We have \(p_i > \max_{j > i} p_j\); that is, \(\) AGH CONFUSION
-    We have two cases: either \(i < i'\), or \(i' < i\).
-    If we had \(p_i \leq p_{i'}\), then \(q_i \geq q_{i'}\)
-
+    So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_i = p_i\) is positive.
+    \par Let \(i, j \in I\) with \(i < j\).
+    Since \(\lambda_i \geq \lambda_j\), we have either \(p_i \geq p_j\) or \(q_i \geq q_j\).
+    Further, since \((p_i, q_i) \neq (p_j, q_j)\) (clear from definition of \(I\)), either \(p_i > p_j\) or \(q_i > q_j\).
+    And for \(i, j \in I'\) we clearly have \(p_i > p_j \iff q_i > q_j\).
+    So in either case, both \(p_i > p_j\) and \(q_i > q_j\), and consequently both \(\rho_i > \rho_j\) and \(\lambda_i - \rho_i > \lambda_j - \rho_j\).
 \end{proof}

### 2024-08-18 paper.tex
preamble to 8.1

@@
 We will find the irreducible components of \(U_0\).
-% \par We write \(b_{ij}'\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}'\).
-% For each row \(i\), let \(p_i'(b) = \max\{j : b_{ij}' \neq 0\}\) (the maximum of the empty set is zero).
-% Then set \(q_i'(b) = \lambda_i' - p_i'(b)\).
-% When it is clear enough from context, we will just write \(p_i'\) and \(q_i'\) instead of \(p_i'(b)\) and \(q_i'(b)\).
-% Then, let \(\{n_1(b), ..., n_k(b)\} = \{1, ..., k\}\) be such that the list 
-% \[(q_{n_1}', n_1), ..., (q_{n_k}', n_k)\]
-% is in reverse lexicographical order; that is, for any \(\alpha < \beta\), we have either \(q_{n_\alpha}' > q_{n_\beta}'\) or \(q_{n_\alpha}' = q_{n_\beta}' \land n_\alpha > n_\beta\).
-% The point is that we want the list \(q_{n_1}', ..., q_{n_k}'\) to be nonincreasing.
-% To break ties in an arbitrary canonical way, we say that if \(q_\gamma' = q_\delta'\), then we put the one with the bigger subscript first.
-% \par Now, in the rest of this section it will be convenient for us to have the values \(q_i'\) in nonincreasing order.
-% To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
-% \par TODO: try to introduce the same notation less obnoxiously.
+\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
+For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
+Then set \(q_i(b) = \lambda_i - p_i(b)\).
+When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
 \par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), and (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), define

### 2024-08-18 paper.tex
outline remainder of section 8

@@
 
+\begin{lemma}
+    Here we have an alternative characterization of \(U_{I, (\rho_i)}\).
+    Namely, \(p_i = \rho_i\) for \(i \in I\) and for \(i \notin I\), we have \(p_i \leq something\).
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+\par TODO: explain here why we are finding a Jordan basis here.
+Fix any \(I\) and \((\rho_i)\) as in Lemma 8.1.
+We will find an algebraic map \(b \mapsto P_b\) with the desired property.
+This is equivalent to finding an algebraic map taking \(b\) to a Jordan basis for \(A_{0,b}\).
+This is what we do.
+
 We note that even finding the irreducible components of \(\{A_{0,0}, U \in V\}\) is a pretty hard problem.
@@
 So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).
+
 \par Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).

### 2024-08-18 paper.tex
remaining setup for finding Jordan basis in section 8

--- 2024-08-18 paper.tex
@@
 \par We mention some results about Springer fibers, which we will use later in this paper.
-TODO: mention them.
+\begin{theorem}
+    (Needs citation!)
+    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
+    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
+\end{theorem}
 
@@
     Is that good enough for my purposes?
+    Ah, I think it is good enough if I instead say that the sets of \(b\)'s are distinct.
 \end{lemma}
@@
 
-We note that even finding the irreducible components of \(\{A_{0,0}, U \in V\}\) is a pretty hard problem.
-Not ambitious enough to try to re-solve that problem, we will use its solution.
-\par To find the irreducible components of \(U_0\), we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
+\begin{lemma}
+    Here we have an alternative characterization of \(U_{I, (\rho_i)}\).
+    Namely, \(p_i = \rho_i\) for \(i \in I\) and for \(i \notin I\), we have \(p_i \leq something\).
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
+We will find the irreducible components of \(U_{I, (\rho_i)}\), and show that their closures are in fact irreducible components of \(U_0\).
+\par I claim that \(A_{0,b}\) has the same shape for every \((A_{0, b}, U) \in U_{I, (\rho_i)}\).
+Call this shape \(\mu\).
+By finding a algebraic map taking \(b\) to a Jordan basis for \(A_{0,b}\), we will put \(U_{I, (\rho_i)}\) in isomorphism with the product (choice of \(b\)) \(\times\) (Springer fiber at \(J(\mu)\)).
+Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(U_{I, (\rho_i)}\).
 (I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
-\begin{theorem}
-    (Needs citation!)
-    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
-    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
-\end{theorem}
+
+\par TODO: where does this paragraph go?
 Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
 We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
-We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
-\par So, our strategy will be to find a subset of the possible values of \(b\) such that \(A_{0,b}\) has some fixed Jordan form \(\mu\), and we have an algebraic map \(b \mapsto P_b\) such that for \(A_{0,b}\) in the subset, \(P_bJ(\mu)P_b^{-1} = A_{0,b}\).
-Then we obtain an irreducible component by picking one of these subsets of the possible values of \(b\) and picking a Springer fiber at \(J(\mu)\).
-\par Finding the map \(b \mapsto P\) amounts to finding a Jordan basis for \(A_{0,b}\).
-So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).
+\par TODO: begin Jordan basis thing in earnest here.
 \par Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).

### 2024-08-18 paper.tex
some work on Jordan basis

@@
 (I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
-
 \par TODO: where does this paragraph go?
@@
 We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
-\par TODO: begin Jordan basis thing in earnest here.
-\par Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
-Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that: from now on, we assume that \(q_i\) is nonincreasing.
-\par We list the chains of the Jordan basis in (roughly) order of decreasing length.
-First, for each \(i\) such that \(q_i \geq n\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
+\par So, now we find a Jordan basis for \(A_{0, b}\).
+\par We list the chains of the Jordan basis.
+First, for each \(i \notin I\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i,p_i + q_i} = e_{i\lambda_i}\)
+% First, for each \(i\) such that \(q_i \geq n\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
+(Agh, the definition of I was wrong, we also need the the condition relating \(q_i\) to \(n\).)
 \par Now we handle \(f_n\).
-Let \(P = \max_{i : q_i < n} p_i\).
+Let \(P = \max_{i : q_i < n} p_i = (something in terms of \rho)\).
 Set 

### 2024-08-18 paper.tex
finish proof of "1"

@@
 
-\newcommand{\leftshift}{$\,\texttt{<<}\,$}
+\newcommand{\leftshift}{\,\texttt{<<}\,}
 \newcommand{\downshift}{\mathbin{\rotatebox[origin=c]{90}{\leftshift}}}
@@
 When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
-\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), and (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), define
+\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I}\) %such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), and (3) \(\lambda_i - \rho_i\) is decreasing with \(i\)
+, define 
 \[U_{I, (\rho_i)} := \] 
-\[\{(A_{0, b}, U) \in U_0 : \{(p_i, q_i) : i \in I\} = \{(p_i, q_i) : p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j \} \] 
+\[\{(A_{0, b}, U) \in U_0 : \]
+\[\{(p_i, q_i) : i \in I\} = \{(p_i, q_i) : n > q_i \land p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j \} \] 
 \[\land \forall i \in I. \; p_i = \rho_i \}.\]
@@
     Let \((A_{0, b}, U) \in U_0\).
-    Let \(I' = \{(p_i, q_i) : p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j\}\).
+    Let \(I' = \{(p_i, q_i) : p_i = n > q_i \land \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j\}\).
     Then let \(I = \{\max\{i : (p_i, q_i) = (p, q)\} : (p, q) \in I'\}\).
@@
     Further, since \((p_i, q_i) \neq (p_j, q_j)\) (clear from definition of \(I\)), either \(p_i > p_j\) or \(q_i > q_j\).
-    And for \(i, j \in I'\) we clearly have \(p_i > p_j \iff q_i > q_j\).
+    And for \(i, j \in I\) we clearly have \(p_i > p_j \iff q_i > q_j\).
     So in either case, both \(p_i > p_j\) and \(q_i > q_j\), and consequently both \(\rho_i > \rho_j\) and \(\lambda_i - \rho_i > \lambda_j - \rho_j\).
@@
 (I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
-\par TODO: where does this paragraph go?
-Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
-We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
+% \par TODO: where does this paragraph go?
+% Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
+% We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
 \par So, now we find a Jordan basis for \(A_{0, b}\).
-\par We list the chains of the Jordan basis.
-First, for each \(i \notin I\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i,p_i + q_i} = e_{i\lambda_i}\)
-% First, for each \(i\) such that \(q_i \geq n\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
-(Agh, the definition of I was wrong, we also need the the condition relating \(q_i\) to \(n\).)
-\par Now we handle \(f_n\).
-Let \(P = \max_{i : q_i < n} p_i = (something in terms of \rho)\).
-Set 
-\[v = f_n - (A^{n + P}f_n \rightshift n + P).\]
+\begin{lemma}
+    Let \(P = \max_{i \in I} \rho_i\), and for \(i \in I\), let \(P_i = \max_{j \in I : j > i} \rho_j\).
+    The following vectors give a Jordan basis for \(A_{0,b}\).
+    (For convenience, we write \(A := A_{0,b}\) in this lemma and proof.)
+    \begin{itemize}
+        \item For \(i \notin I\), the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\)
+        \item The chain of length \(n + P\) beginning with \(f_n - (A^{n + P}f_n \rightshift n + P)\)
+        \item For \(i \in I\), the chain of length \(q_i + P_i\) beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\), where \(v_i := A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\)
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    There are three things to check: (1) the chains are no longer than their claimed lengths, (2) the claimed lengths sum to \(m\), and (3) the span of the chains is \(\mathbb{C}^m\).
+    \par We have defined \(P\) and \(P_i\) in terms of the \(\rho_i\) to make it clear that they only depend on \(I\) and the \(\rho_i\).
+    Now we provide more useful characterizations.
+    It is immediate from the definition of \(U_{I, (\rho_i)}\) that \(P = \max_{l : q_l < n} p_l\), and \(P_i = \max_{l : q_l < q_i} p_l\).
+    \begin{proof}[Proof of (1)]
+        It is obvious that a chain beginning with \(e_{i, p_i + q_i}\) has length \(p_i + q_i\).
+        \par Now consider the chain beginning with \(f_n - (A^{n + P} f_n \rightshift n + P)\).
         Note that \(A^n f_n = b\), so \(A^{n + P} f_n = A^P b = b \leftshift P\).
         By shifting \(b\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n\).
-This ensures that the operation of shifting \(b' \leftshift P\) right \(n + P\) times is invertible by applying \(A\), and thus shifting left, \(n + P\) times.
-So, we take the chain of length \(n + P\) beginning with \(v\).
+        This ensures that the operation of shifting \(b \leftshift P\) right \(n + P\) times is invertible by shifting left \(n + P\) times.
+        That is,
+        \[A^{n + P} f_n = b \leftshift P = ((b \leftshift P) \rightshift n + P) \leftshift n + P = A^{n + P}(A^{n + P}f_n \rightshift n + P).\]
+        This shows that the chain has length at most \(n + P\), as desired.
+        \par Now, let \(i \in I\).
+        We have \(v_i = A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\).
+        First we note that \(q_i < n\) by the definition of \(U_{I, (\rho_i)}\), so the definition of \(v_i\) makes sense.
+        We consider the chain beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\).
+        Note that \(A^{q_i} v_i\) is just \(b\) with row \(i\) zeroed out.
+        For brevity, we write \(b_i := A^{q_i} v_i\).
+        Note that \(b_i \leftshift P_i\) has rows \(l\) zeroed out, for all \(l\) with \(q_l < q_i\).
+        This ensures that shifting \(b_i \leftshift P_i\) right \(q_i + P_i\) times can be inverted by shifting left \(q_i + P_i\) times.
+        That is,
+        \[A^{q_i + P_i} v_i = b_i \leftshift P_i = ((b_i \leftshift P_i) \rightshift q_i + P_i) \leftshift q_i + P_i = A^{q_i + P_i}(A^{q_i + P_i} v_i \rightshift q_i + P_i).\]
+        This shows that the chain has length at most \(q_i + P_i\), as desired.
+    \end{proof}
+    \begin{proof}[Proof of (2)]
+
+    \end{proof}
+\end{proof}
+\par We list the chains of the Jordan basis.
+First, for each \(i \notin I\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i,p_i + q_i} = e_{i\lambda_i}\).
 \par Now, it is clear that each \(f_i\) is in the span of the chains we have listed so far.
@@
 Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).
-\par Otherwise, we set 
-\[v_i = A^{n - q_i} f_n - \sum_{k = 1}^{p_i}b_{i,k} e_{i,k + q_i}.\]
-Note that \(A^{q_i} v_i\) is just \(b\) with row \(i\) zeroed out.
-Then, \(A^{q_i + \max_{k > i} p_k} v_i\) will have, in addition, rows \(k\) zeroed out, for all \(k > i\).
-This ensures that shifting \(A^{q_i + \max_{k > i} p_k} v_i\) right \(q_i + \max_{k > i} p_k\) times will be inverted by applying \(A\), and thus shifting left, \(q_i + \max_{k > i} p_k\) times.
-So, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_i)\), which has length \(q_i + \max_{k > i} p_k\).
 \par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.

### 2024-08-18 paper.tex
proof of 2

@@
 \begin{proof}
-    There are three things to check: (1) the chains are no longer than their claimed lengths, (2) the claimed lengths sum to \(m\), and (3) the span of the chains is \(\mathbb{C}^m\).
+    There are three things to check: (1) the chains are no longer than their claimed lengths, (2) the claimed lengths sum to \(m + n\), and (3) the span of the chains is \(\mathbb{C}^{m + n}\).
     \par We have defined \(P\) and \(P_i\) in terms of the \(\rho_i\) to make it clear that they only depend on \(I\) and the \(\rho_i\).
@@
     \begin{proof}[Proof of (2)]
+        The sum of the lengths is
+        \[\sum_{i \notin I} (p_i + q_i) + (n + P) + \sum_{i \in I} (q_i + P_i).\]
+        Writing \(I = \{i_1 < \cdots < i_{|I|}\}\), we note that \(P = p_{i_1}\), that \(P_{i_{|I|}} = 0\), and that for \(l < |I|\) we have \(P_{i_l} = p_{i_{l + 1}}\).
+        Thus, the sum above is 
+        \[\sum_{i \notin I} (p_i + q_i) + (n + p_{i_1}) + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_{l + 1}}) = \]
+        \[\sum_{i \notin I} (p_i + q_i) + n + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_l}) = n + \sum_i (q_i + p_i) = m + n.\]
+    \end{proof}
+    \begin{proof}
 

### 2024-08-18 paper.tex
finish Jordan basis

@@
     \end{proof}
-    \begin{proof}
-
+    \begin{proof}[Proof of (3)]
+        Let \(W\) be the span of the chains listed.
+        We need to show that \(W = \mathbb{C}^{m + n}\).
+        Because every \(i \in I\) satisfies \(q_i < n\), clearly \(\langle e_{ij}\rangle_{i,j : q_i \geq n} \subseteq W\).
+        \par I claim that \(f_n \in W\) as well.
+        To see this, we consider the chain beginning with \(f_n - (A^{n + P} f_n \rightshift n + P)\).
+        As explained in the proof of (1), we have \(A^{n + P} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
+        Consequently, \((A^{n + P} f_n \rightshift n + P) \in \langle e_{ij} \rangle_{i,j : q_i \geq n} \subseteq W\).
+        Because \(f_n - (A^{n + P} f_n \rightshift n + P) \in W\), this implies that \(f_n \in W\).
+        \par Because \(AW \subseteq W\) (obvious, since \(W\) is the span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
+        \par Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
+        This is obvious for \(i \notin I\).
+        For \(i \in I\), we do it inductively.
+        Fix \(i \in I\), and suppose we have already shown that for all \(i' \in I\) with \(q_{i'} > q_i\), we have \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
+        We will show that \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
+        \par To see this, we consider the chain beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\).
+        (Recall \(v_i = A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\).)
+        Because \(AW \subseteq W\), and \(b_{i,p_i} \neq 0\) (by definition of \(p_i\)), it suffices to show that \(\sum_{l = 1}^{p_i} b_{il} e_{i,k + q_i} \in W\).
+        As explained in the proof of (1), we have \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{q_l \geq q_i}\).
+        And since \(A^{q_i + P_i} v_i\) has row \(i\) zeroed out, in fact \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
+        Hence, \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
+        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i} \subseteq W\), and consequently \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in W\).
+        Since we know \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i) \in W\), this implies that \(v_i \in W\).
+        Because \(A^{n - q_i} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i} \in W\), as desired.
     \end{proof}
+    We proved (1), (2), (3), so we are done.
 \end{proof}
-\par We list the chains of the Jordan basis.
-First, for each \(i \notin I\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i,p_i + q_i} = e_{i\lambda_i}\).
-\par Now, it is clear that each \(f_i\) is in the span of the chains we have listed so far.
-It is also clear that \(b \leftshift k\) is in the span, for each \(k \geq 0\).
-\par Now, we handle the \(i\) with \(q_i < n\).
-We take as an inductive hypothesis that for all \(i' < i\) and all \(j\), we have \(e_{i'j}\) in the span of the chains we have already listed.
-\par If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
-Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).
-\par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.
-Since \(A^{q_i + \max_{k > i} p_k} v_i\) has rows \(k\) zeroed out for \(k \geq i\), our inductive hypothesis tells us that \(A^{q_i + \max_{k > i} p_k} v_i \rightshift q_i + \max_{k > i} p_k\) is in the span of the chains already listed.
-So it suffices to show that the closure of \(\langle v_i \rangle\) under action by \(A\) contains the span of \(e_{ij}\).
-And \(A^{n - q_i} f_n\) is also in the span of chains already listed, so it suffices to show that the closure of \(\langle \sum_k b_{ik} e_{i,k + q_i}\rangle \) under action by \(A\) contains \(\langle e_{ij}\rangle\).
-And this just follows from the fact that \(b_{i,p_i}\) is nonzero.
-\par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
-I list the purported basis here:
-\begin{itemize}
-    \item TODO
-\end{itemize}
-Indeed, the sum of the lengths is
-\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} \begin{cases}
-    p_i + q_i, & p_i \leq \max_{k > i} p_k \\
-    q_i + \max_{k > i} p_i, & p_i > \max_{k > i} p_k
-\end{cases} = \]
-\[\left[\sum_{i : q_i \geq n + r} (p_i + q_i)\right] + (r + n + \max_{i : q_i < n + r} p_i) + \sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)).\]
-Let \(i_1 < \cdots < i_s\) be the `peaks': that is, the set \(I_1 = \{i : q_i < n + r \land p_i > \max_{k > i} p_k\}\).
-(As I should've mentioned before, we take the max of the empty set to be zero.)
-Let \(I_2 = \{i : q_i < n + r\} \setminus I_1\).
-Then 
-\[\sum_{i : q_i < n + r} (q_i + \min(p_i, \max_{k > i} p_i)) = \sum_{i \in I_2} (p_i + q_i) + \sum_{k = 1}^s (q_{i_k} + p_{i_{k + 1}}).\]
-Clearly then, the whole sum is \(m + n\).
 

### 2024-08-19 paper.tex
m

@@
 , define 
-\[U_{I, (\rho_i)} := \] 
-\[\{(A_{0, b}, U) \in U_0 : \]
+\[B_{I, (\rho_i)} := \{b \in \mathbb{C}^m : \]
 \[\{(p_i, q_i) : i \in I\} = \{(p_i, q_i) : n > q_i \land p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j \} \] 
 \[\land \forall i \in I. \; p_i = \rho_i \}.\]
+Then let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
 \begin{lemma}
-    \(U_0 = \bigcup_{I, (\rho_i)} U_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) such that \(\rho_i\) and \(\lambda_i - \rho_i\) are both decreasing with \(i\).
+    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) such that \(\rho_i\) and \(\lambda_i - \rho_i\) are both decreasing with \(i\).
     TODO: something about overlap being small (they're not disjoint).  
@@
 \begin{proof}
-    Let \((A_{0, b}, U) \in U_0\).
+    Let \(b \in \mathbb{C}^m\).
     Let \(I' = \{(p_i, q_i) : p_i = n > q_i \land \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j\}\).
@@
 \begin{lemma}
-    Here we have an alternative characterization of \(U_{I, (\rho_i)}\).
-    Namely, \(p_i = \rho_i\) for \(i \in I\) and for \(i \notin I\), we have \(p_i \leq something\).
+    Here we have an alternative characterization of \(B_{I, (\rho_i)}\).
+    Namely,
+    \[B_{I, (\rho_i)} = \{b \in \mathbb{C}^m : \forall i \in I. \; p_i = \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
+    \[\textrm{ where } k = ...\}\]
 \end{lemma}
 \begin{proof}
+    TODO
+\end{proof}
 
-\end{proof}
+\begin{corollary}
+    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
+\end{corollary}
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.

### 2024-08-19 paper.tex
an isomorphism

@@
 (I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
-% \par TODO: where does this paragraph go?
-% Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
-% We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
 \par So, now we find a Jordan basis for \(A_{0, b}\).
@@
 \end{proof}
+
+Let \(\mu\) be the shape of the Jordan basis given in the previous lemma.
+Let \(X_\mu\) be the Springer fiber at \(J(\mu)\).
+
+\begin{lemma}
+    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
+\end{lemma}
+\begin{proof}
+    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
+    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
+    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
+    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
+    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
+    with inverse
+    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
+\end{proof}
+At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
 

### 2024-08-19 paper.tex
m
twisted product

@@
     All I need is something that allows me to deduce the dimension of the quotient...
+    Ah, it it a twisted product actually.
+    Each \(G_{wr}\)-orbit is isomorphic to \(G_{wr}\).
+    Given \((y, Q) \in G_{wr} (x, P)\), we send it to \(Q^{-1}P\); given \(Q \in G_{wr}\), we send it to \((Q \cdot x, PQ^{-1})\).
+    These are inverse maps.
     % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
@@
 At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
+The irreducible components of \(U_{I, (\rho_i)}\) are blah.
+Thus, the irreducible components of \(U_0\) are blah.
 

### 2024-08-19 paper.tex
remove stuff not needed anymore

@@
 \par We mention some results about Springer fibers, which we will use later in this paper.
-\begin{theorem}
+\begin{theorem}\label{usual_springer_fiber}
     (Needs citation!)
@@
 
-\subsection{When \(X\) is all zeroes}
-In this case we have \(A(y, z) = (z_n b, (a \cdot y, z_1, ..., z_{n - 1}))\), and the condition becomes
-\[\sum_i b_i a_i = 0.\]
-In this case we will be able to write down explicitly the irreducible components of \(F := \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_i\} \cong \pi^{-1}(X)\).
-For any nonnegative \(\delta_0, \delta_1, ..., \delta_n, \delta_{n + 1}\) summing to \(m\), define the corresponding sequence \(i_0 = \delta_0\), \(i_n = \delta_{n + 1} + i_n\), and for \(j \in \{1, ..., n\}\), \(i_j = i_{j - 1} + 1 + \delta_j\).
-Let \(E\) be the span of the \(e_i\)'s, and let \(E' = \{(x, 0) \in E : x \cdot a = 0\}\), where the dot is the \(m\)-dimensional dot product.
-Then define \(F_\delta\) as the set of \((V, a, b) \in F\) such that 
-\begin{itemize}
-    \item \(b \in V_{i_0} \subseteq E'\)
-    \item for all \(j \in \{1, ..., n\}\), we have \(f_j \in V_{i_j} \subseteq E' + \langle f_1, ..., f_j \rangle\)
-\end{itemize}
-I claim that the \(F_\delta\)'s are the irreducible components of \(F\).
-To begin, I show that their union is \(F\).
-
-\begin{lemma}
-    Let \((V, a, b) \in \mathcal{F}\).
-    Write \(f_0 = b\), and \(F = \langle f_0, f_1, ..., f_n \rangle\).
-    For each \(i\), either \(F \subseteq V_i\), or else there exists \(j\) such that \(e_j \notin V_i\), but \(\langle e_0, ..., e_{j - 1} \rangle \subseteq V_i \subseteq E' + \langle e_1, ..., e_j \rangle\).
-\end{lemma}
-\begin{proof}
-    For \(i = 0\), we may take \(j = 0\).
-    Now assume the statement holds for \(i\), and we will prove it for \(i + 1\).
-    If \(F \subseteq V_i\), then \(F \subseteq V_{i + 1}\), and we are done.
-    \par So, suppose there is \(j\) such that \(e_j \notin V_i\), but \(\langle e_0, ..., e_{j - 1} \rangle \subseteq V_i \subseteq E' + \langle e_0, ..., e_j \rangle\).
-    We have two cases: either \(V_{i + 1} = V_i + \langle e_j \rangle\), or not.
-    \begin{itemize}
-        \item If so, then either \(j = n\), in which case \(F \subseteq V_{i + 1}\), or else \(j \neq n\), in which case \(e_{j + 1} \notin V_{i + 1}\), but \(\langle e_0, ..., e_j \rangle \subseteq V_{i + 1} \subseteq E' + \langle e_0, ..., e_{j + 1} \rangle\).
-        \item If not, then \(e_j \notin V_{i + 1}\).
-        Let \(v_{i + 1}\) be so that \(V_{i + 1} = V_i + \langle v_{i + 1} \rangle\).
-        I just need to show that \(v_{i + 1} \in Y + \langle e_1, ..., e_j \rangle\).
-        It suffices to show that \(v_{i + 1}^\top e_k = 0\) for \(k > j\).
-        And to do this, it suffices to show that \((Av_{i + 1})^\top e_{k - 1} = 0\) for \(k > j\).
-        \par Note that \(Av_{i + 1} \in V_i \cap A \mathbb{C}^{2n} \subseteq \langle e_1, ..., e_j \rangle\).
-        So, for \(k > j + 1\) it is clear that \((Av_{i + 1})^\top e_{k - 1} = 0\).
-        Now, suppose for contradiction that \((Av_{i + 1})^\top e_j \neq 0\).
-        Then \(Av_{i + 1}\) is linearly independent of \(e_1, ..., e_{j + 1}\).
-        Since \(Av_{i + 1} \in \langle e_1, ..., e_j \rangle\), it follows that \(e_j \in \langle e_1, ..., e_{j - 1}, Av_{i + 1} \rangle \subseteq V_i\), a contradiction.
-    \end{itemize}
-\end{proof}
-
-\begin{corollary}
-    \(\mathcal{F} = \bigcup_\delta \mathcal{F}_\delta\)
-\end{corollary}
-\begin{proof}
-    Let \((V, a, b) \in F\).
-    Let \(i_0 = \min\{i : b \in V_i\}\), and let \(i' = \max\{i : V_i \subseteq E'\}\).
-    We want that \(b \in V_{i_0} \subseteq E'\), so we want that \(i_0 \leq i'\).
-    For contradiction, suppose \(i' < i_0\).
-
-\end{proof}
-
-\begin{lemma}
-    Each \(\mathcal{F}_\delta\) is a closed subvariety of \(\mathcal{F}\).
-\end{lemma}
-\begin{proof}
-
-\end{proof}
-
-\begin{lemma}
-    Each \(\mathcal{F}_\delta\) is irreducible of dimension \(m\).
-\end{lemma}
-\begin{proof}
-    Let \(\mathcal{E}\) be the variety of partial flags of \(E\) of shape \((\delta_0, ..., \delta_{n + 1})\).
-    Define \(g : \mathcal{F}_\delta \to \mathcal{E}\) by
-    \[(V, a, b) \mapsto 0 \subseteq V_{i_0} \cap E \subseteq V_{i_1} \cap E \subseteq \cdots \subseteq V_{i_{n + 1}} \cap E = E.\]
-    It is clear that \(g\) is surjective, as the definition of \(\mathcal{F}_\delta\) places no restriction on the intersections \(V_i \cap E\).
-    Now let's look more closely at the fibers \(g^{-1}(U)\).
-    \par First let's find the flags \(V\) such that there exist \(a, b\) with \(g(V, a, b) = U\).
-    We see that, for instance, \(V_{i_0} \cap E = U_1\).
-    In fact \(V_{i_0} \subseteq E\), so \(V_{i_0} = U_1\).
-    But we are free to choose the vector spaces between \(0\) and \(V_{i_0}\) however we wish, so we get some degrees of freedom like \(\mathcal{F}_{\delta_0}\), the complete flag variety on \(\mathbb{C}^{\delta_0} \cong V_{i_0} / 0\).
-    Similarly, for every \(j = 1, ..., n + 1\), we can choose the vector spaces between \(V_{i_{j - 1}}\) and \(V_{i_j}\) arbitrarily, so we get degrees of freedom like \(\mathcal{F}_{\delta_{i_j}}\), the complete flag variety on \(\mathbb{C}^{\delta_{i_j}} \cong V_{i_j} / V_{i_{j - 1}}\).
-    Finally, to meet the constraint of \((V, a, b)\) being in \(\mathcal{F}_\delta\), we can choose any \(b \in U_1\) and any \(a\) such that \(\overline{a} \in U_n^\perp\).
-    Thus we get an isomorphism
-    \[g^{-1}(U) \cong \mathcal{F}_{\delta_0} \times \cdots \times \mathcal{F}_{\delta_{n + 1}} \times \mathbb{C}^{\delta_0} \times \mathbb{C}^{\delta_{n + 1}}.\]
-
-\end{proof}
-
-\begin{theorem}
-    The \(\mathcal{F}_\delta\)'s are the irreducible components of \(\mathcal{F}\).
-\end{theorem}
-
-\subsection{In the case that \(X\) is a Jordan block}
-This case seems harder to work with explicitly than the case that \(X\) is zero, so our strategy is to reuse
-
 \section{A different variety}

### 2024-08-19 paper.tex
start reorganizing linear algebra facts
start with irred components

@@
 
-\begin{lemma}
+\begin{lemma}\label{alternative_bs}
     Here we have an alternative characterization of \(B_{I, (\rho_i)}\).
@@
 
-\begin{corollary}
+\begin{corollary}\label{bs_iso}
     \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
@@
 At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
+We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
+\begin{lemma}
+    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties of the form
+    \[\{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
+    There are blah of these, and each has dimension blah.
+\end{lemma}
+\begin{proof}
+    Components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously blah.
+    Their dimensions are blah, and there are... of them.
+    taking image under the isomorphism gives the desired result.
+\end{proof}
+From \cref{bs_iso}, we know that \(B_{I, (\rho_i)}\) is irreducible, of dimension blah.
+
 The irreducible components of \(U_{I, (\rho_i)}\) are blah.
@@
 
-\section{Finding a centralizer}
+\section{Self-contained linear algebra facts}
+\subsection{The centralizer of a nilpotent matrix}
+\begin{definition}
+    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
+    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
+\end{definition}
+\begin{definition}
+    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, only the lower 
+\end{definition}
 For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
@@
 
-\section{A Jordan basis for \(A_{X, a, b}\)}
-
 \subsection{A `normalization' fact about Jordan bases}

### 2024-08-19 paper.tex
reorganize 8

@@
 \section{Finding the irreducible components of \(U_0\)}
+\subsection{Introduction}
 Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
@@
 \end{corollary}
+
+\subsection{Irreducible components of \(U_{I, (\rho_i)}\)}
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
@@
 \begin{lemma}
-    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties of the form
-    \[\{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
-    There are blah of these, and each has dimension blah.
+    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties 
+    \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
+    These are distinct.  
+    There are blah of them, and each has dimension blah.
 \end{lemma}
 \begin{proof}
-    Components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously blah.
+    We know from \cref{bs_iso} that \(B_{I, (\rho_i)}\) is irreducible.
+    So, the components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\).
     Their dimensions are blah, and there are... of them.
@@
 \end{proof}
-From \cref{bs_iso}, we know that \(B_{I, (\rho_i)}\) is irreducible, of dimension blah.
 
-The irreducible components of \(U_{I, (\rho_i)}\) are blah.
-Thus, the irreducible components of \(U_0\) are blah.
+\subsection{Conclusion}
+\begin{lemma}
+    The irreducible components of \(U_0\) are exactly the \(U_{I, (\rho_i), \alpha}\).
+    They are distinct.
+    There are blah of them, each of dimension blah.
+\end{lemma}
 

### 2024-08-19 paper.tex
work on 'preliminaries' section

@@
 
-\section{Springer fibers}
-Let \(G \subseteq \GL_m(\mathbb{C})\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m(\mathbb{C})\) be its Lie algebra.
+\section{Preliminary Definitions and Facts}
+\subsection{Conventions and Notations}
+We write \(\GL_m, \spl_m\) to denote \(\GL_m(\mathbb{C}), \spl_m(\mathbb{C})\), and so on.
+By \(J_m\) we refer to the nilpotent \(m \times m\) Jordan block (which, by convention, has ones \emph{below} the diagonal).
+Given a partition \(\lambda = (\lambda_1, ..., \lambda_k)\), we write \(J(\lambda)\) to denote the block matrix
+\[\begin{pmatrix}
+    J_{\lambda_1} \\
+    & \ddots \\
+    & & J_{\lambda_k}
+\end{pmatrix}.\]
+
+\subsection{Springer fibers}
+Let \(G \subseteq \GL_m\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m\) be its Lie algebra.
+(TODO: either say something interesting about the Lie group, or just get rid of it and talk only about the Lie algebra.)
 % ^I take this scope because it is about what Yuzhou Gu said.
@@
 Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
+We call this the \emph{Springer resolution}.
 For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.
-\par We mention some results about Springer fibers, which we will use later in this paper.
+
+\subsection{Springer fibers in \(\gl_m\)}
+Now we let \(\mathcal{N}\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}\) the variety of Borel subalgebras of \(\gl_m\).
+Let \(H \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
+The variety of Borel subalgebras of \(\gl_m\) is \(\mathcal{B} = \{gHg^{-1} : g \in \GL_m\}\).
+Thus, the Springer fiber at \(X \in \mathcal{N}\) is 
+\[S_X = \{gHg^{-1} : X \in gHg^{-1}\}.\]
+\begin{definition}
+    A \emph{flag} \((V_i)\) of \(\mathbb{C}^m\) is a sequence of subspaces
+    \[0 = V_0 \subseteq V_1 \subseteq \cdots \subseteq V_m = \mathbb{C}^m,\]
+    where \(\dim V_i = i\).
+\end{definition}
+We say that \(X \in \gl_m\) \emph{preserves} a flag \((V_i)\) if \(\forall i. \; XV_i \subseteq V_i\).
+Note that \(X \in \mathcal{N}\) preserves a flag \((V_i)\) if and only if \(\forall i. \; XV_i \subseteq V_{i - 1}\).
+\par The simplest flag is the \emph{standard flag} \((E_i)\), where \(E_i := \langle e_1, ..., e_i \rangle\).
+Note that the group \(H\) is exactly the subset of \(\gl_m\) which preserves \(E_i\).
+\par We can think of \(\mathcal{B}\) as the set of flags of \(\mathbb{C}^m\), via the correspondence 
+\[gHg^{-1} \leftrightarrow (gE_i).\]
+Note that \(X\) preserves \((gE_i)\) if and only if \(X \in gHg^{-1}\).
+Thus, we may write the Springer fiber at \(X \in \mathcal{N}\) in terms of flags, as 
+\[S_X = \{(gE_i) : X \in gHg^{-1}\} = \{(V_i) : \forall i. \; XV_i \subseteq V_{i - 1}\}.\]
+
 \begin{theorem}\label{usual_springer_fiber}
@@
 
-\section{Slodowy slice}
-A basis for \(\spl_2(\mathbb{C})\) is
+\subsection{Slodowy Slices}
+
+A basis for \(\spl_2\) is
 \[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
 Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
-Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (???).
+Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
 If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
@@
 Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(U_{I, (\rho_i)}\).
-(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
 \par So, now we find a Jordan basis for \(A_{0, b}\).

### 2024-08-19 paper.tex
move linalg section
fixup linalg section

@@
 By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.
+
+\section{Some linear algebra facts}
+In this section we prove some facts about linear algebra that will be useful to us later.
+\subsection{The centralizer of a nilpotent matrix}
+\begin{definition}
+    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
+    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
+\end{definition}
+\begin{definition}
+    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, we have \(y_{n - i, j - 1} = 0\) whenever \(i + j \geq \min(m,n)\).
+\end{definition}
+That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the lower-left corner.
+
+\begin{lemma}
+    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition.
+    The centralizer of \(J(\lambda)\) is the set of matrices 
+    \[M = \begin{pmatrix}
+        M_{11} & \cdots & M_{1k}\\
+        \vdots &        & \vdots\\
+        M_{k1} & \cdots & M_{kk}
+    \end{pmatrix},\]
+    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
+\end{lemma}
+\begin{proof}
+    Let 
+    \[M = \begin{pmatrix}
+        M_{11} & \cdots & M_{1k}\\
+        \vdots &        & \vdots\\
+        M_{k1} & \cdots & M_{kk}
+    \end{pmatrix}.\]
+    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
+    \par We have 
+    \[J(\lambda)M = \begin{pmatrix}
+        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
+        \vdots & & \vdots\\
+        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
+    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
+        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
+        \vdots & & \vdots\\
+        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
+    \end{pmatrix}.\]
+    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
+    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
+    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
+\end{proof}
+For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
+\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
+Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
+So, we just have to find 
+\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
+
+It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
+\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
+\[A_{ij} = \begin{pmatrix}
+    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
+\end{pmatrix}.\]
+Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
+\[v_{ij} = \begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
+Now we determine which matrices of this form satisfy \(aA = a\).
+For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
+(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
+\par In the case that \(a = 0\), clearly every \(A\) works.
+Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
+Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
+That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
+This just requires that for each \(j\), we must have 
+\[v_{ij} = \begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
+So, we have now found the set 
+\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
+It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
+\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
+
+\subsection{A `normalization' fact about Jordan bases}
+Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
+Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
+
+\begin{lemma}
+    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+\end{lemma}
+\begin{proof}
+    For any change of basis \(P : V \to V\) commuting with \(A\), we obtain a new Jordan basis \((P(e_{ij}) : i \leq m, j \leq \lambda_i)\).
+    For any such \(P\), define 
+    \[S_P = \sum_i \begin{cases}-1, & \forall j. \; f \circ P(e_{ij}) = 0 \\ \lambda_i - \min\{j : f \circ P(e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
+    Let \(P\) be any operator, among all invertible operators commuting with \(A\), which minimizes \(S_P\).
+    Write \(e_{i,j}' := P(e_{i,j})\).
+    \par Suppose for contradiction that there are two distinct \(i\)'s (and some \(j\)'s) with \(f(e_{ij}') \neq 0\).
+    Then we can take \(e_{i_1, j_1}'\) and \(e_{i_2, j_2}'\), where for \(k \in \{1,2\}\) we have \(f(e_{i_k, j_k}') \neq 0\), and \(\forall j < j_k. \; f(e_{i_k, j}') = 0\).
+    Wlog, assume \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
+    Then, we can define \(Q : V \to V\) by
+    \begin{itemize}
+        \item \(Q(e_{i_1, \lambda_1}') := e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\)
+        \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
+        \item For \(i \neq i_1\), \(Q(e_{ij}') = e_{ij}'\).
+    \end{itemize}
+    Clearly \(Q\) is invertible, and it commutes with \(A\).
+    Further, I claim that \(S_{QP}  < S_P\).
+    It suffices to show that \(\forall j \leq j_1. \; f \circ Q(e_{i_1,j}') = 0\).
+    We have 
+    \[f \circ Q(e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\right)\right) =\]
+    \[f\left(e_{i_1, j}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}'\right) = f(e_{i_1, j}') - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e'_{i_2, j_2 + (j - j_1)}.\]
+    Clearly (by design), this expression is zero when \(j = j_1\).
+    And for \(j < j_1\), we have \(f(e'_{i_1, j}) = f(e'_{i_2, j_2 + (j_2 - j_1)}) = 0\), so it is zero then as well.
+    Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.
+    So there must be at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}') \neq 0\).
+    \par If there is no such \(i\), we have found the desired basis.
+    So, suppose there is such an \(i_0\).
+    Let \(U = \langle e_{i_0, j}' \rangle\).
+    Simply write \(e_j := e_{i_0, j}'\).
+    Let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
+    We just have to change basis to zero out \(e_j\) for \(j \neq j_0\).
+    Let \(P_1(e_{\lambda_{i_0}}) := e_{\lambda_{i_0}} - \frac{f(e_{j_0 + 1})}{f(e_{j_0})} e_{\lambda_{i_0} - 1}\), and notice that \(f \circ P_1(e_j) = 0\) for all \(j \leq j_0 + 1\) except for \(j_0\).
+    Then we define \(P_2(e_{\lambda_{i_0}}) := P_1(e_{\lambda_{i_0}}) - \frac{f\circ P_1(e_{j_0 + 2})}{f\circ P_1(e_{j_0})} e_{\lambda_{i_0} - 2}\), and notice that \(f \circ P_2(e_j) = 0\) for all \(j \leq j_0 + 2\) except for \(j_0\).
+    Eventually we get \(P_{\lambda_{i_0} - j_0}\), and by applying this to the \(e_j\)'s we obtain a basis of \(U\), in which there is exactly one \(j\) with \(f \circ P_{\lambda_{i_0} - j_0}(e_j) \neq 0\).
+\end{proof}
 
@@
 \[\cong \{(\mathfrak{b}, a, b) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{ nilpotent}\}.\]
-We will make one last simplification to this by using a correspondence between Borel subalgebras and complete flags.
-TODO: fix the next few paragraphs, they are out of context.
-\par We have \(\mathcal{M} = \{AHA^{-1} : A \in \GL_{m + n}(\mathbb{C})\}\), where \(H \subseteq \gl_{m + n}(\mathbb{C})\) is the set of upper triangular matrices.
-We say a map \(X : \gl_{m + n} \to \gl_{m + n}\) preserves a flag \(V_0 \subseteq \cdots \subseteq V_{m + n}\) if \(XV_i \subseteq V_i\) for each \(i\).
-Let \(E_0 \subseteq \cdots \subseteq E_{m + n}\) be the standard flag of \(\mathbb{C}^{m + n}\).
-Since \(H\) is the set of \(X\) which preserve \(E\),
-\[\mathcal{M} = \{\{X : \forall i. \; X(AE_i) \subseteq AE_i\} : A \in \GL_n(\mathbb{C})\}.\]
-So, for \(X \in \mathcal{N}\),
-\[\pi^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
+\par Using our correspondence between \(\mathcal{B}_{m + n}\) and complete flags of \(\mathbb{C}^{m + n}\), we obtain 
+\[\pi_{m,n}^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
 
@@
 
-\section{Self-contained linear algebra facts}
-\subsection{The centralizer of a nilpotent matrix}
-\begin{definition}
-    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
-    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
-\end{definition}
-\begin{definition}
-    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, only the lower 
-\end{definition}
-For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
-\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
-Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
-So, we just have to find 
-\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
-We begin by finding 
-\[\{A \in \gl_m : AX = XA\}.\]
-We write the shape of \(X\) as \(\lambda = (\lambda_1, ..., \lambda_k)\), so that 
-\[X = \begin{pmatrix}
-    J_{\lambda_1} & \\
-    & \ddots \\
-    & & J_{\lambda_k}
-\end{pmatrix}.\]
-Then we write \(A\) as the block matrix
-\[A =: \begin{pmatrix}
-    A_{11} & \cdots & A_{1k}\\
-    \vdots & & \vdots\\
-    A_{k1} & \cdots & A_{kk}
-\end{pmatrix},\]
-where \(A_{ij}\) is a block of size \(\lambda_i \times \lambda_j\).
-We have 
-\[XA = \begin{pmatrix}
-    J_{\lambda_1}A_{11} & \cdots & J_{\lambda_1}A_{1k}\\
-    \vdots & & \vdots\\
-    J_{\lambda_k}A_{k1} & \cdots & J_{\lambda_k}A_{kk}
-\end{pmatrix}, \textrm{ and } AX = \begin{pmatrix}
-    A_{11} J_{\lambda_1} & \cdots & A_{1k} J_{\lambda_k}\\
-    \vdots & & \vdots\\
-    A_{k1} J_{\lambda_1} & \cdots & A_{kk} J_{\lambda_k}
-\end{pmatrix}.\]
-So, the constraint that \(XA = AX\) is simply saying that 
-\[\forall i,j. \; J_{\lambda_i} A_{ij} = A_{ij} J_{\lambda_j}.\]
-It's easy to see that left multiplication by \(J_{\lambda_i}\) is just a down-shift by one, and right multiplication by \(J_{\lambda_j}\) is a left-shift by one.
-This means that \(A_{ij}\) is constrained to be a ``lower-left-Toeplitz'' matrix.
-A Toeplitz matrix is one which is constant along diagonal bands: \(\forall ijk. \; x_{ij} = x_{i + k,j + k}\).
-A lower-left-Toeplitz matrix is one which is all zeroes except for the bottom-left corner; that is, the bands start in the bottom-left corner, and continue until hitting the band which includes the lower-right corner or the band which includes the upper-left corner (whichever comes first).
-In other words, an \(n \times m\) lower-left-Toeplitz matrix is one which satisfies \(x_{ij} = 0\) for all \(i,j\) with \(i < j\) and all \(i,j\) with \(i - j < m - n\).
-In yet other words, a matrix is lower-left-Toeplitz if it is Toeplitz, satisfies \(x_{1j} = 0\) for \(j \neq 1\), and satisfies \(x_{in} = 0\) for \(i \neq m\).
-Anyway, it is easy to see that the lower-left-Toeplitz matrices are exactly those matrices \(A\) such that left-shifting \(A\) by one has the same result as down-shifting by one.
-\par So, we have found the set 
-\[C_1 := \{A \in \gl_m : AX = XA\}.\]
-It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
-\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
-\[A_{ij} = \begin{pmatrix}
-    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
-\end{pmatrix}.\]
-Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
-\[v_{ij} = \begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
-Now we determine which matrices of this form satisfy \(aA = a\).
-For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
-(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
-\par In the case that \(a = 0\), clearly every \(A\) works.
-Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
-Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
-That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
-This just requires that for each \(j\), we must have 
-\[v_{ij} = \begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
-So, we have now found the set 
-\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
-It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
-\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
-
-\subsection{A `normalization' fact about Jordan bases}
-Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
-Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
-
-\begin{lemma}
-    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
-\end{lemma}
-\begin{proof}
-    For any change of basis \(P : V \to V\) commuting with \(A\), we obtain a new Jordan basis \((P(e_{ij}) : i \leq m, j \leq \lambda_i)\).
-    For any such \(P\), define 
-    \[S_P = \sum_i \begin{cases}-1, & \forall j. \; f \circ P(e_{ij}) = 0 \\ \lambda_i - \min\{j : f \circ P(e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
-    Let \(P\) be any operator, among all invertible operators commuting with \(A\), which minimizes \(S_P\).
-    Write \(e_{i,j}' := P(e_{i,j})\).
-    \par Suppose for contradiction that there are two distinct \(i\)'s (and some \(j\)'s) with \(f(e_{ij}') \neq 0\).
-    Then we can take \(e_{i_1, j_1}'\) and \(e_{i_2, j_2}'\), where for \(k \in \{1,2\}\) we have \(f(e_{i_k, j_k}') \neq 0\), and \(\forall j < j_k. \; f(e_{i_k, j}') = 0\).
-    Wlog, assume \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
-    Then, we can define \(Q : V \to V\) by
-    \begin{itemize}
-        \item \(Q(e_{i_1, \lambda_1}') := e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\)
-        \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
-        \item For \(i \neq i_1\), \(Q(e_{ij}') = e_{ij}'\).
-    \end{itemize}
-    Clearly \(Q\) is invertible, and it commutes with \(A\).
-    Further, I claim that \(S_{QP}  < S_P\).
-    It suffices to show that \(\forall j \leq j_1. \; f \circ Q(e_{i_1,j}') = 0\).
-    We have 
-    \[f \circ Q(e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\right)\right) =\]
-    \[f\left(e_{i_1, j}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}'\right) = f(e_{i_1, j}') - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e'_{i_2, j_2 + (j - j_1)}.\]
-    Clearly (by design), this expression is zero when \(j = j_1\).
-    And for \(j < j_1\), we have \(f(e'_{i_1, j}) = f(e'_{i_2, j_2 + (j_2 - j_1)}) = 0\), so it is zero then as well.
-    Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.
-    So there must be at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}') \neq 0\).
-    \par If there is no such \(i\), we have found the desired basis.
-    So, suppose there is such an \(i_0\).
-    Let \(U = \langle e_{i_0, j}' \rangle\).
-    Simply write \(e_j := e_{i_0, j}'\).
-    Let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
-    We just have to change basis to zero out \(e_j\) for \(j \neq j_0\).
-    Let \(P_1(e_{\lambda_{i_0}}) := e_{\lambda_{i_0}} - \frac{f(e_{j_0 + 1})}{f(e_{j_0})} e_{\lambda_{i_0} - 1}\), and notice that \(f \circ P_1(e_j) = 0\) for all \(j \leq j_0 + 1\) except for \(j_0\).
-    Then we define \(P_2(e_{\lambda_{i_0}}) := P_1(e_{\lambda_{i_0}}) - \frac{f\circ P_1(e_{j_0 + 2})}{f\circ P_1(e_{j_0})} e_{\lambda_{i_0} - 2}\), and notice that \(f \circ P_2(e_j) = 0\) for all \(j \leq j_0 + 2\) except for \(j_0\).
-    Eventually we get \(P_{\lambda_{i_0} - j_0}\), and by applying this to the \(e_j\)'s we obtain a basis of \(U\), in which there is exactly one \(j\) with \(f \circ P_{\lambda_{i_0} - j_0}(e_j) \neq 0\).
-\end{proof}
-
 \section{A different variety}

### 2024-08-20 paper.tex
fix some linalg stuff; fix principal bundle

@@
 \section{Some linear algebra facts}
-In this section we prove some facts about linear algebra that will be useful to us later.
+In this section we prove linear algebra facts that will be useful later.
 \subsection{The centralizer of a nilpotent matrix}
@@
 That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the lower-left corner.
+In yet other words, only the leftmost \(\min(m,n)\) diagonal bands are nonzero.
 
 \begin{lemma}
-    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition.
-    The centralizer of \(J(\lambda)\) is the set of matrices 
+    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
+    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
     \[M = \begin{pmatrix}
@@
 \begin{lemma}
-    % The map \(\varphi\) is a geometric quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
-    The map \(\varphi\) is some sort of quotient by the action of \(G_{wr}\).
-    % The map \(X \mapsto \overline{\varphi(X \times G)}\) is a bijection from the irreducible components of \(U_{wr}\) to the irreducible components of \(V_{wr}\).
+    The map \(\varphi\) is a principal \(G_{wr}\)-bundle.
 \end{lemma}
 \begin{proof}
-    Let \(y \in V_{wr}\).
+    We need to show that \(G_{wr}\) acts freely and transitively on the fibers of \(\varphi\).
+    It is obvious that \(G_{wr}\) acts freely on \(U_{wr} \times G\); it is enough to note that it acts freely on \(G\).
+    \par Let \(y \in V_{wr}\).
     By definition of \(V_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in U_{wr}\).
     We have
-    \[\varphi^{-1}(y) = \{(x, P) : P \cdot x = y = P_y^{-1} \cdot (P_y \cdot y)\} = \]
-    \[\{(x, P) : x = (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \} = \]
-    \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\} = \] 
-    \[(\textrm{taking } Q := P^{-1}P_y^{-1}, \textrm{ so } P = (QP_y)^{-1} = P_y^{-1} Q^{-1})\]
-    \[\{(Q \cdot (P_y \cdot y), P_y^{-1} Q^{-1}) : Q \in G_{wr}\} = \]
-    \[\{Q \cdot (P_y \cdot y, P_y^{-1}) : Q \in G_{wr}\}.\]
-    So we see that the fibers are exactly the \(G_{wr}\)-orbits.
-    \par Now, what kind of quotient is this?
-    All I need is something that allows me to deduce the dimension of the quotient...
-    Ah, it it a twisted product actually.
-    Each \(G_{wr}\)-orbit is isomorphic to \(G_{wr}\).
-    Given \((y, Q) \in G_{wr} (x, P)\), we send it to \(Q^{-1}P\); given \(Q \in G_{wr}\), we send it to \((Q \cdot x, PQ^{-1})\).
-    These are inverse maps.
+    \begin{align*}
+        \varphi^{-1}(y) = \{(x, P) : P \cdot x = y \} & = \\
+        \{(P^{-1} y, P) : P^{-1} y \in U_{wr} \} & = \\
+        \{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \in U_{wr}\} & .
+    \end{align*}
+    For any \(x \in U_{wr}\) (in particular for \(x = P_y \cdot y\)), we have \(G_{wr} = \{g \in G : g \cdot x \in U_{wr}\}\).
+    Therefore, the fiber above becomes
+    \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\}.\]
+    Setting \(Q := P^{-1} P_y^{-1}\), so that \(P = P_y^{-1} Q^{-1}\), the above becomes
+    \begin{align*}
+        \{(Q \cdot (P_y \cdot y), P_y^{-1} Q^{-1}) : Q \in G_{wr}\} & = \\
+        \{Q \cdot (P_y \cdot y, P_y^{-1}) : Q \in G_{wr}\} & .
+    \end{align*}
+        We see that the fibers are exactly the \(G_{wr}\)-orbits; or in other words, \(G_{wr}\) acts transitively on the fibers, as desired.
     % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.

### 2024-08-20 paper.tex
start rehabilitating normalization proof

@@
 Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
-Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
+% Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
 
 \begin{lemma}
-    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
 \end{lemma}
 \begin{proof}
-    For any change of basis \(P : V \to V\) commuting with \(A\), we obtain a new Jordan basis \((P(e_{ij}) : i \leq m, j \leq \lambda_i)\).
-    For any such \(P\), define 
-    \[S_P = \sum_i \begin{cases}-1, & \forall j. \; f \circ P(e_{ij}) = 0 \\ \lambda_i - \min\{j : f \circ P(e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
-    Let \(P\) be any operator, among all invertible operators commuting with \(A\), which minimizes \(S_P\).
-    Write \(e_{i,j}' := P(e_{i,j})\).
-    \par Suppose for contradiction that there are two distinct \(i\)'s (and some \(j\)'s) with \(f(e_{ij}') \neq 0\).
-    Then we can take \(e_{i_1, j_1}'\) and \(e_{i_2, j_2}'\), where for \(k \in \{1,2\}\) we have \(f(e_{i_k, j_k}') \neq 0\), and \(\forall j < j_k. \; f(e_{i_k, j}') = 0\).
-    Wlog, assume \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
-    Then, we can define \(Q : V \to V\) by
+    For any Jordan basis \((e_{ij})_{ij}\) of \(A\), define
+    \[S((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
+    We proceed by induction on the measure \(S\).
+    That is, let \((e_{ij})_{ij}\) be a Jordan basis for \(A\).
+    Our inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
+    \par Now, we have two cases.
+    In the first case, \((e_{ij})_{ij}\) already satisfies the desired property.
+    In this case we are done.
+    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(f(e_{i_1j_1}) \neq 0\) and \(f(e_{i_2j_2}) \neq 0\).
+    We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
+    Wlog, we assume that \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
+    \par By our inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
+    This is what we do.
+    Define \(e'_{ij}\) as follows.
     \begin{itemize}
-        \item \(Q(e_{i_1, \lambda_1}') := e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\)
+        \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
+        \item CONTINUE HERE
         \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
@@
 Then let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
-\begin{lemma}
+\begin{lemma}\label{bs_union}
     \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) such that \(\rho_i\) and \(\lambda_i - \rho_i\) are both decreasing with \(i\).
-    TODO: something about overlap being small (they're not disjoint).  
-    They are distinct.
-    Is that good enough for my purposes?
-    Ah, I think it is good enough if I instead say that the sets of \(b\)'s are distinct.
 \end{lemma}
@@
     So in either case, both \(p_i > p_j\) and \(q_i > q_j\), and consequently both \(\rho_i > \rho_j\) and \(\lambda_i - \rho_i > \lambda_j - \rho_j\).
+\end{proof}
+
+\begin{lemma}
+    There are blah \(B_{I, (\rho_i)}\) with \((\rho_i)\) satisfying the constraints of \cref{bs_union}, and none is contained in the union of the others.
+\end{lemma}
+\begin{proof}
+    seems hard to count.
+    total number is product over L of (number of rows of length L) times (count where we assume there is only one row of each length).
+
 \end{proof}

### 2024-08-20 paper.tex
continue rehabilitating normalization proof

@@
         \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
-        \item CONTINUE HERE
-        \item For \(j < \lambda_1\), \(Q(e_{i_1, j}') := A^{\lambda_{i_1} - j} Q(e_{i_1, \lambda_{i_1}}')\)
-        \item For \(i \neq i_1\), \(Q(e_{ij}') = e_{ij}'\).
+        \item For \(j < \lambda_1\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\)
+        \item For \(i \neq i_1\), \(e_{ij}' := e_{ij}\).
     \end{itemize}
-    Clearly \(Q\) is invertible, and it commutes with \(A\).
-    Further, I claim that \(S_{QP}  < S_P\).
-    It suffices to show that \(\forall j \leq j_1. \; f \circ Q(e_{i_1,j}') = 0\).
+    Clearly this is a Jordan basis for \(A\).
+    Further, I claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
+    It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).
     We have 
-    \[f \circ Q(e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}'\right)\right) =\]
-    \[f\left(e_{i_1, j}' - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}'\right) = f(e_{i_1, j}') - \frac{f(e'_{i_1, j_1})}{f(e'_{i_2, j_2})} e'_{i_2, j_2 + (j - j_1)}.\]
+    \[f (e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\right)\right) =\]
+    \[f\left(e_{i_1, j} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}\right) = f(e_{i_1, j}) - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} f(e_{i_2, j_2 + (j - j_1)}).\]
     Clearly (by design), this expression is zero when \(j = j_1\).
-    And for \(j < j_1\), we have \(f(e'_{i_1, j}) = f(e'_{i_2, j_2 + (j_2 - j_1)}) = 0\), so it is zero then as well.
+    And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
+    Thus we see that the measure \(S\) of this new basis is smaller, as desired.
+\end{proof}
+
+\begin{lemma}
+    Something else; CONTINUE HERE
+\end{lemma}
+\begin{proof}
     Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.

### 2024-08-20 paper.tex
finish cleaning up normalization proof

@@
 
-\section{Some linear algebra facts}
+\section{Linear Algebra Facts}
 In this section we prove linear algebra facts that will be useful later.
+A reader uninterested in their verification may wish to read the theorem statements and skip ahead to the next section.
+
 \subsection{The centralizer of a nilpotent matrix}
@@
 That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the lower-left corner.
-In yet other words, only the leftmost \(\min(m,n)\) diagonal bands are nonzero.
+In yet other words, all but the leftmost (equivalently, bottommost) \(\min(m,n)\) diagonal bands are zero.
 
@@
 \subsection{A `normalization' fact about Jordan bases}
-Let \(V\) be a finite-dimensional vector space, \(A : V \to V\) a nilpotent operator, and \(f : V \to \mathbb{C}\) a linear map.
-% Let \((e_{ij} : i \leq m, j \leq \lambda_i)\) be a Jordan basis for \(A\).
 
-\begin{lemma}
-    There is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
+\begin{lemma}\label{normalization_helper_one}
+    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
 \end{lemma}
@@
     In this case we are done.
-    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(f(e_{i_1j_1}) \neq 0\) and \(f(e_{i_2j_2}) \neq 0\).
+    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(i_1 \neq i_2\), and \(f(e_{i_1j_1}) \neq 0\), and \(f(e_{i_2j_2}) \neq 0\).
     We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
@@
     And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
-    Thus we see that the measure \(S\) of this new basis is smaller, as desired.
+    Hence the measure \(S\) of this new basis is smaller, as desired.
 \end{proof}
 
-\begin{lemma}
-    Something else; CONTINUE HERE
+\begin{lemma}\label{normalization_helper_two}
+    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \(e_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
 \end{lemma}
 \begin{proof}
-    Thus we see that \(S_{QP} < S_P\), contradicting that \(S_P\) is minimal.
-    So there must be at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}') \neq 0\).
-    \par If there is no such \(i\), we have found the desired basis.
-    So, suppose there is such an \(i_0\).
-    Let \(U = \langle e_{i_0, j}' \rangle\).
-    Simply write \(e_j := e_{i_0, j}'\).
-    Let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
-    We just have to change basis to zero out \(e_j\) for \(j \neq j_0\).
-    Let \(P_1(e_{\lambda_{i_0}}) := e_{\lambda_{i_0}} - \frac{f(e_{j_0 + 1})}{f(e_{j_0})} e_{\lambda_{i_0} - 1}\), and notice that \(f \circ P_1(e_j) = 0\) for all \(j \leq j_0 + 1\) except for \(j_0\).
-    Then we define \(P_2(e_{\lambda_{i_0}}) := P_1(e_{\lambda_{i_0}}) - \frac{f\circ P_1(e_{j_0 + 2})}{f\circ P_1(e_{j_0})} e_{\lambda_{i_0} - 2}\), and notice that \(f \circ P_2(e_j) = 0\) for all \(j \leq j_0 + 2\) except for \(j_0\).
-    Eventually we get \(P_{\lambda_{i_0} - j_0}\), and by applying this to the \(e_j\)'s we obtain a basis of \(U\), in which there is exactly one \(j\) with \(f \circ P_{\lambda_{i_0} - j_0}(e_j) \neq 0\).
+    Let \(e_j\) be a Jordan basis for \(J_n\).
+    If \(\{j : f(e_j) \neq 0\}\) is the empty set, we are done.
+    Otherwise, let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
+    For any Jordan basis \(f_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
+    \[S((f_j)_j) := \begin{cases}
+        -1, & \{j > j_0 : f(e_j) \neq 0\} = \emptyset \\
+        n - \min\{j > j_0 : f(e_j) \neq 0\}, & \textrm{otherwise}
+    \end{cases}.\]
+    We proceed by induction on \(S\).
+    That is, let \((e_j)_j\) be a Jordan basis for \(J_n\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\).
+    Our inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
+    \par We have two cases: either \((e_j)_j\) satisfies the desired property, or not.
+    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \(e_j'\) as follows.
+    \begin{itemize}
+        \item \(e_n' := e_n - \frac{f(e_{j_1})}{f(e_{j_0})} e_{n - (j_1 - j_0)}\)
+        \item For \(j < n\), \(e_j' := J_n^{n - j} e_n'\)
+    \end{itemize}
+    It is straightforward to check that \(j_0 = \min\{j : f(e_j) \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
+    By our inductive hypothesis, we are done.
+\end{proof}
+
+\begin{theorem}\label{normalization}
+    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+\end{theorem}
+\begin{proof}
+    \cref{normalization_helper_one} gives us a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
+    Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
 \end{proof}

### 2024-08-20 paper.tex
started trying to prove alternative characterization of set of bs. found that original definition of set of bs is horrible and unworkable.

@@
 \end{definition}
-That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the lower-left corner.
+That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the entry in the bottom-left corner.
 In yet other words, all but the leftmost (equivalently, bottommost) \(\min(m,n)\) diagonal bands are zero.
@@
 \begin{proof}
-    \cref{normalization_helper_one} gives us a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
+    \cref{normalization_helper_one} provides a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
     Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
@@
 
-\begin{lemma}\label{alternative_bs}
-    Here we have an alternative characterization of \(B_{I, (\rho_i)}\).
-    Namely,
-    \[B_{I, (\rho_i)} = \{b \in \mathbb{C}^m : \forall i \in I. \; p_i = \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
-    \[\textrm{ where } k = ...\}\]
-\end{lemma}
-\begin{proof}
-    TODO
-\end{proof}
-
-\begin{corollary}\label{bs_iso}
-    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
-\end{corollary}
-
-\subsection{Irreducible components of \(U_{I, (\rho_i)}\)}
+\subsection{A study of \(U_{I, (\rho_i)}\)}
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
@@
 
-Let \(\mu\) be the shape of the Jordan basis given in the previous lemma.
+Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
 Let \(X_\mu\) be the Springer fiber at \(J(\mu)\).
@@
 \end{proof}
+
+\subsection{A study of \(B_{I, (\rho_i)}\)}
+Fix any \(I\) and \((\rho_i)\) satisfying the conditions of \cref{bs_union}.
+Define \(\{i_1 < \cdots < i_r\} := I\).
+For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
+Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
+\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
+\begin{lemma}\label{alternative_bs}
+    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
+    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
+    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
+\end{lemma}
+\begin{proof}
+    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
+    Let \(b \in B_{I, (\rho_i)}\).
+    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
+    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
+
+\end{proof}
+
+\begin{corollary}\label{bs_iso}
+    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
+\end{corollary}
+
+\subsection{Conclusion}
 At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
@@
 
-\subsection{Conclusion}
 \begin{lemma}

### 2024-08-20 paper.tex
define set of bs less obnoxiously
write down lemma about set of bs.  should stop making it a lemma and instead make it a definition

@@
 When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
-\par For any \(I \subseteq \{1, ..., k\}\) and any values \((\rho_i)_{i \in I}\) %such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), and (3) \(\lambda_i - \rho_i\) is decreasing with \(i\)
-, define 
-\[B_{I, (\rho_i)} := \{b \in \mathbb{C}^m : \]
-\[\{(p_i, q_i) : i \in I\} = \{(p_i, q_i) : n > q_i \land p_i = \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j \} \] 
-\[\land \forall i \in I. \; p_i = \rho_i \}.\]
+\par For any \(I \subseteq \{1, ..., k\}\) and any map \((i \mapsto \rho_i) : I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\), define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
+\begin{itemize}
+    \item For all \(i \in I\), \(p_i = \rho_i\)
+    \item For all \(i \notin I\), one of the following holds.
+    \begin{itemize}
+        \item \(q_i \geq n\)
+        \item There is an \(i' \in I\) such that \(q_{i'} \leq q_i\) and \(p_{i'} \geq p_i\)
+        \item \(p_i = 0\)
+    \end{itemize}
+\end{itemize}
 Then let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
+
 \begin{lemma}\label{bs_union}
-    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) such that \(\rho_i\) and \(\lambda_i - \rho_i\) are both decreasing with \(i\).
+    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) satisfying the conditions (1),(2),(3),(4).
 \end{lemma}
 \begin{proof}
-    Let \(b \in \mathbb{C}^m\).
+    TODO: redo this proof, now that I changed the definition of \(B_{I, (\rho_i)}\).
+    \par Let \(b \in \mathbb{C}^m\).
     Let \(I' = \{(p_i, q_i) : p_i = n > q_i \land \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j\}\).
@@
 \end{proof}
+
+\subsection{A study of \(B_{I, (\rho_i)}\)}
+Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
+Define \(\{i_1 < \cdots < i_r\} := I\).
+For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
+
+\begin{lemma}\label{bs_fact}
+    For any \(b \in B_{I, (\rho_i)}\) and any \(k \in \{0, ..., r\}\), we have \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
+    \begin{itemize}
+        \item 
+    \end{itemize}
+\end{lemma}
+To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
+\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
+\begin{lemma}\label{alternative_bs}
+    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
+    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
+    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
+\end{lemma}
+\begin{proof}
+    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
+    Let \(b \in B_{I, (\rho_i)}\).
+    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
+    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
+
+\end{proof}
+
+\begin{corollary}\label{bs_iso}
+    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
+\end{corollary}
 
@@
 
-\subsection{A study of \(B_{I, (\rho_i)}\)}
-Fix any \(I\) and \((\rho_i)\) satisfying the conditions of \cref{bs_union}.
-Define \(\{i_1 < \cdots < i_r\} := I\).
-For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
-To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
-Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
-\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
-\begin{lemma}\label{alternative_bs}
-    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
-    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
-    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
-\end{lemma}
-\begin{proof}
-    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
-    Let \(b \in B_{I, (\rho_i)}\).
-    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
-    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
-    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
-
-\end{proof}
-
-\begin{corollary}\label{bs_iso}
-    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
-\end{corollary}
-
 \subsection{Conclusion}

### 2024-08-20 paper.tex
redefine set of bs.  much better now

@@
 When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
-\par For any \(I \subseteq \{1, ..., k\}\) and any map \((i \mapsto \rho_i) : I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\), define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
+\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., k\}\), and let \((\rho_i)_{i \in I}\) be any map \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
+For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
 \begin{itemize}
-    \item For all \(i \in I\), \(p_i = \rho_i\)
-    \item For all \(i \notin I\), one of the following holds.
-    \begin{itemize}
-        \item \(q_i \geq n\)
-        \item There is an \(i' \in I\) such that \(q_{i'} \leq q_i\) and \(p_{i'} \geq p_i\)
-        \item \(p_i = 0\)
+    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
+    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
 \end{itemize}
-\end{itemize}
-Then let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
+Let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
 
@@
 Define \(\{i_1 < \cdots < i_r\} := I\).
-For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
 Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
@@
 \begin{lemma}\label{bs_fact}
-    For any \(b \in B_{I, (\rho_i)}\) and any \(k \in \{0, ..., r\}\), we have \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
     \begin{itemize}

### 2024-08-20 paper.tex
reorganized things to do with the bs.  it's pretty nice. now all i need to do is actually write the proofs.

@@
 \end{itemize}
-Let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
+Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
+\par Let \(U_{I, (\rho_i)} := \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
+The idea here is to show that blah relation holds between U and B.
 
@@
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
-Define \(\{i_1 < \cdots < i_r\} := I\).
-Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
+As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
 
-\begin{lemma}\label{bs_fact}
+\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
+Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
 \begin{itemize}
-        \item 
+    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
+    \item For \(i \notin I\), \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k := \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
 \end{itemize}
-\end{lemma}
-To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
-\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
 \begin{lemma}\label{alternative_bs}
-    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
-    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
-    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
+    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
 \end{lemma}

### 2024-08-21 paper.tex
start on alternative-characterization proof
continue
some notation

@@
 \subsection{Springer fibers in \(\gl_m\)}
-Now we let \(\mathcal{N}\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}\) the variety of Borel subalgebras of \(\gl_m\).
+Now we let \(\mathcal{N}_m\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}_m\) the variety of Borel subalgebras of \(\gl_m\).
 Let \(H \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
@@
 As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+% Now, we also set \(q_{i_{-1}} := 0\), and \(p_{i_0} := \infty\) (just a symbol which is bigger than any integer).
 
@@
     \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
-    \item For \(i \notin I\), \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k := \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
+    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \min S\).
 \end{itemize}
@@
     It is clear that \(\forall i \in I. \; p_i = \rho_i\).
-    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    Now, I claim that for every \(s \in \{0, ..., r\}\), either 
+    So, let \(i \notin I\), and let \(S = \{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    We have two cases: either \(S\) is empty, or not.
+    \par If \(S\) is empty
+
+    and let \(k = \min S\).
     We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
-
+    That is, need to show that \(\)
+    \par Let \(l \in \{0, ..., r\}\), and suppose \(q_i < q_{i_l}\).
+    Then, since \(\max_{j : q_j < q_{i_l}} p_j = p_{i_{l + 1}}\), we have \(p_i \leq p_{i_{l + 1}}\).
+    This implies that 
 \end{proof}

### 2024-08-22 paper.tex
actual progress on alternative characterization of bs

@@
     \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
-    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
     If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
-    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \min S\).
+    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
+    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)...}
 \end{itemize}
@@
     It is clear that \(\forall i \in I. \; p_i = \rho_i\).
+    \par First suppose \(S = \emptyset\).
+    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
+    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
+    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
+    \par Now suppose \(r + 1 \in S\).
+    Then we have \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
+    Then 
+    \par Let \(k \in \{1, ..., r + 1\} \setminus S\).
+    We have \(q_{i_{k - 1}} + p_{i_k} \leq \lambda_i\).
+    Suppose we had \(q_i < q_{i_{k - 1}}\).
+    Then \(p_i \leq \max_{j : q_j < q_{i_{k - 1}}} p_j = p_{i_k}\).
+    But then \(p_i + q_i < q_{i_{k - 1}} + p_{i_k} \leq \lambda_i\), which is nonsense.
+
+    \par There are a few cases: either \(q_i \geq q_{i_0}\), or there's some \(k\) with \(q_{i_{k - 1}} > q_i \geq q_{i_k}\), or else \(q_{i_r} > q_i\).
+    In the case that \(q_i \geq q_{i_0}\) we have \(p_i \leq \lambda_i - q_{i_0}\).
+    In the case that \(q_{i_{k - 1}} > q_i \geq q_{i_{k - 1}}\), we have \(p_i \leq \lambda_i - q_{i_k}\), and also \(p_i \leq \max_{j : q_j < q_{i_{k - 1}}} p_j = p_{i_k}\).
+    That is, \(p_i \leq \min(\lambda_i - q_{i_k}, p_{i_k})\).
+    In the case that \(q_{i_r} > q_i\), we have \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
+    So,
+    \[p_i \leq \max(\lambda_i - q_{i_0}, \max_k \min(\lambda_i - q_{i_k}, p_{i_k}), p_{i_{r + 1}})\]
+
+    For \(s \in \{1, ..., r + 1\}\), we have two cases: either \(q_i < q_{i_s}\), or \(q_i \geq q_{i_s}\).
+
+    then \(p_i \leq \max_{j : q_j < q_{i_s}} p_j = p_{i_{s + 1}}\).
+    So, either \(\)
+
     Now, I claim that for every \(s \in \{0, ..., r\}\), either 

### 2024-08-22 paper.tex
one direction of alternative characterization

--- 2024-08-21 paper.tex
@@
     \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
-    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
+    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
     If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
-    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \min S\).
+    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
+    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)...
+ah, maybe a bit less drastically, I can say something like min(complement of S) instead of max(S)}
 \end{itemize}
@@
     It is clear that \(\forall i \in I. \; p_i = \rho_i\).
-    Now, I claim that for every \(s \in \{0, ..., r\}\), either 
-    So, let \(i \notin I\), and let \(S = \{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
-    We have two cases: either \(S\) is empty, or not.
-    \par If \(S\) is empty
-
-    and let \(k = \min S\).
-    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
-    That is, need to show that \(\)
-    \par Let \(l \in \{0, ..., r\}\), and suppose \(q_i < q_{i_l}\).
-    Then, since \(\max_{j : q_j < q_{i_l}} p_j = p_{i_{l + 1}}\), we have \(p_i \leq p_{i_{l + 1}}\).
-    This implies that 
+    \par First suppose \(S = \emptyset\).
+    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
+    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
+    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
+    \par Now suppose \(r + 1 \in S\).
+    Then \(q_{i_r} = q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
+    Then certainly \(q_i < q_{i_r}\), and therefore \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
+    \par If we are in neither of those cases, let \(k = \max S\).
+    We have \(q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\).
+    Suppose we had \(q_i < q_{i_k}\).
+    Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
+    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which is a contradiction since \(k + 1 \notin S\).
+    Thus \(q_i \geq q_{i_k}\).
+    Now, we have two cases: either \(q_i \geq q_{i_{k - 1}}\), or \(q_i < q_{i_{k - 1}}\).
+    In the second case, we see that \(p_i \leq p_{i_k}\).
+    In the first, recall we also have \(q_{i_{k - 1}} + p_{i_k} > \lambda_i = p_i + q_i\) (since \(k \in S\)), so \(p_{i_k} > p_i\).
+    So, in any case, we have \(q_i \geq q_{i_k}\) and \(p_i \leq p_{i_k}\); or, in other words, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
+    \par Hence \(b \in B'_{I, (\rho_i)}\), and we see that \(B_{I, (\rho_i)} \subseteq B'_{I, (\rho_i)}\).
+    Now we show the opposite inclusion.
+    Let \(b \in B_{I, (\rho_i)}\).
+    Again it is clear that \(\forall i \in I. \; p_i = \rho_i\).
+    \par Let \(k \in \{0, ..., r\}\).
+    I need to show that \(p_{i_{k + 1}} = \max_{j : q_j < q_{i_k}} p_j\).
+    It suffices to show that for every \(i \in I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
+    Agh.  continue here.
 \end{proof}

### 2024-08-23 paper.tex
something
no lie group

@@
 \subsection{Springer fibers}
-Let \(G \subseteq \GL_m\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m\) be its Lie algebra.
-(TODO: either say something interesting about the Lie group, or just get rid of it and talk only about the Lie algebra.)
-% ^I take this scope because it is about what Yuzhou Gu said.
+Let \(\mathfrak{g}\) be a Lie algebra.
 Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
@@
     It suffices to show that for every \(i \in I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
-    Agh.  continue here.
+    First suppose \(k + 1 \in S_i\).
+    Then \(p_i \leq p_{i_{k + 1}}\), by definition of \(S_i\)... (not directly, but basically).
+    Now suppose \(k + 1 \notin S_i\).
+    Then \(q_i \geq ... (something) ... \geq q_{i_k}\).
 \end{proof}
@@
 \begin{corollary}\label{bs_iso}
-    \[B_{I, (\rho_i)} \cong \prod_{i \in I} \mathbb{C}^{blah} \times \prod_{i \notin I}\]
+    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r \mathbb{C}^{\rho_{i_k}} \times \prod_{i \geq q_{i_0}} \mathbb{C}^{\lambda_i - n} \times \prod_{k = 0}^r \prod_{}\mathbb{C}^{}\]
 \end{corollary}

### 2024-08-24 paper.tex
wrote a lot about bs

@@
 \par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
-Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
+\begin{lemma}\label{alternative_bs_one}
+    \(B_{I, (\rho_i)}\) is the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
     \begin{itemize}
-    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
-    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
-    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
-    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
-    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)...
-ah, maybe a bit less drastically, I can say something like min(complement of S) instead of max(S)}
+        \item For all \(k \in \{1, ..., r\}\), \(p_{i_k} = \rho_{i_k}\).
+        \item For all \(i \notin I\),
+        \begin{itemize}
+            \item For all \(k \in \{0, ..., r\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), we have \(q_{i_k} \leq q_i\).
+            \item For all \(k \in \{1, ..., r + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), we have \(p_i \leq p_{i_k}\).
         \end{itemize}
-\begin{lemma}\label{alternative_bs}
-    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
+    \end{itemize}
 \end{lemma}
 \begin{proof}
+    First we show that every element of \(B_{I, (\rho_i)}\) satisfies those conditions.
+    Let \(b \in B_{I, (\rho_i)}\).
+    It is clear that \(\forall k. \; p_{i_k} = \rho_{i_k}\).
+    \par Take \(i \notin I\) and \(k \in \{0, ..., r\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\).
+    Suppose for contradiction that \(q_i < q_{i_k}\).
+    Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
+    Then \(\lambda_i = p_i + q_i < q_{i_k} + p_{i_{k + 1}}\), a contradiction.
+    So we must have \(q_{i_k} \leq q_i\), as desired.
+    \par Now take \(i \notin I\) and \(k \in \{1, ..., r + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\).
+    Suppose for contradiction that \(p_i > p_{i_k}\).
+    Then, putting this together with the first inequality, \(\lambda_i - p_i < q_{i_{k - 1}} + p_{i_k} - p_{i_k}\); that is, \(q_i < q_{i_{k - 1}}\).
+    Consequently, \(p_i \leq \max_{j : q_j < q_{i_{k - 1}}} p_j = p_{i_k}\), as desired.
+    \par Now we have shown that every element of \(B_{I, (\rho_i)}\) satisfies the conditions of the lemma, and we proceed to the converse.
+    Let \(b \in \mathbb{C}^m\) satisfy the conditions.
+    Let \(k \in \{0, ..., r\}\).
+    We need to show that \(\max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
+    Given the conditions (1)--(4) on \(\rho_i\), it suffices to show that for each \(i \notin I\) with \(q_i > q_{i_k}\), we have \(p_i \leq p_{i_{k + 1}}\).
+    Indeed, given \(i \notin I\) with \(q_i > q_{i_k}\), we cannot have \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), as that would imply that \(q_{i_k} \leq q_i\).
+    Hence we must have \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), and consequently \(p_i \leq p_{i_k}\).
+\end{proof}
+
+\begin{corollary}\label{alternative_bs_two}
+    \(B_{I, (\rho_i)}\) is the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
+    \begin{itemize}
+        \item For all \(k \in \{1, ..., r\}\), \(p_{i_k} = \rho_{i_k}\).
+        \item For \(i \notin I\),
+        \begin{itemize}
+            \item If \(\lambda_i \geq q_{i_0} + p_{i_1}\), then \(p_i \leq \lambda_i - q_{i_0}\).
+            \item If there is \(k \in \{0, ..., r\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
+            \item If \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\), then \(p_i \leq p_{i_{r + 1}}\).
+        \end{itemize}
+    \end{itemize}
+\end{corollary}
+\begin{proof}
+
+    We begin by noting that the \(B_{I, (\rho_i)}\) is exactly the set of \(b \in \mathbb{C}^m\) satisfying the following conditions:
+    \begin{itemize}
+        \item For \(i \in I\), \(p_i = \rho_i\).
+        \item For \(i \notin I\), for all \(k \in \{0, ..., r\}\), either \(q_i \geq q_{i_k}\), or else both \(q_i < q_{i_k}\) and \(p_i \leq p_{i_{k + 1}}\).
+    \end{itemize}
+    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
+    Let \(b \in B_{I, (\rho_i)}\).
+    Clearly \(\forall i \in I. \; p_i = \rho_i\).
+    Now, let \(i \notin I\).
+    \begin{itemize}
+        \item First suppose \(\lambda_i \geq q_{i_0} + p_{i_1}\).
+        We cannot have both \(q_i < q_{i_0}\) and \(p_i \leq p_{i_1}\), as this would imply \(\lambda_i = p_i + q_i < p_{i_1} + q_{i_0}\).
+        So, we must have \(q_i \geq q_{i_0}\).
+        \item
+
+    \end{itemize}
+    \par Clearly \(b \in B_{I, (\rho_i)}\) iff for all \(k \in \{0, ..., r\}\) and all \(i \notin I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
+    Let \(i \notin I\).
+    As in the definition of \(B_{I, (\rho_i)}'\), we break into three cases.
+    \begin{itemize}
+        \item First suppose \(\lambda_i \geq q_{i_0} + p_{i_1}\).
+        If \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
+    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
+    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
+    \end{itemize}
     First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
@@
     \par First suppose \(S = \emptyset\).
-    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
-    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
-    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
+    Then if we had \(q_i < q_{i_0}\), 
     \par Now suppose \(r + 1 \in S\).
@@
     Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
-    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which is a contradiction since \(k + 1 \notin S\).
+    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which contradicts that \(p_i + q_i = \lambda_i\).
     Thus \(q_i \geq q_{i_k}\).

### 2024-08-24 paper.tex
deleted stuff about bs

@@
 \begin{proof}
-
-    We begin by noting that the \(B_{I, (\rho_i)}\) is exactly the set of \(b \in \mathbb{C}^m\) satisfying the following conditions:
-    \begin{itemize}
-        \item For \(i \in I\), \(p_i = \rho_i\).
-        \item For \(i \notin I\), for all \(k \in \{0, ..., r\}\), either \(q_i \geq q_{i_k}\), or else both \(q_i < q_{i_k}\) and \(p_i \leq p_{i_{k + 1}}\).
-    \end{itemize}
-    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
-    Let \(b \in B_{I, (\rho_i)}\).
-    Clearly \(\forall i \in I. \; p_i = \rho_i\).
-    Now, let \(i \notin I\).
-    \begin{itemize}
-        \item First suppose \(\lambda_i \geq q_{i_0} + p_{i_1}\).
-        We cannot have both \(q_i < q_{i_0}\) and \(p_i \leq p_{i_1}\), as this would imply \(\lambda_i = p_i + q_i < p_{i_1} + q_{i_0}\).
-        So, we must have \(q_i \geq q_{i_0}\).
-        \item
-
-    \end{itemize}
-    \par Clearly \(b \in B_{I, (\rho_i)}\) iff for all \(k \in \{0, ..., r\}\) and all \(i \notin I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
-    Let \(i \notin I\).
-    As in the definition of \(B_{I, (\rho_i)}'\), we break into three cases.
-    \begin{itemize}
-        \item First suppose \(\lambda_i \geq q_{i_0} + p_{i_1}\).
-        If \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
-    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
-    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
-    \end{itemize}
-    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
-    Let \(b \in B_{I, (\rho_i)}\).
-    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
-    \par First suppose \(S = \emptyset\).
-    Then if we had \(q_i < q_{i_0}\), 
-    \par Now suppose \(r + 1 \in S\).
-    Then \(q_{i_r} = q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
-    Then certainly \(q_i < q_{i_r}\), and therefore \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
-    \par If we are in neither of those cases, let \(k = \max S\).
-    We have \(q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\).
-    Suppose we had \(q_i < q_{i_k}\).
-    Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
-    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which contradicts that \(p_i + q_i = \lambda_i\).
-    Thus \(q_i \geq q_{i_k}\).
-    Now, we have two cases: either \(q_i \geq q_{i_{k - 1}}\), or \(q_i < q_{i_{k - 1}}\).
-    In the second case, we see that \(p_i \leq p_{i_k}\).
-    In the first, recall we also have \(q_{i_{k - 1}} + p_{i_k} > \lambda_i = p_i + q_i\) (since \(k \in S\)), so \(p_{i_k} > p_i\).
-    So, in any case, we have \(q_i \geq q_{i_k}\) and \(p_i \leq p_{i_k}\); or, in other words, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
-    \par Hence \(b \in B'_{I, (\rho_i)}\), and we see that \(B_{I, (\rho_i)} \subseteq B'_{I, (\rho_i)}\).
-    Now we show the opposite inclusion.
-    Let \(b \in B_{I, (\rho_i)}\).
-    Again it is clear that \(\forall i \in I. \; p_i = \rho_i\).
-    \par Let \(k \in \{0, ..., r\}\).
-    I need to show that \(p_{i_{k + 1}} = \max_{j : q_j < q_{i_k}} p_j\).
-    It suffices to show that for every \(i \in I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
-    First suppose \(k + 1 \in S_i\).
-    Then \(p_i \leq p_{i_{k + 1}}\), by definition of \(S_i\)... (not directly, but basically).
-    Now suppose \(k + 1 \notin S_i\).
-    Then \(q_i \geq ... (something) ... \geq q_{i_k}\).
+    Both \(q_{i_k}\) and \(p_{i_k}\) are decreasing as \(k\) increases, so this follows directly from \cref{alternative_bs_one}.
 \end{proof}

### 2024-08-24 paper.tex
finish section about the bs
deletions and another bs proof

@@
 \section{Finding the irreducible components of \(U_0\)}
-\subsection{Introduction}
+\subsection{Setup}
 Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
@@
     \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) satisfying the conditions (1),(2),(3),(4).
+    Further, none of the \(B_{I, (\rho_i)}\) is contained in the union of the others.
 \end{lemma}
 \begin{proof}
-    TODO: redo this proof, now that I changed the definition of \(B_{I, (\rho_i)}\).
-    \par Let \(b \in \mathbb{C}^m\).
-    Let \(I' = \{(p_i, q_i) : p_i = n > q_i \land \max_{j : q_j = q_i} p_j > \max_{j : q_j < q_i} p_j\}\).
-    Then let \(I = \{\max\{i : (p_i, q_i) = (p, q)\} : (p, q) \in I'\}\).
-    Choosing the maximal \(i\) is an arbitrary choice; we just have to pick one.
-    For \(i \in I\), \(\rho_i := p_i\).
-    All we need to do is show that each \(\rho_i\) is positive, and that \(\rho_i\) and \(\lambda_i - \rho_i\) are decreasing.
-    Then we get that \((A_{0,b}, U) \in U_{I, (\rho_i)}\), and we are done.
-    \par Recall that by convention the maximum of the empty set is zero.
-    So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_i = p_i\) is positive.
-    \par Let \(i, j \in I\) with \(i < j\).
-    Since \(\lambda_i \geq \lambda_j\), we have either \(p_i \geq p_j\) or \(q_i \geq q_j\).
-    Further, since \((p_i, q_i) \neq (p_j, q_j)\) (clear from definition of \(I\)), either \(p_i > p_j\) or \(q_i > q_j\).
-    And for \(i, j \in I\) we clearly have \(p_i > p_j \iff q_i > q_j\).
-    So in either case, both \(p_i > p_j\) and \(q_i > q_j\), and consequently both \(\rho_i > \rho_j\) and \(\lambda_i - \rho_i > \lambda_j - \rho_j\).
-\end{proof}
-
-\begin{lemma}
-    There are blah \(B_{I, (\rho_i)}\) with \((\rho_i)\) satisfying the constraints of \cref{bs_union}, and none is contained in the union of the others.
-\end{lemma}
-\begin{proof}
-    seems hard to count.
-    total number is product over L of (number of rows of length L) times (count where we assume there is only one row of each length).
-
+    Let \(b \in \mathbb{C}^m\).
+    If \(\{i : q_{i_0} > q_i\}\) is the empty set, then stop.
+    Otherwise, take any \(i_1 \in \argmax_{i : q_{i_0} > q_i} p_i\), and set \(\rho_{i_1} := p_{i_1}\).
+    If \(\{i : q_{i_1} > q_i\} = \emptyset\), then stop.
+    Otherwise, take any \(i_2 \in \argmax_{i : q_{i_1} > q_i} p_i\), and set \(\rho_{i_2} := p_{i_2}\).
+    Continuing on in this way, eventually we reach a point where \(\{i : q_{i_k} > q_i\} = \emptyset\).
+    Then we set \(I = \{i_1, ..., i_k\}\).
+    Note that \(I, (\rho_i)\) satisfy conditions (1)--(4), and furthermore \(b \in B_{I, (\rho_i)}\).
+    \par Now, we show that no \(B_{I, (\rho_i)}\) is contained in the union of the others.
+    Indeed, fix \(I\) and \((\rho_i)\).
+    Take any \(b \in B_{I, (\rho_i)}\) with \(p_i = \rho_i\) for \(i \in I\) and \(p_i = 0\) for \(i \notin I\).
+    It is clear that \(b \notin B_{I', (\rho_i')}\) whenever \(I' \neq I\) or \((\rho_i') \neq (\rho_i)\).
 \end{proof}
@@
 As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
-% Now, we also set \(q_{i_{-1}} := 0\), and \(p_{i_0} := \infty\) (just a symbol which is bigger than any integer).
 
@@
     Both \(q_{i_k}\) and \(p_{i_k}\) are decreasing as \(k\) increases, so this follows directly from \cref{alternative_bs_one}.
+    (Note that \(p_i \leq \lambda_i - q_{i_k}\) iff \(q_{i_k} \leq q_i\).)
 \end{proof}
@@
 \begin{corollary}\label{bs_iso}
-    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r \mathbb{C}^{\rho_{i_k}} \times \prod_{i \geq q_{i_0}} \mathbb{C}^{\lambda_i - n} \times \prod_{k = 0}^r \prod_{}\mathbb{C}^{}\]
+    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 0}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
 \end{corollary}
+\begin{proof}
+    Here I use the notation \(x \times y = (x, y)\), and so on.
+    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
+    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
+    \[\prod_{k = 0}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
+    \cref{alternative_bs_two} tells us that this is an isomorphism.
+\end{proof}
+
+\begin{corollary}\label{bs_dim}
+    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 0}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
+\end{corollary}
+\begin{proof}
+    Immediate from \cref{bs_iso}.
+\end{proof}
 
@@
 Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
-Let \(X_\mu\) be the Springer fiber at \(J(\mu)\).
+Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
+
+\begin{lemma}
+    For each \(\alpha\), \(\dim X_{\mu, \alpha}\) is blah.
+\end{lemma}
+\begin{proof}
+    CONTINUE HERE
+\end{proof}
 
@@
 We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
-(TODO: why is this a subvariety?  Is it?  Is this even the right way of explaining the significance of the \(m^2\)?)
 We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
@@
 
-\subsection{TODO}
-\begin{itemize}
-    \item Why are SOn flags what they are.
-\end{itemize}
-
 \bibliography{paper}

### 2024-08-24 paper.tex
start with other dimension calculation

@@
 Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
+\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
+We will be interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).
+Let \(s\) be the function taking integer lists to lists which sorts the input in nonincreasing order.
 
 \begin{lemma}
-    For each \(\alpha\), \(\dim X_{\mu, \alpha}\) is blah.
+    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
 \end{lemma}
 \begin{proof}
-    CONTINUE HERE
+    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
+    First we compute
+    \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
+    Now, we have \(s(L) = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}, ...]\).
+    Let \(L' = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., q_{i_2} + p_{i_3}, ..., q_{i_r} + p_{i_{r + 1}}]\).
+    We compute 
+    \[\gamma(s(L)) - \gamma()\]
+    yep and so on
 \end{proof}

### 2024-08-24 paper.tex
start big dimension calculation

@@
     Now, we have \(s(L) = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}, ...]\).
-    Let \(L' = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., q_{i_2} + p_{i_3}, ..., q_{i_r} + p_{i_{r + 1}}]\).
+    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
+    Let \(L'\) be like \(\mu\), but with \(q_{i_x} + p_{i_{x + 1}}\) replaced by \(q_{i_x} + p_{i_x}\); that is,
+    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
     We compute 
-    \[\gamma(s(L)) - \gamma()\]
-    yep and so on
+    \[\gamma(L') - \gamma(\mu) = \sum_{k = 0}^{r - 1} p_{i_{k + 1}} (\#\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_{k + 1}} + p_{i_{k + 2}}\} + 1) = \]
+    \[\sum_{k = 0}^{r - 1} \#\{i : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_{k + 1}} + p_{i_{k + 2}}\}.\]
+    We compute 
+    \[\gamma(s(L')) - \gamma(L') = \]
+    \[q_{i_0} \#\{i \notin I : q_{i_k} + p_{i_1} > \lambda_i \geq q_{i_0} \} - \sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} \lambda_i + \]
+    \[\sum_{k = 0}^s \left[q_{i_k} + p_{i_k}\#\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\} - \sum_{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}} \lambda_i\right] = \]
+    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (q_{i_0} - \lambda_i) + \sum_{k = 0}^s \left[q_{i_k} + \sum_{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}} (p_{i_k} - \lambda_i)\right] = \]
+    \[\sum_{i : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (q_{i_0} - \lambda_i) + \sum_{k = 0}^s \sum_{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}} (p_{i_k} - \lambda_i).\]
+    TODO: there are some errors with the above calculation.
+    \par Now,
+    \begin{align*}
+        \gamma(L) - \gamma(\mu) & = \\
+        [\gamma(L) - \gamma(s(L))] + [\gamma(s(L')) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
+        something
+    \end{align*}
+
 \end{proof}

### 2024-08-24 paper.tex
fix some of dimension calculation

--- 2024-08-24 paper.tex
@@
     \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
-    Now, we have \(s(L) = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}, ...]\).
-    Let \(L' = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., q_{i_2} + p_{i_3}, ..., q_{i_r} + p_{i_{r + 1}}]\).
-    We compute 
-    \[\gamma(s(L)) - \gamma()\]
-    yep and so on
+    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
+    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
+    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
+    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
+    So,
+    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_{k + 1}} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
+    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
+    Now we consider how to get from \(L'\) to \(s(L')\).
+    Sorting \(L'\) just requires shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
+    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
+    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
+    So,
+    \[\gamma(s(L')) - \gamma(L') = \]
+    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
+    TODO: the thing above would be cleaner if \(p_{i_0} := 0\).
+    \par Now,
+    \begin{align*}
+        \gamma(L) - \gamma(\mu) & = \\
+        [\gamma(L) - \gamma(s(L))] + [\gamma(s(L')) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
+        something
+    \end{align*}
+
 \end{proof}

### 2024-08-24 paper.tex
improve dimension calculation

@@
     Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
-    First we compute
-    \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
     Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
@@
     \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
-    Now we consider how to get from \(L'\) to \(s(L')\).
-    Sorting \(L'\) just requires shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
+    Now we consider how to get from \(L'\) to \(L\).
+    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
+    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
+    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
     Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
@@
     So,
-    \[\gamma(s(L')) - \gamma(L') = \]
+    \[\gamma(L) - \gamma(L') = \]
     \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
@@
         \gamma(L) - \gamma(\mu) & = \\
-        [\gamma(L) - \gamma(s(L))] + [\gamma(s(L')) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
-        something
+        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
     \end{align*}    
-
 \end{proof}

### 2024-08-24 paper.tex
move determinant calculation into linalg section
fixup notation in proof of jordan basis, up to the end of 'proof of (1)'

@@
 
+\subsection{A determinant}
+\begin{lemma}
+    Let \(X \in \gl_m\), and let 
+    \[Y = \begin{pmatrix}
+        y_{11} & y_{12} & y_{13} & \cdots & y_{1,n-1} & y_{1n} \\
+        d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
+            & d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
+            & & \ddots & \cdots & \vdots  & \vdots \\
+            & & & d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
+            & & & & d_{n - 1} & y_{nn}
+    \end{pmatrix} \in \gl_n.\]
+    For any \(a, b \in \mathbb{C}^m\),
+    \[\det 
+    \begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y & \\
+       & & &  \\
+       \end{pNiceArray} = \]
+       \[\det X \det Y + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+            & & & \vert \\
+            & X & & b     \\
+            & & & \vert \\
+            \hline 
+        \text{---} & a & \text{---} & 0
+       \end{pNiceArray}\]
+\end{lemma}
+\begin{proof}
+    By induction on \(n\).
+    In the case \(n = 1\), expanding along the last row (taking the usual interpretation of the empty product) gives the desired result.
+    \par Now suppose \(n > 1\).
+    Expanding along the last row, we get 
+    \[d_{n - 1} \det \begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y_{n,n-1} & \\
+       & & &  \\
+       \end{pNiceArray} -
+    y_{nn} \det \begin{pNiceArray}{ccc|ccc}
+        & & & & & \\
+        & X & & & &   \\
+        & & & & & \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y_{n,n} & \\
+       & & &  \\
+       \end{pNiceArray}.\]
+    Using our inductive hypothesis for the first determiniant, and using that \(\det \begin{pNiceArray}{c|c}
+        A_{11} & 0 \\
+        A_{21} & A_{22}
+    \end{pNiceArray} = \det A_{11} \det A_{22}\) for the second, the expression becomes
+    \[d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}\right)
+   - y_{nn} \det X \det Y_{nn} = \]
+   \[(d_{n - 1} Y_{n,n-1} - y_{nn} \det Y_{nn})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray} = \]
+   \[\det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}.\]
+\end{proof}
+
+\begin{corollary}
+    If \(X\) is nilpotent, and
+    \[\begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y & \\
+       & & &  \\
+       \end{pNiceArray}\]
+    is nilpotent  as well, then \(Y\) is nilpotent.
+    If all the \(d_i\) are nonzero, then
+    \[\begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}\]
+   is nilpotent as well.
+    \begin{proof}
+        By the previous lemma, the characteristic polynomial of the big matrix is
+        \[g_X(\lambda) g_Y(\lambda) + f(\lambda),\]
+        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
+    \end{proof}
+\end{corollary}
+
 \section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
@@
 
-\begin{lemma}
-    Let \(X \in \gl_m\), and let 
-    \[Y = \begin{pmatrix}
-        y_{11} & y_{12} & y_{13} & \cdots & y_{1,n-1} & y_{1n} \\
-        d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
-            & d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
-            & & \ddots & \cdots & \vdots  & \vdots \\
-            & & & d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
-            & & & & d_{n - 1} & y_{nn}
-    \end{pmatrix} \in \gl_n.\]
-    For any \(a, b \in \mathbb{C}^m\),
-    \[\det 
-    \begin{pNiceArray}{ccc|ccc}
-        & & & & & \vert \\
-        & X & & & & b    \\
-        & & & & & \vert \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y & \\
-       & & &  \\
-       \end{pNiceArray} = \]
-       \[\det X \det Y + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
-            & & & \vert \\
-            & X & & b     \\
-            & & & \vert \\
-            \hline 
-        \text{---} & a & \text{---} & 0
-       \end{pNiceArray}\]
-\end{lemma}
-\begin{proof}
-    By induction on \(n\).
-    In the case \(n = 1\), expanding along the last row (taking the usual interpretation of the empty product) gives the desired result.
-    \par Now suppose \(n > 1\).
-    Expanding along the last row, we get 
-    \[d_{n - 1} \det \begin{pNiceArray}{ccc|ccc}
-        & & & & & \vert \\
-        & X & & & & b    \\
-        & & & & & \vert \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y_{n,n-1} & \\
-       & & &  \\
-       \end{pNiceArray} -
-    y_{nn} \det \begin{pNiceArray}{ccc|ccc}
-        & & & & & \\
-        & X & & & &   \\
-        & & & & & \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y_{n,n} & \\
-       & & &  \\
-       \end{pNiceArray}.\]
-    Using our inductive hypothesis for the first determiniant, and using that \(\det \begin{pNiceArray}{c|c}
-        A_{11} & 0 \\
-        A_{21} & A_{22}
-    \end{pNiceArray} = \det A_{11} \det A_{22}\) for the second, the expression becomes
-    \[d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray}\right)
-   - y_{nn} \det X \det Y_{nn} = \]
-   \[(d_{n - 1} Y_{n,n-1} - y_{nn} \det Y_{nn})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray} = \]
-   \[\det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray}.\]
-\end{proof}
-
-\begin{corollary}
-    If \(X\) is nilpotent, and
-    \[\begin{pNiceArray}{ccc|ccc}
-        & & & & & \vert \\
-        & X & & & & b    \\
-        & & & & & \vert \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y & \\
-       & & &  \\
-       \end{pNiceArray}\]
-    is nilpotent  as well, then \(Y\) is nilpotent (TODO: and that other determinant is zero).
-    \begin{proof}
-        By the previous lemma, the characteristic polynomial of the big matrix is
-        \[g_X(\lambda) g_Y(\lambda) + f(\lambda),\]
-        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
-    \end{proof}
-\end{corollary}
 \par Now, taking the previous corolloary and the first lemma together, we see that 
@@
 \begin{lemma}
-    Let \(P = \max_{i \in I} \rho_i\), and for \(i \in I\), let \(P_i = \max_{j \in I : j > i} \rho_j\).
     The following vectors give a Jordan basis for \(A_{0,b}\).
@@
         \item For \(i \notin I\), the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\)
-        \item The chain of length \(n + P\) beginning with \(f_n - (A^{n + P}f_n \rightshift n + P)\)
-        \item For \(i \in I\), the chain of length \(q_i + P_i\) beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\), where \(v_i := A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\)
+        \item The chain of length \(n + p_{i_1}\) beginning with \(f_n - (A^{n + p_{i_1}}f_n \rightshift n + p_{i_1})\)
+        \item For \(k \in \{1, ..., r\}\), the chain of length \(q_{i_k} + p_{i_{k + 1}}\) beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\), where \(v_{i_k} := A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i,l + q_{i_k}}\)
     \end{itemize}
@@
     There are three things to check: (1) the chains are no longer than their claimed lengths, (2) the claimed lengths sum to \(m + n\), and (3) the span of the chains is \(\mathbb{C}^{m + n}\).
-    \par We have defined \(P\) and \(P_i\) in terms of the \(\rho_i\) to make it clear that they only depend on \(I\) and the \(\rho_i\).
-    Now we provide more useful characterizations.
-    It is immediate from the definition of \(U_{I, (\rho_i)}\) that \(P = \max_{l : q_l < n} p_l\), and \(P_i = \max_{l : q_l < q_i} p_l\).
     \begin{proof}[Proof of (1)]
         It is obvious that a chain beginning with \(e_{i, p_i + q_i}\) has length \(p_i + q_i\).
-        \par Now consider the chain beginning with \(f_n - (A^{n + P} f_n \rightshift n + P)\).
-        Note that \(A^n f_n = b\), so \(A^{n + P} f_n = A^P b = b \leftshift P\).
-        By shifting \(b\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n\).
-        This ensures that the operation of shifting \(b \leftshift P\) right \(n + P\) times is invertible by shifting left \(n + P\) times.
+        \par Now consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).
+        Note that \(A^n f_n = b\), so \(A^{n + p_{i_1}} f_n = A^{p_{i_1}} b = b \leftshift p_{i_1}\).
+        By shifting \(b\) left \(p_{i_1}\) times, we zero out all the rows \(i\) where \(q_i < n\).
+        This ensures that the operation of shifting \(b \leftshift p_{i_1}\) right \(n + p_{i_1}\) times is invertible by shifting left \(n + p_{i_1}\) times.
         That is,
-        \[A^{n + P} f_n = b \leftshift P = ((b \leftshift P) \rightshift n + P) \leftshift n + P = A^{n + P}(A^{n + P}f_n \rightshift n + P).\]
-        This shows that the chain has length at most \(n + P\), as desired.
-        \par Now, let \(i \in I\).
-        We have \(v_i = A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\).
-        First we note that \(q_i < n\) by the definition of \(U_{I, (\rho_i)}\), so the definition of \(v_i\) makes sense.
-        We consider the chain beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\).
-        Note that \(A^{q_i} v_i\) is just \(b\) with row \(i\) zeroed out.
-        For brevity, we write \(b_i := A^{q_i} v_i\).
-        Note that \(b_i \leftshift P_i\) has rows \(l\) zeroed out, for all \(l\) with \(q_l < q_i\).
-        This ensures that shifting \(b_i \leftshift P_i\) right \(q_i + P_i\) times can be inverted by shifting left \(q_i + P_i\) times.
+        \begin{align*}
+            A^{n + p_{i_1}} f_n & = \\
+            b \leftshift p_{i_1} & = \\
+            ((b \leftshift p_{i_1}) \rightshift n + p_{i_1}) \leftshift n + p_{i_1} & = \\
+            A^{n + p_{i_1}}(A^{n + p_{i_1}}f_n \rightshift n + p_{i_1}) & .
+        \end{align*}
+        This shows that the chain has length at most \(n + p_{i_1}\), as desired.
+        \par Now, let \(k \in \{1, ..., r\}\).
+        We have \(v_{i_k} = A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}}\).
+        First we note that \(q_{i_k} < n\) by the definition of \(U_{I, (\rho_i)}\), so the definition of \(v_{i_k}\) makes sense.
+        We consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
+        Note that \(A^{q_{i_k}} v_{i_k}\) is just \(b\) with row \(i_k\) zeroed out.
+        For brevity, we write \(b_{i_k} := A^{q_{i_k}} v_{i_k}\).
+        Note that \(b_{i_k} \leftshift p_{i_{k + 1}}\) has rows \(l\) zeroed out, for all \(l\) with \(q_l < q_{i_k}\).
+        This ensures that shifting \(b_{i_k} \leftshift p_{i_{k + 1}}\) right \(q_{i_k} + p_{i_{k + 1}}\) times can be inverted by shifting left \(q_{i_k} + p_{i_{k + 1}}\) times.
         That is,
-        \[A^{q_i + P_i} v_i = b_i \leftshift P_i = ((b_i \leftshift P_i) \rightshift q_i + P_i) \leftshift q_i + P_i = A^{q_i + P_i}(A^{q_i + P_i} v_i \rightshift q_i + P_i).\]
-        This shows that the chain has length at most \(q_i + P_i\), as desired.
+        \begin{align*}
+            A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} & = \\
+            b_{i_k} \leftshift p_{i_{k + 1}} & = \\
+            ((b_{i_k} \leftshift p_{i_{k + 1}}) \rightshift q_{i_k} + p_{i_{k + 1}}) \leftshift q_{i_k} + p_{i_{k + 1}} & = \\
+            A^{q_{i_k} + p_{i_{k + 1}}}(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}}) & .
+        \end{align*}
+        This shows that the chain has length at most \(q_{i_k} + p_{i_{k + 1}}\), as desired.
     \end{proof}

### 2024-08-25 paper.tex
more about dimensions

@@
             \item If \(\lambda_i \geq q_{i_0} + p_{i_1}\), then \(p_i \leq \lambda_i - q_{i_0}\).
-            \item If there is \(k \in \{0, ..., r\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
+            \item If there is \(k \in \{1, ..., r\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
             \item If \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\), then \(p_i \leq p_{i_{r + 1}}\).
@@
 \begin{corollary}\label{bs_iso}
-    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 0}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
+    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
 \end{corollary}
@@
     \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
-    \[\prod_{k = 0}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
+    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
     \cref{alternative_bs_two} tells us that this is an isomorphism.
@@
 \begin{corollary}\label{bs_dim}
-    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 0}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
+    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
 \end{corollary}
@@
 \begin{lemma}
-    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
+    \[\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
+    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
 \end{lemma}
@@
     So,
-    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_{k + 1}} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
+    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
     \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
@@
     \[\gamma(L) - \gamma(L') = \]
-    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
-    TODO: the thing above would be cleaner if \(p_{i_0} := 0\).
+    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
     \par Now,
@@
         [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
+        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
+        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
+        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
+        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
+        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
     \end{align*}    
@@
 
-\begin{lemma}
+\begin{lemma}\label{u_i_rho_iso}
     \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
@@
     \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
+\end{proof}
+
+\begin{corollary}\label{u_i_rho_irred_and_dim}
+    The 
+    \(U_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
+\end{corollary}
+\begin{proof}
+    Irreducibility follows from \cref{u_i_rho_iso}, since \(B_{I, (\rho_i)}\) is irreducible (by \cref{bs_iso}), as is \(X_\mu\).
+    To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_\mu\).
+    The dimension of \(X_\mu\) is 
 \end{proof}

### 2024-08-25 paper.tex
some introduction

@@
 Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
+\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
+The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
+Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
+The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
+Let
+\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
+\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
+We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
+\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
+We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
+Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
+Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
+We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
+Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
+(It turns out that this map is surjective.)
+Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
+Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 
@@
     \end{itemize}
-    It is straightforward to check that \(j_0 = \min\{j : f(e_j) \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
+    It is straightforward to check that \(j_0 = \min\{j : f(e_j') \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
     By our inductive hypothesis, we are done.
@@
 \par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
-We will be interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).
-Let \(s\) be the function taking integer lists to lists which sorts the input in nonincreasing order.
+We are interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).
 
@@
     Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
-    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
+    To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
     So,

### 2024-08-26 paper.tex
more of intro and organization

@@
 Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par In this paper we will study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 
@@
 
-\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
-\par Let
-\[e = \begin{pNiceArray}{ccccc}
- 0 \\
-    1 & 0 \\
-  & 1 & \ddots \\
-   & & \ddots & 0 \\
-   &   &  & 1 & 0
-   \end{pNiceArray} \in \mathfrak{gl}_{n},\]
-and let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
-We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
-First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).
-
+\section{Principal \(\spl_2\)-triple in \(\gl_n\)}
+The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
+In this section we use this to find that there is a unique principal \(\spl_2\)-triple in \(\gl_n\).
+Write \(e = J_n\).
 \begin{lemma}\label{simple_sl2_triple}
@@
 \end{proof}
+
+\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
+TODO: I am unsure why this section is interesting or what to say about it.
+Should I delete it?
+For now I will ignore it and try to make the paper flow nicely without it.
+
+Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
+We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
+% First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).
 
@@
 
-\section{A different variety}
+\section{The components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
 Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).

### 2024-08-26 paper.tex
more of intro

@@
 The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
+The main section of this paper will study the fibers of this map.
+Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
 
@@
 \section{Linear Algebra Facts}
-In this section we prove linear algebra facts that will be useful later.
-A reader uninterested in their verification may wish to read the theorem statements and skip ahead to the next section.
+In this section we prove linear algebra facts that will be used later.
+They are proved in this section to avoid interrupting the flow of the remainder of the paper.
 

### 2024-08-26 paper.tex
comment out section

@@
 
-\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
-TODO: I am unsure why this section is interesting or what to say about it.
-Should I delete it?
-For now I will ignore it and try to make the paper flow nicely without it.
-
-Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
-We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
-% First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).
-
-\begin{lemma}\label{sl2_triple}
-    There is exactly one way to choose \(H, F \in \gl_{m + n}\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
-\end{lemma}
-\begin{proof}
-Suppose we have \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
-Writing \(F =: \begin{pmatrix}
-    F_{11} & F_{12} \\
-    F_{21} & f
-\end{pmatrix}\), and similarly for \(H\), we have
-\[2E = [H, E] = \begin{pmatrix}
-    0 & H_{12}e \\
-    0 & he
-\end{pmatrix} - \begin{pmatrix}
-    0 & 0 \\
-    e H_{21} & eh
-\end{pmatrix},\]
-\[H = [E, F] = \begin{pmatrix}
-    0 & 0 \\
-    e F_{21} & ef
-\end{pmatrix} - \begin{pmatrix}
-    0 & F_{12}e \\
-    0 & fe
-\end{pmatrix}.\]
-From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in \cref{simple_sl2_triple}.
-We also see that \(H_{11} = 0\).
-Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
-% Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
-Then our final constraint is that 
-\[-2F = [H, F] = \]
-\[\begin{pmatrix}
-    H_{12} F_{21} & H_{12} F_{22} \\
-    H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
-\end{pmatrix} - \begin{pmatrix}
-    F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
-    F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
-\end{pmatrix}.\]
-Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
-Substituting in the equation above then,
-\[-2F = \begin{pmatrix}
-    F_{12} e F_{21} & F_{12}e f \\
-    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
-\end{pmatrix} - \begin{pmatrix}
-    F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
-    f eF_{21} & F_{21} F_{12}e + fh
-\end{pmatrix} =\]
-\[\begin{pmatrix}
-    0 & F_{12}(fe + h) \\
-    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
-\end{pmatrix} - \begin{pmatrix}
-    0 & F_{11} F_{12}e + F_{12} h \\
-    (ef - h)F_{21} & F_{21} F_{12}e + fh
-\end{pmatrix} =\]
-\[\begin{pmatrix}
-    0 & F_{12}fe \\
-    eF_{21} F_{11} & eF_{21} F_{12} + hf
-\end{pmatrix} - \begin{pmatrix}
-    0 & F_{11} F_{12}e \\
-    ef F_{21} & F_{21} F_{12}e + fh
-\end{pmatrix}.\]
-Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
-This shows that \(H_{12} = H_{21} = 0\).
-We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
-\end{proof}
+% \section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
+% TODO: I am unsure why this section is interesting or what to say about it.
+% Should I delete it?
+% For now I will ignore it and try to make the paper flow nicely without it.
+
+% Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
+% We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
+% % First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).
+
+% \begin{lemma}\label{sl2_triple}
+%     There is exactly one way to choose \(H, F \in \gl_{m + n}\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
+% \end{lemma}
+% \begin{proof}
+% Suppose we have \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
+% Writing \(F =: \begin{pmatrix}
+%     F_{11} & F_{12} \\
+%     F_{21} & f
+% \end{pmatrix}\), and similarly for \(H\), we have
+% \[2E = [H, E] = \begin{pmatrix}
+%     0 & H_{12}e \\
+%     0 & he
+% \end{pmatrix} - \begin{pmatrix}
+%     0 & 0 \\
+%     e H_{21} & eh
+% \end{pmatrix},\]
+% \[H = [E, F] = \begin{pmatrix}
+%     0 & 0 \\
+%     e F_{21} & ef
+% \end{pmatrix} - \begin{pmatrix}
+%     0 & F_{12}e \\
+%     0 & fe
+% \end{pmatrix}.\]
+% From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in \cref{simple_sl2_triple}.
+% We also see that \(H_{11} = 0\).
+% Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
+% % Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
+% Then our final constraint is that 
+% \[-2F = [H, F] = \]
+% \[\begin{pmatrix}
+%     H_{12} F_{21} & H_{12} F_{22} \\
+%     H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
+% \end{pmatrix} - \begin{pmatrix}
+%     F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
+%     F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
+% \end{pmatrix}.\]
+% Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
+% Substituting in the equation above then,
+% \[-2F = \begin{pmatrix}
+%     F_{12} e F_{21} & F_{12}e f \\
+%     eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
+% \end{pmatrix} - \begin{pmatrix}
+%     F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
+%     f eF_{21} & F_{21} F_{12}e + fh
+% \end{pmatrix} =\]
+% \[\begin{pmatrix}
+%     0 & F_{12}(fe + h) \\
+%     eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
+% \end{pmatrix} - \begin{pmatrix}
+%     0 & F_{11} F_{12}e + F_{12} h \\
+%     (ef - h)F_{21} & F_{21} F_{12}e + fh
+% \end{pmatrix} =\]
+% \[\begin{pmatrix}
+%     0 & F_{12}fe \\
+%     eF_{21} F_{11} & eF_{21} F_{12} + hf
+% \end{pmatrix} - \begin{pmatrix}
+%     0 & F_{11} F_{12}e \\
+%     ef F_{21} & F_{21} F_{12}e + fh
+% \end{pmatrix}.\]
+% Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
+% This shows that \(H_{12} = H_{21} = 0\).
+% We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
+% \end{proof}
 

### 2024-08-26 paper.tex
move linalg section

@@
 By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.
-
-\section{Linear Algebra Facts}
-In this section we prove linear algebra facts that will be used later.
-They are proved in this section to avoid interrupting the flow of the remainder of the paper.
-
-\subsection{The centralizer of a nilpotent matrix}
-\begin{definition}
-    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
-    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
-\end{definition}
-\begin{definition}
-    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, we have \(y_{n - i, j - 1} = 0\) whenever \(i + j \geq \min(m,n)\).
-\end{definition}
-That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the entry in the bottom-left corner.
-In yet other words, all but the leftmost (equivalently, bottommost) \(\min(m,n)\) diagonal bands are zero.
-
-\begin{lemma}
-    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
-    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
-    \[M = \begin{pmatrix}
-        M_{11} & \cdots & M_{1k}\\
-        \vdots &        & \vdots\\
-        M_{k1} & \cdots & M_{kk}
-    \end{pmatrix},\]
-    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
-\end{lemma}
-\begin{proof}
-    Let 
-    \[M = \begin{pmatrix}
-        M_{11} & \cdots & M_{1k}\\
-        \vdots &        & \vdots\\
-        M_{k1} & \cdots & M_{kk}
-    \end{pmatrix}.\]
-    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
-    \par We have 
-    \[J(\lambda)M = \begin{pmatrix}
-        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
-        \vdots & & \vdots\\
-        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
-    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
-        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
-        \vdots & & \vdots\\
-        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
-    \end{pmatrix}.\]
-    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
-    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
-    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
-\end{proof}
-For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
-\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
-Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
-So, we just have to find 
-\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
-
-It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
-\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
-\[A_{ij} = \begin{pmatrix}
-    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
-\end{pmatrix}.\]
-Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
-\[v_{ij} = \begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
-Now we determine which matrices of this form satisfy \(aA = a\).
-For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
-(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
-\par In the case that \(a = 0\), clearly every \(A\) works.
-Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
-Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
-That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
-This just requires that for each \(j\), we must have 
-\[v_{ij} = \begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
-So, we have now found the set 
-\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
-It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
-\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
-
-\subsection{A `normalization' fact about Jordan bases}
-
-\begin{lemma}\label{normalization_helper_one}
-    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
-\end{lemma}
-\begin{proof}
-    For any Jordan basis \((e_{ij})_{ij}\) of \(A\), define
-    \[S((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
-    We proceed by induction on the measure \(S\).
-    That is, let \((e_{ij})_{ij}\) be a Jordan basis for \(A\).
-    Our inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
-    \par Now, we have two cases.
-    In the first case, \((e_{ij})_{ij}\) already satisfies the desired property.
-    In this case we are done.
-    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(i_1 \neq i_2\), and \(f(e_{i_1j_1}) \neq 0\), and \(f(e_{i_2j_2}) \neq 0\).
-    We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
-    Wlog, we assume that \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
-    \par By our inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
-    This is what we do.
-    Define \(e'_{ij}\) as follows.
-    \begin{itemize}
-        \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
-        \item For \(j < \lambda_1\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\)
-        \item For \(i \neq i_1\), \(e_{ij}' := e_{ij}\).
-    \end{itemize}
-    Clearly this is a Jordan basis for \(A\).
-    Further, I claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
-    It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).
-    We have 
-    \[f (e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\right)\right) =\]
-    \[f\left(e_{i_1, j} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}\right) = f(e_{i_1, j}) - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} f(e_{i_2, j_2 + (j - j_1)}).\]
-    Clearly (by design), this expression is zero when \(j = j_1\).
-    And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
-    Hence the measure \(S\) of this new basis is smaller, as desired.
-\end{proof}
-
-\begin{lemma}\label{normalization_helper_two}
-    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \(e_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
-\end{lemma}
-\begin{proof}
-    Let \(e_j\) be a Jordan basis for \(J_n\).
-    If \(\{j : f(e_j) \neq 0\}\) is the empty set, we are done.
-    Otherwise, let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
-    For any Jordan basis \(f_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
-    \[S((f_j)_j) := \begin{cases}
-        -1, & \{j > j_0 : f(e_j) \neq 0\} = \emptyset \\
-        n - \min\{j > j_0 : f(e_j) \neq 0\}, & \textrm{otherwise}
-    \end{cases}.\]
-    We proceed by induction on \(S\).
-    That is, let \((e_j)_j\) be a Jordan basis for \(J_n\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\).
-    Our inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
-    \par We have two cases: either \((e_j)_j\) satisfies the desired property, or not.
-    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \(e_j'\) as follows.
-    \begin{itemize}
-        \item \(e_n' := e_n - \frac{f(e_{j_1})}{f(e_{j_0})} e_{n - (j_1 - j_0)}\)
-        \item For \(j < n\), \(e_j' := J_n^{n - j} e_n'\)
-    \end{itemize}
-    It is straightforward to check that \(j_0 = \min\{j : f(e_j') \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
-    By our inductive hypothesis, we are done.
-\end{proof}
-
-\begin{theorem}\label{normalization}
-    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
-\end{theorem}
-\begin{proof}
-    \cref{normalization_helper_one} provides a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
-    Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
-\end{proof}
-
-\subsection{A determinant}
-\begin{lemma}
-    Let \(X \in \gl_m\), and let 
-    \[Y = \begin{pmatrix}
-        y_{11} & y_{12} & y_{13} & \cdots & y_{1,n-1} & y_{1n} \\
-        d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
-            & d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
-            & & \ddots & \cdots & \vdots  & \vdots \\
-            & & & d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
-            & & & & d_{n - 1} & y_{nn}
-    \end{pmatrix} \in \gl_n.\]
-    For any \(a, b \in \mathbb{C}^m\),
-    \[\det 
-    \begin{pNiceArray}{ccc|ccc}
-        & & & & & \vert \\
-        & X & & & & b    \\
-        & & & & & \vert \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y & \\
-       & & &  \\
-       \end{pNiceArray} = \]
-       \[\det X \det Y + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
-            & & & \vert \\
-            & X & & b     \\
-            & & & \vert \\
-            \hline 
-        \text{---} & a & \text{---} & 0
-       \end{pNiceArray}\]
-\end{lemma}
-\begin{proof}
-    By induction on \(n\).
-    In the case \(n = 1\), expanding along the last row (taking the usual interpretation of the empty product) gives the desired result.
-    \par Now suppose \(n > 1\).
-    Expanding along the last row, we get 
-    \[d_{n - 1} \det \begin{pNiceArray}{ccc|ccc}
-        & & & & & \vert \\
-        & X & & & & b    \\
-        & & & & & \vert \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y_{n,n-1} & \\
-       & & &  \\
-       \end{pNiceArray} -
-    y_{nn} \det \begin{pNiceArray}{ccc|ccc}
-        & & & & & \\
-        & X & & & &   \\
-        & & & & & \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y_{n,n} & \\
-       & & &  \\
-       \end{pNiceArray}.\]
-    Using our inductive hypothesis for the first determiniant, and using that \(\det \begin{pNiceArray}{c|c}
-        A_{11} & 0 \\
-        A_{21} & A_{22}
-    \end{pNiceArray} = \det A_{11} \det A_{22}\) for the second, the expression becomes
-    \[d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray}\right)
-   - y_{nn} \det X \det Y_{nn} = \]
-   \[(d_{n - 1} Y_{n,n-1} - y_{nn} \det Y_{nn})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray} = \]
-   \[\det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray}.\]
-\end{proof}
-
-\begin{corollary}
-    If \(X\) is nilpotent, and
-    \[\begin{pNiceArray}{ccc|ccc}
-        & & & & & \vert \\
-        & X & & & & b    \\
-        & & & & & \vert \\
-       \hline
-       \text{---} & a & \text{---} &  \\
-       & & & & Y & \\
-       & & &  \\
-       \end{pNiceArray}\]
-    is nilpotent  as well, then \(Y\) is nilpotent.
-    If all the \(d_i\) are nonzero, then
-    \[\begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray}\]
-   is nilpotent as well.
-    \begin{proof}
-        By the previous lemma, the characteristic polynomial of the big matrix is
-        \[g_X(\lambda) g_Y(\lambda) + f(\lambda),\]
-        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
-    \end{proof}
-\end{corollary}
 
@@
 
+\section{Linear Algebra Facts}
+In this section we prove linear algebra facts that were used in the paper.
+They are confined to this section to avoid interrupting the flow of the paper.
+
+\subsection{The centralizer of a nilpotent matrix}
+\begin{definition}
+    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
+    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
+\end{definition}
+\begin{definition}
+    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, we have \(y_{n - i, j - 1} = 0\) whenever \(i + j \geq \min(m,n)\).
+\end{definition}
+That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the entry in the bottom-left corner.
+In yet other words, all but the leftmost (equivalently, bottommost) \(\min(m,n)\) diagonal bands are zero.
+
+\begin{lemma}
+    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
+    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
+    \[M = \begin{pmatrix}
+        M_{11} & \cdots & M_{1k}\\
+        \vdots &        & \vdots\\
+        M_{k1} & \cdots & M_{kk}
+    \end{pmatrix},\]
+    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
+\end{lemma}
+\begin{proof}
+    Let 
+    \[M = \begin{pmatrix}
+        M_{11} & \cdots & M_{1k}\\
+        \vdots &        & \vdots\\
+        M_{k1} & \cdots & M_{kk}
+    \end{pmatrix}.\]
+    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
+    \par We have 
+    \[J(\lambda)M = \begin{pmatrix}
+        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
+        \vdots & & \vdots\\
+        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
+    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
+        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
+        \vdots & & \vdots\\
+        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
+    \end{pmatrix}.\]
+    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
+    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
+    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
+\end{proof}
+For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
+\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
+Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
+So, we just have to find 
+\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
+
+It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
+\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
+\[A_{ij} = \begin{pmatrix}
+    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
+\end{pmatrix}.\]
+Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
+\[v_{ij} = \begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
+Now we determine which matrices of this form satisfy \(aA = a\).
+For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
+(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
+\par In the case that \(a = 0\), clearly every \(A\) works.
+Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
+Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
+That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
+This just requires that for each \(j\), we must have 
+\[v_{ij} = \begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
+So, we have now found the set 
+\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
+It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
+\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
+    0\\
+    v_{ij}'
+\end{pmatrix},\]
+where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
+
+\subsection{A `normalization' fact about Jordan bases}
+
+\begin{lemma}\label{normalization_helper_one}
+    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
+\end{lemma}
+\begin{proof}
+    For any Jordan basis \((e_{ij})_{ij}\) of \(A\), define
+    \[S((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
+    We proceed by induction on the measure \(S\).
+    That is, let \((e_{ij})_{ij}\) be a Jordan basis for \(A\).
+    Our inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
+    \par Now, we have two cases.
+    In the first case, \((e_{ij})_{ij}\) already satisfies the desired property.
+    In this case we are done.
+    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(i_1 \neq i_2\), and \(f(e_{i_1j_1}) \neq 0\), and \(f(e_{i_2j_2}) \neq 0\).
+    We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
+    Wlog, we assume that \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
+    \par By our inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
+    This is what we do.
+    Define \(e'_{ij}\) as follows.
+    \begin{itemize}
+        \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
+        \item For \(j < \lambda_1\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\)
+        \item For \(i \neq i_1\), \(e_{ij}' := e_{ij}\).
+    \end{itemize}
+    Clearly this is a Jordan basis for \(A\).
+    Further, I claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
+    It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).
+    We have 
+    \[f (e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\right)\right) =\]
+    \[f\left(e_{i_1, j} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}\right) = f(e_{i_1, j}) - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} f(e_{i_2, j_2 + (j - j_1)}).\]
+    Clearly (by design), this expression is zero when \(j = j_1\).
+    And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
+    Hence the measure \(S\) of this new basis is smaller, as desired.
+\end{proof}
+
+\begin{lemma}\label{normalization_helper_two}
+    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \(e_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
+\end{lemma}
+\begin{proof}
+    Let \(e_j\) be a Jordan basis for \(J_n\).
+    If \(\{j : f(e_j) \neq 0\}\) is the empty set, we are done.
+    Otherwise, let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
+    For any Jordan basis \(f_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
+    \[S((f_j)_j) := \begin{cases}
+        -1, & \{j > j_0 : f(e_j) \neq 0\} = \emptyset \\
+        n - \min\{j > j_0 : f(e_j) \neq 0\}, & \textrm{otherwise}
+    \end{cases}.\]
+    We proceed by induction on \(S\).
+    That is, let \((e_j)_j\) be a Jordan basis for \(J_n\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\).
+    Our inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
+    \par We have two cases: either \((e_j)_j\) satisfies the desired property, or not.
+    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \(e_j'\) as follows.
+    \begin{itemize}
+        \item \(e_n' := e_n - \frac{f(e_{j_1})}{f(e_{j_0})} e_{n - (j_1 - j_0)}\)
+        \item For \(j < n\), \(e_j' := J_n^{n - j} e_n'\)
+    \end{itemize}
+    It is straightforward to check that \(j_0 = \min\{j : f(e_j') \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
+    By our inductive hypothesis, we are done.
+\end{proof}
+
+\begin{theorem}\label{normalization}
+    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+\end{theorem}
+\begin{proof}
+    \cref{normalization_helper_one} provides a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
+    Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
+\end{proof}
+
+\subsection{A determinant}
+\begin{lemma}
+    Let \(X \in \gl_m\), and let 
+    \[Y = \begin{pmatrix}
+        y_{11} & y_{12} & y_{13} & \cdots & y_{1,n-1} & y_{1n} \\
+        d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
+            & d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
+            & & \ddots & \cdots & \vdots  & \vdots \\
+            & & & d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
+            & & & & d_{n - 1} & y_{nn}
+    \end{pmatrix} \in \gl_n.\]
+    For any \(a, b \in \mathbb{C}^m\),
+    \[\det 
+    \begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y & \\
+       & & &  \\
+       \end{pNiceArray} = \]
+       \[\det X \det Y + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+            & & & \vert \\
+            & X & & b     \\
+            & & & \vert \\
+            \hline 
+        \text{---} & a & \text{---} & 0
+       \end{pNiceArray}\]
+\end{lemma}
+\begin{proof}
+    By induction on \(n\).
+    In the case \(n = 1\), expanding along the last row (taking the usual interpretation of the empty product) gives the desired result.
+    \par Now suppose \(n > 1\).
+    Expanding along the last row, we get 
+    \[d_{n - 1} \det \begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y_{n,n-1} & \\
+       & & &  \\
+       \end{pNiceArray} -
+    y_{nn} \det \begin{pNiceArray}{ccc|ccc}
+        & & & & & \\
+        & X & & & &   \\
+        & & & & & \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y_{n,n} & \\
+       & & &  \\
+       \end{pNiceArray}.\]
+    Using our inductive hypothesis for the first determiniant, and using that \(\det \begin{pNiceArray}{c|c}
+        A_{11} & 0 \\
+        A_{21} & A_{22}
+    \end{pNiceArray} = \det A_{11} \det A_{22}\) for the second, the expression becomes
+    \[d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}\right)
+   - y_{nn} \det X \det Y_{nn} = \]
+   \[(d_{n - 1} Y_{n,n-1} - y_{nn} \det Y_{nn})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray} = \]
+   \[\det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}.\]
+\end{proof}
+
+\begin{corollary}
+    If \(X\) is nilpotent, and
+    \[\begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+       & & & & Y & \\
+       & & &  \\
+       \end{pNiceArray}\]
+    is nilpotent  as well, then \(Y\) is nilpotent.
+    If all the \(d_i\) are nonzero, then
+    \[\begin{pNiceArray}{ccc|c}
+        & & & \vert \\
+        & X & & b     \\
+        & & & \vert \\
+        \hline 
+    \text{---} & a & \text{---} & 0
+   \end{pNiceArray}\]
+   is nilpotent as well.
+    \begin{proof}
+        By the previous lemma, the characteristic polynomial of the big matrix is
+        \[g_X(\lambda) g_Y(\lambda) + f(\lambda),\]
+        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
+    \end{proof}
+\end{corollary}
+
 \bibliography{paper}

### 2024-08-26 paper.tex
outline paper

@@
 Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
+\par In section 2, we review some preliminary material.
+In section 3, we find the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
+In section 4, we embed this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
+We compute the Slodowy slice, and we end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par In section 5, we discuss how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
+In section 6 we solve the easier problem.
+In section 7 we find the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
+In section 8 we apply the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+In section 9 we discuss an interesting direction for future work.
+Then in section 10 we prove some linear algebra facts that were used in the paper.
 

### 2024-08-26 paper.tex
improve intro.  finalize-ish section 3 and beginning of 4.

@@
 \section{Introduction}
-We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
-For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
-Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
-\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
-The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
-Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
-The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
-Let
-\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
-\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
-We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
+Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
+% The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
+% Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
+% The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
+% Let
+% \[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
+% \[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
+Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) be the Springer resolution.
 \par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
@@
 Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-\par In this paper we will study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-\par As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
+\par In this paper we study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+% The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
 The main section of this paper will study the fibers of this map.
@@
 
-\section{Finding the Slodowy slices with the same \(E\)}
-First we find \(\ker \ad_f\).
-We have \((fX)_{ij} = i (n - i) A_{i + 1,j}\), and \((Xf)_{ij} = (j - 1) (n - (j - 1)) A_{i, j - 1}\).
-So, for all \(i, j \in \{1, ..., n\}\), we have 
-\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{i, j - 1}.\]
-Taking \(j = 1\), we find that \(A_{i,1} = 0\) for \(i \geq 2\).
-Then, taking \(j > 1\), we find that for \(i, j \in \{1, ..., n - 1\}\),
-\[A_{i + 1, j + 1} = \frac{(j - 1)(n - (j - 1))}{i(n - i)} A_{ij}.\]
-So, \(\ker\ad_f\) is the set of matrices which are upper triangular and satisfy the above condition.
-\par To find the Slodowy slice associated to the previous \(\spl_2\)-triple \((E, H, F)\), we just need to find \(\ker\ad_F\).
+\section{Finding \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
+\subsection{Finding the Slodowy slice \(S\)}
+In the previous section we computed the principal \(\spl_2\)-triple \((e, h, f)\) in \(\gl_n\).
+Embedding this into \(\gl_{m + n}\) as described previously, we obtain
+\[(E, H, F) = \left(\begin{pmatrix}0 & 0 \\0 & e\end{pmatrix}, \begin{pmatrix}0 & 0 \\0 & h\end{pmatrix}, \begin{pmatrix}0 & 0 \\0 & f\end{pmatrix}\right).\]
+
+\begin{lemma}\label{small_centralizer}
+    \(\mathfrak{z}_{\gl_n}(f)\) is the set of upper-triangular \(X \in \gl_n\) such that for all \(i,j\),
+    \[X_{i + 1,j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
+\end{lemma}
+\begin{proof}
+    Let \(X \in \mathfrak{z}_{\gl_n}(f)\).
+    Looking at the definition of \(f\) from the previous section (and zero-padding the matrices), we see that \((fX)_{ij} = i (n - i) X_{i + 1,j}\), and \((Xf)_{ij} = (j - 1)(n - (j - 1)) X_{i, j - 1}\).
+    So,
+    \[\forall i, j \in \{1, ..., n\}. \; i(n - i)X_{i + 1,j} = (j - 1)(n - (j - 1))X_{i, j - 1}.\]
+    Taking \(j = 1\), the condition above tells us that \(\forall i \geq 2. \; X_{i, 1} = 0\).
+    Taking \(j > 1\) and \(i < n\), we obtain that
+    \[\forall i, j \in \{1, ..., n - 1\}. \; X_{i + 1, j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
+    So, every \(X \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular and satisfies the condition above.
+    Conversely, it is clear that for such \(X\) we have \(fX = Xf\).
+\end{proof}
+
+\begin{lemma}\label{big_centralizer}
+    \[\mathfrak{z}_{\gl_{m + n}}(F) =  \left\{\begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+        &  & &  & Y  \\
+        & & & & & 
+       \end{pNiceArray} : X \in \gl_m; Y \in \mathfrak{z}_{\gl_n}; a,b \in \mathbb{C}^m \right\}.\]
+\end{lemma}
+\begin{proof}
+    Let \(Z = \begin{pmatrix}Z_{11} & Z_{12}\\Z_{21} & Z_{22}\end{pmatrix} \in \mathfrak{z}_{m + n}(F)\).
     We have 
-\[[F, X] = \begin{pmatrix}
-    0 & 0 \\
-    f X_{21} & fX_{22}
-\end{pmatrix} - \begin{pmatrix}
-    0 & X_{12} f\\
-    0 & X_{22} f
-\end{pmatrix}.\]
-Thus, \(X_{21}\) must be all zeroes except for the first row, and \(X_{12}\) must be all zeroes except for the last column, and \(X_{22} \in \ker\ad_f\).
-There is no restriction on \(X_{11}\).
-This describes \(\ker\ad_F\).
-\par For \(X \in \mathcal{S}_{m,n}\), define \(u(X) := X_{11}\).
-
-\subsection{Finding \(\widetilde{\mathcal{N}}_{m,n}\)}
+    \[\begin{pmatrix}0 & Z_{12}f\\0 & Z_{22} f\end{pmatrix} =  ZF = FZ = \begin{pmatrix}0 & 0\\fZ_{21} & fZ_{22}\end{pmatrix}.\]
+    We see that there is no restriction on \(Z_{11}\).
+    The condition \(Z_{12}f = 0\) means that all but the last column of \(Z_{12}\) must be zero, and the condition \(0 = fZ_{21}\) means that all but the first row of \(Z_{21}\) must be zero.
+    And the condition \(Z_{22}f = fZ_{22}\) means that \(Z_{22} \in \mathfrak{z}_{\gl_{m + n}}(f)\).
+\end{proof}
+These lemmas provide an explicit characterization of the Slodowy slice \(E + \mathfrak{z}_{\gl_{m + n}}(F)\).
+
+\subsection{Finding \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
 Let \(\mathcal{N}_m \subseteq \gl_m\) be the nilpotent elements.

### 2024-08-26 paper.tex
some stuff

@@
 \end{proof}
-These lemmas provide an explicit characterization of the Slodowy slice \(E + \mathfrak{z}_{\gl_{m + n}}(F)\).
-
-\subsection{Finding \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
-Let \(\mathcal{N}_m \subseteq \gl_m\) be the nilpotent elements.
-Let \(\mathcal{S}_{m,n}'\) be the set of \(X \in \mathcal{S}_{m,n}\) such that both \(X\) and \(u(X)\) are nilpotent.
-Let \(\widetilde{\mathcal{N}}_{m,n} = \{(\mathfrak{b}, X) : X \in \mathfrak{b}\} \subseteq \mathcal{B}_{m + n} \times \mathcal{S}_{m,n}'\).
-Define \(\pi_{m,n} : \widetilde{\mathcal{N}}_{m,n} \to \mathcal{N}_m\) by \((\mathfrak{b}, X) \mapsto X_{11}\).
-For \(Y \in \gl_m\), we call \(\pi_{m,n}^{-1}(Y)\) the \emph{Springer fiber at the \(n\)-Slodowy slice at \(Y\)}.
+These lemmas provide an explicit characterization of the Slodowy slice \(S = E + \mathfrak{z}_{\gl_{m + n}}(F)\).
+
+\subsection{A description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
+Recall that we have the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p(Z), Z)\), where \(p : \gl_{m + n} \to \gl_m\) is the coordinate projection.
+Then we have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
+And from these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will find the set of \(Z \in S\) such that there exists \(x \in \widetilde{\mathcal{N}}\) with \((Z, x) \in S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), this amounts to finding the set \(S' = \{Z \in S : p(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
+\par
 
 \begin{lemma}
-    Let \(J\) be a jordan block with zeroes along the diagonal, and let \(A\) be upper triangular and nonzero.
-    Then \(J + A\) is not nilpotent.
-\end{lemma}
-\begin{proof}
+    Let \(A \in \gl_n\) be upper triangular.
+    Then \(J_n + A\) is nilpotent if and only if \(A = 0\).
+\end{lemma}
+\begin{proof}
+    Let \(e_1, ..., e_n\) be the standard basis, with \(J_n e_i = e_{i + 1}\).
     It is straightforward to show by induction that if \(v_i = 0\) for \(i < j\), and \(v_j \neq 0\), then \(((J + A)^k v_j)_{j + k} = v_j\).

### 2024-08-27 paper.tex
fix completely wrong proof about nilpotency

@@
 \begin{lemma}
-    Let \(A \in \gl_n\) be upper triangular.
-    Then \(J_n + A\) is nilpotent if and only if \(A = 0\).
-\end{lemma}
-\begin{proof}
+    Let \(X \in \gl_n\) be upper triangular.
+    Then \(J_n + X\) is nilpotent if and only if \(X = 0\).
+\end{lemma}
+\begin{proof}
+    Clearly if \(X = 0\), then \(J_n + X\) is nilpotent.
+    Inversely, suppose \(X \neq 0\).
     Let \(e_1, ..., e_n\) be the standard basis, with \(J_n e_i = e_{i + 1}\).
-    It is straightforward to show by induction that if \(v_i = 0\) for \(i < j\), and \(v_j \neq 0\), then \(((J + A)^k v_j)_{j + k} = v_j\).
-    Let \(i\) be such that \(Ae_i \neq 0\).
-    Then \((J + A)^{i - 1} e_1\) has nonzero \(e_i\)-component.
-    Then \((J + A)^i e_1\) has some nonzero \(e_{i'}\)-component for some \(i' \leq i\).
-    Then \((J + A)^{i + (n - i')} e_1\) has some nonzero \(e_n\)-component.
-    And \(i + (n - i') \geq n\), so we're done.
+    Let \(i_1 = \max\{i : Xe_i \neq 0\}\).
+    As \(X\) is upper triangular, we have \(X e_{i_1} = v + ae_{i_2}\), with \(a \in \mathbb{C}\setminus\{0\}\), \(i_2 \leq i_1\), and \(v \in \langle e_1, ..., e_{i_1 - 1}\rangle\).
+    \par Now, \((J_n + X)^{i_1} e_1 = e_{i_1 + 1} + v + ae_{i_2}\).
+    Then, \((J_n + X)^{i_1 + (n - i_1)} e_1 = 0 + (J_n + X)^{n - i_1} (v + ae_{i_2})\).
+    Clearly \((J_n + X)^{n - i_1} (v + ae_{i_2}) = v' + ae_{i_2 + n - i_1}\), with \(v' \in \langle e_1, ..., e_{i_2 + n - i_1 - 1} \rangle\).
+    Now, since \(i_2 \leq i_1\), we have \(i_2 + n - i_1 \leq n\), and therefore \((J_n + X)^n e_1 \neq 0\).
+    It follows that \(J_n + X\) is not nilpotent.
 \end{proof}

### 2024-08-27 paper.tex
reorganize, move more stuff to linalg section
lemma about S'

@@
         & & & & & 
-       \end{pNiceArray} : X \in \gl_m; Y \in \mathfrak{z}_{\gl_n}; a,b \in \mathbb{C}^m \right\}.\]
+       \end{pNiceArray} : X \in \gl_m; Y \in \mathfrak{z}_{\gl_n}(f); a,b \in \mathbb{C}^m \right\}.\]
 \end{lemma}
@@
 \end{proof}
+
 These lemmas provide an explicit characterization of the Slodowy slice \(S = E + \mathfrak{z}_{\gl_{m + n}}(F)\).
+\begin{corollary}\label{slodowy_slice}
+    \[S = \left\{\begin{pNiceArray}{ccc|ccc}
+        & & & & & \vert \\
+        & X & & & & b    \\
+        & & & & & \vert \\
+       \hline
+       \text{---} & a & \text{---} &  \\
+        & & &  & e + Y\\
+        &  & &  &   
+       \end{pNiceArray} : a, b \in \mathbb{C}^m, X \in \gl_m, Y \in \mathfrak{z}_{\gl_n}(f)\right\}.\]
+\end{corollary}
 
@@
 Recall that we have the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p(Z), Z)\), where \(p : \gl_{m + n} \to \gl_m\) is the coordinate projection.
-Then we have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
+We also have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
 And from these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will find the set of \(Z \in S\) such that there exists \(x \in \widetilde{\mathcal{N}}\) with \((Z, x) \in S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), this amounts to finding the set \(S' = \{Z \in S : p(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
-\par
-
+\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
+As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' = \{Z \in S : p(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
 \begin{lemma}
-    Let \(X \in \gl_n\) be upper triangular.
-    Then \(J_n + X\) is nilpotent if and only if \(X = 0\).
-\end{lemma}
-\begin{proof}
-    Clearly if \(X = 0\), then \(J_n + X\) is nilpotent.
-    Inversely, suppose \(X \neq 0\).
-    Let \(e_1, ..., e_n\) be the standard basis, with \(J_n e_i = e_{i + 1}\).
-    Let \(i_1 = \max\{i : Xe_i \neq 0\}\).
-    As \(X\) is upper triangular, we have \(X e_{i_1} = v + ae_{i_2}\), with \(a \in \mathbb{C}\setminus\{0\}\), \(i_2 \leq i_1\), and \(v \in \langle e_1, ..., e_{i_1 - 1}\rangle\).
-    \par Now, \((J_n + X)^{i_1} e_1 = e_{i_1 + 1} + v + ae_{i_2}\).
-    Then, \((J_n + X)^{i_1 + (n - i_1)} e_1 = 0 + (J_n + X)^{n - i_1} (v + ae_{i_2})\).
-    Clearly \((J_n + X)^{n - i_1} (v + ae_{i_2}) = v' + ae_{i_2 + n - i_1}\), with \(v' \in \langle e_1, ..., e_{i_2 + n - i_1 - 1} \rangle\).
-    Now, since \(i_2 \leq i_1\), we have \(i_2 + n - i_1 \leq n\), and therefore \((J_n + X)^n e_1 \neq 0\).
-    It follows that \(J_n + X\) is not nilpotent.
-\end{proof}
-
-\par Now, taking the previous corolloary and the first lemma together, we see that 
-\[\mathcal{S}_{m,n}' = \left\{\begin{pNiceArray}{ccc|cccc}
+    \[S' = \left\{A_{X, a, b} := \begin{pNiceArray}{ccc|cccc}
     & & & & & & \vert \\
@@
     & & & & & 1 & 0
-   \end{pNiceArray} : a, b \in \mathbb{C}^m, X \in \gl_m \textrm{ is nilpotent}\right\}.\]
+   \end{pNiceArray} \in \mathcal{N}_{m + n}: a, b \in \mathbb{C}^m, X \in \mathcal{N}_m\right\}.\]
+\end{lemma}
+\begin{proof}
+    As every element of \(\mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{bottom_right_nilp} tells us that if a matrix of the form given in \cref{slodowy_slice} is nilpotent, and the upper-left block \(X\) is nilpotent as well, then \(e + Y\) must be nilpotent.
+    Then, again using that every element \(Y \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{upper_triangle_zero} tells us that if \(e + Y\) is nilpotent, then \(Y = 0\).
+    \par Hence every element of \(S'\) must simply have \(e\) in its bottom-right block.
+    We see that every element of \(S'\) is of the desired form.
+\end{proof}
+This is not a fully explicit characterization of \(S'\), since we don't say which choices of \(X\) and \(a, b \in \mathbb{C}^m\) lead to \(A_{X, a, b}\) being nilpotent.
+We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the description above of \(S'\) will be good enough for our purposes.
 
@@
 
-\subsection{A determinant}
-\begin{lemma}
+\subsection{Nilpotency Lemmas}
+\begin{lemma}\label{upper_triangle_zero}
+    Let \(X \in \gl_n\) be upper triangular.
+    Then \(J_n + X\) is nilpotent if and only if \(X = 0\).
+\end{lemma}
+\begin{proof}
+    Clearly if \(X = 0\), then \(J_n + X\) is nilpotent.
+    Inversely, suppose \(X \neq 0\).
+    Let \(e_1, ..., e_n\) be the standard basis, with \(J_n e_i = e_{i + 1}\).
+    Let \(i_1 = \max\{i : Xe_i \neq 0\}\).
+    As \(X\) is upper triangular, we have \(X e_{i_1} = v + ae_{i_2}\), with \(a \in \mathbb{C}\setminus\{0\}\), \(i_2 \leq i_1\), and \(v \in \langle e_1, ..., e_{i_1 - 1}\rangle\).
+    \par Now, \((J_n + X)^{i_1} e_1 = e_{i_1 + 1} + v + ae_{i_2}\).
+    Then, \((J_n + X)^{i_1 + (n - i_1)} e_1 = 0 + (J_n + X)^{n - i_1} (v + ae_{i_2})\).
+    Clearly \((J_n + X)^{n - i_1} (v + ae_{i_2}) = v' + ae_{i_2 + n - i_1}\), with \(v' \in \langle e_1, ..., e_{i_2 + n - i_1 - 1} \rangle\).
+    Now, since \(i_2 \leq i_1\), we have \(i_2 + n - i_1 \leq n\), and therefore \((J_n + X)^n e_1 \neq 0\).
+    It follows that \(J_n + X\) is not nilpotent.
+\end{proof}
+
+\begin{lemma}\label{block_determinant}
     Let \(X \in \gl_m\), and let 
@@
 
-\begin{corollary}
+\begin{corollary}\label{bottom_right_nilp}
     If \(X\) is nilpotent, and
@@
     is nilpotent  as well, then \(Y\) is nilpotent.
-    If all the \(d_i\) are nonzero, then
-    \[\begin{pNiceArray}{ccc|c}
-        & & & \vert \\
-        & X & & b     \\
-        & & & \vert \\
-        \hline 
-    \text{---} & a & \text{---} & 0
-   \end{pNiceArray}\]
-   is nilpotent as well.
+%     If all the \(d_i\) are nonzero, then
+%     \[\begin{pNiceArray}{ccc|c}
+%         & & & \vert \\
+%         & X & & b     \\
+%         & & & \vert \\
+%         \hline 
+%     \text{---} & a & \text{---} & 0
+%    \end{pNiceArray}\]
+%    is nilpotent as well.
+% ^That is false.  I want to say something about its characteristic polynomial.  not sure that I care enough to take the space though.
     \begin{proof}

### 2024-08-27 paper.tex
finish up section 4 (leadup into section 6)

@@
 We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the description above of \(S'\) will be good enough for our purposes.
+\begin{corollary}
+    \begin{align*}
+        S \times_\mathfrak{g} \widetilde{\mathcal{N}} & = \\
+        \{((X, A_{X, a, b}), ((X, A_{X, a, b}), \mathfrak{b})) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathcal{N} \cap \mathfrak{b}\} & \cong \\
+        \{(A_{X, a, b}, \mathfrak{b}) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
+    \end{align*}
+\end{corollary}
+We have a map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by \((A_{X, a, b}, \mathfrak{b}) \mapsto X\).
+We define the \emph{\(n\)-Slodowy-slice Springer fiber} at \(X \in \mathcal{N}\) to be the fiber \(\pi^{-1}(X)\).
+Because \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\),  
+\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
+The right factor of the product is simply the usual Springer fiber at \(X\).
+\par Let 
+\[\mathcal{P}_X = \{(A_{X, a, b}, (V_i)) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
+Using our correspondence between Springer fibers in \(\mathcal{B}_{m + n}\) and flags of \(\mathbb{C}^{m + n}\), we see that \(\mathcal{P}_X\) is isomorphic to the left factor of \(\pi^{-1}(X)\).
+In the next few sections, we will find the irreducible components of \(\mathcal{P}_X\).
+Then we will use this, along with the result about the usual Springer fiber at \(X\), to find the irreducible components of \(\pi^{-1}(X)\) and then of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 

### 2024-08-27 paper.tex
delete section 5 (no longer need it hooray)

@@
 
-\section{Simplifying the definition of a Springer fiber at a Slodowy slice}
-\par Let \(\mathcal{N}_m \subseteq \gl_m(\mathbb{C})\) be the subset consisting of nilpotent elements.
-For \(X \in \mathcal{N}_m\) and \(a, b \in \mathbb{C}^m\), let
-\[A_{X, a, b} = \begin{pNiceArray}{ccc|ccccc}
- & & & & & & & \vert \\
- & X & & & & & & b    \\
- & & & & & & & \vert \\
-\hline
-\text{---} & a & \text{---} & 0 \\
-& & & 1 & 0 \\
-& & &  & 1 & \ddots \\
-& & &  &   & \ddots & 0 \\
-& & &  &   &  & 1 & 0
-\end{pNiceArray} \in \mathfrak{gl}_{m + n}(\mathbb{C}).\]
-By the definition given in the previous section, we have 
-\[\widetilde{\mathcal{N}}_{m, n} = \{(\mathfrak{b}, X) : X \in \mathfrak{b}\} \subseteq \mathcal{B}_{m + n} \times \mathcal{S}_{m,n}',\]
-and the Springer fiber at the \(n\)-Slodowy slice at a nilpotent \(X \in \gl_m\) is
-\[\pi_{m,n}^{-1}(X) = \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \in \mathcal{S}_{m, n}'\} \] 
-\[= \{(\mathfrak{b}, A_{X, a, b}) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{nilpotent}\}\]
-\[\cong \{(\mathfrak{b}, a, b) : A_{X, a, b} \in \mathfrak{b}, A_{X, a, b} \textrm{ nilpotent}\}.\]
-\par Using our correspondence between \(\mathcal{B}_{m + n}\) and complete flags of \(\mathbb{C}^{m + n}\), we obtain 
-\[\pi_{m,n}^{-1}(X) \cong \{(V, a, b) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
-
 \section{Strategy and setup for finding the irreducible components of a Springer fiber at a Slodowy slice}

### 2024-08-27 paper.tex
lemmas about Pwrs

@@
 We have a map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by \((A_{X, a, b}, \mathfrak{b}) \mapsto X\).
-We define the \emph{\(n\)-Slodowy-slice Springer fiber} at \(X \in \mathcal{N}\) to be the fiber \(\pi^{-1}(X)\).
+We define the \emph{\(n\)-Slodowy-slice Springer fiber} at \(X \in \mathcal{N}_m\) to be the fiber \(\pi^{-1}(X)\).
 Because \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\),  
@@
 
-\section{Strategy and setup for finding the irreducible components of a Springer fiber at a Slodowy slice}
-\par Fix any \(X \in \mathcal{N}\).
-As we have fixed \(X\), we now write \(A_{a, b} := A_{X, a, b}\).
-Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be a Jordan basis for \(X\).
-For convenience we define \(e_{i0} := 0\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
-\par In this section we find the irreducible components of
-\[\pi^{-1}(X) \cong V := \{(A_{a, b}, U) : \forall i. \; A_{a, b} U_{i + 1} \subseteq U_i\}.\]
+\section{Strategy for finding components of \(\mathcal{P}_{J(\lambda)}\)}
+\par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
+In this section we write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\) and \(A_{a, b} := A_{J(\lambda), a, b}\).
+Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard basis for \(\mathbb{C}^m\).
+For convenience we write \(e_{ij} := 0\) for \(j < 1\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
+\par In this section we begin finding the irreducible components of
+\[\mathcal{P} = \{(A_{a, b}, (V_i)) : \forall i. \; A_{a, b} V_{i + 1} \subseteq V_i\}.\]
 \par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
-\[V_{w,r} := \{(A_{a, b}, U) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'} \}.\]
+\[\mathcal{P}_{w,r} := \{(A_{a, b}, V) \in \mathcal{P} : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'} \}.\]
 
 \begin{lemma}
-    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
-    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
-    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
-\end{lemma}
-\begin{proof}
-    TODO
-\end{proof}
+    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
+\end{lemma}
+\begin{proof}
+    Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
+    Define \(f : \mathbb{C}^m \to \mathbb{C}\) by \(f(e_{ij}) = a_{ij}\).
+    Since \(A_{a, b}\) is nilpotent, \cref{normalization} says that there is a change of basis \(P\) such that \(P^{-1}XP = X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
+    Since \(P^{-1}XP = X\), it is easy to see (writing out the matrix multiplication, if necessary) that there are \(a',b'\) such that \((P^{-1}, I_n)A_{a,b}(P, I_n) = A_{a',b'}\).
+    \par Now,
+    \begin{align*}
+        P^{-1}XPe_{ij} + f(Pe_{ij}) f_n & = \\
+        (P^{-1}, I_n)A_{a,b}(P, I_n)(e_{ij}, 0) & = \\
+        A_{a'b'} (e_{ij},0) & = \\
+        Xe_{ij} + a'_{ij} f_n & .
+    \end{align*}
+    Thus we see that \(a'_{ij} = 0\) for all pairs \((i,j)\) except one; or in other words, \(A_{a'b'}\) is of the form \(A_{e_{wr}b'}\).
+\end{proof}
+\begin{lemma}
+    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
+    When \(\mathcal{P}_{w_1r_1} \neq \mathcal{P}_{w_2r_2}\), we have \(\mathcal{P}_{w_1r_1} \cap \mathcal{P}_{w_2r_2} = \emptyset\). 
+\end{lemma}
+\begin{proof}
+    Now, if \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
+    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
+    Inversely, suppose
+
+\end{proof}
+
 Now, fix any \(w\) and \(r\).

### 2024-08-27 paper.tex
different proof of change of basis.  not sure if better or not.

@@
     Define \(f : \mathbb{C}^m \to \mathbb{C}\) by \(f(e_{ij}) = a_{ij}\).
-    Since \(A_{a, b}\) is nilpotent, \cref{normalization} says that there is a change of basis \(P\) such that \(P^{-1}XP = X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
-    Since \(P^{-1}XP = X\), it is easy to see (writing out the matrix multiplication, if necessary) that there are \(a',b'\) such that \((P^{-1}, I_n)A_{a,b}(P, I_n) = A_{a',b'}\).
-    \par Now,
-    \begin{align*}
-        P^{-1}XPe_{ij} + f(Pe_{ij}) f_n & = \\
-        (P^{-1}, I_n)A_{a,b}(P, I_n)(e_{ij}, 0) & = \\
-        A_{a'b'} (e_{ij},0) & = \\
-        Xe_{ij} + a'_{ij} f_n & .
-    \end{align*}
-    Thus we see that \(a'_{ij} = 0\) for all pairs \((i,j)\) except one; or in other words, \(A_{a'b'}\) is of the form \(A_{e_{wr}b'}\).
+    We take the coordinate-free view of \(A_{a,b}\) as the linear transformation \(T\) that sends \(e_{ij}\) to \(e_{i,j - 1} + f(e_{ij})\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
+    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P\) such that \(Pe_{ij}\) forms a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
+    \par Because \(Pe_{ij}\) is a Jordan basis, \(A_{a',b'}\) of \(T\) in this new basis has the same upper-left corner \(X\); and since \(f(Pe_{ij}) = 0\) for all but one pair \((i,j)\), we have \(a'_{ij} = 0\) for all but one pair \((i,j)\).
 \end{proof}
@@
     And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
-    Inversely, suppose
-
+    Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
+    Then there is \(P\) such that \((P^{-1},I_n) A_{e_{w_1r_1},b} (P, I_n) = A_{e_{w_2r_2}, b'}\).
+
+    Then, either there is \(k\) such that (for any \(b_1',b_2'\)) \(A_{e_{w_1r_1}b_1'}^k \)
+    \par The second observation, that the nonequal sets are disjoint, just follows from the fact that (this restricted form of) similarity is an equivalence relation.
 \end{proof}

### 2024-08-27 paper.tex
basically kinda finish section 5

@@
 Now, fix any \(w\) and \(r\).
-We will find the irreducible components of \(V_{w,r}\).
-These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
+We will find the irreducible components of \(\mathcal{P}_{w,r}\).
+These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(\mathcal{P}\) will be the irreducible components of \(\mathcal{P}\).
 \par Let 
@@
 \par Now, define 
-\[U_{wr} = \{(A_{e_{wr}, b}, U) \in V_{wr}\}.\]
-Let \(G\) act on \(V_{wr}\) by
-\[P \cdot (A_{e_{wr},b}, U) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)U) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) U).\]
-\par Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\) defined by
+\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, (V_i)) \in \mathcal{P}_{wr}\}.\]
+Let \(G\) act on \(\mathcal{P}_{wr}\) by
+\[P \cdot (A_{e_{wr},b}, (V_i)) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)(V_i)) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) (V_i)).\]
+Note that for any \(x \in \mathcal{Q}_{wr}\), we have \(G_{wr} = \{g \in G : g \cdot x \in \mathcal{Q}_{wr}\}\).
+So, by restriction of \(G\) to \(G_{wr}\) and \(\mathcal{P}_{wr}\) to \(\mathcal{Q}_{wr}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr}\).
+\par Consider the map \(\varphi : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\) defined by
 \[(x, P) \mapsto P \cdot x.\]
-By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
-Then, letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
-\begin{lemma}
-    As an algebraic variety, \(G\) is irreducible.
-\end{lemma}
-\begin{proof}
-    It's just \(\mathbb{C}^{something}\), since its blocks are the lower-left-toeplitz matrices.
-\end{proof}
+Then, letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr} \times G\).
+
 \begin{lemma}
@@
     We need to show that \(G_{wr}\) acts freely and transitively on the fibers of \(\varphi\).
-    It is obvious that \(G_{wr}\) acts freely on \(U_{wr} \times G\); it is enough to note that it acts freely on \(G\).
-    \par Let \(y \in V_{wr}\).
-    By definition of \(V_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in U_{wr}\).
+    It is obvious that \(G_{wr}\) acts freely on \(\mathcal{Q}_{wr} \times G\); it is enough to note that it acts freely on \(G\).
+    \par Let \(y \in \mathcal{P}_{wr}\).
+    By definition of \(\mathcal{P}_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in \mathcal{Q}_{wr}\).
     We have
@@
         \varphi^{-1}(y) = \{(x, P) : P \cdot x = y \} & = \\
-        \{(P^{-1} y, P) : P^{-1} y \in U_{wr} \} & = \\
-        \{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \in U_{wr}\} & .
+        \{(P^{-1} y, P) : P^{-1} y \in \mathcal{Q}_{wr} \} & = \\
+        \{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \in \mathcal{Q}_{wr}\} & .
     \end{align*}
-    For any \(x \in U_{wr}\) (in particular for \(x = P_y \cdot y\)), we have \(G_{wr} = \{g \in G : g \cdot x \in U_{wr}\}\).
-    Therefore, the fiber above becomes
+    Using that \(G_{wr} = \{g \in G : g \cdot (P_y \cdot y) = P_y \cdot y\}\), the expression above becomes
     \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\}.\]
@@
     % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
-    % Let \(X_1, ..., X_k\) be the irreducible components of \(U_{wr}\).
+    % Let \(X_1, ..., X_k\) be the irreducible components of \(\mathcal{Q}_{wr}\).
     % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
@@
 \end{proof}
-Our strategy is to find the irreducible components \(X \subseteq U_{wr}\), and we will then argue that the irreducible components of \(V_{wr}\) are of the form \(\varphi(X \times G)\).
-So, we will now find the irreducible components of \(U_{wr}\).
-\par Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
+Our strategy is to find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we will then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi(X \times G)\).
+So, we will now find the irreducible components of \(\mathcal{Q}_{wr}\).
+\par Actually \(\mathcal{Q}_{wr}\) might be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
 So, we will change basis to make \(r = 0\).
+Let \(m' = m - r\), and \(n' = n + r\).
 Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
-Let \(X'\) be in Jordan normal form with shape \(\lambda'\).
-Let \(U_{wr}' = \{(A_{X', 0, b}, U) : \forall i. A_{X', 0, b} U_{i + 1} \subseteq U_i\}\).
-Let \(e_{ij}'\) be a Jordan basis for \(X'\).
-Let \(f_1, ..., f_n\) be a Jordan basis for the restriction of \(A_{X, 0, b}\) to \(\mathbb{}\)...
+Let \(X' = J(\lambda)\).
+Let \(\mathcal{Q}' = \{(A_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
+\begin{lemma}
+    \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\)
+\end{lemma}
+\begin{proof}
+    Let \(e_{ij}'\) be the standard Jordan basis for \(X'\).
+    Let \(f_1', ..., f_{n'}'\) be a basis for \(\mathbb{C}^n\), with \(A_{X', 0, b} f_{i + 1}' = f_i'\), and \(A_{X', 0, b} f_1 = (b, 0)\).
     Set \(m' := m - r\), and \(n' := n + r\).
-Let \(f_1', ..., f_{n'}'\) blah.
     Define the linear map \(Q_{wr} : \mathbb{C}^{m' + n'} \to \mathbb{C}^{m + n}\) by:
@@
     % \end{itemize}
-Observe that conjugation by \(Q_{wr}\) maps \(U_{wr}\) to \(U'_{wr}\), and conjugation by \(Q_{wr}^{-1}\) maps \(U'_{wr}\) to \(U_{wr}\).
-We conclude that \(U_{wr} \cong U_{wr}'\); so to find the irreducible components of \(U_{wr}\) we just need to find the irreducible components of \(U_{wr}'\).
-To clear the context, which is rather cluttered by now, and to avoid writing primes everywhere, we move to a new section.
-
-\section{Finding the irreducible components of \(U_0\)}
+    Observe that conjugation by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and conjugation by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
+\end{proof}
+In the next section we will find the irreducible components of \(\mathcal{Q}'\).
+To avoid death by primes, we will refer to it as \(\mathcal{Q}\), and refer to \(m',n'\) as \(m,n\), and so on, throughout the next section.
+
+\section{The components of \(\mathcal{Q}\)}
 \subsection{Setup}

### 2024-08-27 paper.tex
future work

@@
 
-\section{Finding the irreducible components of a springer fiber at a slodowy slice}
+\section{The components of \(\mathcal{P}_{J(\lambda)}\)}
 Apply things from the previous two sections, and conclude.
@@
 We will verify these things using our prvious computations of springer fibers.
+
+\section{Future work}
+The paper (TODO: cite) describes a correspondence between Steinberg variety and pairs of young tableaux.  
+We observe that \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something liek the stienber variety.
+Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of yound tableaux: one of shape of \(X\), one of shape of \(A_{X, a, b}\).
+\par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 

### 2024-08-28 paper.tex
typo correction and so on.  read up to corollary 6.4

@@
 \subsection{Setup}
-Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
-Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
+Let \(X = J(\lambda) \in \gl_m\).
+Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
 Let
-\[U_0 = \{(A_{0,b}, U) \in V\}.\]
-We will find the irreducible components of \(U_0\).
+\[\mathcal{Q} = \{(A_{0,b}, (V_i)) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
+In this section we find the irreducible components of \(\mathcal{Q}\).
 \par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
@@
 Then set \(q_i(b) = \lambda_i - p_i(b)\).
-When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
+When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
 \par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., k\}\), and let \((\rho_i)_{i \in I}\) be any map \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
@@
 Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
-\par Let \(U_{I, (\rho_i)} := \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).
-The idea here is to show that blah relation holds between U and B.
+\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, (V_i)) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
+We will show that the \(\mathcal{Q}_{I, (\rho_i)}\)'s are the irreducible components of \(\mathcal{Q}\).
 
@@
     Otherwise, take any \(i_2 \in \argmax_{i : q_{i_1} > q_i} p_i\), and set \(\rho_{i_2} := p_{i_2}\).
-    Continuing on in this way, eventually we reach a point where \(\{i : q_{i_k} > q_i\} = \emptyset\).
+    Continuing on in this way, eventually we reach a \(k\) where \(\{i : q_{i_k} > q_i\} = \emptyset\).
     Then we set \(I = \{i_1, ..., i_k\}\).
     Note that \(I, (\rho_i)\) satisfy conditions (1)--(4), and furthermore \(b \in B_{I, (\rho_i)}\).
-    \par Now, we show that no \(B_{I, (\rho_i)}\) is contained in the union of the others.
-    Indeed, fix \(I\) and \((\rho_i)\).
+    \par Now, we check that no \(B_{I, (\rho_i)}\) is contained in the union of the others.
+    Fix \(I\) and \((\rho_i)\).
     Take any \(b \in B_{I, (\rho_i)}\) with \(p_i = \rho_i\) for \(i \in I\) and \(p_i = 0\) for \(i \notin I\).
@@
 
-\subsection{A study of \(B_{I, (\rho_i)}\)}
+\subsection{Study of \(B_{I, (\rho_i)}\)}
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
@@
     We need to show that \(\max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
-    Given the conditions (1)--(4) on \(\rho_i\), it suffices to show that for each \(i \notin I\) with \(q_i > q_{i_k}\), we have \(p_i \leq p_{i_{k + 1}}\).
-    Indeed, given \(i \notin I\) with \(q_i > q_{i_k}\), we cannot have \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), as that would imply that \(q_{i_k} \leq q_i\).
-    Hence we must have \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), and consequently \(p_i \leq p_{i_k}\).
+    Given the conditions (1)--(4) on \(\rho_i\), it suffices to show that for each \(i \notin I\) with \(q_i < q_{i_k}\), we have \(p_i \leq p_{i_{k + 1}}\).
+    Indeed, given \(i \notin I\) with \(q_i < q_{i_k}\), we cannot have \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), as that would imply (by hypothesis) that \(q_{i_k} \leq q_i\).
+    Hence \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), and consequently (by hypothesis) \(p_i \leq p_{i_k}\).
 \end{proof}

### 2024-08-28 paper.tex
pass further

@@
 Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
-\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, (V_i)) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
-We will show that the \(\mathcal{Q}_{I, (\rho_i)}\)'s are the irreducible components of \(\mathcal{Q}\).
 
@@
 \end{proof}
+\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, (V_i)) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
+We will show that \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times (\textrm{some springer fiber})\).
+Then we will use the result about the irreducible components of a Springer fiber to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\), and the closures of these will be the irreducible components of \(\mathcal{Q}\).
 
 \subsection{Study of \(B_{I, (\rho_i)}\)}
-Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
+Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
 As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
@@
 \begin{corollary}\label{bs_iso}
-    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
+    \begin{align*}
+        B_{I, (\rho_i)} \cong & \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \\
+        & \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}.
+    \end{align*}
 \end{corollary}
@@
     \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
-    \cref{alternative_bs_two} tells us that this is an isomorphism.
+    \cref{alternative_bs_two} says that this is an isomorphism.
 \end{proof}
@@
 
-\subsection{A study of \(U_{I, (\rho_i)}\)}
-Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
-We will find the irreducible components of \(U_{I, (\rho_i)}\), and show that their closures are in fact irreducible components of \(U_0\).
-\par I claim that \(A_{0,b}\) has the same shape for every \((A_{0, b}, U) \in U_{I, (\rho_i)}\).
-Call this shape \(\mu\).
-By finding a algebraic map taking \(b\) to a Jordan basis for \(A_{0,b}\), we will put \(U_{I, (\rho_i)}\) in isomorphism with the product (choice of \(b\)) \(\times\) (Springer fiber at \(J(\mu)\)).
-Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(U_{I, (\rho_i)}\).
+\subsection{Study of \(\mathcal{Q}_{I, (\rho_i)}\)}
+Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
+In this subsection we find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
+\par I claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).
+By finding a algebraic map taking \(b \in B_{I, (\rho_i)}\) to a Jordan basis for \(A_{0,b}\), we will put \(\mathcal{Q}_{I, (\rho_i)}\) in isomorphism with the product \(B_{I, (\rho_i)} \times (Springer fiber at J(\mu))\).
+Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
 \par So, now we find a Jordan basis for \(A_{0, b}\).
+As before, we write \(\{i_1, ..., i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+We also write, somewhat abusively, \(b \in \mathbb{C}^{m + n}\) to refer to the vector \((b, 0) \in \mathbb{C}^{m + n}\).
 \begin{lemma}
@@
         We have \(v_{i_k} = A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}}\).
-        First we note that \(q_{i_k} < n\) by the definition of \(U_{I, (\rho_i)}\), so the definition of \(v_{i_k}\) makes sense.
+        First we note that \(q_{i_k} < n\) by the definition of \(\mathcal{Q}_{I, (\rho_i)}\), so the definition of \(v_{i_k}\) makes sense.
         We consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
@@
         The sum of the lengths is
-        \[\sum_{i \notin I} (p_i + q_i) + (n + P) + \sum_{i \in I} (q_i + P_i).\]
-        Writing \(I = \{i_1 < \cdots < i_{|I|}\}\), we note that \(P = p_{i_1}\), that \(P_{i_{|I|}} = 0\), and that for \(l < |I|\) we have \(P_{i_l} = p_{i_{l + 1}}\).
-        Thus, the sum above is 
-        \[\sum_{i \notin I} (p_i + q_i) + (n + p_{i_1}) + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_{l + 1}}) = \]
-        \[\sum_{i \notin I} (p_i + q_i) + n + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_l}) = n + \sum_i (q_i + p_i) = m + n.\]
+        \[\sum_{i \notin I} (p_i + q_i) + \sum_{k = 0}^r (q_{i_k} + p_{i_{k + 1}}) = \sum_i (q_i + p_i) = m + n.\]
     \end{proof}
@@
         \par I claim that \(f_n \in W\) as well.
-        To see this, we consider the chain beginning with \(f_n - (A^{n + P} f_n \rightshift n + P)\).
-        As explained in the proof of (1), we have \(A^{n + P} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
-        Consequently, \((A^{n + P} f_n \rightshift n + P) \in \langle e_{ij} \rangle_{i,j : q_i \geq n} \subseteq W\).
-        Because \(f_n - (A^{n + P} f_n \rightshift n + P) \in W\), this implies that \(f_n \in W\).
-        \par Because \(AW \subseteq W\) (obvious, since \(W\) is the span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
-        \par Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
+        To see this, we consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).
+        As explained in the proof of (1), we have \(A^{n + p_{i_1}} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
+        Consequently, \((A^{n + p_{i_1}} f_n \rightshift n + p_{i_1}) \in \langle e_{ij} \rangle_{i,j : q_i \geq n} \subseteq W\).
+        Because \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1}) \in W\), this implies that \(f_n \in W\).
+        \par Because \(AW \subseteq W\) (obvious, since \(W\) is a span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
+        \par CONTINUE HERE.
+        Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
         This is obvious for \(i \notin I\).
+        So, we just need to show that \(e_{i_kj}\)
         For \(i \in I\), we do it inductively.
@@
 \begin{lemma}\label{u_i_rho_iso}
-    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
+    \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
 \end{lemma}
@@
     \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
-    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
+    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to \mathcal{Q}_{I, (\rho_i)}\).
     \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
@@
     The 
-    \(U_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
+    \(\mathcal{Q}_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
 \end{corollary}
@@
 \begin{lemma}
-    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties 
+    The irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\) are exactly the subvarieties 
     \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]

### 2024-08-28 paper.tex
read up to lemma 6.7

@@
         \par Because \(AW \subseteq W\) (obvious, since \(W\) is a span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
-        \par CONTINUE HERE.
-        Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
+        \par Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
+        It suffices to show that \(e_{i, \lambda_i} \in W\) for each \(i\) with \(q_i < n\).
         This is obvious for \(i \notin I\).
-        So, we just need to show that \(e_{i_kj}\)
-        For \(i \in I\), we do it inductively.
-        Fix \(i \in I\), and suppose we have already shown that for all \(i' \in I\) with \(q_{i'} > q_i\), we have \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
-        We will show that \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
-        \par To see this, we consider the chain beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\).
-        (Recall \(v_i = A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\).)
-        Because \(AW \subseteq W\), and \(b_{i,p_i} \neq 0\) (by definition of \(p_i\)), it suffices to show that \(\sum_{l = 1}^{p_i} b_{il} e_{i,k + q_i} \in W\).
-        As explained in the proof of (1), we have \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{q_l \geq q_i}\).
-        And since \(A^{q_i + P_i} v_i\) has row \(i\) zeroed out, in fact \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
+        So, we just need to show that \(e_{i_k\lambda_{i_k}} \in W\) for each \(k \in \{1, ..., r\}\).
+        We do this inductively; fix \(k\), and suppose we have already shown that \(e_{i_{k'}, \lambda_{i_{k'}}} \in W\) for \(k' < k\).
+        We will show that \(e_{i_k, \lambda_{i_k}} \in W\).
+        \par To see this, consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
+        (Recall \(v_{i_k} = A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}}\).)
+        Since \(b_{i_k,p_{i_k}} \neq 0\) (by definition of \(p_{i_k}\)), it suffices to show that \(\sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}} \in W\).
+        As explained in the proof of (1), we have \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{lj} \rangle_{q_l \geq q_{i_k}}\).
+        And since \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k}\) has row \(i_k\) zeroed out, in fact \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{lj} \rangle_{l : l \neq i_k \land q_l \geq q_{i_k}}\).
         Hence, \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
-        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i} \subseteq W\), and consequently \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in W\).
-        Since we know \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i) \in W\), this implies that \(v_i \in W\).
-        Because \(A^{n - q_i} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i} \in W\), as desired.
+        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i_k \land q_l \geq q_{i_k}} \subseteq W\), and consequently \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}} \in W\).
+        Since we know \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}}) \in W\), this implies that \(v_{i_k} \in W\).
+        Because \(A^{n - q_{i_k}} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}} \in W\), as desired.
     \end{proof}
@@
 
-Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
+Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the lemma.
 Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
 \par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
-We are interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).
+We are interested in this thing because for any \(\alpha\), the dimension of \(X_{\mu, \alpha}\) is \(\gamma([\mu_1, ..., \mu_{k + 1}])\).
 
 \begin{lemma}
-    \[\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
+    \[\gamma([\mu_1, ..., \mu_{k + 1}]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
     \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
@@
 \section{Linear Algebra Facts}
-In this section we prove linear algebra facts that were used in the paper.
+In this section we prove linear algebra facts that were used earlier.
 They are confined to this section to avoid interrupting the flow of the paper.

### 2024-08-28 paper.tex
up to lemma 6.8

@@
     Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
-    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
+    Note that
+    \[\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...].\]
     Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
-    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
-    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
+    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}].\]
+    We can transform \(\mu\) into \(L'\) by just `moving' each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
     So,
@@
     \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
-    Now we consider how to get from \(L'\) to \(L\).
+    \par Now we consider how to transform \(L'\) into \(L\).
     First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
@@
     \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
-    \par Now,
+    \par Now, we put these two results together to get \(\gamma(L) - \gamma(\mu)\).
     \begin{align*}
@@
         \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
-        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
+        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
     \end{align*}
+    Observing that \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_k])\), the equation above gives the desired result.
 \end{proof}

### 2024-08-28 paper.tex
finish section 6

@@
 
-\begin{lemma}
+\begin{lemma}\label{springer_fiber_dim}
     \[\gamma([\mu_1, ..., \mu_{k + 1}]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
@@
     For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
-    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
-    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
-    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to \mathcal{Q}_{I, (\rho_i)}\).
-    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
+    From looking at the Jordan basis, it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
+    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b (V_i) : (V_i) \in X_\mu\}\).
+    This gives the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to \mathcal{Q}_{I, (\rho_i)}\) defined by
+    \[(b, (V_i)) \mapsto (P_b J(\mu) P_b^{-1}, P_b (V_i)),\]
     with inverse
-    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
+    \[(A_{0,b}, (V_i)) \mapsto (b, P_b^{-1} (V_i)).\]
 \end{proof}
@@
 \begin{corollary}\label{u_i_rho_irred_and_dim}
-    The 
-    \(\mathcal{Q}_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
+    For \(\alpha \in \mathrm{SYT}(\mu)\), let \(\mathcal{Q}_{I, (\rho_i), \alpha}\) be the subvariety of \(\mathcal{Q}_{I, (\rho_i)}\) which corresponds to \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\) via the isomorphism of \cref{u_i_rho_iso}.
+    The subvarieties \((\mathcal{Q}_{I, (\rho_i), \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) are the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
+    Each has dimension \(\gamma([0, \lambda_1, ..., \lambda_k])\).
 \end{corollary}
 \begin{proof}
-    Irreducibility follows from \cref{u_i_rho_iso}, since \(B_{I, (\rho_i)}\) is irreducible (by \cref{bs_iso}), as is \(X_\mu\).
-    To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_\mu\).
-    The dimension of \(X_\mu\) is 
+    We know that \(B_{I, (\rho_i)}\) is irreducible by \cref{bs_iso}.
+    Then, the fact that the \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\) are the irreducible components of \(B_{I, (\rho_i)} \times X_\mu\) just follows from the fact that the \(X_{\mu, \alpha}\) are the irreducible components of \(X_\mu\).
+    \par To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_{\mu, \alpha}\).
+    We get the dimension of \(B_{I, (\rho_i)}\) from \cref{bs_dim}, and we get the dimension of \(X_{\mu, \alpha}\) from \cref{springer_fiber_dim}.
+    Adding them together, things cancel out and we get \(\gamma([0, \lambda_1, ..., \lambda_k])\).
 \end{proof}
@@
 \subsection{Conclusion}
-At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
-We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
-\begin{lemma}
-    The irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\) are exactly the subvarieties 
-    \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
-    These are distinct.  
-    There are blah of them, and each has dimension blah.
-\end{lemma}
-\begin{proof}
-    We know from \cref{bs_iso} that \(B_{I, (\rho_i)}\) is irreducible.
-    So, the components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\).
-    Their dimensions are blah, and there are... of them.
-    taking image under the isomorphism gives the desired result.
-\end{proof}
-
-\begin{lemma}
-    The irreducible components of \(U_0\) are exactly the \(U_{I, (\rho_i), \alpha}\).
-    They are distinct.
-    There are blah of them, each of dimension blah.
-\end{lemma}
+\begin{theorem}
+    The irreducible components of \(\mathcal{Q}\) are the closures of the subvarieties \(\mathcal{Q}_{I, (\rho_i), \alpha}\), as we let \(I, (\rho_i)\) range over all possibilities satisfying the conditions (1)--(4) of \cref{bs_union}, and we let \(\alpha \in \mathrm{SYT}(\mu(I, (\rho_i)))\).
+\end{theorem}
+\begin{proof}
+    We see from \cref{u_i_rho_irred_and_dim} that the \(\mathcal{Q}_{I, (\rho_i), \alpha}\) are irreducible and equidimensional.
+    Then \cref{bs_union} tells us that their union is \(\mathcal{Q}\), and in addition that none is contained in the union of the others.
+\end{proof}
 

### 2024-08-28 paper.tex
get a good start on section 7

@@
 \[\sum_i h_{ii} = 0.\]
-Remark: this is just the statement that \(h \in \spl_n\); in other words, we will see that every choice of \(\spl_2\)-triple in \(\gl_{m + n}\) is also an \(\spl_2\)-triple in \(\spl_{m + n}\).
+(That is, \(h \in \spl_n\).)
 This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
@@
 Let \(X' = J(\lambda)\).
-Let \(\mathcal{Q}' = \{(A_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
-\begin{lemma}
+(TODO: explain that \(A'\) is like \(A\), but with \(m',n'\) taking the place of \(m,n\).)
+Let \(\mathcal{Q}' = \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
+\begin{lemma}\label{a_zero}
     \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\)
@@
 \subsection{Conclusion}
-\begin{theorem}
+\begin{theorem}\label{Q_comps}
     The irreducible components of \(\mathcal{Q}\) are the closures of the subvarieties \(\mathcal{Q}_{I, (\rho_i), \alpha}\), as we let \(I, (\rho_i)\) range over all possibilities satisfying the conditions (1)--(4) of \cref{bs_union}, and we let \(\alpha \in \mathrm{SYT}(\mu(I, (\rho_i)))\).
@@
 \section{The components of \(\mathcal{P}_{J(\lambda)}\)}
-Apply things from the previous two sections, and conclude.
+As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
+We write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\), and \(A_{a,b} := A_{J(\lambda), a, b}\).
+And as before, \((e_{ij})_{ij}\) and \((f_j)_j\) form the standard basis for \(\mathbb{C}^{m + n}\).
+\subsection{The components of \(\mathcal{Q}_{wr}\)}
+Recall from section 5 the varieties
+\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, (V_i)) \in \mathcal{P}\}.\]
+Fix any \(w,r\).
+\cref{a_zero} tells us that 
+\[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
+where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
+\par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) give by \cref{Q_comps}.
+Write \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) to denote the irreducible component of \(\mathcal{Q}_{wr}\) corresponding to \(\mathcal{Q}'_{I, (\rho_i), \alpha}\) via the isomorphism \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\) of \cref{a_zero}.
+
+\begin{corollary}
+    The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
+    Each has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+\end{corollary}
+\begin{proof}
+    From the foregoing discussion, it is clear that they are indeed the irreducible components.
+    To calculate the dimension, we refer to \cref{u_i_rho_irred_and_dim}, which says the dimension is \(\gamma([0, \lambda_1', ..., \lambda_k'])\).
+\end{proof}
+
+\par In section 5 we defined the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\) and the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
 

### 2024-08-28 paper.tex
kinda basically finished section 7

@@
 
-\begin{lemma}
+\begin{lemma}\label{principal_bundle}
     The map \(\varphi\) is a principal \(G_{wr}\)-bundle.
@@
 
-\begin{corollary}
+\begin{theorem}
     The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
     Each has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
-\end{corollary}
+\end{theorem}
 \begin{proof}
@@
 
-\par In section 5 we defined the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\) and the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
+\subsection{The varieties \(G_{wr}\) and \(G\)}
+Fix \(w,r\).
+Recall from section 5 the groups \(G = \{P \in \GL_m : P^{-1}XP = X\}\) and \(G_{wr} = \{A \in G : e_{wr} A = e_{wr}\}\).
+\begin{lemma}\label{g_irred_dim}
+    \(G\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
+\end{lemma}
+\begin{proof}
+    The closure of \(G\) in \(\gl_m\) is \(\mathfrak{z}_{\gl_m}(X)\).
+    \cref{nilpotent_centralizer} says that \(\mathfrak{z}_{\gl_m}(X)\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i, \lambda_j)}\).
+\end{proof}
+
+\begin{lemma}\label{gwr_irred_dim}
+    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+\end{lemma}
+\begin{proof}
+    The closure of \(G_{wr}\) in \(\gl_m\) is \(V = \{Y \in \mathfrak{z}_{\gl_m}(Y) : e_{wr} Y = e_{wr}\}\).
+    Lemma TODO says that \(V\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i', \lambda_j')}\).
+\end{proof}
+
+\subsection{The components of \(\mathcal{P}_{wr}\)}
+Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
+From \cref{principal_bundle} we have the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
+% \par Together, \cref{g_irred_dim} and \cref{gwr_irred_dim} tell us that the irreducible components of \(\mathcal{Q}_{wr} \times G\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\).
+
+\begin{theorem}\label{pwr_comps}
+    The irreducible components of \(\mathcal{P}_{wr}\) are the closures of the images \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\).
+    Some irreduble components of \(\mathcal{P}_{wr}\) are double-counted; we have equality iff there's a bijection \(i \leftrightarrow i'\) with \(\rho_i = \rho'_{i'}\) and \(\lambda_i = \lambda_{i'}\).
+    When there is no equality, none is in the union of the others.
+    Each has dimension blah.
+\end{theorem}
+\begin{proof}
+    TODO: fix statement and proof here.
+    Together, \cref{Q_comps} and \cref{g_irred_dim} tell us that \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) is irreducible, and therefore its image is irreducible.
+    They are equidimensional, as we will verify in a moment.
+    So, to verify that their closures are the irreducible components of \(\mathcal{P}_{wr}\), we need only check that none is contained in the union of the others.
+\end{proof}
+
+\subsection{The components of \(\mathcal{P}\)}
+\begin{corollary}
+    They are just the components of the \(\mathcal{P}_{wr}\)'s.
+\end{corollary}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{nilpotent_centralizer}
     Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).

### 2024-08-29 paper.tex
start on fixing linalg

@@
 \end{proof}
-For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
-\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
-Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
-So, we just have to find 
-\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]
-
-It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
-\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
-\[A_{ij} = \begin{pmatrix}
-    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
-\end{pmatrix}.\]
-Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
-\[v_{ij} = \begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
+
+\begin{lemma}
+    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
+    Let \(w \in \{1, ..., k\}\) and \(r \in \{1, ..., \lambda_w\}\).
+    The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that \(aM = a\) 
+\end{lemma}
 Now we determine which matrices of this form satisfy \(aA = a\).

### 2024-08-29 paper.tex
more about the linalg

@@
 \begin{proof}
-    The closure of \(G_{wr}\) in \(\gl_m\) is \(V = \{Y \in \mathfrak{z}_{\gl_m}(Y) : e_{wr} Y = e_{wr}\}\).
+    The closure of \(G_{wr}\) in \(\gl_m\) is \(V = \{Y \in \mathfrak{z}_{\gl_m}(X) : e_{wr} Y = e_{wr}\}\).
+    In the case that \(r = 0\), the constraint that \(e_{wr}Y = e_{wr}\) is no constraint at all, so we have \(G_{wr} = G\), and the result follows from \cref{g_irred_dim}.
+    \par In the case that \(r > 0\), we appeal to \cref{nilpotent_centralizer}, which tells us exactly what \(\mathfrak{z}_{\gl_m}(X)\) looks like.
+    Note that \(V = \{Y + I : Y \in \mathfrak{z}_{\gl_m}(X), e_{wr}Y = 0\}\).
+    The constraint \(e_{wr}Y = 0\) is just saying that a certain row of \(Y\) must be all zeroes.
+    Looking at the form of \(\mathfrak{z}_{\gl_m}(X)\), we see that requiring this row equal to zero for \(M \in \mathfrak{z}_{\gl_m}(X)\) is just the statement that \(M_{wr}\) is of the form
+    \[\]
+
+    From looking at the form of \(\mathfrak{z}_{\gl_m}(X)\) given in \cref{nilpotent_centralizer}, it is clear that 
     Lemma TODO says that \(V\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i', \lambda_j')}\).
@@
     Let \(w \in \{1, ..., k\}\) and \(r \in \{1, ..., \lambda_w\}\).
-    The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that \(aM = a\) 
+    Let \(i = [\sum_{j < w} \lambda_j] + (r - 1)\).
+    The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that \(\mathbbm{1}_iM = \mathbbm{1}_i\) is  
 \end{lemma}

### 2024-08-29 paper.tex
more linalg

@@
     In the case that \(r = 0\), the constraint that \(e_{wr}Y = e_{wr}\) is no constraint at all, so we have \(G_{wr} = G\), and the result follows from \cref{g_irred_dim}.
-    \par In the case that \(r > 0\), we appeal to \cref{nilpotent_centralizer}, which tells us exactly what \(\mathfrak{z}_{\gl_m}(X)\) looks like.
-    Note that \(V = \{Y + I : Y \in \mathfrak{z}_{\gl_m}(X), e_{wr}Y = 0\}\).
+    \par In the case that \(r > 0\), we observe that \(V = \{Y + I : Y \in \mathfrak{z}_{\gl_m}(X), e_{wr}Y = 0\}\).
     The constraint \(e_{wr}Y = 0\) is just saying that a certain row of \(Y\) must be all zeroes.
+    Looking at \cref{nilpotent_centralizer_row_zero}
     Looking at the form of \(\mathfrak{z}_{\gl_m}(X)\), we see that requiring this row equal to zero for \(M \in \mathfrak{z}_{\gl_m}(X)\) is just the statement that \(M_{wr}\) is of the form
@@
 
-\begin{lemma}
+\begin{corollary}\label{nilpotent_centralizer_row_zero}
     Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
     Let \(w \in \{1, ..., k\}\) and \(r \in \{1, ..., \lambda_w\}\).
-    Let \(i = [\sum_{j < w} \lambda_j] + (r - 1)\).
-    The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that \(\mathbbm{1}_iM = \mathbbm{1}_i\) is  
-\end{lemma}
-Now we determine which matrices of this form satisfy \(aA = a\).
-For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
-(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
-\par In the case that \(a = 0\), clearly every \(A\) works.
-Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
-Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
-That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
-This just requires that for each \(j\), we must have 
-\[v_{ij} = \begin{pmatrix}
+    Let \(i = [\sum_{j < w} \lambda_j] + r\).
+    The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that the \(i\)th row of \(M\) is equal to zero is the set of matrices
+    \[M = \begin{pmatrix}
+        M_{11} & \cdots & M_{1k} \\
+        \vdots & & \vdots\\
+        M_{k1} & \cdots & M_{kk}
+    \end{pmatrix},\]
+    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that:
+    \begin{itemize}
+        \item For \(i \neq w\), \(M_{ij}\) is lower-left Toeplitz
+        \item Each \(M_{wj}\) is of the form
+        \[M_{wj} = \begin{pmatrix}
             0\\
-    v_{ij}'
+            M_{wj}'
         \end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
-So, we have now found the set 
-\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
-It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
-\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
-    0\\
-    v_{ij}'
-\end{pmatrix},\]
-where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
+        where \(M_{wj}'\) is a \((\lambda_w - r) \times \lambda_j\) lower-left Toeplitz matrix.
+    \end{itemize}
+\end{corollary}
 
 \subsection{A `normalization' fact about Jordan bases}
-
 \begin{lemma}\label{normalization_helper_one}

### 2024-08-29 paper.tex
finish linalg thing (and use it!)

@@
     The constraint \(e_{wr}Y = 0\) is just saying that a certain row of \(Y\) must be all zeroes.
-    Looking at \cref{nilpotent_centralizer_row_zero}
-    Looking at the form of \(\mathfrak{z}_{\gl_m}(X)\), we see that requiring this row equal to zero for \(M \in \mathfrak{z}_{\gl_m}(X)\) is just the statement that \(M_{wr}\) is of the form
-    \[\]
-
-    From looking at the form of \(\mathfrak{z}_{\gl_m}(X)\) given in \cref{nilpotent_centralizer}, it is clear that 
-    Lemma TODO says that \(V\) is isomorphic to \(\mathbb{C}^{\sum_{ij} \min(\lambda_i', \lambda_j')}\).
+    So, the set of \(Y\) such that \(Y + I \in V\) is the set described by \cref{nilpotent_centralizer_row_zero}.
+    Hence \(V \cong \mathbb{C}^{\sum_{ij}\min(\lambda_i', \lambda_j')}\).
 \end{proof}

### 2024-08-29 paper.tex
title, etc
hyperref fanciness

@@
 
+\usepackage{hyperref}
 \usepackage[capitalize,nameinlink,noabbrev]{cleveref} % to emulate \autoref style
@@
 \newtheorem{corollary}[theorem]{Corollary}
-% \newcommand{\theoremautorefname}{Theorem}
-\newcommand{\lemmaautorefname}{Lemma}
-\newcommand{\definitionautorefname}{Definition}
 
@@
 
-% \author{Owen Conoly}
-% \date{Date}
-% \title{Title}
+\author{
+UROP+ Final Paper, Summer 2024\\
+Owen Conoly\\
+Mentor: Haoshuo Fu\\
+Project Suggested by: TODO: also Haoshuo?
+}
+\date{}
+\title{Title}
 
@@
 
-% \maketitle
+\maketitle
+\begin{abstract}
+
+\end{abstract}
 
@@
 
-\subsection{Springer fibers in \(\gl_m\)}
+\subsection{Springer fibers in \texorpdfstring{\(\gl_m\)}{gl\_m}}
 Now we let \(\mathcal{N}_m\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}_m\) the variety of Borel subalgebras of \(\gl_m\).
@@
 
-\section{Principal \(\spl_2\)-triple in \(\gl_n\)}
+\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}
 The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
@@
 
-\section{Finding \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
-\subsection{Finding the Slodowy slice \(S\)}
+\section{Finding \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
+\subsection{Finding the Slodowy slice \texorpdfstring{\(S\)}{S}}
 In the previous section we computed the principal \(\spl_2\)-triple \((e, h, f)\) in \(\gl_n\).
@@
 
-\subsection{A description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
+\subsection{A description of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
 Recall that we have the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p(Z), Z)\), where \(p : \gl_{m + n} \to \gl_m\) is the coordinate projection.
@@
 
-\section{Strategy for finding components of \(\mathcal{P}_{J(\lambda)}\)}
+\section{Strategy for finding components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}
 \par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
@@
 
-\section{The components of \(\mathcal{Q}\)}
+\section{The components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}
 \subsection{Setup}
@@
 
-\subsection{Study of \(B_{I, (\rho_i)}\)}
+\subsection{Study of \texorpdfstring{\(B_{I, (\rho_i)}\)}{B\_\{I, (p\_i)\}}}
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
@@
 
-\subsection{Study of \(\mathcal{Q}_{I, (\rho_i)}\)}
+\subsection{Study of \texorpdfstring{\(\mathcal{Q}_{I, (\rho_i)}\)}{Q\_\{I, (p\_i)\}}}
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
@@
 
-\section{The components of \(\mathcal{P}_{J(\lambda)}\)}
+\section{The components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}
 As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
@@
 And as before, \((e_{ij})_{ij}\) and \((f_j)_j\) form the standard basis for \(\mathbb{C}^{m + n}\).
-\subsection{The components of \(\mathcal{Q}_{wr}\)}
+\subsection{The components of \texorpdfstring{\(\mathcal{Q}_{wr}\)}{Q\_\{wr\}}}
 Recall from section 5 the varieties
@@
 
-\subsection{The varieties \(G_{wr}\) and \(G\)}
+\subsection{The varieties \texorpdfstring{\(G_{wr}\)}{G\_\{wr\}} and \texorpdfstring{\(G\)}{G}}
 Fix \(w,r\).
@@
 
-\subsection{The components of \(\mathcal{P}_{wr}\)}
+\subsection{The components of \texorpdfstring{\(\mathcal{P}_{wr}\)}{P\_\{wr\}}}
 Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
@@
 
-\subsection{The components of \(\mathcal{P}\)}
+\subsection{The components of \texorpdfstring{\(\mathcal{P}\)}{P}}
 \begin{corollary}
@@
 
-\section{The components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}
+\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
 Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).

### 2024-08-29 paper.tex
a couple typos, and fix gitignore
work on components of pwr.  I think the proof is not quite right.

@@
 \newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{remark}[theorem]{Remark}
 
@@
 Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
-Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
+Let \(S\) be the Slodowy slice \(E + \mathfrak{z}_{\gl_m}(F)\).
 We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
@@
 We also have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
-And from these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+From these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 \par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
@@
 \begin{proof}
-    We see from \cref{u_i_rho_irred_and_dim} that the \(\mathcal{Q}_{I, (\rho_i), \alpha}\) are irreducible and equidimensional.
-    Then \cref{bs_union} tells us that their union is \(\mathcal{Q}\), and in addition that none is contained in the union of the others.
+    By \cref{u_i_rho_irred_and_dim}, the \(\mathcal{Q}_{I, (\rho_i), \alpha}\) are irreducible and equidimensional.
+    Then \cref{bs_union} says that their union is \(\mathcal{Q}\), and in addition that none is contained in the union of the others.
 \end{proof}
@@
 
-\begin{theorem}
+\begin{theorem}\label{qwr_comps}
     The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
@@
 \begin{theorem}\label{pwr_comps}
-    The irreducible components of \(\mathcal{P}_{wr}\) are the closures of the images \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\).
-    Some irreduble components of \(\mathcal{P}_{wr}\) are double-counted; we have equality iff there's a bijection \(i \leftrightarrow i'\) with \(\rho_i = \rho'_{i'}\) and \(\lambda_i = \lambda_{i'}\).
-    When there is no equality, none is in the union of the others.
-    Each has dimension blah.
+    Every irreducible component of \(\mathcal{P}_{wr}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
+    Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
 \end{theorem}
-\begin{proof}
-    TODO: fix statement and proof here.
-    Together, \cref{Q_comps} and \cref{g_irred_dim} tell us that \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) is irreducible, and therefore its image is irreducible.
-    They are equidimensional, as we will verify in a moment.
-    So, to verify that their closures are the irreducible components of \(\mathcal{P}_{wr}\), we need only check that none is contained in the union of the others.
+\begin{remark}
+    \cref{pwr_comps} does not say ``the irreducible components of \(\mathcal{P}_{wr}\) are the closures of the subvarieties \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\)'', as that would seem to suggest some claim about distinctness.
+    Some more-careful analysis is required to determine which ones are distinct.
+\end{remark}
+\begin{proof}
+    Together, \cref{Q_comps} and \cref{g_irred_dim} tell us that the \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) are irreducible, and their union is \(\mathcal{Q}_{wr}\).
+    Hence their images are irreducible, and the surjectivity of \(\varphi_{wr}\) implies that their union of their images is \(\mathcal{P}_{wr}\).
+    \par Now, to verify that each image is an irreducible component, we need only verify that they are equidimensional.
+    Indeed, since \(\varphi_{wr}\) is a principal \(G_{wr}\)-bundle by \cref{principal_bundle}, we infer that the dimension of \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\) is \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha} + \dim G - \dim G_{wr}\).
+    We calculated these dimensions in \cref{qwr_comps}, \cref{g_irred_dim}, \cref{gwr_irred_dim}.
+    We see that \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) cancels with \(\dim G_{wr}\), and we are left with \(\dim G = \sum_{ij} \min(\lambda_i, \lambda_j)\).
+    \par TODO: can we conclude the difference-of-dimensions thing when the preimage isn't closed under action by \(G_{wr}\)?
+    Surely not... so this is all wrong.
+    I need to find out what happens when you let \(G_{wr}\) act on \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
 \end{proof}

### 2024-08-29 paper.tex
fix pwr components - fortunately the problem was small

@@
     \par Now, to verify that each image is an irreducible component, we need only verify that they are equidimensional.
-    Indeed, since \(\varphi_{wr}\) is a principal \(G_{wr}\)-bundle by \cref{principal_bundle}, we infer that the dimension of \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\) is \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha} + \dim G - \dim G_{wr}\).
-    We calculated these dimensions in \cref{qwr_comps}, \cref{g_irred_dim}, \cref{gwr_irred_dim}.
-    We see that \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) cancels with \(\dim G_{wr}\), and we are left with \(\dim G = \sum_{ij} \min(\lambda_i, \lambda_j)\).
-    \par TODO: can we conclude the difference-of-dimensions thing when the preimage isn't closed under action by \(G_{wr}\)?
-    Surely not... so this is all wrong.
-    I need to find out what happens when you let \(G_{wr}\) act on \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
+    We use the result of \cref{principal_bundle}, namely that \(\varphi_{wr}\) is a principal \(G_{wr}\)-bundle.
+    \par Let \(V_{w,r,I,(\rho_i),\alpha}\) be the closure of \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\) in \(\mathcal{Q}_{wr} \times G\) under action by \(G_{wr}\).
+    Clearly \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G) = \varphi_{wr}(V_{w,r,I,(\rho_i),\alpha})\).
+    So, we have only to compute the dimension of \(\varphi(V_{w,r,I,(\rho_i),\alpha})\).
+    \par This is easy, because \(\varphi_{wr}\) (and, consequently, the restriction of \(\varphi_{wr}\) to \(V_{w,r,I,(\rho_i),\alpha}\)) is a principal \(G_{wr}\)-bundle, and principal bundles play nicely with dimensions.
+    That is, we can conclude that 
+    \[\dim \varphi_{wr}(V_{w,r,I,(\rho_i),\alpha}) = \dim V_{w,r,I,(\rho_i),\alpha} - \dim G_{wr}.\]
+    Since \(\dim (\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G) = \dim (\mathcal{Q}_{wr} \times G)\) by \cref{qwr_comps}, we know that \(\dim V_{w,r,I,(\rho_i),\alpha} = \dim (\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G) = \dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha} + \dim G\).
+    By the equation above then, we get 
+    \[\dim \varphi_{wr}(V_{w,r,I,(\rho_i),\alpha}) = \dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha} + \dim G - \dim G_{wr}.\]
+    We already calculated those dimensions in \cref{qwr_comps}, \cref{g_irred_dim}, and \cref{gwr_irred_dim} respectively.
+    Referring to those, we see that \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) cancels with \(\dim G_{wr}\), and we are left with \(\dim G = \sum_{ij} \min(\lambda_i, \lambda_j)\).
 \end{proof}

### 2024-08-29 paper.tex
p comps

@@
 \begin{corollary}
-    They are just the components of the \(\mathcal{P}_{wr}\)'s.
+    Every irreducible components of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
+    Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
 \end{corollary}
+\begin{proof}
+    Follows directly from \cref{pwr_comps}.
+\end{proof}
 

### 2024-08-29 paper.tex
springer fiber components

--- 2024-08-29 paper.tex
@@
 We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the description above of \(S'\) will be good enough for our purposes.
-\begin{corollary}
+\begin{corollary}\label{sn_iso}
     \begin{align*}
@@
     \cref{pwr_comps} does not say ``the irreducible components of \(\mathcal{P}_{wr}\) are the closures of the subvarieties \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\)'', as that would seem to suggest some claim about distinctness.
-    Some more-careful analysis is required to determine which ones are distinct.
+    Further analysis is required to determine which ones are distinct.
 \end{remark}
@@
 \subsection{The components of \texorpdfstring{\(\mathcal{P}\)}{P}}
-\begin{corollary}
-    They are just the components of the \(\mathcal{P}_{wr}\)'s.
+\begin{corollary}\label{p_comps}
+    Every irreducible component of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
+    Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
 \end{corollary}
+\begin{proof}
+    Follows directly from \cref{pwr_comps}.
+\end{proof}
 
 \section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
+Recall from \cref{sn_iso} that 
+\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, (U_i), (V_i)) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
+We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, (U_i), (V_i)) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
+\begin{theorem}\label{springer_fiber_comps}
+    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
+    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j) + \sum_{i \neq j} \min(\lambda_i, \lambda_j)\).
+\end{theorem}
+\begin{proof}
+    The isomorphism sends \((A_{X,a,b}, (U_i), (V_i))\) to \(((A_{X, a, b}, U_i), (V_i))\).
+    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
+    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
+    Adding the dimensions gives the claimed result.
+\end{proof}
+
+Conjugating \(\pi^{-1}(J(\lambda))\) by \((centralizer of X) \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
+
+the Springer fiber at the \(n\)-Slodowy slice at
+
 Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).

### 2024-08-29 paper.tex
delete some garbage

@@
 \end{proof}
-
-Conjugating \(\pi^{-1}(J(\lambda))\) by \((centralizer of X) \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
-
-the Springer fiber at the \(n\)-Slodowy slice at
-
-Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).
-We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
-We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
-We will verify these things using our prvious computations of springer fibers.
+Conjugating \(\pi^{-1}(J(\lambda))\) by \(\GL_m \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
 

### 2024-08-30 paper.tex
find error.  didn't fix yet.  outline what still needs fixing.

@@
     The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
-    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
+    Further, the irreducible components are equidimensional, of dimension \(\sum_{i < j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
 \end{theorem}
@@
 \begin{theorem}\label{qwr_comps}
-    The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
-    Each has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+    The irreducible components of \(\mathcal{Q}_{wr}\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
+    Each has dimension \(\sum_{i \leq j} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
 \end{theorem}
@@
     \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+    TODO: this is wrong. fix.
 \end{lemma}
@@
     Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
+    TODO: error propagated here from \cref{gwr_irred_dim}. fix.
 \end{theorem}
@@
     Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
+    TODO: error propagated here from \cref{pwr_comps}. fix.
 \end{corollary}
@@
     Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j) + \sum_{i \neq j} \min(\lambda_i, \lambda_j)\).
+    TODO: error propagated here from \cref{p_comps}.
 \end{theorem}
@@
 \end{proof}
+
+\begin{theorem}
+    Components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) are blah.
+\end{theorem}
+\begin{proof}
     Conjugating \(\pi^{-1}(J(\lambda))\) by \(\GL_m \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
+\end{proof}
 

### 2024-08-30 paper.tex
mostly fix error

@@
 \begin{lemma}\label{gwr_irred_dim}
-    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
-    TODO: this is wrong. fix.
+    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
 \end{lemma}
@@
     We already calculated those dimensions in \cref{qwr_comps}, \cref{g_irred_dim}, and \cref{gwr_irred_dim} respectively.
-    Referring to those, we see that \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) cancels with \(\dim G_{wr}\), and we are left with \(\dim G = \sum_{ij} \min(\lambda_i, \lambda_j)\).
+    Referring to those, we get 
+    \[\sum_{i \leq j} \min(\lambda_i', \lambda_j') + \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_{ij} \min(\lambda_i, \lambda_j').\]
+    Now, \(\sum_{i \leq j} \min(\lambda_i', \lambda_j') + r \#\{i : \lambda_i \geq= \sum_{i \leq j} \min(\lambda_i, \lambda_j)\)
+    something something cancels out.
+    see that \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) cancels with \(\dim G_{wr}\), and we are left with \(\dim G = \sum_{ij} \min(\lambda_i, \lambda_j)\).
 \end{proof}

### 2024-08-30 paper.tex
fix dimension calculations

@@
     Every irreducible component of \(\mathcal{P}_{wr}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
-    Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
-    TODO: error propagated here from \cref{gwr_irred_dim}. fix.
+    Each has dimension \(\sum_{i \leq j} \min(\lambda_i, \lambda_j)\).
 \end{theorem}
@@
     Referring to those, we get 
-    \[\sum_{i \leq j} \min(\lambda_i', \lambda_j') + \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_{ij} \min(\lambda_i, \lambda_j').\]
-    Now, \(\sum_{i \leq j} \min(\lambda_i', \lambda_j') + r \#\{i : \lambda_i \geq= \sum_{i \leq j} \min(\lambda_i, \lambda_j)\)
-    something something cancels out.
-    see that \(\dim \mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) cancels with \(\dim G_{wr}\), and we are left with \(\dim G = \sum_{ij} \min(\lambda_i, \lambda_j)\).
+    \begin{equation}\label{the_equation}
+        \dim \varphi_{wr}(V_{w,r,I,(\rho_i),\alpha}) = \sum_{i \leq j} \min(\lambda_i', \lambda_j') + \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_{ij} \min(\lambda_i, \lambda_j').
+    \end{equation}
+    Now,
+    \[\sum_{i \leq j} \min(\lambda_i', \lambda_j') = \sum_{i \leq j} \min(\lambda_i, \lambda_j) - \sum_j \min(\lambda_w, \lambda_j) + \sum_j \min(\lambda_w - r, \lambda_j),\]
+    and
+    \[\sum_{ij} \min(\lambda_i, \lambda_j') = \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_i \min(\lambda_i, \lambda_w) + \sum_i \min(\lambda_i, \lambda_w - r).\]
+    Substituting these into the RHS of \cref{the_equation}, things cancel out, and we get
+    \[\sum_{i \leq j} \min(\lambda_i, \lambda_j) + \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_{ij} \min(\lambda_i, \lambda_j) = \sum_{i \leq j} \min(\lambda_i, \lambda_j).\]
 \end{proof}
@@
     Every irreducible component of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
-    Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
-    TODO: error propagated here from \cref{pwr_comps}. fix.
+    Each has dimension \(\sum_{i \leq j} \min(\lambda_i, \lambda_j)\).
 \end{corollary}
@@
     \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
-    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j) + \sum_{i \neq j} \min(\lambda_i, \lambda_j)\).
-    TODO: error propagated here from \cref{p_comps}.
+    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
 \end{theorem}
@@
     Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
-    Adding the dimensions gives the claimed result.
+    Adding the dimensions gives 
+    \[\sum_{i \leq j} \min(\lambda_i, \lambda_j) + \sum_{i < j} \min(\lambda_i, \lambda_j) = \sum_{ij} \min(\lambda_i, \lambda_j).\]
 \end{proof}
@@
 \begin{proof}
+    TODO.
     Conjugating \(\pi^{-1}(J(\lambda))\) by \(\GL_m \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
@@
 In this section we prove linear algebra facts that were used earlier.
-They are confined to this section to avoid interrupting the flow of the paper.
+They are confined to this section to avoid interrupting the rest of the paper.
 

### 2024-08-30 paper.tex
start talking about components of s x n

@@
 \begin{proof}
-    The isomorphism sends \((A_{X,a,b}, (U_i), (V_i))\) to \(((A_{X, a, b}, U_i), (V_i))\).
+    The isomorphism sends \((A_{X,a,b}, (U_i), (V_i))\) to \(((A_{X, a, b}, (U_i)), (V_i))\).
     The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
@@
 
+Let \(\lambda\) be any partition of \(m\).
+Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by conjugation; that is,
+\[(P, I_n) \cdot (A_{X, a, b}, (U_i), (V_i)) := ((P,I_n)A_{X,a,b}P^{-1},(P,I_n)^{-1}(U_i), (P,I_n)(V_i)).\]
+
+Similarly to the \(\varphi_{wr}\)'s, define \(\phi_\lambda : \pi^{-1}(J(\lambda)) \times (\GL_m \times \{I_n\}) \to S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) by \(\phi_\lambda(x, g) = g \cdot x\).
 \begin{theorem}
-    Components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) are blah.
+    The irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) are indexed by partitions \(\lambda\) of \(m\).
+    For each irreducible component
+    closures of the images \(\varphi_\lambda\)
 \end{theorem}

### 2024-08-30 paper.tex
make intro less wordy

@@
 Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
-\par In section 2, we review some preliminary material.
-In section 3, we find the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
-In section 4, we embed this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
-We compute the Slodowy slice, and we end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-\par In section 5, we discuss how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
-In section 6 we solve the easier problem.
-In section 7 we find the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
-In section 8 we apply the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-In section 9 we discuss an interesting direction for future work.
-Then in section 10 we prove some linear algebra facts that were used in the paper.
+\par Section 2 reviews some preliminary material.
+Section 3 finds the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
+Section 4 embeds this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
+We compute the Slodowy slice and end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par Section 5 discusses how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
+Section 6 solves the easier problem.
+Section 7 finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
+Section 8 applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+Section 9 discusses an interesting direction for future work.
+Finally, section 10 proves some linear algebra lemmas that were used in the paper.
 

### 2024-08-30 paper.tex
acknowledgement
finish section 8!

@@
 Finally, section 10 proves some linear algebra lemmas that were used in the paper.
+
+\subsection{Acknowledgment}
+TODO.  UROP+ program and Haoshuo.
+MIT (provided funding)?
 
@@
 \begin{proof}
+    TODO: clean up.
     Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
@@
 \begin{proof}
+    TODO: fix.
     Now, if \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
@@
     % \end{itemize}
-    Observe that conjugation by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and conjugation by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
-\end{proof}
-In the next section we will find the irreducible components of \(\mathcal{Q}'\).
+    Change of basis by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and conjugation by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
+\end{proof}
+The next section finds the irreducible components of \(\mathcal{Q}'\).
 To avoid death by primes, we will refer to it as \(\mathcal{Q}\), and refer to \(m',n'\) as \(m,n\), and so on, throughout the next section.
@@
 Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by conjugation; that is,
-\[(P, I_n) \cdot (A_{X, a, b}, (U_i), (V_i)) := ((P,I_n)A_{X,a,b}P^{-1},(P,I_n)^{-1}(U_i), (P,I_n)(V_i)).\]
-
-Similarly to the \(\varphi_{wr}\)'s, define \(\phi_\lambda : \pi^{-1}(J(\lambda)) \times (\GL_m \times \{I_n\}) \to S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) by \(\phi_\lambda(x, g) = g \cdot x\).
+\[(P, I_n) \cdot (A_{X, a, b}, (U_i), (V_i)) := \]
+\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},(P,I_n)(U_i), (P,I_n)(V_i)).\]
+Let 
+\[K = \{(g, I_n) \in \GL_m \times \{I_n\} : gXg^{-1} = X\}.\]
+
+Define \(\phi_\lambda : \pi^{-1}(J(\lambda)) \times (\GL_m \times \{I_n\}) \to S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) by \(\phi_\lambda(x, g) = g \cdot x\).
+
+\begin{lemma}\label{principal_bundle_two}
+    For each partition \(\lambda\) of \(m\), the map \(\phi_\lambda\) is a principal \(K\)-bundle.
+\end{lemma}
+\begin{proof}
+    Analogous to \cref{principal_bundle}.
+\end{proof}
+
+Let \((C_{\lambda, \beta})_\beta\) be the irreducible components of \(\pi^{-1}(J(\lambda))\).
+These are described by \cref{springer_fiber_comps}.
+
 \begin{theorem}
-    The irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) are indexed by partitions \(\lambda\) of \(m\).
-    For each irreducible component
-    closures of the images \(\varphi_\lambda\)
+    Every irreducible component of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is the closure of some subvariety of the form \(\phi_\lambda(C_{\lambda,\beta} \times (\GL_m \times \{I_n\}))\), and the closure of each subvariety of this form is an irreducible component.
+    Each has dimension \(m^2\).
 \end{theorem}
 \begin{proof}
-    TODO.
-    Conjugating \(\pi^{-1}(J(\lambda))\) by \(\GL_m \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
+    This is analogous to \cref{pwr_comps}; the only difference is the dimension calculation.
+    This time, we have 
+    \begin{align*}
+        \dim \phi_\lambda(C_{\lambda, \beta} \times (\GL_m \times \{I_n\})) & = \\
+        \dim C_{\lambda,\beta} + \dim \GL_m - \dim K & = \\
+        \sum_{ij} \min(\lambda_i, \lambda_j) + m^2 - \sum_{ij} \min(\lambda_i, \lambda_j) & = \\
+        m^2 & .
+    \end{align*}
+    The dimension of \(C_{\lambda, \beta}\) comes from \cref{pwr_comps}; the dimension of \(\GL_m\) is obvious; and the dimension of \(K\) comes from \cref{nilpotent_centralizer}.
 \end{proof}

### 2024-08-30 paper.tex
mostly finish future work section

@@
 \section{Future work}
-The paper (TODO: cite) describes a correspondence between Steinberg variety and pairs of young tableaux.  
-We observe that \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something liek the stienber variety.
-Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of yound tableaux: one of shape of \(X\), one of shape of \(A_{X, a, b}\).
+The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
+The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
+Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
 \par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

### 2024-08-30 paper.tex
remove garbage.  small wording fixes.

@@
 Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
-Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
+% Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
 If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
@@
     \[\begin{pmatrix}0 & Z_{12}f\\0 & Z_{22} f\end{pmatrix} =  ZF = FZ = \begin{pmatrix}0 & 0\\fZ_{21} & fZ_{22}\end{pmatrix}.\]
-    We see that there is no restriction on \(Z_{11}\).
+    There is no restriction on \(Z_{11}\).
     The condition \(Z_{12}f = 0\) means that all but the last column of \(Z_{12}\) must be zero, and the condition \(0 = fZ_{21}\) means that all but the first row of \(Z_{21}\) must be zero.
@@
     \par Hence every element of \(S'\) must simply have \(e\) in its bottom-right block.
-    We see that every element of \(S'\) is of the desired form.
+    So, every element of \(S'\) is of the desired form.
 \end{proof}
@@
     \end{align*}
-        We see that the fibers are exactly the \(G_{wr}\)-orbits; or in other words, \(G_{wr}\) acts transitively on the fibers, as desired.
-    % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
-    % Let \(X_1, ..., X_k\) be the irreducible components of \(\mathcal{Q}_{wr}\).
-    % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
-    % And if we take \(x \in X_i \setminus \bigcup_{j \neq i} X_j\), it is clear (since \(G\) acts faithfully on itself) that \(\varphi(x, I_m)\)
-    % All that remains is to show that \(X_i \notin \bigcup_{j \neq i} \overline{\varphi(X_i \times G)}\).
-    % Indeed, 
+    Thus the fibers are exactly the \(G_{wr}\)-orbits; or in other words, \(G_{wr}\) acts transitively on the fibers, as desired.
 \end{proof}
@@
     \end{align*}
-    Observing that \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_k])\), the equation above gives the desired result.
+    Since \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_k])\), the equation above implies the desired result.
 \end{proof}
@@
 Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
-\par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par Separately, this paper would benefit from an introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 

### 2024-08-30 paper.tex
fix pronouns???  i think they're better now

@@
 \begin{proof}
-    Here I use the notation \(x \times y = (x, y)\), and so on.
+    Here we use the notation \(x \times y = (x, y)\), and so on.
     The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
@@
 In this subsection we find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
-\par I claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).
+\par We claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).
 By finding a algebraic map taking \(b \in B_{I, (\rho_i)}\) to a Jordan basis for \(A_{0,b}\), we will put \(\mathcal{Q}_{I, (\rho_i)}\) in isomorphism with the product \(B_{I, (\rho_i)} \times (Springer fiber at J(\mu))\).
@@
         Because every \(i \in I\) satisfies \(q_i < n\), clearly \(\langle e_{ij}\rangle_{i,j : q_i \geq n} \subseteq W\).
-        \par I claim that \(f_n \in W\) as well.
-        To see this, we consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).
+        \par We claim that \(f_n \in W\) as well.
+        To see this, consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).
         As explained in the proof of (1), we have \(A^{n + p_{i_1}} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
@@
     Clearly this is a Jordan basis for \(A\).
-    Further, I claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
+    Further, we claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
     It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).

### 2024-08-30 paper.tex
fix (I hope) the last mathematically defective proof. now I think there are only expositionally defective proofs.

@@
 \end{pmatrix}.\]
+A partition is always indexed in nonincreasing order, even if it is defined differently.
+For example, if \(\mu = (4, 6, 3)\), then \(\mu_1 = 6, \mu_2 = 4, \mu_3 = 3\).
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{pwr_union}
     \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
@@
 \begin{proof}
-    TODO: clean up.
-    Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
-    Define \(f : \mathbb{C}^m \to \mathbb{C}\) by \(f(e_{ij}) = a_{ij}\).
-    We take the coordinate-free view of \(A_{a,b}\) as the linear transformation \(T\) that sends \(e_{ij}\) to \(e_{i,j - 1} + f(e_{ij})\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
-    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P\) such that \(Pe_{ij}\) forms a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
-    \par Because \(Pe_{ij}\) is a Jordan basis, \(A_{a',b'}\) of \(T\) in this new basis has the same upper-left corner \(X\); and since \(f(Pe_{ij}) = 0\) for all but one pair \((i,j)\), we have \(a'_{ij} = 0\) for all but one pair \((i,j)\).
+    For any \(a \in \mathbb{C}^m\), define \(f_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_i \mapsto 0\).
+    For this proof we take the coordinate-free view of \(A_{a,b}\) as the linear transformation \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + f_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
+    \par Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
+    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that \(Pe_{ij}\) forms a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
+    \par Now let \(Q = (P^{-1}, I_n)A_{a,b}(P, I_n)\).
+    Since \(Pe_{ij}\) is a Jordan basis, we have \(Q = A_{a',b'}\) for some \(a',b' \in \mathbb{C}^m\).
+    All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
+    Indeed, this results from the fact that \(f_{a'}(e_{ij}) = f_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
 \end{proof}
@@
     \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
+\end{lemma}
+\begin{proof}
+    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
+    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
+    \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
+    Let \(k \geq 0\) be minimal so that \(A_{e_{w_1r_1},0} f_1 \neq 0\).
+    Obviously \(k = r_1\).
+    Since \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
+    Hence \(r_1 = r_2\).
+    Now, if \(r_1 = 0\), we are done.
+    \par Otherwise, we have \(r_1 > 0\).
+    Let \(k' \geq 0\) be maximal so that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
+    Obviously \(k' = \lambda_{w_1} - r_1\).
+    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so we see that \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
+\end{proof}
+
+\begin{lemma}
     When \(\mathcal{P}_{w_1r_1} \neq \mathcal{P}_{w_2r_2}\), we have \(\mathcal{P}_{w_1r_1} \cap \mathcal{P}_{w_2r_2} = \emptyset\). 
@@
 \begin{proof}
-    TODO: fix.
-    Now, if \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
-    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
-    Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
-    Then there is \(P\) such that \((P^{-1},I_n) A_{e_{w_1r_1},b} (P, I_n) = A_{e_{w_2r_2}, b'}\).
-
-    Then, either there is \(k\) such that (for any \(b_1',b_2'\)) \(A_{e_{w_1r_1}b_1'}^k \)
-    \par The second observation, that the nonequal sets are disjoint, just follows from the fact that (this restricted form of) similarity is an equivalence relation.
+    It suffices to remark that \(\{(x,y) : \exists w,r. \; x,y \in \mathcal{P}_{wr}\}\) is an equivalence relation.
+    Reflexivity is the statement of \cref{pwr_union}, and associativity and transitivity are obvious from the definition of \(\mathcal{P}_{wr}\).
 \end{proof}

### 2024-08-30 paper.tex
thoughts from meeting

@@
 \usepackage[capitalize,nameinlink,noabbrev]{cleveref} % to emulate \autoref style
+% \usepackage{fullpage}
 
@@
 Mentor: Haoshuo Fu\\
-Project Suggested by: TODO: also Haoshuo?
+Project Suggested by: Haoshuo Fu
 }
 \date{}
-\title{Title}
-
+\title{Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice}
+
+% email to andre when done
 \begin{document}
@@
 \begin{abstract}
-
+    with more words than symbols, what is springer fiber of hook-type slodowy slice.
+    we show that its irreducible components have the same dimensions.
+    and use this to study another variety.
 \end{abstract}
+
+\tableofcontents
 
@@
 Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
+\par Before talking about future work, say what is the main result of the paper.
+
+\subsection{Future Work}
+\par irreducble components have module structure of group algebra of Sn.
+has applications to representation theory.
+write about this here.
+The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
+The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
+Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
+
+\subsection{Overview}
 \par Section 2 reviews some preliminary material.
@@
 Thus, the Springer fiber at \(X \in \mathcal{N}\) is 
-\[S_X = \{gHg^{-1} : X \in gHg^{-1}\}.\]
+\[\mathcal{F}_X = \{gHg^{-1} : X \in gHg^{-1}\}.\]
+% ^ use that notation everywhere for springer fiber
 \begin{definition}
@@
 
-\section{Future work}
-The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
-The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
-Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
-\par Separately, this paper would benefit from an introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+% \section{Future work}
+% \par Separately, this paper would benefit from an introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 

### 2024-09-01 paper.tex
future work section

@@
 \DeclareMathOperator{\ad}{ad}
+\DeclareMathOperator{\irrrep}{IrrRep}
+\DeclareMathOperator{\Irr}{Irr}
+\DeclareMathOperator{\Hom}{Hom}
+\DeclareMathOperator{\St}{St}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \subsection{Future Work}
-\par irreducble components have module structure of group algebra of Sn.
-has applications to representation theory.
-write about this here.
-The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
-The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
-Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
+We describe a possible extension to this work and an application to representation theory.
+\par The \emph{Steinberg variety} of a Lie algebra \(\mathfrak{h}\) is \(\St_\mathfrak{h} = \widetilde{\mathcal{N}}_\mathfrak{h} \times_\mathfrak{h} \widetilde{\mathcal{N}}_\mathfrak{h}\), where the map \(\widetilde{\mathcal{N}}_\mathfrak{h} \to \mathfrak{h}\) is the Springer resolution.
+For nice (TODO: how nice?) \(\mathfrak{h}\), there is a correspondence between the Weyl group of \(\mathfrak{h}\) and irreducible components of \(\St_\mathfrak{h}\)\cite{zhiweiyun}[1.5.10].
+\par There is a nice bijection between \(\St_{\gl_m}\) and the set \(T_m = \{(t_1, t_2) : \lambda \vdash m; t_1, t_2 \in \mathrm{SYT}(\lambda)\}\).
+(Note that \(\mathrm{SYT}(\lambda)\) denotes the set of standard Young tableaux of shape \(\lambda\).)
+One way to obtain this bijection is as follows.
+First take the aforementioned correspondence between \(\St_{\gl_m}\) and the Weyl group of \(\gl_m\)---the Weyl group of \(\gl_m\) is the symmetric group \(S_m\).
+Then take the Robinson-Schensted-Knuth correspondence, which is a bijection between \(S_m\) and \(T_m\).
+More details about the the correspondence \(\St_{\gl_m} \leftrightarrow T_m\) can be found in \cite{wolff}.
+\par An element of \(\St_{\gl_m}\) consists of a triple \((X, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(\mathfrak{b}_1\) and \(\mathfrak{b}_2\) are elements of the Springer fiber at \(X\).
+When the Jordan form of \(X\) has shape \(\lambda\), the correspondence sends this triple to a pair \((t_1, t_2)\), where both are of shape \(\lambda\).
+\par Somewhat similarly, we will show that an element of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) consists of a tuple \((X, Y, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(X \in \mathcal{N}_m, Y \in \mathcal{N}_{m + n}\), and \(\mathfrak{b}_1, \mathfrak{b}_2\) are elements of the Springer fiber at \(X, Y\) respectively.
+(Some nontrivial relation will hold between \(X\) and \(Y\), but we ignore that for now.)
+For any given relation \(R \subseteq \{\lambda : \lambda \vdash m\} \times \{\mu : \mu \vdash (m + n)\}\), we can define 
+\[T_{m,n} = \{(t_1, t_2) : \lambda \vdash m; \mu \vdash (m + n); t_1 \in \mathrm{SYT}(\lambda); t_2 \in \mathrm{SYT}(\mu); R(\lambda, \mu)\}.\]
+We conjecture that there is a correspondence, analogous to \(\St_{\gl_m} \leftrightarrow T_m\), between \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and \(T_{m,n}\) (for some appropriate choice of the relation \(R\)).
+An extension of this project would determine the details of this correspondence.
+\par Given \(C \in \Irr(\St_{\gl_m})\), we can first map it to the corresponding \((t_1, t_2) \in T_m\), and then obtain an element of \(\End(\mathbb{C}[\mathrm{SYT}(\lambda)])\) by taking the map which sends \(t_1 \mapsto t_2\) and \(t' \mapsto 0\) for \(t' \in \mathrm{SYT}(\lambda) \setminus \{t_1\}\).
+In this way, we obtain a \(\mathbb{C}\)-algebra isomorphism
+\[\mathbb{C}[\Irr(\widetilde{\mathcal{N}} \times_\mathfrak{g} \widetilde{\mathcal{N}})] \cong \bigoplus_{\lambda \vdash m} \End(\mathbb{C}[\mathrm{SYT}(\lambda))).\]
+This is an instance of the fact that for any finite group \(G\), we have \(\mathbb{C}[G] \cong \bigoplus_{V \in \irrrep(G)} \End(\mathbb{C}[\mathrm{SYT}(\lambda)])\).
+\par If we found a correspondence \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \leftrightarrow T_{m,n}\), this could give an analogous isomorphism 
+\[\mathbb{C}[\Irr(S \times_\mathfrak{g} \widetilde{\mathcal{N}})] \cong \bigoplus_{(\lambda, \mu) \in R} \Hom(\mathbb{C}[\mathrm{SYT}(\lambda)], \mathbb{C}[\mathrm{SYT}(\mu)]),\]
+which would be an isomorphism of \(\mathbb{C}[S_m]\)- or \(\mathbb{C}[S_{m + n}]\)-modules instead of \(\mathbb{C}\)-algebras.
+(To give the RHS the structure of a \(\mathbb{C}[S_m]\)-module, we just view \(\mathbb{C}[\mathrm{SYT}(\lambda)]\) as a representation of \(S_m\) in the standard way.)
+% \par irreducble components have module structure of group algebra of Sn.
+% has applications to representation theory.
+% write about this here.
+% The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
+% The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
+% Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
 

### 2024-09-01 paper.tex
abstract

@@
 \begin{abstract}
-    with more words than symbols, what is springer fiber of hook-type slodowy slice.
-    we show that its irreducible components have the same dimensions.
+    Let \(e\), be a regular nilpotent element of \(\gl_n\), \(n \geq 1\).
+    We consider the Slodowy slice \(S\) at the element \((0, e) \in \gl_m \times \gl_n \subseteq \gl_{m + n}\).
+    We define the \emph{Springer fiber of S} at a nilpotent \(X \in \gl_m\) as consisting of the following data: some \(Y \in S\), along with an element of the usual Springer fiber at \((X, Y) \in \gl_m \times \gl_{m + n}\).
+    The main result of this paper is finding the (equidimensional) irreducible components of a Springer fiber of \(S\).
+    To do this, we use a well-known result classifying the irreducible components of the usual Springer fiber at a nilpotent element of \(\gl_m\).
+    We then use our result to find the (equidimensional) irreducible components of the variety consisting of pairs \((X, \mathcal{F})\), where \(X \in \gl_m\) is nilpotent and \(\mathcal{F}\) is an element of the Springer fiber of \(S\) at \(X\).
+    We conjecture that there is a correspondence, akin to the geometric RSK correspondence, between irreducible components of this last variety and certain pairs of standard Young tableaux. 
     and use this to study another variety.

### 2024-09-01 paper.tex
beginning of intro

--- 2024-08-30 paper.tex
@@
 \begin{abstract}
-    with more words than symbols, what is springer fiber of hook-type slodowy slice.
-    we show that its irreducible components have the same dimensions.
-    and use this to study another variety.
+    Let \(n \geq 1\), and let \(e\) be a regular nilpotent element of \(\gl_n\).
+    Let \(m \geq 0\), and consider the Slodowy slice \(S\) at the element \((0, e) \in \gl_m \times \gl_n \subseteq \gl_{m + n}\).
+    We define the \emph{Springer fiber of S} at a nilpotent \(X \in \gl_m\) as consisting of the following data: an element \(Y \in S\) which projects to \(X\) coordinate-wise, along with an element of the usual Springer fiber at \((X, Y) \in \gl_m \times \gl_{m + n}\).
+    The main result of this paper is finding the (equidimensional) irreducible components of a Springer fiber of \(S\).
+    To do this, we use a well-known result classifying the irreducible components of the usual Springer fiber at a nilpotent element of \(\gl_m\).
+    We then use our result to find the (equidimensional) irreducible components of the variety consisting of pairs \((X, \mathcal{F})\), where \(X \in \gl_m\) is nilpotent and \(\mathcal{F}\) is an element of the Springer fiber of \(S\) at \(X\).
+    We conjecture that there is a correspondence, akin to the geometric RSK correspondence, between irreducible components of this last variety and certain pairs of standard Young tableaux. 
 \end{abstract}
@@
 \section{Introduction}
-Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
-% The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
-% Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
-% The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
-% Let
-% \[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
-% \[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
-Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) be the Springer resolution.
-\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
+Let \(m \geq 0, n \geq 1\), and define \(\mathfrak{g} = \gl_m \times \gl_{m + n}\).
+Let \(\mathcal{N}\) be the nilpotent cone in \(\mathfrak{g}\), and let \(\widetilde{\mathcal{N}} \to \mathcal{N}\) be the Springer resolution.
+\par Let \((e, h, f)\) be a principal \(\spl_2\)-triple in \(\gl_n\).
 We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
@@
 We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
-Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
-(It turns out that this map is surjective.)
-Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
-Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+Restricting to \(S\), we obtain a projection \(p' : S \to \gl_m\).
+(It turns out that \(p'\) is surjective.)
+Then, we obtain \(p : S \to \mathfrak{g}\) by \(x \mapsto (x, p'(x))\).
+Taking the map \(p : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 \par In this paper we study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-% The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
-The main section of this paper will study the fibers of this map.
-Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
-\par Before talking about future work, say what is the main result of the paper.
+As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
+Given \(X \in \mathcal{N}_m\), we call \(\pi^{-1}(X)\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
+\par The main result of this paper is a classification of the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
+Then we use this result to determine the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 
 \subsection{Future Work}
-\par irreducble components have module structure of group algebra of Sn.
-has applications to representation theory.
-write about this here.
-The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
-The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
-Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
+We describe a possible extension of the result of this paper, as well as an application to representation theory.
+\par The \emph{Steinberg variety} of a Lie algebra \(\mathfrak{h}\) is \(\St_\mathfrak{h} = \widetilde{\mathcal{N}}_\mathfrak{h} \times_\mathfrak{h} \widetilde{\mathcal{N}}_\mathfrak{h}\), where the map \(\widetilde{\mathcal{N}}_\mathfrak{h} \to \mathfrak{h}\) is the Springer resolution.
+There is a bijective correspondence between the Weyl group of \(\gl_m\) and irreducible components of \(\St_\mathfrak{\gl_m}\)(see \cite{ehf}[3.6] for details).
+\par There is a nice bijection between \(\St_{\gl_m}\) and the set \(T_m = \{(t_1, t_2) : \lambda \vdash m; t_1, t_2 \in \mathrm{SYT}(\lambda)\}\).
+(Note that \(\mathrm{SYT}(\lambda)\) denotes the set of standard Young tableaux of shape \(\lambda\).)
+One way to obtain such a bijection is as follows.
+First take the aforementioned correspondence between \(\St_{\gl_m}\) and the Weyl group \(S_m\) of \(\gl_m\).
+Then take the Robinson-Schensted-Knuth (RSK) correspondence, which gives a bijection between \(S_m\) and \(T_m\).
+A more direct and illuminating explanation of the correspondence \(\St_{\gl_m} \leftrightarrow T_m\) is given by the geometric RSK correspondence, as described in \cite{geomRSK}.
+\par An element of \(\St_{\gl_m}\) is a triple \((X, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(\mathfrak{b}_1\) and \(\mathfrak{b}_2\) are elements of the Springer fiber at \(X\).
+When the Jordan form of \(X\) has shape \(\lambda\), the correspondence sends this triple to a pair \((t_1, t_2)\), where both are of shape \(\lambda\).
+\par Somewhat similarly, we will show that an element of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is a subset of the set of tuples \((X, Y, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(X \in \mathcal{N}_m, Y \in \mathcal{N}_{m + n}\), and \(\mathfrak{b}_1, \mathfrak{b}_2\) are elements of the Springer fiber at \(X, Y\) respectively.
+For any given relation \(R \subseteq \{\lambda : \lambda \vdash m\} \times \{\mu : \mu \vdash (m + n)\}\), we can define 
+\[T_{m,n} = \{(t_1, t_2) : \lambda \vdash m; \mu \vdash (m + n); t_1 \in \mathrm{SYT}(\lambda); t_2 \in \mathrm{SYT}(\mu); R(\lambda, \mu)\}.\]
+We conjecture that, for some appropriate choice of the relation \(R\), there is a correspondence, analogous to \(\St_{\gl_m} \leftrightarrow T_m\), between \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and \(T_{m,n}\).
+An extension of this project would determine the details of this correspondence.
+\par Given an irreducible component \(C \in \Irr(\St_{\gl_m})\), we can first map it to the corresponding \((t_1, t_2) \in T_m\), and then obtain an element of \(\End(\mathbb{C}[\mathrm{SYT}(\lambda)])\) by taking the map which sends \(t_1 \mapsto t_2\) and \(t' \mapsto 0\) for \(t' \in \mathrm{SYT}(\lambda) \setminus \{t_1\}\).
+In this way, we obtain a \(\mathbb{C}\)-algebra isomorphism
+\[\mathbb{C}[\Irr(\St_{\mathfrak{\gl_m}})] \cong \bigoplus_{\lambda \vdash m} \End(\mathbb{C}[\mathrm{SYT}(\lambda))).\]
+This is an instance of the fact that for any finite group \(G\), we have \(\mathbb{C}[G] \cong \bigoplus_{V \in \irrrep(G)} \End(V)\).
+\par If we had a correspondence \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \leftrightarrow T_{m,n}\), this could give an analogous isomorphism 
+\[\mathbb{C}[\Irr(S \times_\mathfrak{g} \widetilde{\mathcal{N}})] \cong \bigoplus_{(\lambda, \mu) \in R} \Hom(\mathbb{C}[\mathrm{SYT}(\lambda)], \mathbb{C}[\mathrm{SYT}(\mu)]),\]
+which would be an isomorphism of \(\mathbb{C}[S_m]\)- or \(\mathbb{C}[S_{m + n}]\)-modules rather than \(\mathbb{C}\)-algebras.
+(To give the RHS the structure of a \(\mathbb{C}[S_m]\)-module, we just view \(\mathbb{C}[\mathrm{SYT}(\lambda)]\) as a representation of \(S_m\) in the standard way.)
 

### 2024-09-01 paper.tex
label sections.  delete commented-out section.

@@
 
-\section{Preliminary Definitions and Facts}
+\section{Preliminary Definitions and Facts}\label{prelim}
 \subsection{Conventions and Notations}
@@
 
-\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}
+\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{prelim}
 The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
@@
 
-% \section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
-% TODO: I am unsure why this section is interesting or what to say about it.
-% Should I delete it?
-% For now I will ignore it and try to make the paper flow nicely without it.
-
-% Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
-% We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
-% % First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).
-
-% \begin{lemma}\label{sl2_triple}
-%     There is exactly one way to choose \(H, F \in \gl_{m + n}\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
-% \end{lemma}
-% \begin{proof}
-% Suppose we have \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
-% Writing \(F =: \begin{pmatrix}
-%     F_{11} & F_{12} \\
-%     F_{21} & f
-% \end{pmatrix}\), and similarly for \(H\), we have
-% \[2E = [H, E] = \begin{pmatrix}
-%     0 & H_{12}e \\
-%     0 & he
-% \end{pmatrix} - \begin{pmatrix}
-%     0 & 0 \\
-%     e H_{21} & eh
-% \end{pmatrix},\]
-% \[H = [E, F] = \begin{pmatrix}
-%     0 & 0 \\
-%     e F_{21} & ef
-% \end{pmatrix} - \begin{pmatrix}
-%     0 & F_{12}e \\
-%     0 & fe
-% \end{pmatrix}.\]
-% From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in \cref{simple_sl2_triple}.
-% We also see that \(H_{11} = 0\).
-% Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
-% % Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
-% Then our final constraint is that 
-% \[-2F = [H, F] = \]
-% \[\begin{pmatrix}
-%     H_{12} F_{21} & H_{12} F_{22} \\
-%     H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
-% \end{pmatrix} - \begin{pmatrix}
-%     F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
-%     F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
-% \end{pmatrix}.\]
-% Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
-% Substituting in the equation above then,
-% \[-2F = \begin{pmatrix}
-%     F_{12} e F_{21} & F_{12}e f \\
-%     eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
-% \end{pmatrix} - \begin{pmatrix}
-%     F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
-%     f eF_{21} & F_{21} F_{12}e + fh
-% \end{pmatrix} =\]
-% \[\begin{pmatrix}
-%     0 & F_{12}(fe + h) \\
-%     eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
-% \end{pmatrix} - \begin{pmatrix}
-%     0 & F_{11} F_{12}e + F_{12} h \\
-%     (ef - h)F_{21} & F_{21} F_{12}e + fh
-% \end{pmatrix} =\]
-% \[\begin{pmatrix}
-%     0 & F_{12}fe \\
-%     eF_{21} F_{11} & eF_{21} F_{12} + hf
-% \end{pmatrix} - \begin{pmatrix}
-%     0 & F_{11} F_{12}e \\
-%     ef F_{21} & F_{21} F_{12}e + fh
-% \end{pmatrix}.\]
-% Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
-% This shows that \(H_{12} = H_{21} = 0\).
-% We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
-% \end{proof}
-
-\section{Finding \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
+\section{Finding \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{find_sxn}
 \subsection{Finding the Slodowy slice \texorpdfstring{\(S\)}{S}}
@@
 
-\section{Strategy for finding components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}
+\section{Strategy for finding components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp_strat}
 \par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
@@
 
-\section{The components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}
+\section{The components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}\label{q_comp}
 \subsection{Setup}
@@
 
-\section{The components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}
+\section{The components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
 As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
@@
 
-\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
+\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
 Recall from \cref{sn_iso} that 
@@
 
-% \section{Future work}
-% \par Separately, this paper would benefit from an introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-
-\section{Linear Algebra Facts}
+\section{Linear Algebra Facts}\label{linalg}
 In this section we prove linear algebra facts that were used earlier.

### 2024-09-01 paper.tex
section refs and acknowledgment

@@
 \subsection{Overview}
-\par Section 2 reviews some preliminary material.
-Section 3 finds the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
-Section 4 embeds this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
+\par \cref{prelim} reviews some preliminary material.
+\cref{principal_sl2} finds the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
+\cref{find_sxn} embeds this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
 We compute the Slodowy slice and end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-\par Section 5 discusses how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
-Section 6 solves the easier problem.
-Section 7 finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
-Section 8 applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-Section 9 discusses an interesting direction for future work.
-Finally, section 10 proves some linear algebra lemmas that were used in the paper.
-
-\subsection{Acknowledgment}
-TODO.  UROP+ program and Haoshuo.
-MIT (provided funding)?
+\par \cref{p_comp_strat} discusses how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
+\cref{q_comp} solves the easier problem.
+\cref{p_comp} finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
+\cref{sxn_comps} applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+Finally, \cref{linalg} proves some linear algebra lemmas that were used in the paper.
+
+\subsection{Acknowledgments}
+Thank you to Haoshuo Fu for suggesting the fun project, guiding me through it, and helping me to learn many things, both by talking to me about them and by suggesting things to read.
+Thank you also to the organizers of the MIT math department's UROP+ program, and to MIT for providing funding.
 
@@
 
-\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{prelim}
+\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{principal_sl2}
 The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).

### 2024-09-01 paper.tex
read through section 2 up to theorem 2.2

@@
 We write \(\GL_m, \spl_m\) to denote \(\GL_m(\mathbb{C}), \spl_m(\mathbb{C})\), and so on.
-By \(J_m\) we refer to the nilpotent \(m \times m\) Jordan block (which, by convention, has ones \emph{below} the diagonal).
-Given a partition \(\lambda = (\lambda_1, ..., \lambda_k)\), we write \(J(\lambda)\) to denote the block matrix
+By \(J_m\) we refer to the nilpotent \(m \times m\) Jordan block (which has ones \emph{below} the diagonal).
+Given a partition \(\lambda = (\lambda_1, ..., \lambda_\ell)\), we write \(J(\lambda)\) to denote the block matrix
 \[\begin{pmatrix}
@@
     & \ddots \\
-    & & J_{\lambda_k}
+    & & J_{\lambda_\ell}
 \end{pmatrix}.\]
-A partition is always indexed in nonincreasing order, even if it is defined differently.
-For example, if \(\mu = (4, 6, 3)\), then \(\mu_1 = 6, \mu_2 = 4, \mu_3 = 3\).
+A partition is always indexed in nonincreasing order, even if it is written down differently when defined.
+For example, if \(\mu = (4, 6, 3)\), then \((\mu_1, \mu_2, \mu_3) = (6, 4, 3)\).
+\par Throughout the paper, when a nilpotent operator \(X : \mathbb{C}^m \to \mathbb{C}^m\) of shape \(\lambda = (\lambda_1, ..., \lambda_\ell) \vdash m\) is in the context, we write \((e_{ij})_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i}\) to denote a Jordan basis of \(\mathbb{C}^m\) with the property that for all \(i,j\) we have \(Xe_{ij} = e_{i,j - 1}\).
+(By convention, \(e_{ij} := 0\) for \(j < 1\), so that condition makes sense.)
+Also, we will write \(f_n, ..., f_1\) to denote the basis of \(\mathbb{C}^n\) with the property that \(J_n f_i = f_{i - 1}\).
 
 \subsection{Springer fibers}
-Let \(\mathfrak{g}\) be a Lie algebra.
-Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
-Let \(\mathcal{B}\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
-Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{b}, n) : n \in \mathfrak{b}\} \subseteq \mathcal{B} \times \mathcal{N}\).
-Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
+Let \(\mathfrak{h}\) be a Lie algebra, let \(\mathcal{N}_\mathfrak{h} \subseteq \mathfrak{h}\) be the nilpotent cone in \(\mathfrak{h}\), and let \(\mathcal{B}_\mathfrak{h}\) be the variety of Borel subalgebras of \(\mathfrak{h}\).
+Let \(\widetilde{\mathcal{N}}_\mathfrak{h} = \{(\mathfrak{b}, n) \in \mathcal{B}_\mathfrak{h} \times \mathcal{N}_\mathfrak{h} : n \in \mathfrak{b}\}\).
+Let \(\pi_\mathfrak{h} : \widetilde{\mathcal{N}}_\mathfrak{h} \to \mathcal{N}_\mathfrak{h}\) be the projection onto the second coordinate.
 We call this the \emph{Springer resolution}.
-For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.
+For \(n \in \mathcal{N}_\mathfrak{h}\), we call \(\pi_\mathfrak{h}^{-1}(n)\) the \emph{Springer fiber at \(n\)}.
 
 \subsection{Springer fibers in \texorpdfstring{\(\gl_m\)}{gl\_m}}
-Now we let \(\mathcal{N}_m\) be the set of nilpotent elements in \(\gl_m\), and \(\mathcal{B}_m\) the variety of Borel subalgebras of \(\gl_m\).
-Let \(H \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
-The variety of Borel subalgebras of \(\gl_m\) is \(\mathcal{B} = \{gHg^{-1} : g \in \GL_m\}\).
-Thus, the Springer fiber at \(X \in \mathcal{N}\) is 
-\[\mathcal{F}_X = \{gHg^{-1} : X \in gHg^{-1}\}.\]
-% ^ use that notation everywhere for springer fiber
+Let \(\mathcal{N}_m\) be the nilpotent cone in \(\gl_m\), and let \(\mathcal{B}_m\) the variety of Borel subalgebras of \(\gl_m\).
+Let \(\mathfrak{h} \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
+The variety of Borel subalgebras of \(\gl_m\) is \(\mathcal{B}_m = \{g\mathfrak{h}g^{-1} : g \in \GL_m\}\).
+Thus, the Springer fiber at \(X \in \mathcal{N}_m\) is 
+\[\mathcal{F}_X = \{g\mathfrak{h}g^{-1} : g \in \GL_m; X \in g\mathfrak{h}g^{-1}\}.\]
 \begin{definition}
-    A \emph{flag} \((V_i)\) of \(\mathbb{C}^m\) is a sequence of subspaces
+    A \emph{flag} \(V_\bullet\) of \(\mathbb{C}^m\) is a sequence of subspaces
     \[0 = V_0 \subseteq V_1 \subseteq \cdots \subseteq V_m = \mathbb{C}^m,\]
@@
 \end{definition}
-We say that \(X \in \gl_m\) \emph{preserves} a flag \((V_i)\) if \(\forall i. \; XV_i \subseteq V_i\).
-Note that \(X \in \mathcal{N}\) preserves a flag \((V_i)\) if and only if \(\forall i. \; XV_i \subseteq V_{i - 1}\).
-\par The simplest flag is the \emph{standard flag} \((E_i)\), where \(E_i := \langle e_1, ..., e_i \rangle\).
-Note that the group \(H\) is exactly the subset of \(\gl_m\) which preserves \(E_i\).
-\par We can think of \(\mathcal{B}\) as the set of flags of \(\mathbb{C}^m\), via the correspondence 
-\[gHg^{-1} \leftrightarrow (gE_i).\]
-Note that \(X\) preserves \((gE_i)\) if and only if \(X \in gHg^{-1}\).
-Thus, we may write the Springer fiber at \(X \in \mathcal{N}\) in terms of flags, as 
-\[S_X = \{(gE_i) : X \in gHg^{-1}\} = \{(V_i) : \forall i. \; XV_i \subseteq V_{i - 1}\}.\]
+We say that \(X \in \gl_m\) \emph{preserves} a flag \(V_\bullet\) if for each \(i\) we have \(XV_i \subseteq V_i\).
+Note that for \(X \in \gl_m\), we have [\(X \in \mathcal{N}_m\), and \(X\) preserves \(V_\bullet\)] if and only if [for all \(i\), \(XV_{i + 1} \subseteq V_i\)].
+\par One flag is the \emph{standard flag} \(E_\bullet\), where \(E_i\) is generated by the first \(i\) standard basis vectors.
+The subalgebra \(\mathfrak{h}\) is exactly the subset of \(\gl_m\) which preserves \(E_\bullet\).
+So, we can think of \(\mathcal{B}_m\) as the variety of flags of \(\mathbb{C}^m\), via the correspondence 
+\[g\mathfrak{h}g^{-1} \leftrightarrow g \cdot E_\bullet.\]
+(\(\GL_n\) acts on the set of flags via \((g \cdot V_\bullet)_j = gV_j\).)
+Note that \(X\) preserves \(g \cdot E_\bullet\) if and only if \(X \in g \mathfrak{h} g^{-1}\).
+Thus, we may write the Springer fiber at \(X\) in terms of flags, as 
+\[\mathcal{F}_X = \{g \cdot E_\bullet : X \in gHg^{-1}\} = \{V_\bullet : \forall i. \; XV_i \subseteq V_{i - 1}\}.\]
 

### 2024-09-01 paper.tex
citation for springer fiber components

@@
 We say that \(X \in \gl_m\) \emph{preserves} a flag \(V_\bullet\) if for each \(i\) we have \(XV_i \subseteq V_i\).
-Note that for \(X \in \gl_m\), we have [\(X \in \mathcal{N}_m\), and \(X\) preserves \(V_\bullet\)] if and only if [for all \(i\), \(XV_{i + 1} \subseteq V_i\)].
+For \(X \in \gl_m\), we have [\(X \in \mathcal{N}_m\), and \(X\) preserves \(V_\bullet\)] if and only if [for all \(i\), \(XV_{i + 1} \subseteq V_i\)].
 \par One flag is the \emph{standard flag} \(E_\bullet\), where \(E_i\) is generated by the first \(i\) standard basis vectors.
@@
 \[g\mathfrak{h}g^{-1} \leftrightarrow g \cdot E_\bullet.\]
-(\(\GL_n\) acts on the set of flags via \((g \cdot V_\bullet)_j = gV_j\).)
+(\(\GL_m\) acts on the set of flags via \((g \cdot V_\bullet)_j = gV_j\).)
 Note that \(X\) preserves \(g \cdot E_\bullet\) if and only if \(X \in g \mathfrak{h} g^{-1}\).
@@
 
-\begin{theorem}\label{usual_springer_fiber}
-    (Needs citation!)
+\begin{theorem}[{\cite[2.1]{springer_fiber}}]\label{usual_springer_fiber}
     The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
-    Further, the irreducible components are equidimensional, of dimension \(\sum_{i < j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
+    The irreducible components are equidimensional, of dimension \(\sum_{i < j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
 \end{theorem}

### 2024-09-01 paper.tex
finish reading section 2

@@
 \[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
-Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
-% Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (TODO: what?)
-If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
-\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
-By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.
+Given a Lie algebra \(\mathfrak{h}\) and a homomorphism \(\phi : \spl_2 \to \mathfrak{h}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
+If \(\mathfrak{h}\) is semisimple, then given any nilpotent \(e \in \mathfrak{h}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{h}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
+\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(S_e := e + \ker \ad_f\).
+By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{h}\), whenever \(\mathfrak{h}\) is semisimple.
+In particular, we can find a Slodowy slice at any nilpotent \(e \in \gl_n\), since \(\spl_n \subseteq \gl_n\) is semisimple and contains every nilpotent element of \(\gl_n\).
 

### 2024-09-01 paper.tex
not much

@@
 \cref{p_comp} finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
-\cref{sxn_comps} applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\cref{sxn_comps} applies the results of \cref{p_comp} to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 Finally, \cref{linalg} proves some linear algebra lemmas that were used in the paper.
@@
 The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
-In this section we use this to find that there is a unique principal \(\spl_2\)-triple in \(\gl_n\).
+In this section we show that, in fact, there is a unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
 Write \(e = J_n\).
@@
 The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
-Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
+% Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
 We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).

### 2024-09-01 paper.tex
add sxn ref
read intro

@@
 \par Let \((e, h, f)\) be a principal \(\spl_2\)-triple in \(\gl_n\).
-We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
-Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
-Let \(S\) be the Slodowy slice \(E + \mathfrak{z}_{\gl_m}(F)\).
+Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via the embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
+Let \(S\) be the Slodowy slice \(E + \mathfrak{z}_{\gl_{m + n}}(F)\).
 We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
@@
 (It turns out that \(p'\) is surjective.)
-Then, we obtain \(p : S \to \mathfrak{g}\) by \(x \mapsto (x, p'(x))\).
+Then, define \(p : S \to \mathfrak{g}\) by \(x \mapsto (p'(x), x)\).
 Taking the map \(p : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is also discussed in \cite{sxn}[3].
 \par In this paper we study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
+As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we let \(\mathcal{N}_m\) be the nilpotent cone in \(\gl_m\), and we consider the map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
 Given \(X \in \mathcal{N}_m\), we call \(\pi^{-1}(X)\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
@@
 \par The \emph{Steinberg variety} of a Lie algebra \(\mathfrak{h}\) is \(\St_\mathfrak{h} = \widetilde{\mathcal{N}}_\mathfrak{h} \times_\mathfrak{h} \widetilde{\mathcal{N}}_\mathfrak{h}\), where the map \(\widetilde{\mathcal{N}}_\mathfrak{h} \to \mathfrak{h}\) is the Springer resolution.
-There is a bijective correspondence between the Weyl group of \(\gl_m\) and irreducible components of \(\St_\mathfrak{\gl_m}\)(see \cite{ehf}[3.6] for details).
-\par There is a nice bijection between \(\St_{\gl_m}\) and the set \(T_m = \{(t_1, t_2) : \lambda \vdash m; t_1, t_2 \in \mathrm{SYT}(\lambda)\}\).
-(Note that \(\mathrm{SYT}(\lambda)\) denotes the set of standard Young tableaux of shape \(\lambda\).)
-One way to obtain such a bijection is as follows.
-First take the aforementioned correspondence between \(\St_{\gl_m}\) and the Weyl group \(S_m\) of \(\gl_m\).
+There is a bijective correspondence between the Weyl group of \(\gl_m\) and the set \(\Irr(\St_{\gl_m})\) of irreducible components of \(\St_\mathfrak{\gl_m}\)(see \cite{ehf}[3.6] for details).
+The Weyl group of \(\gl_m\) is the symmetric group \(S_m\).
+\par There is a bijection between the set of irreducible components of \(\St_{\gl_m}\)---which we denote by \(\Irr(\St_{\gl_m})\)---and the set
+\[T_m = \{(t_1, t_2) : \lambda \vdash m; t_1, t_2 \in \mathrm{SYT}(\lambda)\}.\]
+(We write \(\mathrm{SYT}(\lambda)\) to denote the set of standard Young tableaux of shape \(\lambda\).)
+One way to obtain the bijection is as follows.
+First take the aforementioned correspondence between \(\St_{\gl_m}\) and the Weyl group \(S_m\).
 Then take the Robinson-Schensted-Knuth (RSK) correspondence, which gives a bijection between \(S_m\) and \(T_m\).
+Putting these together, we get a correspondence \(\St_{\gl_m} \leftrightarrow T_m\).
 A more direct and illuminating explanation of the correspondence \(\St_{\gl_m} \leftrightarrow T_m\) is given by the geometric RSK correspondence, as described in \cite{geomRSK}.
-\par An element of \(\St_{\gl_m}\) is a triple \((X, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(\mathfrak{b}_1\) and \(\mathfrak{b}_2\) are elements of the Springer fiber at \(X\).
-When the Jordan form of \(X\) has shape \(\lambda\), the correspondence sends this triple to a pair \((t_1, t_2)\), where both are of shape \(\lambda\).
-\par Somewhat similarly, we will show that an element of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is a subset of the set of tuples \((X, Y, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(X \in \mathcal{N}_m, Y \in \mathcal{N}_{m + n}\), and \(\mathfrak{b}_1, \mathfrak{b}_2\) are elements of the Springer fiber at \(X, Y\) respectively.
-For any given relation \(R \subseteq \{\lambda : \lambda \vdash m\} \times \{\mu : \mu \vdash (m + n)\}\), we can define 
+\par An element of \(\St_{\gl_m}\) is a triple \((X, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(X \in \mathcal{N}_m\), and \(\mathfrak{b}_1, \mathfrak{b}_2\) are elements of the Springer fiber at \(X\).
+When the Jordan form of \(X\) has shape \(\lambda\), the geometric RSK correspondence sends this triple to a pair \((t_1, t_2)\), where both are of shape \(\lambda\).
+\par Somewhat similarly, we will show that \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is a subset of the set of tuples \((X, Y, \mathfrak{b}_1, \mathfrak{b}_2)\), where \(X \in \mathcal{N}_m, Y \in \mathcal{N}_{m + n}\), and \(\mathfrak{b}_1\) (resp.
+\(\mathfrak{b}_2\)) is an element of the Springer fiber at \(X\) (resp.
+\(Y\)).
+\par For any given relation \(R \subseteq \{\lambda : \lambda \vdash m\} \times \{\mu : \mu \vdash (m + n)\}\), we can define 
 \[T_{m,n} = \{(t_1, t_2) : \lambda \vdash m; \mu \vdash (m + n); t_1 \in \mathrm{SYT}(\lambda); t_2 \in \mathrm{SYT}(\mu); R(\lambda, \mu)\}.\]
 We conjecture that, for some appropriate choice of the relation \(R\), there is a correspondence, analogous to \(\St_{\gl_m} \leftrightarrow T_m\), between \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and \(T_{m,n}\).
-An extension of this project would determine the details of this correspondence.
-\par Given an irreducible component \(C \in \Irr(\St_{\gl_m})\), we can first map it to the corresponding \((t_1, t_2) \in T_m\), and then obtain an element of \(\End(\mathbb{C}[\mathrm{SYT}(\lambda)])\) by taking the map which sends \(t_1 \mapsto t_2\) and \(t' \mapsto 0\) for \(t' \in \mathrm{SYT}(\lambda) \setminus \{t_1\}\).
+A natural extension of this project would explore this correspondence.
+\par Given an element of \(\Irr(\St_{\gl_m})\), we can first map it to the corresponding \((t_1, t_2) \in T_m\), and then obtain an element of \(\End(\mathbb{C}[\mathrm{SYT}(\lambda)])\) by taking the map which sends \(t_1 \mapsto t_2\) and \(t' \mapsto 0\) for \(t' \in \mathrm{SYT}(\lambda) \setminus \{t_1\}\).
 In this way, we obtain a \(\mathbb{C}\)-algebra isomorphism
@@
 \subsection{Acknowledgments}
-Thank you to Haoshuo Fu for suggesting the fun project, guiding me through it, and helping me to learn many things, both by talking to me about them and by suggesting things to read.
+Thank you to Haoshuo Fu for suggesting the fun project, guiding me through it, and helping me learn many things, both by talking to me about them and by suggesting things to read.
 Thank you also to the organizers of the MIT math department's UROP+ program, and to MIT for providing funding.

### 2024-09-01 paper.tex
read section 2

@@
 (By convention, \(e_{ij} := 0\) for \(j < 1\), so that condition makes sense.)
-Also, we will write \(f_n, ..., f_1\) to denote the basis of \(\mathbb{C}^n\) with the property that \(J_n f_i = f_{i - 1}\).
-
-\subsection{Springer fibers}
+Also, we write \(f_n, ..., f_1\) to denote the basis of \(\mathbb{C}^n\) with the property that \(J_n f_i = f_{i - 1}\).
+
+\subsection{Springer Fibers}
 Let \(\mathfrak{h}\) be a Lie algebra, let \(\mathcal{N}_\mathfrak{h} \subseteq \mathfrak{h}\) be the nilpotent cone in \(\mathfrak{h}\), and let \(\mathcal{B}_\mathfrak{h}\) be the variety of Borel subalgebras of \(\mathfrak{h}\).
@@
 Let \(\pi_\mathfrak{h} : \widetilde{\mathcal{N}}_\mathfrak{h} \to \mathcal{N}_\mathfrak{h}\) be the projection onto the second coordinate.
-We call this the \emph{Springer resolution}.
+We call \(\pi_\mathfrak{h}\) the \emph{Springer resolution}.
 For \(n \in \mathcal{N}_\mathfrak{h}\), we call \(\pi_\mathfrak{h}^{-1}(n)\) the \emph{Springer fiber at \(n\)}.
 
-\subsection{Springer fibers in \texorpdfstring{\(\gl_m\)}{gl\_m}}
-Let \(\mathcal{N}_m\) be the nilpotent cone in \(\gl_m\), and let \(\mathcal{B}_m\) the variety of Borel subalgebras of \(\gl_m\).
+\subsection{Springer Fibers in \texorpdfstring{\(\gl_m\)}{gl\_m}}
+Let \(\mathcal{N}_m\) be the nilpotent cone in \(\gl_m\), and let \(\mathcal{B}_m\) be the variety of Borel subalgebras of \(\gl_m\).
 Let \(\mathfrak{h} \subseteq \gl_m\) be the subalgebra of upper triangular matrices.
@@
 \[g\mathfrak{h}g^{-1} \leftrightarrow g \cdot E_\bullet.\]
-(\(\GL_m\) acts on the set of flags via \((g \cdot V_\bullet)_j = gV_j\).)
+(\(\GL_m\) acts on the set of flags via \((g \cdot V_\bullet)_j := gV_j\).)
 Note that \(X\) preserves \(g \cdot E_\bullet\) if and only if \(X \in g \mathfrak{h} g^{-1}\).
 Thus, we may write the Springer fiber at \(X\) in terms of flags, as 
-\[\mathcal{F}_X = \{g \cdot E_\bullet : X \in gHg^{-1}\} = \{V_\bullet : \forall i. \; XV_i \subseteq V_{i - 1}\}.\]
+\[\mathcal{F}_X = \{g \cdot E_\bullet : g \in \GL_m; X \in gHg^{-1}\} = \{V_\bullet : \forall i. \; XV_{i + 1} \subseteq V_i\}.\]
 
@@
 If \(\mathfrak{h}\) is semisimple, then given any nilpotent \(e \in \mathfrak{h}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{h}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
-\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(S_e := e + \ker \ad_f\).
-By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{h}\), whenever \(\mathfrak{h}\) is semisimple.
+\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(S_e = e + \ker \ad_f\).
+By the Jacobson-Morozov theorem, if \(\mathfrak{h}\) is semisimple, then we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{h}\).
 In particular, we can find a Slodowy slice at any nilpotent \(e \in \gl_n\), since \(\spl_n \subseteq \gl_n\) is semisimple and contains every nilpotent element of \(\gl_n\).
 
-\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{principal_sl2}
+\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triples in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{principal_sl2}
 The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).

### 2024-09-01 paper.tex
read section 3

@@
 In this section we show that, in fact, there is a unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
-Write \(e = J_n\).
+Let \(e = J_n\).
 \begin{lemma}\label{simple_sl2_triple}
@@
 The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
-% Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
-We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
-Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
-\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
-We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
-Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
-From the first equation we find that
-\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
-\[\sum_i h_{ii} = 0.\]
-(That is, \(h \in \spl_n\).)
-This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
+So, \([h,e] = 2e\) implies that \(h_{ij} = 0\), except when \(i = j\) or \((i,j) = (n,1)\).
+It also implies that \(h_{ii} = h_{i - 1, i - 1} + 2\), and hence \(h_{ii} = h_{11} + 2(i - 1)\).
+\par Similarly, \(ef - fe = h\); this implies that \(f_{ij} = 0\), except when \(j = i + 1\) or \((i,j) = (n,1)\).
+Also, \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), and \(f_{1,2} = -h_{1, 1}\), and \(f_{n - 1, n} = h_{n,n}\).
+Putting these equations together,
+\begin{align*}
+    h_{nn} + h_{11} & = \\
+    f_{n - 1,n} - f_{1,2} & = \\
+    \sum_{i = 1}^{n - 2} (f_{i + 1, i + 2} - f_{i,i + 1}) & = \\
+    - \sum_{i = 1}^{n - 2} h_{i + 1, i + 1} & .
+\end{align*}
+That is, \(h \in \spl_n\).
+This shows that \(h_{11} = 1 - n, h_{22} = 3 - n, ..., h_{nn} = n - 1\).
+\par Now that we have mostly determined \(h\) and \(f\), looking at \([e,f] = h\) and \([h,f] = -2f\) shows that \(h_{n,1} = f_{n,1} = 0\).
 So we have determined \(h\); it is 
 \[h = \begin{pmatrix}
-    n - 1  & \\
-    & n - 3 \\
+    1 - n  & \\
+    & 3 - n \\
     & & \ddots \\
-    & & & 3 - n \\
-    & & & & 1 - n 
+    & & & n - 3 \\
+    & & & & n - 1 
 \end{pmatrix}.\]
@@
 \[f = \begin{pmatrix}
-    0 & 1 - n \\
-    & 0 & (1 - n) + (3 - n) \\
+    0 & n - 1 \\
+    & 0 & (n - 1) + (n - 3) \\
     & & \ddots & \ddots \\
-    & & & 0 & (1 - n) + \cdots + (n - 1) \\
+    & & & 0 & (n - 1) + \cdots + (3 - n) \\
     & & & & 0
@@
 \[\begin{pmatrix}
-    0 & 1 (1 - n) \\
-      & 0 & 2 (2 - n) \\
-    & & 0 & (n - 2) (-2) \\
-    & & & 0 & (n - 1) (-1)\\
-    & &  & & 0
+    0 & (1) (n - 1) \\
+      & 0 & (2) (n - 2) \\
+      & & \ddots & \ddots & \\
+    & & & 0 & (-2)(n - 2) \\
+    & & & & 0 & (-1)(n - 1)\\
+    & &  & & & 0
 \end{pmatrix}.\]

### 2024-09-01 paper.tex
centralizer notation

@@
 We write \(\GL_m, \spl_m\) to denote \(\GL_m(\mathbb{C}), \spl_m(\mathbb{C})\), and so on.
-By \(J_m\) we refer to the nilpotent \(m \times m\) Jordan block (which has ones \emph{below} the diagonal).
+The notation \(\mathfrak{z}_\mathfrak{h}(X)\) denotes the centralizer of \(X\) in the Lie algebra \(\mathfrak{h}\).
+\par By \(J_m\) we refer to the nilpotent \(m \times m\) Jordan block (which has ones \emph{below} the diagonal).
 Given a partition \(\lambda = (\lambda_1, ..., \lambda_\ell)\), we write \(J(\lambda)\) to denote the block matrix
@@
 \subsection{Slodowy Slices}
-
 A basis for \(\spl_2\) is
@@
 If \(\mathfrak{h}\) is semisimple, then given any nilpotent \(e \in \mathfrak{h}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{h}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
-\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(S_e = e + \ker \ad_f\).
+\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(S_e = e + \mathfrak{z}_\mathfrak{h}(f)\).
 By the Jacobson-Morozov theorem, if \(\mathfrak{h}\) is semisimple, then we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{h}\).
@@
 \section{Finding \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{find_sxn}
-\subsection{Finding the Slodowy slice \texorpdfstring{\(S\)}{S}}
+\subsection{Finding the Slodowy Slice \texorpdfstring{\(S\)}{S}}
 In the previous section we computed the principal \(\spl_2\)-triple \((e, h, f)\) in \(\gl_n\).

### 2024-09-01 paper.tex
up to section 4.2

@@
 \begin{lemma}\label{small_centralizer}
-    \(\mathfrak{z}_{\gl_n}(f)\) is the set of upper-triangular \(X \in \gl_n\) such that for all \(i,j\),
+    \(\mathfrak{z}_{\gl_n}(f)\) is the set of upper-triangular \(X \in \gl_n\) such that for all \(i,j \in \{1,...,n-1\}\),
     \[X_{i + 1,j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
@@
     Looking at the definition of \(f\) from the previous section (and zero-padding the matrices), we see that \((fX)_{ij} = i (n - i) X_{i + 1,j}\), and \((Xf)_{ij} = (j - 1)(n - (j - 1)) X_{i, j - 1}\).
-    So,
-    \[\forall i, j \in \{1, ..., n\}. \; i(n - i)X_{i + 1,j} = (j - 1)(n - (j - 1))X_{i, j - 1}.\]
-    Taking \(j = 1\), the condition above tells us that \(\forall i \geq 2. \; X_{i, 1} = 0\).
-    Taking \(j > 1\) and \(i < n\), we obtain that
-    \[\forall i, j \in \{1, ..., n - 1\}. \; X_{i + 1, j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
+    So, for any \(i, j \in \{1,...,n\}\),
+    \[i(n - i)X_{i + 1,j} = (j - 1)(n - (j - 1))X_{i, j - 1}.\]
+    Taking \(j = 1\), the condition above tells us that for all \(i \geq 2\) we have \(X_{i, 1} = 0\).
+    Taking \(j > 1\) and \(i < n\), we get that for all \(i,j \in \{1,...,n-1\}\),
+    \[X_{i + 1, j + 1} = \frac{j(n - j)}{i(n - i)} X_{ij}.\]
     So, every \(X \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular and satisfies the condition above.
@@
     The condition \(Z_{12}f = 0\) means that all but the last column of \(Z_{12}\) must be zero, and the condition \(0 = fZ_{21}\) means that all but the first row of \(Z_{21}\) must be zero.
-    And the condition \(Z_{22}f = fZ_{22}\) means that \(Z_{22} \in \mathfrak{z}_{\gl_{m + n}}(f)\).
-\end{proof}
-
-These lemmas provide an explicit characterization of the Slodowy slice \(S = E + \mathfrak{z}_{\gl_{m + n}}(F)\).
+    Finally, the condition \(Z_{22}f = fZ_{22}\) means that \(Z_{22} \in \mathfrak{z}_{\gl_n}(f)\).
+\end{proof}
+
+Taken together, the previous lemmas provide a nice characterization of the Slodowy slice \(S = E + \mathfrak{z}_{\gl_{m + n}}(F)\).
 \begin{corollary}\label{slodowy_slice}

### 2024-09-01 paper.tex
up to section 5

@@
 \subsection{A description of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
-Recall that we have the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p(Z), Z)\), where \(p : \gl_{m + n} \to \gl_m\) is the coordinate projection.
+Recall the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p'(Z), Z)\), where \(p' : \gl_{m + n} \to \gl_m\) is coordinate projection taking a matrix to its upper-left corner.
 We also have the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\).
-From these two maps we define the fibered product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we will begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
-As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' = \{Z \in S : p(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
+From these two maps we define the fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
+As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' := \{Z \in S : p'(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
 \begin{lemma}
-    \[S' = \left\{A_{X, a, b} := \begin{pNiceArray}{ccc|cccc}
-    & & & & & & \vert \\
-    & X & & & & & b    \\
-    & & & & & & \vert \\
+    \[S' = \left\{A_{X, a, b} := \begin{pNiceArray}{ccc|ccc}
+    & & & & & \vert \\
+    & X & & & & b    \\
+    & & & & & \vert \\
    \hline
-   \text{---} & a & \text{---} & 0 \\
-    & & & 1 & 0  & \\
-    &  & & & \ddots & \ddots  \\
-    & & & & & 1 & 0
+   \text{---} & a & \text{---} \\
+    & & & & e & \\
+    & & &  & 
    \end{pNiceArray} \in \mathcal{N}_{m + n}: a, b \in \mathbb{C}^m, X \in \mathcal{N}_m\right\}.\]
@@
 \begin{proof}
-    As every element of \(\mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{bottom_right_nilp} tells us that if a matrix of the form given in \cref{slodowy_slice} is nilpotent, and the upper-left block \(X\) is nilpotent as well, then \(e + Y\) must be nilpotent.
-    Then, again using that every element \(Y \in \mathfrak{z}_{\gl_n}(f)\) is upper triangular, \cref{upper_triangle_zero} tells us that if \(e + Y\) is nilpotent, then \(Y = 0\).
-    \par Hence every element of \(S'\) must simply have \(e\) in its bottom-right block.
+    Since every element of \(\mathfrak{z}_{\gl_n}(f)\) is upper triangular by \cref{small_centralizer}, \cref{bottom_right_nilp} says that if a matrix \(Z \in S\) of the form given in \cref{slodowy_slice} is nilpotent, and the upper-left block \(p'(Z) = X\) is nilpotent as well, then \(e + Y\) must be nilpotent.
+    Finally, \cref{upper_triangle_zero} says that if \(e + Y\) is nilpotent for \(Y \in \mathfrak{z}_{\gl_n}(f)\), then \(Y = 0\).
+    \par Thus every element of \(S'\) must simply have \(e\) in its bottom-right block.
     So, every element of \(S'\) is of the desired form.
@@
 This is not a fully explicit characterization of \(S'\), since we don't say which choices of \(X\) and \(a, b \in \mathbb{C}^m\) lead to \(A_{X, a, b}\) being nilpotent.
-We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the description above of \(S'\) will be good enough for our purposes.
+We could use \cref{block_determinant} to find a necessary and sufficient condition on \(X, a, b\); however, the above description of \(S'\) will be good enough for our purposes.
 \begin{corollary}\label{sn_iso}
@@
         S \times_\mathfrak{g} \widetilde{\mathcal{N}} & = \\
-        \{((X, A_{X, a, b}), ((X, A_{X, a, b}), \mathfrak{b})) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathcal{N} \cap \mathfrak{b}\} & \cong \\
-        \{(A_{X, a, b}, \mathfrak{b}) : \mathfrak{b} \in \mathcal{B}, (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
+        \{((X, A_{X, a, b}), ((X, A_{X, a, b}), \mathfrak{b})) \in S \times \widetilde{\mathcal{N}}\} & \cong \\
+        \{(A_{X, a, b}, \mathfrak{b}) : X \in \gl_m; a,b \in \mathbb{C}; \mathfrak{b} \in \mathcal{B}; (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
     \end{align*}
 \end{corollary}
-We have a map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by \((A_{X, a, b}, \mathfrak{b}) \mapsto X\).
+Define \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X, a, b}, \mathfrak{b}) \mapsto X\).
 We define the \emph{\(n\)-Slodowy-slice Springer fiber} at \(X \in \mathcal{N}_m\) to be the fiber \(\pi^{-1}(X)\).
 Because \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\),  
-\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
-The right factor of the product is simply the usual Springer fiber at \(X\).
+\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : a,b \in \mathbb{C}; A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
+The right factor of the product is simply the usual Springer fiber \(\mathcal{F}_X\).
 \par Let 
-\[\mathcal{P}_X = \{(A_{X, a, b}, (V_i)) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
-Using our correspondence between Springer fibers in \(\mathcal{B}_{m + n}\) and flags of \(\mathbb{C}^{m + n}\), we see that \(\mathcal{P}_X\) is isomorphic to the left factor of \(\pi^{-1}(X)\).
-In the next few sections, we will find the irreducible components of \(\mathcal{P}_X\).
-Then we will use this, along with the result about the usual Springer fiber at \(X\), to find the irreducible components of \(\pi^{-1}(X)\) and then of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
+\[\mathcal{P}_X = \{(A_{X, a, b}, V_\bullet) : \forall i. \; A_{X, a, b} V_i \subseteq V_{i - 1}\}.\]
+By the correspondence between Springer fibers in \(\mathcal{B}_{m + n}\) and flags of \(\mathbb{C}^{m + n}\), the variety \(\mathcal{P}_X\) is isomorphic to the left factor of \(\pi^{-1}(X)\).
+\par In the next few sections, we will find the irreducible components of \(\mathcal{P}_X\).
+Then we will use this result, along with the result about the usual Springer fiber \(\mathcal{F}_X\), to find the irreducible components of \(\pi^{-1}(X)\) and then of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
 

### 2024-09-01 paper.tex
almost finish reading section 5

@@
         \{((X, A_{X, a, b}), ((X, A_{X, a, b}), \mathfrak{b})) \in S \times \widetilde{\mathcal{N}}\} & \cong \\
-        \{(A_{X, a, b}, \mathfrak{b}) : X \in \gl_m; a,b \in \mathbb{C}; \mathfrak{b} \in \mathcal{B}; (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
+        \{(A_{X, a, b}, \mathfrak{b}) : X \in \gl_m; a,b \in \mathbb{C}^m; \mathfrak{b} \in \mathcal{B}; (X, A_{X, a, b}) \in \mathfrak{b} \cap \mathcal{N}\} & .
     \end{align*}
@@
 Because \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\),  
-\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : a,b \in \mathbb{C}; A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
+\[\pi^{-1}(X) \cong \{(A_{X, a, b}, \mathfrak{b}_{m + n}) : a,b \in \mathbb{C}^m; A_{X, a, b} \in \mathfrak{b}_{m + n} \cap \mathcal{N}_{m + n}\} \times \{\mathfrak{b}_m : X \in \mathfrak{b}_m\}.\]
 The right factor of the product is simply the usual Springer fiber \(\mathcal{F}_X\).
@@
 \section{Strategy for finding components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp_strat}
-\par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
-In this section we write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\) and \(A_{a, b} := A_{J(\lambda), a, b}\).
+\par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
+In this section we write \(\mathcal{P} := \mathcal{P}_X\) and \(A_{a, b} := A_{X, a, b}\).
 Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard basis for \(\mathbb{C}^m\).
-For convenience we write \(e_{ij} := 0\) for \(j < 1\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
+Let \((f_j)_{1 \leq j \leq k}\) be the standard basis for \(\mathbb{C}^n\).
+We index the bases such that \(Xe_{ij} = e_{i,j - 1}\), and \(J_n f_j = f_{j - 1}\).
 \par In this section we begin finding the irreducible components of
-\[\mathcal{P} = \{(A_{a, b}, (V_i)) : \forall i. \; A_{a, b} V_{i + 1} \subseteq V_i\}.\]
-\par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
-\[\mathcal{P}_{w,r} := \{(A_{a, b}, V) \in \mathcal{P} : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'} \}.\]
+\[\mathcal{P} = \{(A_{a, b}, V_\bullet) : \forall i. \; A_{a, b} V_{i + 1} \subseteq V_i\}.\]
+\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\); recall \(e_{i0} = 0\)), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^n\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'}\).
 
@@
 \begin{proof}
-    For any \(a \in \mathbb{C}^m\), define \(f_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_i \mapsto 0\).
-    For this proof we take the coordinate-free view of \(A_{a,b}\) as the linear transformation \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + f_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
-    \par Let \((A_{a, b}, (V_i)) \in \mathcal{P}\).
-    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that \(Pe_{ij}\) forms a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(f(Pe_{ij}) = 0\).
-    \par Now let \(Q = (P^{-1}, I_n)A_{a,b}(P, I_n)\).
-    Since \(Pe_{ij}\) is a Jordan basis, we have \(Q = A_{a',b'}\) for some \(a',b' \in \mathbb{C}^m\).
+    For any \(a \in \mathbb{C}^m\), define the linear map \(\phi_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_j \mapsto 0\).
+    Note that \(A_{a,b}\) is the unique linear map \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + \phi_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
+    \par Let \((A_{a, b}, V_\bullet) \in \mathcal{P}\).
+    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
+    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n)\) for some \(a',b' \in \mathbb{C}^m\).
     All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
-    Indeed, this results from the fact that \(f_{a'}(e_{ij}) = f_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
+    Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
 \end{proof}
@@
 \begin{proof}
-    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so clearly \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
-    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then clearly any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
+    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
+    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
     \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
@@
     Obviously \(k = r_1\).
-    Since \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
+    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
     Hence \(r_1 = r_2\).
     Now, if \(r_1 = 0\), we are done.
-    \par Otherwise, we have \(r_1 > 0\).
-    Let \(k' \geq 0\) be maximal so that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
+    \par Otherwise, \(r_1 > 0\).
+    Let \(k' \geq 0\) be maximal such that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
     Obviously \(k' = \lambda_{w_1} - r_1\).
-    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so we see that \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
+    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
 \end{proof}
@@
     It suffices to remark that \(\{(x,y) : \exists w,r. \; x,y \in \mathcal{P}_{wr}\}\) is an equivalence relation.
-    Reflexivity is the statement of \cref{pwr_union}, and associativity and transitivity are obvious from the definition of \(\mathcal{P}_{wr}\).
+    Reflexivity is the statement of \cref{pwr_union}, and symmetry and transitivity are obvious from the definition of \(\mathcal{P}_{wr}\).
 \end{proof}
@@
 We will find the irreducible components of \(\mathcal{P}_{w,r}\).
-These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(\mathcal{P}\) will be the irreducible components of \(\mathcal{P}\).
+These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(\mathcal{P}\) will be irreducible components of \(\mathcal{P}\).
 \par Let 
-\[G := \{P \in \GL_m : P^{-1} X P = X\},\]
+\[G = \{P \in \GL_m : P X P^{-1} = X\},\]
 and
 \[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
-\par Now, define 
-\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, (V_i)) \in \mathcal{P}_{wr}\}.\]
+Also, define 
+\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}_{wr}\}.\]
 Let \(G\) act on \(\mathcal{P}_{wr}\) by
-\[P \cdot (A_{e_{wr},b}, (V_i)) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)(V_i)) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) (V_i)).\]
+\[P \cdot (A_{a,b}, V_\bullet) := ((P, I_n) A_{a, b} (P, I_n)^{-1}, (P, I_n)V_\bullet) = (A_{a P^{-1}, Pb}, (P, I_n) V_\bullet).\]
 Note that for any \(x \in \mathcal{Q}_{wr}\), we have \(G_{wr} = \{g \in G : g \cdot x \in \mathcal{Q}_{wr}\}\).
@@
 \[(x, P) \mapsto P \cdot x.\]
-Then, letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr} \times G\).
+Letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr} \times G\).
 
@@
     It is obvious that \(G_{wr}\) acts freely on \(\mathcal{Q}_{wr} \times G\); it is enough to note that it acts freely on \(G\).
+    Now we check that it acts transitively.
     \par Let \(y \in \mathcal{P}_{wr}\).
     By definition of \(\mathcal{P}_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in \mathcal{Q}_{wr}\).
-    We have
     \begin{align*}
@@
     \end{align*}
-    Using that \(G_{wr} = \{g \in G : g \cdot (P_y \cdot y) = P_y \cdot y\}\), the expression above becomes
+    Since \(G_{wr} = \{g \in G : g \cdot (P_y \cdot y) \in \mathcal{Q}_{wr}\}\), the expression above becomes
     \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\}.\]
-    Setting \(Q := P^{-1} P_y^{-1}\), so that \(P = P_y^{-1} Q^{-1}\), the above becomes
+    Setting \(Q := P^{-1} P_y^{-1}\), and observing that \(P = P_y^{-1} Q^{-1}\), the above becomes
     \begin{align*}
@@
 \end{proof}
-Our strategy is to find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we will then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi(X \times G)\).
-So, we will now find the irreducible components of \(\mathcal{Q}_{wr}\).
-\par Actually \(\mathcal{Q}_{wr}\) might be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
+We will find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi(X \times G)\).
+So, next we find the irreducible components of \(\mathcal{Q}_{wr}\).
+\par Actually, \(\mathcal{Q}_{wr}\) is unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
 So, we will change basis to make \(r = 0\).
 Let \(m' = m - r\), and \(n' = n + r\).
-Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
-Let \(X' = J(\lambda)\).
-(TODO: explain that \(A'\) is like \(A\), but with \(m',n'\) taking the place of \(m,n\).)
-Let \(\mathcal{Q}' = \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
+TODO: should not be \(\lambda_w - r\); should be \(r - 1\); fixup other things (incl. proof!) accordingly.
+Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_\ell)\).
+Let \(X' = J(\lambda')\).
+Let \(\mathcal{Q}' = \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\}\), where
+\[A'_{X',a,b} := \begin{pNiceArray}{ccc|ccc}
+    & & & & & \vert \\
+    & X' & & & & b    \\
+    & & & & & \vert \\
+   \hline
+   \text{---} & a & \text{---} \\
+    & & & & J_{n'} & \\
+    & & &  & 
+   \end{pNiceArray} \in \gl_{m' + n'}\]
 \begin{lemma}\label{a_zero}
-    \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\)
-\end{lemma}
-\begin{proof}
-    Let \(e_{ij}'\) be the standard Jordan basis for \(X'\).
-    Let \(f_1', ..., f_{n'}'\) be a basis for \(\mathbb{C}^n\), with \(A_{X', 0, b} f_{i + 1}' = f_i'\), and \(A_{X', 0, b} f_1 = (b, 0)\).
-    Set \(m' := m - r\), and \(n' := n + r\).
+    \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\).
+\end{lemma}
+\begin{proof}
+    Let \((e_{ij}')_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i - \delta_{jw} r}\) be the standard Jordan basis for \(X'\).
+    (The \(\delta\) is the Kronecker \(\delta\).)
+    Let \(f_1', ..., f_{n'}'\) be a basis for \(\mathbb{C}^{n'}\) such that \(A_{X', 0, b} f_{i + 1}' = f_i'\), and \(A_{X', 0, b} f_1 = (b, 0)\).
     Define the linear map \(Q_{wr} : \mathbb{C}^{m' + n'} \to \mathbb{C}^{m + n}\) by:
     \begin{itemize}
-        \item For all \(i\), \(e_{ij}' \mapsto e_{ij}\).
-        \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,(\lambda_w - r) + j}\).
-        \item For \(j = 1, ..., n\), \(f_j' \mapsto f_j + e_{w, (\lambda_w - r) - n + j}\).
+        \item For all \(i,j\), \(e_{ij}' \mapsto e_{ij}\).
+        \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,\lambda_w + j}\).
+        \item For \(j = 1, ..., n'\), \(f_j' \mapsto f_j + e_{w, \lambda_w - n' + j}\).
     \end{itemize}
@@
     % \end{itemize}
-    Change of basis by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and conjugation by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
+    Change of basis by \(Q_{wr}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\), and change of basis by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\).
 \end{proof}
 The next section finds the irreducible components of \(\mathcal{Q}'\).
-To avoid death by primes, we will refer to it as \(\mathcal{Q}\), and refer to \(m',n'\) as \(m,n\), and so on, throughout the next section.
+To make the notation nicer, we will refer to it as \(\mathcal{Q}\), and refer to \(m',n'\) as \(m,n\) (and so on), throughout the next section.
 
@@
 Let
-\[\mathcal{Q} = \{(A_{0,b}, (V_i)) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
+\[\mathcal{Q} = \{(A_{0,b}, V_\bullet) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
 In this section we find the irreducible components of \(\mathcal{Q}\).
@@
 \end{proof}
-\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, (V_i)) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
+\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, V_\bullet) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
 We will show that \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times (\textrm{some springer fiber})\).
@@
     From looking at the Jordan basis, it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
-    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b (V_i) : (V_i) \in X_\mu\}\).
+    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b V_\bullet : V_\bullet \in X_\mu\}\).
     This gives the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to \mathcal{Q}_{I, (\rho_i)}\) defined by
-    \[(b, (V_i)) \mapsto (P_b J(\mu) P_b^{-1}, P_b (V_i)),\]
+    \[(b, V_\bullet) \mapsto (P_b J(\mu) P_b^{-1}, P_b V_\bullet),\]
     with inverse
-    \[(A_{0,b}, (V_i)) \mapsto (b, P_b^{-1} (V_i)).\]
+    \[(A_{0,b}, V_\bullet) \mapsto (b, P_b^{-1} V_\bullet).\]
 \end{proof}
@@
 Recall from section 5 the varieties
-\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, (V_i)) \in \mathcal{P}\}.\]
+\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}\}.\]
 Fix any \(w,r\).
 \cref{a_zero} tells us that 
-\[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
+\[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
 where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
@@
 Recall from \cref{sn_iso} that 
-\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, (U_i), (V_i)) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
-We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, (U_i), (V_i)) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
+\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, U_\bullet, V_\bullet) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
+We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
 \begin{theorem}\label{springer_fiber_comps}
@@
 \begin{proof}
-    The isomorphism sends \((A_{X,a,b}, (U_i), (V_i))\) to \(((A_{X, a, b}, (U_i)), (V_i))\).
+    The isomorphism sends \((A_{X,a,b}, U_\bullet, V_\bullet)\) to \(((A_{X, a, b}, U_\bullet), V_\bullet)\).
     The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
@@
 Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by conjugation; that is,
-\[(P, I_n) \cdot (A_{X, a, b}, (U_i), (V_i)) := \]
-\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},(P,I_n)(U_i), (P,I_n)(V_i)).\]
+\[(P, I_n) \cdot (A_{X, a, b}, U_\bullet, V_\bullet) := \]
+\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},(P,I_n)U_\bullet, (P,I_n)V_\bullet).\]
 Let 

### 2024-09-02 paper.tex
stuff to revert

@@
 \par To obtain an explicit description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we begin by finding the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\).
-As the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' := \{Z \in S : p'(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
+Since the image of the Springer resolution is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), the image of the projection \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to S\) is simply \(S' := \{Z \in S : p'(Z) \in \mathcal{N}_m, Z \in \mathcal{N}_{m + n}\}\).
 \begin{lemma}
@@
 
-\section{Strategy for finding components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp_strat}
+\section{Strategy for Finding Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp_strat}
 \par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
@@
 We index the bases such that \(Xe_{ij} = e_{i,j - 1}\), and \(J_n f_j = f_{j - 1}\).
-\par In this section we begin finding the irreducible components of
-\[\mathcal{P} = \{(A_{a, b}, V_\bullet) : \forall i. \; A_{a, b} V_{i + 1} \subseteq V_i\}.\]
-\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\); recall \(e_{i0} = 0\)), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^n\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'}\).
+\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w - 1\), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^m\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{w,r + 1}, b'}\).
+Also, for \(1 \leq w \leq \ell\), define \(\mathcal{P}_{w,\lambda_w}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^m\) such that \((P^{-1}, I_n)A_{a,b}(P,I_n) = A_{0,b'}\).
+\par The point of the definition above is that \((A_{a,b}, V_\bullet) \in \mathcal{P}_{wr}\) if and only if we can change basis of \(\mathbb{C}^m\) to get from \(A_{a,b}\) to some \(A_{a',b'}\) such that (1) \(a'_{ij} = 0\) for \(i \neq w\), and (2) \(a_{wj}' = 0\) for all but (at most) one \(j\), and (3) \(r\) is the biggest number s.t.
+\(a_{w1}' = a_{w2}' = \cdots = a_{wr}' = 0\).
 
@@
     Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
-    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n)\) for some \(a',b' \in \mathbb{C}^m\).
-    All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
+    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n) = A_{a',b'}\) for some \(a',b' \in \mathbb{C}^m\).
+    All that is left is to show that \(a'_{ij} = 0\) for all but one pair \((i,j)\).
     Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
@@
 \begin{lemma}
-    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
-\end{lemma}
-\begin{proof}
-    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
+    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(\lambda_{w_1} - r_1 = \lambda_{w_2} - r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
+\end{lemma}
+\begin{proof}
+    If \(r_1 = \lambda_{w1}\) and \(r_2 = \lambda_{w_2}\), then by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
     And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
     \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
-    Let \(k \geq 0\) be minimal so that \(A_{e_{w_1r_1},0} f_1 \neq 0\).
+    Let \(k \geq 0\) be minimal such that there exists \(v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0} f_1 \neq 0\).
     Obviously \(k = r_1\).
@@
 So, by restriction of \(G\) to \(G_{wr}\) and \(\mathcal{P}_{wr}\) to \(\mathcal{Q}_{wr}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr}\).
-\par Consider the map \(\varphi : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\) defined by
+\par Consider the map \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\) defined by
 \[(x, P) \mapsto P \cdot x.\]
@@
 \begin{lemma}\label{principal_bundle}
-    The map \(\varphi\) is a principal \(G_{wr}\)-bundle.
-\end{lemma}
-\begin{proof}
-    We need to show that \(G_{wr}\) acts freely and transitively on the fibers of \(\varphi\).
+    The map \(\varphi_{wr}\) is a principal \(G_{wr}\)-bundle.
+\end{lemma}
+\begin{proof}
+    We need to show that \(G_{wr}\) acts freely and transitively on the fibers of \(\varphi_{wr}\).
     It is obvious that \(G_{wr}\) acts freely on \(\mathcal{Q}_{wr} \times G\); it is enough to note that it acts freely on \(G\).
@@
     \begin{align*}
-        \varphi^{-1}(y) = \{(x, P) : P \cdot x = y \} & = \\
+        \varphi_{wr}^{-1}(y) = \{(x, P) : P \cdot x = y \} & = \\
         \{(P^{-1} y, P) : P^{-1} y \in \mathcal{Q}_{wr} \} & = \\
@@
 \end{proof}
-We will find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi(X \times G)\).
-So, next we find the irreducible components of \(\mathcal{Q}_{wr}\).
+Next, we will find the irreducible components \(X \subseteq \mathcal{Q}_{wr}\), and we then argue that the irreducible components of \(\mathcal{P}_{wr}\) are of the form \(\varphi_{wr}(X \times G)\).
 \par Actually, \(\mathcal{Q}_{wr}\) is unnecessarily difficult to think about; it is easiest in the case \(r = 0\).
-So, we will change basis to make \(r = 0\).
+So, we change basis to make \(r = 0\).
 Let \(m' = m - r\), and \(n' = n + r\).
-TODO: should not be \(\lambda_w - r\); should be \(r - 1\); fixup other things (incl. proof!) accordingly.
-Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_\ell)\).
+Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, r - 1, \lambda_{w + 1}, ..., \lambda_\ell)\).
 Let \(X' = J(\lambda')\).

### 2024-09-02 paper.tex
Revert "stuff to revert"
This reverts commit dcfef4b5c5a0744446c6976c4a63d06dc1158fdb.

@@
 We index the bases such that \(Xe_{ij} = e_{i,j - 1}\), and \(J_n f_j = f_{j - 1}\).
-\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w - 1\), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^m\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{w,r + 1}, b'}\).
-Also, for \(1 \leq w \leq \ell\), define \(\mathcal{P}_{w,\lambda_w}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^m\) such that \((P^{-1}, I_n)A_{a,b}(P,I_n) = A_{0,b'}\).
-\par The point of the definition above is that \((A_{a,b}, V_\bullet) \in \mathcal{P}_{wr}\) if and only if we can change basis of \(\mathbb{C}^m\) to get from \(A_{a,b}\) to some \(A_{a',b'}\) such that (1) \(a'_{ij} = 0\) for \(i \neq w\), and (2) \(a_{wj}' = 0\) for all but (at most) one \(j\), and (3) \(r\) is the biggest number s.t.
-\(a_{w1}' = a_{w2}' = \cdots = a_{wr}' = 0\).
+\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\); recall \(e_{i0} = 0\)), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^n\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'}\).
 
@@
     Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
-    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n) = A_{a',b'}\) for some \(a',b' \in \mathbb{C}^m\).
-    All that is left is to show that \(a'_{ij} = 0\) for all but one pair \((i,j)\).
+    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n)\) for some \(a',b' \in \mathbb{C}^m\).
+    All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
     Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
@@
 \begin{lemma}
-    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(\lambda_{w_1} - r_1 = \lambda_{w_2} - r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
-\end{lemma}
-\begin{proof}
-    If \(r_1 = \lambda_{w1}\) and \(r_2 = \lambda_{w_2}\), then by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
+    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
+\end{lemma}
+\begin{proof}
+    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
     And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
     \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
-    Let \(k \geq 0\) be minimal such that there exists \(v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0} f_1 \neq 0\).
+    Let \(k \geq 0\) be minimal so that \(A_{e_{w_1r_1},0} f_1 \neq 0\).
     Obviously \(k = r_1\).

### 2024-09-02 paper.tex
fix proof of 5.2

@@
     \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
-    Let \(k \geq 0\) be minimal so that \(A_{e_{w_1r_1},0} f_1 \neq 0\).
-    Obviously \(k = r_1\).
-    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
+    Clearly either \(r_1 = r_2 = 0\) or \(r_1 \neq 0\) and \(r_2 \neq 0\).
+    In the first case, we're done.
+    \par Otherwise, let \(k \geq 0\) be minimal such that there exist \(u,v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0} (u,0) = (v,0) + f_n\) and \(A_{e_{w_1r_2},0}^k (v,0) = 0\).
+    Obviously \(k = r_1 - 1\).
+    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2 - 1\).
     Hence \(r_1 = r_2\).
-    Now, if \(r_1 = 0\), we are done.
-    \par Otherwise, \(r_1 > 0\).
-    Let \(k' \geq 0\) be maximal such that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
-    Obviously \(k' = \lambda_{w_1} - r_1\).
-    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
+    Now we only need to show that \(\lambda_{w_1} = \lambda_{w_2}\).
+    \par Let \(k' \geq 0\) be maximal such that there exist \(u,v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0}^{k'} (u,0) = (v,0) + f_n\).
+    Obviously \(k' = \lambda_{w_1} - r_1 + 1\).
+    Since \(k'\) is independent of \(\mathbb{C}^m\)-basis, we get \(\lambda_{w_1} - r_1 + 1 = k' = \lambda_{w_2} - r_2 + 1\), and therefore \(\lambda_{w_1} = \lambda_{w_2}\).
 \end{proof}

### 2024-09-02 paper.tex
finish section 5 i think

@@
     Obviously \(k' = \lambda_{w_1} - r_1 + 1\).
-    Since \(k'\) is independent of \(\mathbb{C}^m\)-basis, we get \(\lambda_{w_1} - r_1 + 1 = k' = \lambda_{w_2} - r_2 + 1\), and therefore \(\lambda_{w_1} = \lambda_{w_2}\).
+    Since (like \(k\)) \(k'\) is independent of \(\mathbb{C}^m\)-basis, we get \(\lambda_{w_1} - r_1 + 1 = k' = \lambda_{w_2} - r_2 + 1\), and therefore \(\lambda_{w_1} = \lambda_{w_2}\).
 \end{proof}
@@
 So, we change basis to make \(r = 0\).
-Let \(m' = m - r\), and \(n' = n + r\).
-Let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, r - 1, \lambda_{w + 1}, ..., \lambda_\ell)\).
+Let \(R(r) := \lambda_w\) if \(r = 0\), or \(r - 1\) otherwise.
+(The point is that \(R(r) = \max\{i \in \{0, ..., \lambda_w\} : \forall j \leq i. \; (e_{wr})_{wj} = 0\}\).)
+\par Let \(m' = m + R(r) - \lambda_w\) and \(n' = n + \lambda_w - R(r)\).
+Also, let \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, R(r), \lambda_{w + 1}, ..., \lambda_\ell)\).
 Let \(X' = J(\lambda')\).
@@
     & & &  & 
-   \end{pNiceArray} \in \gl_{m' + n'}\]
+   \end{pNiceArray} \in \gl_{m' + n'}.\]
 \begin{lemma}\label{a_zero}
@@
 \begin{proof}
-    Let \((e_{ij}')_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i - \delta_{jw} r}\) be the standard Jordan basis for \(X'\).
-    (The \(\delta\) is the Kronecker \(\delta\).)
+    Let \(k_i = \lambda_i\) for \(i \neq w\), and let \(k_w = R(r)\).
+    Let \((e_{ij}')_{1 \leq i \leq \ell, 1 \leq j \leq k_i}\) be the standard Jordan basis for \(X'\).
     Let \(f_1', ..., f_{n'}'\) be a basis for \(\mathbb{C}^{n'}\) such that \(A_{X', 0, b} f_{i + 1}' = f_i'\), and \(A_{X', 0, b} f_1 = (b, 0)\).
@@
     \begin{itemize}
-        \item For all \(i,j\), \(e_{ij}' \mapsto e_{ij}\).
-        \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,\lambda_w + j}\).
-        \item For \(j = 1, ..., n'\), \(f_j' \mapsto f_j + e_{w, \lambda_w - n' + j}\).
+        \item For all \(i\) and \(j\), \(e_{ij}' \mapsto e_{ij}\).
+        \item For \(j \in \{1, ..., \lambda_w - R(r)\}\), \(f_{n + j}' \mapsto e_{w, R(r) + j}\).
+        \item For \(j \in \{1, ..., n\}\), \(f_j' \mapsto f_j + e_{w, R(r) - n + j}\).
     \end{itemize}
@@
     % \end{itemize}
-    Change of basis by \(Q_{wr}\) maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\), and change of basis by \(Q_{wr}^{-1}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\).
+    It is straightforward to check that for any \(b\) such that \(A_{X,e_{wr},b}\) is nilpotent, there exists \(b'\) such that \(Q_{wr}^{-1} A_{X,e_{wr},b} Q_{wr} = A_{X',0,b'}\).
+    Similarly, for any \(b'\), there exists \(b\) such that \(Q_{wr} A_{X',0,b'} Q_{wr}^{-1} = A_{X,e_{wr},b}\).
+    \par Thus change of basis by \(Q_{wr}\) maps \(\mathcal{Q}_{wr}\) to \(\mathcal{Q}'\), and the inverse map, change of basis by \(Q_{wr}^{-1}\), maps \(\mathcal{Q}'\) to \(\mathcal{Q}_{wr}\).
 \end{proof}

### 2024-09-02 paper.tex
no parentheses
up to lemma 6.6

@@
 Let \(R(r) := \lambda_w\) if \(r = 0\), or \(r - 1\) otherwise.
-(The point is that \(R(r) = \max\{i \in \{0, ..., \lambda_w\} : \forall j \leq i. \; (e_{wr})_{wj} = 0\}\).)
+The point is that \(R(r) = \max\{i \in \{0, ..., \lambda_w\} : \forall j \leq i. \; (e_{wr})_{wj} = 0\}\).
 \par Let \(m' = m + R(r) - \lambda_w\) and \(n' = n + \lambda_w - R(r)\).
@@
 Let \(X = J(\lambda) \in \gl_m\).
-Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
+Let \((e_{ij})_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
 Let
@@
 \par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
-For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
+For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (by convention, the max of the empty set is zero).
 Then set \(q_i(b) = \lambda_i - p_i(b)\).
 When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
-\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., k\}\), and let \((\rho_i)_{i \in I}\) be any map \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
-For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., \ell\}\), and let \((\rho_i)_{i \in I}\) be any function \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
+For notational convenience---although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)---we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
 Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
@@
 \begin{lemma}\label{bs_union}
-    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) satisfying the conditions (1),(2),(3),(4).
+    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., \ell\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) satisfying conditions (1),(2),(3),(4).
     Further, none of the \(B_{I, (\rho_i)}\) is contained in the union of the others.
@@
     Otherwise, take any \(i_2 \in \argmax_{i : q_{i_1} > q_i} p_i\), and set \(\rho_{i_2} := p_{i_2}\).
-    Continuing on in this way, eventually we reach a \(k\) where \(\{i : q_{i_k} > q_i\} = \emptyset\).
-    Then we set \(I = \{i_1, ..., i_k\}\).
+    Continuing on in this way, eventually we reach an \(r\) where \(\{i : q_{i_r} > q_i\} = \emptyset\).
+    Then we set \(I = \{i_1, ..., i_r\}\).
     Note that \(I, (\rho_i)\) satisfy conditions (1)--(4), and furthermore \(b \in B_{I, (\rho_i)}\).
@@
     Take any \(b \in B_{I, (\rho_i)}\) with \(p_i = \rho_i\) for \(i \in I\) and \(p_i = 0\) for \(i \notin I\).
-    It is clear that \(b \notin B_{I', (\rho_i')}\) whenever \(I' \neq I\) or \((\rho_i') \neq (\rho_i)\).
-\end{proof}
-\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, V_\bullet) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
-We will show that \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times (\textrm{some springer fiber})\).
-Then we will use the result about the irreducible components of a Springer fiber to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\), and the closures of these will be the irreducible components of \(\mathcal{Q}\).
+    It is clear that for any \(I'\) and \((\rho_i')\), if \(I' \neq I\) or \((\rho_i') \neq (\rho_i)\), then \(b \notin B_{I', (\rho_i')}\).
+\end{proof}
+\par Let \(\mathcal{Q}_{I, (\rho_i)} = \{(A_{0, b}, V_\bullet) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
+We will show that there is some partition \(\mu\) such that \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times \mathcal{F}_{J(\mu)}\).
+Then we will use \cref{usual_springer_fiber} to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\), and the closures of these will be the irreducible components of \(\mathcal{Q}\).
 
@@
     Let \(b \in B_{I, (\rho_i)}\).
-    It is clear that \(\forall k. \; p_{i_k} = \rho_{i_k}\).
-    \par Take \(i \notin I\) and \(k \in \{0, ..., r\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\).
+    It is clear that for each \(k\) we have \(p_{i_k} = \rho_{i_k}\).
+    \par Let \(i \notin I\) and \(k \in \{0, ..., r\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\).
     Suppose for contradiction that \(q_i < q_{i_k}\).
@@
     So we must have \(q_{i_k} \leq q_i\), as desired.
-    \par Now take \(i \notin I\) and \(k \in \{1, ..., r + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\).
+    \par Now let \(i \notin I\) and \(k \in \{1, ..., r + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\).
     Suppose for contradiction that \(p_i > p_{i_k}\).
-    Then, putting this together with the first inequality, \(\lambda_i - p_i < q_{i_{k - 1}} + p_{i_k} - p_{i_k}\); that is, \(q_i < q_{i_{k - 1}}\).
+    Then, putting this together with the first inequality, we obtain \(\lambda_i - p_i < q_{i_{k - 1}} + p_{i_k} - p_{i_k}\); that is, \(q_i < q_{i_{k - 1}}\).
     Consequently, \(p_i \leq \max_{j : q_j < q_{i_{k - 1}}} p_j = p_{i_k}\), as desired.
@@
     Indeed, given \(i \notin I\) with \(q_i < q_{i_k}\), we cannot have \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), as that would imply (by hypothesis) that \(q_{i_k} \leq q_i\).
-    Hence \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), and consequently (by hypothesis) \(p_i \leq p_{i_k}\).
+    Hence \(\lambda_i \leq q_{i_k} + p_{i_{k + 1}} \leq q_{i_{k - 1}} + p_{i_k}\), and consequently (by hypothesis) \(p_i \leq p_{i_k}\).
 \end{proof}
@@
     Both \(q_{i_k}\) and \(p_{i_k}\) are decreasing as \(k\) increases, so this follows directly from \cref{alternative_bs_one}.
-    (Note that \(p_i \leq \lambda_i - q_{i_k}\) iff \(q_{i_k} \leq q_i\).)
+    (Here we use that \(p_i \leq \lambda_i - q_{i_k}\) if and only if \(q_{i_k} \leq q_i\).)
 \end{proof}
@@
 In this subsection we find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
-\par We claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).
-By finding a algebraic map taking \(b \in B_{I, (\rho_i)}\) to a Jordan basis for \(A_{0,b}\), we will put \(\mathcal{Q}_{I, (\rho_i)}\) in isomorphism with the product \(B_{I, (\rho_i)} \times (Springer fiber at J(\mu))\).
-Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
+\par We will find a partition \(\mu\), depending only on \(I\) and \((\rho_i)\), such that for every \(b \in B_{I, (\rho_i)}\), the matrix \(A_{0,b}\) is similar to \(J(\mu)\).
+By finding an algebraic map taking \(b \in B_{I, (\rho_i)}\) to a Jordan basis for \(A_{0,b}\), we will put \(\mathcal{Q}_{I, (\rho_i)}\) in isomorphism with the product \(B_{I, (\rho_i)} \times \mathcal{F}_{J(\mu)}\).
 \par So, now we find a Jordan basis for \(A_{0, b}\).
 As before, we write \(\{i_1, ..., i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
-We also write, somewhat abusively, \(b \in \mathbb{C}^{m + n}\) to refer to the vector \((b, 0) \in \mathbb{C}^{m + n}\).
+We will also write, somewhat abusively, \(b \in \mathbb{C}^{m + n}\) to refer to the vector \((b, 0) \in \mathbb{C}^{m} \times \mathbb{C}^n\).
+Also, given a vector \(v\) such that \(A^k v \neq 0\) but \(A^{k + 1} v = 0\), we refer to the list of vectors \([v, A_{0,b} v, ..., A_{0,b}^k v]\) as the \emph{chain starting with \(v\)}.
+\par Given a vector \(v = \sum_{ij} v_{ij} e_{ij} \in \mathbb{C}^m\), we define the ``left shift'' operator \(v \leftshift k := \sum_{ij} v_{ij} e_{i,j - k}\).
+If (and only if) \(v \in \langle e_{ij} \rangle_{i,j: j \leq \lambda_i - k}\), then we define the ``right shift'' \(v \rightshift k := \sum_{ij} v_{ij} e_{i,j + k}\).
+
 \begin{lemma}
@@
     \begin{itemize}
-        \item For \(i \notin I\), the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\)
-        \item The chain of length \(n + p_{i_1}\) beginning with \(f_n - (A^{n + p_{i_1}}f_n \rightshift n + p_{i_1})\)
+        \item For \(i \notin I\), the chain of length \(\lambda_i\) beginning with \(e_{i, \lambda_i}\)
+        \item The chain of length \(q_{i_0} + p_{i_1}\) beginning with \(f_n - (A^{n + p_{i_1}}f_n \rightshift n + p_{i_1})\)
         \item For \(k \in \{1, ..., r\}\), the chain of length \(q_{i_k} + p_{i_{k + 1}}\) beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\), where \(v_{i_k} := A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i,l + q_{i_k}}\)

### 2024-09-03 paper.tex
up to lemma 6.7

@@
 \par So, now we find a Jordan basis for \(A_{0, b}\).
-As before, we write \(\{i_1, ..., i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+As before, we write \(\{i_1 <  \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
 We will also write, somewhat abusively, \(b \in \mathbb{C}^{m + n}\) to refer to the vector \((b, 0) \in \mathbb{C}^{m} \times \mathbb{C}^n\).
-Also, given a vector \(v\) such that \(A^k v \neq 0\) but \(A^{k + 1} v = 0\), we refer to the list of vectors \([v, A_{0,b} v, ..., A_{0,b}^k v]\) as the \emph{chain starting with \(v\)}.
-\par Given a vector \(v = \sum_{ij} v_{ij} e_{ij} \in \mathbb{C}^m\), we define the ``left shift'' operator \(v \leftshift k := \sum_{ij} v_{ij} e_{i,j - k}\).
-If (and only if) \(v \in \langle e_{ij} \rangle_{i,j: j \leq \lambda_i - k}\), then we define the ``right shift'' \(v \rightshift k := \sum_{ij} v_{ij} e_{i,j + k}\).
+\par Given a vector \(v\) such that \(A^k v \neq 0\) but \(A^{k + 1} v = 0\), we refer to the list of vectors \([v, A_{0,b} v, ..., A_{0,b}^k v]\) as the \emph{chain starting with \(v\)}.
+Given a vector \(v = \sum_{ij} v_{ij} e_{ij} \in \mathbb{C}^{m + n}\), we define the left-shift operator \(v \leftshift k := \sum_{ij} v_{ij} e_{i,j - k}\).
+If (and only if) \(v \in \langle e_{ij} \rangle_{i,j: j \leq \lambda_i - k}\), then we define the right-shift operator \(v \rightshift k := \sum_{ij} v_{ij} e_{i,j + k}\).
 
 \begin{lemma}
-    The following vectors give a Jordan basis for \(A_{0,b}\).
+    For any \(b \in B_{I, (\rho_i)}\), the following vectors give a Jordan basis for \(A_{0,b}\).
     (For convenience, we write \(A := A_{0,b}\) in this lemma and proof.)
@@
         \item The chain of length \(q_{i_0} + p_{i_1}\) beginning with \(f_n - (A^{n + p_{i_1}}f_n \rightshift n + p_{i_1})\)
-        \item For \(k \in \{1, ..., r\}\), the chain of length \(q_{i_k} + p_{i_{k + 1}}\) beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\), where \(v_{i_k} := A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i,l + q_{i_k}}\)
+        \item For \(k \in \{1, ..., r\}\), the chain of length \(q_{i_k} + p_{i_{k + 1}}\) beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\), where \(v_{i_k} := A^{n - q_{i_k}} f_n - \sum_{j = 1}^{p_{i_k}} b_{i_kj} e_{i,j + q_{i_k}}\)
     \end{itemize}
@@
     \begin{proof}[Proof of (1)]
-        It is obvious that a chain beginning with \(e_{i, p_i + q_i}\) has length \(p_i + q_i\).
+        It is obvious that a chain beginning with \(e_{i, \lambda_i}\) has length \(\lambda_i\).
         \par Now consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).
@@
         By shifting \(b\) left \(p_{i_1}\) times, we zero out all the rows \(i\) where \(q_i < n\).
-        This ensures that the operation of shifting \(b \leftshift p_{i_1}\) right \(n + p_{i_1}\) times is invertible by shifting left \(n + p_{i_1}\) times.
+        (More formally speaking, for all \(i\) and \(j\) such that \(q_i < n\), we have \((b \leftshift p_{i_1})_{ij} = 0\).)
+        This ensures that the operation of shifting \(b \leftshift p_{i_1}\) right \(n + p_{i_1}\) times is defined, and thus it is invertible by shifting left \(n + p_{i_1}\) times.
         That is,
@@
         \par Now, let \(k \in \{1, ..., r\}\).
-        We have \(v_{i_k} = A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}}\).
-        First we note that \(q_{i_k} < n\) by the definition of \(\mathcal{Q}_{I, (\rho_i)}\), so the definition of \(v_{i_k}\) makes sense.
+        Since \(b \in B_{I, (\rho_i)}\), we have \(q_{i_k} < n\), and thus the definition of \(v_{i_k}\) makes sense---i.e., the exponent of \(A\) is nonnegative.
         We consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
@@
         For brevity, we write \(b_{i_k} := A^{q_{i_k}} v_{i_k}\).
-        Note that \(b_{i_k} \leftshift p_{i_{k + 1}}\) has rows \(l\) zeroed out, for all \(l\) with \(q_l < q_{i_k}\).
-        This ensures that shifting \(b_{i_k} \leftshift p_{i_{k + 1}}\) right \(q_{i_k} + p_{i_{k + 1}}\) times can be inverted by shifting left \(q_{i_k} + p_{i_{k + 1}}\) times.
+        For each \(i\) with \(q_i < q_{i_k}\), the vector \(b_{i_k} \leftshift p_{i_{k + 1}}\) has row \(i\) zeroed out.
+        This ensures that the operation of shifting \(b_{i_k} \leftshift p_{i_{k + 1}}\) right \(q_{i_k} + p_{i_{k + 1}}\) times is defined, and thus it is invertible by shifting left \(q_{i_k} + p_{i_{k + 1}}\) times.
         That is,
@@
         The sum of the lengths is
-        \[\sum_{i \notin I} (p_i + q_i) + \sum_{k = 0}^r (q_{i_k} + p_{i_{k + 1}}) = \sum_i (q_i + p_i) = m + n.\]
+        \[\sum_{i \notin I} \lambda_i + \sum_{k = 0}^r (q_{i_k} + p_{i_{k + 1}}) = n + \sum_i (q_i + p_i) = m + n.\]
     \end{proof}
@@
         We will show that \(e_{i_k, \lambda_{i_k}} \in W\).
-        \par To see this, consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
-        (Recall \(v_{i_k} = A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}}\).)
-        Since \(b_{i_k,p_{i_k}} \neq 0\) (by definition of \(p_{i_k}\)), it suffices to show that \(\sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}} \in W\).
-        As explained in the proof of (1), we have \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{lj} \rangle_{q_l \geq q_{i_k}}\).
-        And since \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k}\) has row \(i_k\) zeroed out, in fact \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{lj} \rangle_{l : l \neq i_k \land q_l \geq q_{i_k}}\).
-        Hence, \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).
-        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i_k \land q_l \geq q_{i_k}} \subseteq W\), and consequently \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}} \in W\).
-        Since we know \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}}) \in W\), this implies that \(v_{i_k} \in W\).
-        Because \(A^{n - q_{i_k}} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}} \in W\), as desired.
-    \end{proof}
-    We proved (1), (2), (3), so we are done.
-\end{proof}
-
-Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the lemma.
-Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
-\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
-We are interested in this thing because for any \(\alpha\), the dimension of \(X_{\mu, \alpha}\) is \(\gamma([\mu_1, ..., \mu_{k + 1}])\).
+        \par Since \(AW \subseteq W\), and \(b_{i_k,p_{i_k}} \neq 0\) by definition of \(p_{i_k}\), it suffices to show that \(\sum_{j = 1}^{p_{i_k}} b_{i_kj} e_{i_k,j + q_{i_k}} \in W\).
+        To see that \(\sum_j b_{i_kj}e_{i_k,j + q_{i_k}} \in W\), consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
+        As explained in the proof of (1), \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{ij} \rangle_{i,j: q_i \geq q_{i_k}}\).
+        And since \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k}\) has row \(i_k\) zeroed out, in fact \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{ij} \rangle_{i,j : i \neq i_k \land q_i \geq q_{i_k}}\).
+        Therefore, \(A^{q_i + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}} \in \langle e_{ij} \rangle_{ij : i \neq i_k \land q_i \geq q_{i_k}}\).
+        By our inductive hypothesis, \(\langle e_{ij} \rangle_{i,j : i \neq i_k \land q_i \geq q_{i_k}} \subseteq W\), and consequently \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}} \in W\).
+        Since we know that \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}}) \in W\), this implies that \(v_{i_k} \in W\).
+        Because \(A^{n - q_{i_k}} f_n \in W\), this implies that \(\sum_j b_{i_kj} e_{i_k,j + q_{i_k}} \in W\), as desired.
+    \end{proof}
+\end{proof}
+
+Let \(\mu = (\mu_1, ..., \mu_{\ell + 1})\) be the shape of the Jordan basis given in the lemma.
+Let \((\mathcal{F}_{\mu,\alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components of the Springer fiber \(\mathcal{F}_{J(\mu)}\).
+\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), define \(\gamma(L) = \sum_i i L_i\).
+We are interested in \(\gamma\) because the dimension of each \(\mathcal{F}_{\mu, \alpha}\) is \(\gamma(\mu) = \gamma([\mu_1, ..., \mu_{\ell + 1}])\).
 
@@
     This is analogous to \cref{pwr_comps}; the only difference is the dimension calculation.
-    This time, we have 
+    This time, 
     \begin{align*}

### 2024-09-03 paper.tex
some fixes.  still at the beginning of 6.7

@@
     \[i(n - i)X_{i + 1,j} = (j - 1)(n - (j - 1))X_{i, j - 1}.\]
-    Taking \(j = 1\), the condition above tells us that for all \(i \geq 2\) we have \(X_{i, 1} = 0\).
+    Taking \(j = 1\), the condition above says that for all \(i \geq 2\) we have \(X_{i, 1} = 0\).
     Taking \(j > 1\) and \(i < n\), we get that for all \(i,j \in \{1,...,n-1\}\),
@@
 \[P \cdot (A_{a,b}, V_\bullet) := ((P, I_n) A_{a, b} (P, I_n)^{-1}, (P, I_n)V_\bullet) = (A_{a P^{-1}, Pb}, (P, I_n) V_\bullet).\]
-Note that for any \(x \in \mathcal{Q}_{wr}\), we have \(G_{wr} = \{g \in G : g \cdot x \in \mathcal{Q}_{wr}\}\).
+For any \(x \in \mathcal{Q}_{wr}\), we have \(G_{wr} = \{g \in G : g \cdot x \in \mathcal{Q}_{wr}\}\).
 So, by restriction of \(G\) to \(G_{wr}\) and \(\mathcal{P}_{wr}\) to \(\mathcal{Q}_{wr}\), we obtain an action of \(G_{wr}\) on \(\mathcal{Q}_{wr}\).
@@
 
-\section{The components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}\label{q_comp}
+\section{The Components of \texorpdfstring{\(\mathcal{Q}\)}{Q}}\label{q_comp}
 \subsection{Setup}
@@
 \end{itemize}
-Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
+For any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
 
@@
 \begin{proof}
-    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
-    Note that
+    We have
     \[\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...].\]
-    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
-    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}].\]
+    Let \(L'\) be the result of taking \(\mu\) and, for each \(k\), replacing one occurence of \(q_{i_k} + p_{i_{k + 1}}\) by \(q_{i_k} + p_{i_k}\); that is,
+    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., ..., q_{i_r} + p_{i_r}, ...].\]
     We can transform \(\mu\) into \(L'\) by just `moving' each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
@@
     \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
-    \par Now we consider how to transform \(L'\) into \(L\).
+    \par Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
+    Now we consider how to transform \(L'\) into \(L\).
     First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
     Then we leave \(q_{i_0}\) in place and sort the rest of the list.
-    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
-    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
+    This entails shifting each \(q_{i_k} + p_{i_k}\) to the left by \(\#\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
+    Shifting \(q_{i_k} + p_{i_k}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_k} + p_{i_k})\).
     To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
@@
 
-\section{The components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
+\section{The Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
 As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
@@
 And as before, \((e_{ij})_{ij}\) and \((f_j)_j\) form the standard basis for \(\mathbb{C}^{m + n}\).
-\subsection{The components of \texorpdfstring{\(\mathcal{Q}_{wr}\)}{Q\_\{wr\}}}
+\subsection{The Components of \texorpdfstring{\(\mathcal{Q}_{wr}\)}{Q\_\{wr\}}}
 Recall from section 5 the varieties
@@
 Fix any \(w,r\).
-\cref{a_zero} tells us that 
+\cref{a_zero} says that 
 \[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
 where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
-\par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) give by \cref{Q_comps}.
+\par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) given by \cref{Q_comps}.
 Write \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) to denote the irreducible component of \(\mathcal{Q}_{wr}\) corresponding to \(\mathcal{Q}'_{I, (\rho_i), \alpha}\) via the isomorphism \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\) of \cref{a_zero}.
@@
 
-\subsection{The varieties \texorpdfstring{\(G_{wr}\)}{G\_\{wr\}} and \texorpdfstring{\(G\)}{G}}
+\subsection{The Varieties \texorpdfstring{\(G_{wr}\)}{G\_\{wr\}} and \texorpdfstring{\(G\)}{G}}
 Fix \(w,r\).
@@
 
-\subsection{The components of \texorpdfstring{\(\mathcal{P}_{wr}\)}{P\_\{wr\}}}
+\subsection{The Components of \texorpdfstring{\(\mathcal{P}_{wr}\)}{P\_\{wr\}}}
 Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
@@
 
-\subsection{The components of \texorpdfstring{\(\mathcal{P}\)}{P}}
+\subsection{The Components of \texorpdfstring{\(\mathcal{P}\)}{P}}
 \begin{corollary}\label{p_comps}
@@
 
-\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
+\section{The Components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
 Recall from \cref{sn_iso} that 

### 2024-09-03 paper.tex
capitalization and dois
some stuff.  rename r -> s

@@
 When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
-\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., \ell\}\), and let \((\rho_i)_{i \in I}\) be any function \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
-For notational convenience---although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)---we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+\par Let \(I = \{i_1 < \cdots < i_s\} \subseteq \{1, ..., \ell\}\), and let \((\rho_i)_{i \in I}\) be any function \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
+For notational convenience---although we assign meaning to neither \(i_0\) nor \(i_{s + 1}\)---we define \(q_{i_0} := n\), and \(p_{i_{s + 1}} := 0\).
 Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
 \begin{itemize}
-    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
-    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
+    \item For all \(k \in \{1, ..., s\}\), \(p_i = \rho_i\).
+    \item For all \(k \in \{0, ..., s\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
 \end{itemize}
-For any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
+For any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_s} > p_{i_{s + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_s}\).
 
@@
     Otherwise, take any \(i_2 \in \argmax_{i : q_{i_1} > q_i} p_i\), and set \(\rho_{i_2} := p_{i_2}\).
-    Continuing on in this way, eventually we reach an \(r\) where \(\{i : q_{i_r} > q_i\} = \emptyset\).
-    Then we set \(I = \{i_1, ..., i_r\}\).
+    Continuing on in this way, eventually we reach an \(s\) where \(\{i : q_{i_s} > q_i\} = \emptyset\).
+    Then we set \(I = \{i_1, ..., i_s\}\).
     Note that \(I, (\rho_i)\) satisfy conditions (1)--(4), and furthermore \(b \in B_{I, (\rho_i)}\).
@@
 Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
-As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+As before, we write \(\{i_1 < \cdots < i_s\} := I\), and \(q_{i_0} := n\), and \(p_{i_{s + 1}} := 0\).
 
@@
     \begin{itemize}
-        \item For all \(k \in \{1, ..., r\}\), \(p_{i_k} = \rho_{i_k}\).
+        \item For all \(k \in \{1, ..., s\}\), \(p_{i_k} = \rho_{i_k}\).
         \item For all \(i \notin I\),
         \begin{itemize}
-            \item For all \(k \in \{0, ..., r\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), we have \(q_{i_k} \leq q_i\).
-            \item For all \(k \in \{1, ..., r + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), we have \(p_i \leq p_{i_k}\).
+            \item For all \(k \in \{0, ..., s\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\), we have \(q_{i_k} \leq q_i\).
+            \item For all \(k \in \{1, ..., s + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\), we have \(p_i \leq p_{i_k}\).
         \end{itemize}
@@
     It is clear that for each \(k\) we have \(p_{i_k} = \rho_{i_k}\).
-    \par Let \(i \notin I\) and \(k \in \{0, ..., r\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\).
+    \par Let \(i \notin I\) and \(k \in \{0, ..., s\}\) such that \(\lambda_i > q_{i_k} + p_{i_{k + 1}}\).
     Suppose for contradiction that \(q_i < q_{i_k}\).
@@
     So we must have \(q_{i_k} \leq q_i\), as desired.
-    \par Now let \(i \notin I\) and \(k \in \{1, ..., r + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\).
+    \par Now let \(i \notin I\) and \(k \in \{1, ..., s + 1\}\) such that \(\lambda_i \leq q_{i_{k - 1}} + p_{i_k}\).
     Suppose for contradiction that \(p_i > p_{i_k}\).
@@
     Let \(b \in \mathbb{C}^m\) satisfy the conditions.
-    Let \(k \in \{0, ..., r\}\).
+    Let \(k \in \{0, ..., s\}\).
     We need to show that \(\max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
@@
     \begin{itemize}
-        \item For all \(k \in \{1, ..., r\}\), \(p_{i_k} = \rho_{i_k}\).
+        \item For all \(k \in \{1, ..., s\}\), \(p_{i_k} = \rho_{i_k}\).
         \item For \(i \notin I\),
@@
             \item If \(\lambda_i \geq q_{i_0} + p_{i_1}\), then \(p_i \leq \lambda_i - q_{i_0}\).
-            \item If there is \(k \in \{1, ..., r\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
-            \item If \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\), then \(p_i \leq p_{i_{r + 1}}\).
+            \item If there is \(k \in \{1, ..., s\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
+            \item If \(q_{i_s} + p_{i_{s + 1}} > \lambda_i\), then \(p_i \leq p_{i_{s + 1}}\).
         \end{itemize}
@@
     \begin{align*}
-        B_{I, (\rho_i)} \cong & \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \\
-        & \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}.
+        B_{I, (\rho_i)} \cong & \prod_{k = 1}^s (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \\
+        & \prod_{k = 1}^s \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}.
     \end{align*}
@@
     The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
-    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
-    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
+    \[\prod_{k = 1}^s (b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
+    \[\prod_{k = 1}^s \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
     \cref{alternative_bs_two} says that this is an isomorphism.
@@
 \begin{corollary}\label{bs_dim}
-    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
+    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
 \end{corollary}
@@
 \par So, now we find a Jordan basis for \(A_{0, b}\).
-As before, we write \(\{i_1 <  \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
+As before, we write \(\{i_1 <  \cdots < i_s\} := I\), and \(q_{i_0} := n\), and \(p_{i_{s + 1}} := 0\).
 We will also write, somewhat abusively, \(b \in \mathbb{C}^{m + n}\) to refer to the vector \((b, 0) \in \mathbb{C}^{m} \times \mathbb{C}^n\).
@@
         \item The chain of length \(q_{i_0} + p_{i_1}\) beginning with \(f_n - (A^{n + p_{i_1}}f_n \rightshift n + p_{i_1})\)
-        \item For \(k \in \{1, ..., r\}\), the chain of length \(q_{i_k} + p_{i_{k + 1}}\) beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\), where \(v_{i_k} := A^{n - q_{i_k}} f_n - \sum_{j = 1}^{p_{i_k}} b_{i_kj} e_{i,j + q_{i_k}}\)
+        \item For \(k \in \{1, ..., s\}\), the chain of length \(q_{i_k} + p_{i_{k + 1}}\) beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\), where \(v_{i_k} := A^{n - q_{i_k}} f_n - \sum_{j = 1}^{p_{i_k}} b_{i_kj} e_{i,j + q_{i_k}}\)
     \end{itemize}
@@
         This shows that the chain has length at most \(n + p_{i_1}\), as desired.
-        \par Now, let \(k \in \{1, ..., r\}\).
+        \par Now, let \(k \in \{1, ..., s\}\).
         Since \(b \in B_{I, (\rho_i)}\), we have \(q_{i_k} < n\), and thus the definition of \(v_{i_k}\) makes sense---i.e., the exponent of \(A\) is nonnegative.
@@
         This is obvious for \(i \notin I\).
-        So, we just need to show that \(e_{i_k\lambda_{i_k}} \in W\) for each \(k \in \{1, ..., r\}\).
+        So, we just need to show that \(e_{i_k\lambda_{i_k}} \in W\) for each \(k \in \{1, ..., s\}\).
         We do this inductively; fix \(k\), and suppose we have already shown that \(e_{i_{k'}, \lambda_{i_{k'}}} \in W\) for \(k' < k\).
@@
 \begin{lemma}\label{springer_fiber_dim}
-    \[\gamma([\mu_1, ..., \mu_{k + 1}]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
+    \[\gamma(\mu) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
     \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
 \end{lemma}
-\begin{proof}
-    We have
-    \[\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...].\]
-    Let \(L'\) be the result of taking \(\mu\) and, for each \(k\), replacing one occurence of \(q_{i_k} + p_{i_{k + 1}}\) by \(q_{i_k} + p_{i_k}\); that is,
-    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., ..., q_{i_r} + p_{i_r}, ...].\]
+\begin{proof} We have
+    \[\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_s} + p_{i_{s + 1}}, ...].\]
+    Let \(L'\) be the result of taking \(\mu\) and, for each \(k\), replacing an occurence of \(q_{i_k} + p_{i_{k + 1}}\) by \(q_{i_k} + p_{i_k}\); that is,
+    \[L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., ..., q_{i_s} + p_{i_s}, ...].\]
     We can transform \(\mu\) into \(L'\) by just `moving' each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
@@
 
-\subsection{The centralizer of a nilpotent matrix}
+\subsection{The Centralizer of a Nilpotent Matrix}
 \begin{definition}
@@
 
-\subsection{A `normalization' fact about Jordan bases}
+\subsection{A `Standardization' Fact about Jordan Bases}
 \begin{lemma}\label{normalization_helper_one}

### 2024-09-03 paper.tex
up to lemma 6.8

@@
         The sum of the lengths is
-        \[\sum_{i \notin I} \lambda_i + \sum_{k = 0}^r (q_{i_k} + p_{i_{k + 1}}) = n + \sum_i (q_i + p_i) = m + n.\]
+        \[\sum_{i \notin I} \lambda_i + \sum_{k = 0}^s (q_{i_k} + p_{i_{k + 1}}) = n + \sum_i (q_i + p_i) = m + n.\]
     \end{proof}
@@
 \begin{lemma}\label{springer_fiber_dim}
-    \[\gamma(\mu) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
-    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
+    \[\gamma(\mu) = \gamma([0, \lambda_1, ..., \lambda_\ell]) - \] 
+    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
 \end{lemma}
@@
     So,
-    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
-    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
-    \par Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
+    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^s p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
+    \[\sum_{k = 1}^s p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
+    \par Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_\ell]\).
     Now we consider how to transform \(L'\) into \(L\).
@@
     \end{align*}
-    Since \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_k])\), the equation above implies the desired result.
+    Since \(\gamma(L) = \gamma([0, \lambda_1, ..., \lambda_\ell])\), the equation above implies the desired result.
 \end{proof}
@@
     The subvarieties \((\mathcal{Q}_{I, (\rho_i), \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) are the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
-    Each has dimension \(\gamma([0, \lambda_1, ..., \lambda_k])\).
+    Each has dimension \(\gamma([0, \lambda_1, ..., \lambda_\ell])\).
 \end{corollary}
@@
     We get the dimension of \(B_{I, (\rho_i)}\) from \cref{bs_dim}, and we get the dimension of \(X_{\mu, \alpha}\) from \cref{springer_fiber_dim}.
-    Adding them together, things cancel out and we get \(\gamma([0, \lambda_1, ..., \lambda_k])\).
+    Adding them together, things cancel out and we get \(\gamma([0, \lambda_1, ..., \lambda_\ell])\).
 \end{proof}
@@
 \section{The Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
-As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
+As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
 We write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\), and \(A_{a,b} := A_{J(\lambda), a, b}\).
@@
 \[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
-where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
+where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_\ell)\), and \(m' = m - r\), and \(n' = n + r\).
 \par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) given by \cref{Q_comps}.
@@
     The irreducible components of \(\mathcal{Q}_{wr}\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
-    Each has dimension \(\sum_{i \leq j} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+    Each has dimension \(\sum_{i \leq j} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_\ell)\).
 \end{theorem}
@@
     From the foregoing discussion, it is clear that they are indeed the irreducible components.
-    To calculate the dimension, we refer to \cref{u_i_rho_irred_and_dim}, which says the dimension is \(\gamma([0, \lambda_1', ..., \lambda_k'])\).
+    To calculate the dimension, we refer to \cref{u_i_rho_irred_and_dim}, which says the dimension is \(\gamma([0, \lambda_1', ..., \lambda_\ell'])\).
 \end{proof}
@@
 \begin{lemma}\label{gwr_irred_dim}
-    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
+    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_\ell)\).
 \end{lemma}

### 2024-09-03 paper.tex
up to section 7

@@
 
-\begin{lemma}
+\begin{lemma}\label{jordan_basis}
     For any \(b \in B_{I, (\rho_i)}\), the following vectors give a Jordan basis for \(A_{0,b}\).
@@
 \begin{lemma}\label{u_i_rho_iso}
-    \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
-\end{lemma}
-\begin{proof}
-    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
+    \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times \mathcal{F}_{J(\mu)}\).
+\end{lemma}
+\begin{proof}
+    For each \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of \cref{jordan_basis}, such that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
     From looking at the Jordan basis, it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
-    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b V_\bullet : V_\bullet \in X_\mu\}\).
-    This gives the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to \mathcal{Q}_{I, (\rho_i)}\) defined by
+    \par The Springer fiber at \(A_{0,b}\) is \(\{P_b V_\bullet : V_\bullet \in \mathcal{F}_{J(\mu)}\}\).
+    So, there is an isomorphism \(B_{I, (\rho_i)} \times \mathcal{F}_{J(\mu)} \to \mathcal{Q}_{I, (\rho_i)}\) given by
     \[(b, V_\bullet) \mapsto (P_b J(\mu) P_b^{-1}, P_b V_\bullet),\]
@@
 \begin{corollary}\label{u_i_rho_irred_and_dim}
-    For \(\alpha \in \mathrm{SYT}(\mu)\), let \(\mathcal{Q}_{I, (\rho_i), \alpha}\) be the subvariety of \(\mathcal{Q}_{I, (\rho_i)}\) which corresponds to \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\) via the isomorphism of \cref{u_i_rho_iso}.
+    For \(\alpha \in \mathrm{SYT}(\mu)\), let \(\mathcal{Q}_{I, (\rho_i), \alpha}\) be the subvariety of \(\mathcal{Q}_{I, (\rho_i)}\) corresponding to \(B_{I, (\rho_i)} \times \mathcal{F}_{\mu, \alpha}\) via the isomorphism of \cref{u_i_rho_iso}.
     The subvarieties \((\mathcal{Q}_{I, (\rho_i), \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) are the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
@@
     We know that \(B_{I, (\rho_i)}\) is irreducible by \cref{bs_iso}.
-    Then, the fact that the \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\) are the irreducible components of \(B_{I, (\rho_i)} \times X_\mu\) just follows from the fact that the \(X_{\mu, \alpha}\) are the irreducible components of \(X_\mu\).
-    \par To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_{\mu, \alpha}\).
-    We get the dimension of \(B_{I, (\rho_i)}\) from \cref{bs_dim}, and we get the dimension of \(X_{\mu, \alpha}\) from \cref{springer_fiber_dim}.
+    Then, the fact that the \(B_{I, (\rho_i)} \times \mathcal{F}_{\mu, \alpha}\) are the irreducible components of \(B_{I, (\rho_i)} \times \mathcal{F}_{J(\mu)}\) just follows from the fact that the \(\mathcal{F}_{\mu, \alpha}\) are the irreducible components of \(\mathcal{F}_{J(\mu)}\).
+    \par To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(\mathcal{F}_{\mu, \alpha}\).
+    We get the dimension of \(B_{I, (\rho_i)}\) from \cref{bs_dim}, and we get the dimension of \(\mathcal{F}_{\mu, \alpha}\) from \cref{springer_fiber_dim}.
     Adding them together, things cancel out and we get \(\gamma([0, \lambda_1, ..., \lambda_\ell])\).
@@
     By \cref{u_i_rho_irred_and_dim}, the \(\mathcal{Q}_{I, (\rho_i), \alpha}\) are irreducible and equidimensional.
-    Then \cref{bs_union} says that their union is \(\mathcal{Q}\), and in addition that none is contained in the union of the others.
+    Then \cref{bs_union} says that their union is \(\mathcal{Q}\), and none is contained in the union of the others.
 \end{proof}

### 2024-09-03 paper.tex
fix dimension discrepancy.  up to section 7.3 now.

@@
 \section{The Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp}
-As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
+As before, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
 We write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\), and \(A_{a,b} := A_{J(\lambda), a, b}\).
@@
 \subsection{The Components of \texorpdfstring{\(\mathcal{Q}_{wr}\)}{Q\_\{wr\}}}
-Recall from section 5 the varieties
-\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}\}.\]
-Fix any \(w,r\).
+Fix any \(w\) and \(r\).
+Recall from \cref{p_comp_strat} the variety \(\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, V_\bullet) \in \mathcal{P}\}\).
 \cref{a_zero} says that 
 \[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, V_\bullet) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
-where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_\ell)\), and \(m' = m - r\), and \(n' = n + r\).
+where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., R(r), ..., \lambda_\ell)\), and \(m' = m - \lambda_w + R(r)\), and \(n' = n + \lambda_w - R(r)\).
 \par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) given by \cref{Q_comps}.
@@
     The irreducible components of \(\mathcal{Q}_{wr}\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
-    Each has dimension \(\sum_{i \leq j} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_\ell)\).
+    Each has dimension \(\sum_{i \leq j} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, R(r), \lambda_{w + 1}, ..., \lambda_\ell)\).
 \end{theorem}
@@
 Fix \(w,r\).
-Recall from section 5 the groups \(G = \{P \in \GL_m : P^{-1}XP = X\}\) and \(G_{wr} = \{A \in G : e_{wr} A = e_{wr}\}\).
+Recall from \cref{p_comp_strat} the groups \(G = \{P \in \GL_m : P^{-1}XP = X\}\) and \(G_{wr} = \{A \in G : e_{wr} A = e_{wr}\}\).
 \begin{lemma}\label{g_irred_dim}
@@
 \begin{lemma}\label{gwr_irred_dim}
-    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_\ell)\).
+    \(G_{wr}\) is irreducible and has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, R(r), \lambda_{w + 1}, ..., \lambda_\ell)\).
 \end{lemma}
@@
     In the case that \(r = 0\), the constraint that \(e_{wr}Y = e_{wr}\) is no constraint at all, so we have \(G_{wr} = G\), and the result follows from \cref{g_irred_dim}.
-    \par In the case that \(r > 0\), we observe that \(V = \{Y + I : Y \in \mathfrak{z}_{\gl_m}(X), e_{wr}Y = 0\}\).
-    The constraint \(e_{wr}Y = 0\) is just saying that a certain row of \(Y\) must be all zeroes.
+    \par In the case that \(r > 0\), observe that \(V = \{Y + I : Y \in \mathfrak{z}_{\gl_m}(X), e_{wr}Y = 0\}\).
+    The constraint \(e_{wr}Y = 0\) just says that a certain row of \(Y\), the row with index \(\sum_{i \leq w} \lambda_i - R(r)\), must be all zeroes.
     So, the set of \(Y\) such that \(Y + I \in V\) is the set described by \cref{nilpotent_centralizer_row_zero}.
-    Hence \(V \cong \mathbb{C}^{\sum_{ij}\min(\lambda_i', \lambda_j')}\).
+    Hence \(V \cong \mathbb{C}^{\sum_{ij}\min(\lambda_i, \lambda_j')}\).
 \end{proof}
@@
 \begin{corollary}\label{nilpotent_centralizer_row_zero}
-    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
-    Let \(w \in \{1, ..., k\}\) and \(r \in \{1, ..., \lambda_w\}\).
-    Let \(i = [\sum_{j < w} \lambda_j] + r\).
+    Let \(\lambda = (\lambda_1, ..., \lambda_\ell)\) be a partition of \(m\).
+    Let \(w \in \{1, ..., \ell\}\) and \(R \in \{0, ..., \lambda_w - 1\}\).
+    Let \(i = [\sum_{j \leq w} \lambda_j] - R\).
     The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that the \(i\)th row of \(M\) is equal to zero is the set of matrices
     \[M = \begin{pmatrix}
-        M_{11} & \cdots & M_{1k} \\
+        M_{11} & \cdots & M_{1\ell} \\
         \vdots & & \vdots\\
-        M_{k1} & \cdots & M_{kk}
+        M_{\ell 1} & \cdots & M_{\ell\ell}
     \end{pmatrix},\]
@@
         \end{pmatrix},\]
-        where \(M_{wj}'\) is a \((\lambda_w - r) \times \lambda_j\) lower-left Toeplitz matrix.
+        where \(M_{wj}'\) is a \(R \times \lambda_j\) lower-left Toeplitz matrix.
     \end{itemize}

### 2024-09-03 paper.tex
up to section 8

@@
 
-\begin{theorem}\label{qwr_comps}
+\begin{lemma}\label{qwr_comps}
     The irreducible components of \(\mathcal{Q}_{wr}\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
     Each has dimension \(\sum_{i \leq j} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, R(r), \lambda_{w + 1}, ..., \lambda_\ell)\).
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
 \subsection{The Components of \texorpdfstring{\(\mathcal{P}_{wr}\)}{P\_\{wr\}}}
-Recall from section 5 the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
+Recall from \cref{p_comp_strat} the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\).
 From \cref{principal_bundle} we have the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
-% \par Together, \cref{g_irred_dim} and \cref{gwr_irred_dim} tell us that the irreducible components of \(\mathcal{Q}_{wr} \times G\) are the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\).
-
-\begin{theorem}\label{pwr_comps}
+
+\begin{lemma}\label{pwr_comps}
     Every irreducible component of \(\mathcal{P}_{wr}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
     Each has dimension \(\sum_{i \leq j} \min(\lambda_i, \lambda_j)\).
-\end{theorem}
+\end{lemma}
 \begin{remark}
@@
 \begin{proof}
-    Together, \cref{Q_comps} and \cref{g_irred_dim} tell us that the \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) are irreducible, and their union is \(\mathcal{Q}_{wr}\).
-    Hence their images are irreducible, and the surjectivity of \(\varphi_{wr}\) implies that their union of their images is \(\mathcal{P}_{wr}\).
+    Together, \cref{Q_comps} and \cref{g_irred_dim} imply that the \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G\) are irreducible, and their union is \(\mathcal{Q}_{wr} \times G\).
+    Hence their images are irreducible, and the surjectivity of \(\varphi_{wr}\) implies that the union of their images is \(\mathcal{P}_{wr}\).
     \par Now, to verify that each image is an irreducible component, we need only verify that they are equidimensional.
@@
     So, we have only to compute the dimension of \(\varphi(V_{w,r,I,(\rho_i),\alpha})\).
-    \par This is easy, because \(\varphi_{wr}\) (and, consequently, the restriction of \(\varphi_{wr}\) to \(V_{w,r,I,(\rho_i),\alpha}\)) is a principal \(G_{wr}\)-bundle, and principal bundles play nicely with dimensions.
-    That is, we can conclude that 
+    \par This is easy, because \(\varphi_{wr}\)---and, consequently, the restriction of \(\varphi_{wr}\) to \(V_{w,r,I,(\rho_i),\alpha}\)---is a principal \(G_{wr}\)-bundle, and principal bundles respect dimensions.
+    That is,
     \[\dim \varphi_{wr}(V_{w,r,I,(\rho_i),\alpha}) = \dim V_{w,r,I,(\rho_i),\alpha} - \dim G_{wr}.\]
@@
     Now,
-    \[\sum_{i \leq j} \min(\lambda_i', \lambda_j') = \sum_{i \leq j} \min(\lambda_i, \lambda_j) - \sum_j \min(\lambda_w, \lambda_j) + \sum_j \min(\lambda_w - r, \lambda_j),\]
+    \[\sum_{i \leq j} \min(\lambda_i', \lambda_j') = \sum_{i \leq j} \min(\lambda_i, \lambda_j) - \sum_j \min(\lambda_w, \lambda_j) + \sum_j \min(R(r), \lambda_j),\]
     and
-    \[\sum_{ij} \min(\lambda_i, \lambda_j') = \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_i \min(\lambda_i, \lambda_w) + \sum_i \min(\lambda_i, \lambda_w - r).\]
+    \[\sum_{ij} \min(\lambda_i, \lambda_j') = \sum_{ij} \min(\lambda_i, \lambda_j) - \sum_i \min(\lambda_i, \lambda_w) + \sum_i \min(\lambda_i, R(r)).\]
     Substituting these into the RHS of \cref{the_equation}, things cancel out, and we get
@@
 \subsection{The Components of \texorpdfstring{\(\mathcal{P}\)}{P}}
-\begin{corollary}\label{p_comps}
-    Every irreducible component of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
+\begin{theorem}\label{p_comps}
+    Every irreducible component of \(\mathcal{P}\) is the closure of a subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
     Each has dimension \(\sum_{i \leq j} \min(\lambda_i, \lambda_j)\).
-\end{corollary}
+\end{theorem}
 \begin{proof}

### 2024-09-03 paper.tex
up to section 9

@@
 \[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, U_\bullet, V_\bullet) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
-We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
+We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and we called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
 \begin{theorem}\label{springer_fiber_comps}
-    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
+    For any partition \(\lambda\) of \(m\), we have \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times \mathcal{F}_{J(\lambda)}\).
     Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
@@
     The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
-    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
+    Those of \(\mathcal{F}_{J(\lambda)}\) are given by \cref{usual_springer_fiber}.
     Adding the dimensions gives 
@@
 
-Let \(\lambda\) be any partition of \(m\).
-Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by conjugation; that is,
+Let \(\lambda\) be any partition of \(m\), and let \(X = J(\lambda)\).
+Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by change of basis; that is,
 \[(P, I_n) \cdot (A_{X, a, b}, U_\bullet, V_\bullet) := \]
-\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},(P,I_n)U_\bullet, (P,I_n)V_\bullet).\]
+\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},PU_\bullet, (P,I_n)V_\bullet).\]
 Let 
@@
 \begin{theorem}
-    Every irreducible component of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is the closure of some subvariety of the form \(\phi_\lambda(C_{\lambda,\beta} \times (\GL_m \times \{I_n\}))\), and the closure of each subvariety of this form is an irreducible component.
+    Every irreducible component of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is the closure of a subvariety of the form \(\phi_\lambda(C_{\lambda,\beta} \times (\GL_m \times \{I_n\}))\), and the closure of each subvariety of this form is an irreducible component.
     Each has dimension \(m^2\).
@@
 \begin{proof}
-    This is analogous to \cref{pwr_comps}; the only difference is the dimension calculation.
+    This is analogous to \cref{pwr_comps}; the main difference is the dimension calculation.
     This time, 
@@
     \end{align*}
-    The dimension of \(C_{\lambda, \beta}\) comes from \cref{pwr_comps}; the dimension of \(\GL_m\) is obvious; and the dimension of \(K\) comes from \cref{nilpotent_centralizer}.
+    The dimension of \(C_{\lambda, \beta}\) comes from \cref{springer_fiber_comps}; the dimension of \(\GL_m\) is obvious; and the dimension of \(K\) comes from \cref{nilpotent_centralizer}.
 \end{proof}

### 2024-09-03 paper.tex
up to 9.2

@@
     A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
-    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
+    That is, \(Y\) is Toeplitz if for all \(i,j,k\) we have \(Y_{ij} = Y_{i + k, j + k}\).
 \end{definition}
 \begin{definition}
-    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, we have \(y_{n - i, j - 1} = 0\) whenever \(i + j \geq \min(m,n)\).
+    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, for all \(i\) and \(j\) with \(i + j \geq \min(m,n)\), we have \(y_{n - i, j - 1} = 0\).
 \end{definition}
@@
 \begin{lemma}\label{nilpotent_centralizer}
-    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
-    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
+    Let \(\lambda = (\lambda_1, ..., \lambda_\ell)\) be a partition of \(m\).
+    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of the matrices 
     \[M = \begin{pmatrix}
-        M_{11} & \cdots & M_{1k}\\
+        M_{11} & \cdots & M_{1\ell}\\
         \vdots &        & \vdots\\
-        M_{k1} & \cdots & M_{kk}
+        M_{\ell 1} & \cdots & M_{\ell\ell}
     \end{pmatrix},\]
@@
     \[M = \begin{pmatrix}
-        M_{11} & \cdots & M_{1k}\\
+        M_{11} & \cdots & M_{1\ell}\\
         \vdots &        & \vdots\\
-        M_{k1} & \cdots & M_{kk}
+        M_{\ell 1} & \cdots & M_{\ell\ell}
     \end{pmatrix}.\]
@@
     \par We have 
-    \[J(\lambda)M = \begin{pmatrix}
-        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
+    \begin{align*}
+        J(\lambda)M = \begin{pmatrix}
+            J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1\ell}\\
             \vdots & & \vdots\\
-        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
-    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
-        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
+            J_{\lambda_\ell}M_{\ell 1} & \cdots & J_{\lambda_\ell}M_{\ell\ell}
+        \end{pmatrix} & , \textrm{ and} \\
+        MJ(\lambda) = \begin{pmatrix}
+            M_{11} J_{\lambda_1} & \cdots & M_{1\ell} J_{\lambda_\ell}\\
             \vdots & & \vdots\\
-        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
-    \end{pmatrix}.\]
-    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
+            M_{\ell 1} J_{\lambda_1} & \cdots & M_{\ell\ell} J_{\lambda_\ell}
+        \end{pmatrix} & .
+    \end{align*}
+    So, \(J(\lambda)M = MJ(\lambda)\) if and only if for all \(i\) and \(j\) we have \(J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
     Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.

### 2024-09-03 paper.tex
up to 9.3

@@
 \begin{lemma}\label{normalization_helper_one}
-    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
+    For any finite-dimensional \(V\), nilpotent \(A : V \to V\) of Jordan type \(\lambda = (\lambda_1, ..., \lambda_\ell)\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \((e_{ij})_{1 \leq i \leq \ell, 1 \leq j \leq \lambda_i}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
 \end{lemma}
@@
     For any Jordan basis \((e_{ij})_{ij}\) of \(A\), define
-    \[S((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
+    \[S((e_{ij})_{ij}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
     We proceed by induction on the measure \(S\).
     That is, let \((e_{ij})_{ij}\) be a Jordan basis for \(A\).
-    Our inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
+    The inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
     \par Now, we have two cases.
@@
     In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(i_1 \neq i_2\), and \(f(e_{i_1j_1}) \neq 0\), and \(f(e_{i_2j_2}) \neq 0\).
-    We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
-    Wlog, we assume that \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
-    \par By our inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
+    Let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
+    Without loss of generality, \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
+    \par By the inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
     This is what we do.
-    Define \(e'_{ij}\) as follows.
+    Define \((e'_{ij})_{ij}\) as follows.
     \begin{itemize}
-        \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
-        \item For \(j < \lambda_1\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\)
+        \item \(e_{i_1, \lambda_{i_1}}' := e_{i_1, \lambda_{i_1}} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\).
+        \item For \(j < \lambda_{i_1}\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\).
         \item For \(i \neq i_1\), \(e_{ij}' := e_{ij}\).
@@
     Further, we claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
-    It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).
-    We have 
+    It suffices to show that for all \(j \leq j_1\) we have  \(f (e_{i_1,j}) = 0\).
+    Indeed,
     \[f (e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\right)\right) =\]
@@
     Clearly (by design), this expression is zero when \(j = j_1\).
-    And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
-    Hence the measure \(S\) of this new basis is smaller, as desired.
+    And for \(j < j_1\), both \(f(e_{i_1, j})\) and \(f(e_{i_2, j_2 + (j - j_1)})\) are zero, so it is zero then as well.
+    Thus the measure \(S\) of this new basis is smaller, as desired.
 \end{proof}
@@
 \begin{lemma}\label{normalization_helper_two}
-    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \(e_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
-\end{lemma}
-\begin{proof}
-    Let \(e_j\) be a Jordan basis for \(J_n\).
-    If \(\{j : f(e_j) \neq 0\}\) is the empty set, we are done.
-    Otherwise, let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
-    For any Jordan basis \(f_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
-    \[S((f_j)_j) := \begin{cases}
+    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \((e_j)_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
+\end{lemma}
+\begin{proof}
+    Let \((x_j)_j\) be a Jordan basis for \(J_n\).
+    If \(\{j : f(x_j) \neq 0\}\) is the empty set, we are done.
+    Otherwise, let \(j_0 = \min\{j : f(x_j) \neq 0\}\).
+    \par For any Jordan basis \((e_j)_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
+    \[S((e_j)_j) := \begin{cases}
         -1, & \{j > j_0 : f(e_j) \neq 0\} = \emptyset \\
@@
     That is, let \((e_j)_j\) be a Jordan basis for \(J_n\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\).
-    Our inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
+    The inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
     \par We have two cases: either \((e_j)_j\) satisfies the desired property, or not.
-    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \(e_j'\) as follows.
+    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \((e_j')_j\) as follows.
     \begin{itemize}
@@
     It is straightforward to check that \(j_0 = \min\{j : f(e_j') \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
-    By our inductive hypothesis, we are done.
+    By the inductive hypothesis, we are done.
 \end{proof}
@@
 \begin{theorem}\label{normalization}
-    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
+    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \((e_{ij})_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
 \end{theorem}
 \begin{proof}
-    \cref{normalization_helper_one} provides a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
-    Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
+    \cref{normalization_helper_one} provides a Jordan basis \((e_{ij})_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
+    Restricting \(A\) to \(\langle e_{ij}\rangle_{i,j : i = i_0}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
 \end{proof}

### 2024-09-03 paper.tex
finish section 9 and check citations

@@
     Inversely, suppose \(X \neq 0\).
-    Let \(e_1, ..., e_n\) be the standard basis, with \(J_n e_i = e_{i + 1}\).
-    Let \(i_1 = \max\{i : Xe_i \neq 0\}\).
-    As \(X\) is upper triangular, we have \(X e_{i_1} = v + ae_{i_2}\), with \(a \in \mathbb{C}\setminus\{0\}\), \(i_2 \leq i_1\), and \(v \in \langle e_1, ..., e_{i_1 - 1}\rangle\).
-    \par Now, \((J_n + X)^{i_1} e_1 = e_{i_1 + 1} + v + ae_{i_2}\).
-    Then, \((J_n + X)^{i_1 + (n - i_1)} e_1 = 0 + (J_n + X)^{n - i_1} (v + ae_{i_2})\).
-    Clearly \((J_n + X)^{n - i_1} (v + ae_{i_2}) = v' + ae_{i_2 + n - i_1}\), with \(v' \in \langle e_1, ..., e_{i_2 + n - i_1 - 1} \rangle\).
-    Now, since \(i_2 \leq i_1\), we have \(i_2 + n - i_1 \leq n\), and therefore \((J_n + X)^n e_1 \neq 0\).
+    Let \(e_1, ..., e_n\) be the standard basis, with \(J_n e_i = e_{i - 1}\).
+    Let \(i_1 = \min\{i : Xe_i \neq 0\}\).
+    Since \(X\) is upper triangular, there are \(a \in \mathbb{C} \setminus \{0\}\), \(i_2 \geq i_1\), and \(v \in \langle e_n, ..., e_{i_2 + 1}\rangle\) such that \(X e_{i_1} = v + ae_{i_2}\).
+    \par Now, \((J_n + X)^{n - i_1 + 1} e_n = e_{i_1 - 1} + v + ae_{i_2}\).
+    Then, \((J_n + X)^n e_n = 0 + (J_n + X)^{i_1 - 1} (v + ae_{i_2})\).
+    Clearly \((J_n + X)^{i_1 - 1} (v + ae_{i_2}) = v' + ae_{i_2 - (i_1 - 1)}\), with \(v' \in \langle e_n, ..., e_{i_2 - i_1} \rangle\).
+    Since \(i_2 \geq i_1\), we have \(i_2 - (i_1 - 1) \geq 1\), and therefore \((J_n + X)^n e_n \neq 0\).
     It follows that \(J_n + X\) is not nilpotent.
@@
         y_{11} & y_{12} & y_{13} & \cdots & y_{1,n-1} & y_{1n} \\
-        d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
-            & d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
+        -d_1 & y_{22} & y_{23} & \cdots & y_{2,n-1} & y_{2n} \\
+            & -d_2   & y_{33} & \cdots & y_{3,n-1} & y_{3n} \\
             & & \ddots & \cdots & \vdots  & \vdots \\
-            & & & d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
-            & & & & d_{n - 1} & y_{nn}
+            & & & -d_{n - 2} & y_{n-1,n-1} & y_{n - 1,n}\\
+            & & & & -d_{n - 1} & y_{nn}
     \end{pmatrix} \in \gl_n.\]
@@
     By induction on \(n\).
-    In the case \(n = 1\), expanding along the last row (taking the usual interpretation of the empty product) gives the desired result.
+    In the case \(n = 1\), expanding along the last row (taking the empty product equal to 1) gives the desired result.
     \par Now suppose \(n > 1\).
@@
        & & &  \\
-       \end{pNiceArray} -
+       \end{pNiceArray} +
     y_{nn} \det \begin{pNiceArray}{ccc|ccc}
@@
        \end{pNiceArray}.\]
-    Using our inductive hypothesis for the first determiniant, and using that \(\det \begin{pNiceArray}{c|c}
+    Applying the inductive hypothesis to the first determinant, and using that \(\det \begin{pmatrix}
         A_{11} & 0 \\
         A_{21} & A_{22}
-    \end{pNiceArray} = \det A_{11} \det A_{22}\) for the second, the expression becomes
-    \[d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
+    \end{pmatrix} = \det A_{11} \det A_{22}\) for the second, the expression becomes
+    \begin{align*}
+        y_{nn} \det X \det Y_{nn} + & \\
+        d_{n - 1} \left(\det X \det Y_{n,n-1} + \left(\prod_{i \leq n - 2} d_i\right) \det \begin{pNiceArray}{ccc|c}
             & & & \vert \\
@@
         \text{---} & a & \text{---} & 0
-   \end{pNiceArray}\right)
-   - y_{nn} \det X \det Y_{nn} = \]
-   \[(d_{n - 1} Y_{n,n-1} - y_{nn} \det Y_{nn})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+       \end{pNiceArray}\right) & = \\
+       (y_{nn} \det Y_{nn} + d_{n - 1} Y_{n,n-1})\det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
         & & & \vert \\
@@
     \text{---} & a & \text{---} & 0
-   \end{pNiceArray} = \]
-   \[\det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
+   \end{pNiceArray} & = \\
+   \det Y \det X + \left(\prod_i d_i\right) \det \begin{pNiceArray}{ccc|c}
     & & & \vert \\
@@
 \text{---} & a & \text{---} & 0
-   \end{pNiceArray}.\]
+\end{pNiceArray} & .
+\end{align*}
 \end{proof}
@@
 \begin{corollary}\label{bottom_right_nilp}
-    If \(X\) is nilpotent, and
+    Let \(X \in \gl_m\) be nilpotent.
+    Let \(Y \in \gl_n\) be such that for all \(i\) and \(j\) with \(i > j + 1\) we have \(y_{ij} = 0\).
+    If the matrix
     \[\begin{pNiceArray}{ccc|ccc}
@@
        \end{pNiceArray}\]
-    is nilpotent  as well, then \(Y\) is nilpotent.
+    is nilpotent, then \(Y\) is nilpotent.
 %     If all the \(d_i\) are nonzero, then
@@
     \begin{proof}
-        By the previous lemma, the characteristic polynomial of the big matrix is
+        By \cref{block_determinant}, the characteristic polynomial of the big matrix is
         \[g_X(\lambda) g_Y(\lambda) + f(\lambda),\]
-        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
+        where \(g_X(\lambda) = \lambda^m\) is the characteristic polynomial of \(X\), \(g_Y(\lambda)\) is the characteristic polynomial of \(Y\), and \(f(\lambda)\) is some polynomial of degree at most \(m - 1\).
+        Since the characteristic polynomial of the big matrix is \(\lambda^{m + n}\), we must have \(g_Y(\lambda) = \lambda^n\).
     \end{proof}

### 2024-09-03 paper.tex
small fixes

@@
     Let \(n \geq 1\), and let \(e\) be a regular nilpotent element of \(\gl_n\).
-    Let \(m \geq 0\), and consider the Slodowy slice \(S\) at the element \((0, e) \in \gl_m \times \gl_n \subseteq \gl_{m + n}\).
+    Let \(m \geq 0\), and consider the Slodowy slice \(S\) at \((0, e) \in \gl_m \times \gl_n \subseteq \gl_{m + n}\).
     We define the \emph{Springer fiber of S} at a nilpotent \(X \in \gl_m\) as consisting of the following data: an element \(Y \in S\) which projects to \(X\) coordinate-wise, along with an element of the usual Springer fiber at \((X, Y) \in \gl_m \times \gl_{m + n}\).
@@
 Thank you to Haoshuo Fu for suggesting the fun project, guiding me through it, and helping me learn many things, both by talking to me about them and by suggesting things to read.
-Thank you also to the organizers of the MIT math department's UROP+ program, and to MIT for providing funding.
+Thank you also to the organizers of the MIT math department's UROP+ program, and also to MIT for providing funding.
 
@@
 
-\subsection{A description of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
+\subsection{A Description of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
 Recall the map \(S \to \mathfrak{g}\) given by \(Z \mapsto (p'(Z), Z)\), where \(p' : \gl_{m + n} \to \gl_m\) is coordinate projection taking a matrix to its upper-left corner.

### 2024-09-03 paper.tex
not much

@@
 \par In this paper we study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
-As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we let \(\mathcal{N}_m\) be the nilpotent cone in \(\gl_m\), and we consider the map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
+As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), let \(\mathcal{N}_m\) be the nilpotent cone in \(\gl_m\), and consider the map \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
 Given \(X \in \mathcal{N}_m\), we call \(\pi^{-1}(X)\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.

### 2024-09-03 paper.tex
not much

@@
 Let \(\pi_\mathfrak{h} : \widetilde{\mathcal{N}}_\mathfrak{h} \to \mathcal{N}_\mathfrak{h}\) be the projection onto the second coordinate.
-We call \(\pi_\mathfrak{h}\) the \emph{Springer resolution}.
-For \(n \in \mathcal{N}_\mathfrak{h}\), we call \(\pi_\mathfrak{h}^{-1}(n)\) the \emph{Springer fiber at \(n\)}.
+The map \(\pi_\mathfrak{h}\) is called the \emph{Springer resolution}.
+For \(n \in \mathcal{N}_\mathfrak{h}\), the variety \(\pi_\mathfrak{h}^{-1}(n)\) is called the \emph{Springer fiber at \(n\)}.
 
